### 2024-02-22 draft/wigglyhedra.tex
start git with programmation and draft paper

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, multido, xifthen, a4wide, ae, aecompl, blkarray, pifont, mathtools, etoolbox, dsfont}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage[bottom]{footmisc}
\usepackage{tikz}
%\usepackage{tkz-graph}
%\usepackage{tikz-qtree}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\usepackage[external]{forest}
%\tikzexternalize
\graphicspath{{figures/}{figures/nodes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[export]{adjustbox}
\usepackage{ulem}\normalem

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}%[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\crefname{notation}{Notation}{Notations}
\crefname{problem}{Problem}{Problems}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{\mathbb{K}} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fB}{\mathfrak{S}^\textsc{b}} % signed symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\c}[1]{\mathcal{#1}} % caligraphic letters
\renewcommand{\b}[1]{{\boldsymbol{#1}}} % bold letters
\newcommand{\bb}[1]{\mathbb{#1}} % bb letters
\newcommand{\f}[1]{\mathfrak{#1}} % frak letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{\b{1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\b{\triangle}} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\inv}{inv} % inversions
\DeclareMathOperator{\ninv}{ninv} % inversions
\DeclareMathOperator{\Ima}{Im} % image
\DeclareMathOperator{\Vol}{Vol} % (mixed) volume

% others
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % darkblue color
\definecolor{violet}{RGB}{147,39,143} % darkblue color
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\smallskip\noindent\uline{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
%\renewcommand\labelitemi{$\diamond$} % redefine itemize default symbol

% marginal comments
\usepackage{todonotes}
\newcommand{\vincent}[1]{\todo[color=blue!30]{\rm #1 \\ \hfill --- V.}}

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommandx{\projDown}[1][1={}]{\smash{\pi_\downarrow^{#1}}} % down projection map
\newcommandx{\projUp}[1][1={}]{\smash{\pi^\uparrow_{#1}}} % up projection map
\newcommand{\con}{\mathrm{con}} % congruence

% geometry
\newcommandx{\Fan}[1][1=D]{\mathcal{F}_{#1}} % fan
\newcommand{\polytope}[1]{\mathds{#1}} % font polytope
\newcommandx{\Zono}[1][1=D]{\polytope{Z}_{#1}} % zonotope
\newcommandx{\Asso}[1][1=n]{\polytope{A}_{#1}} % associahedron

% specific wiggly
\newcommand{\wigglyComplex}{\mathrm{WC}} % wiggly complex
\newcommand{\wigglyFlipGraph}{\mathrm{WFG}} % wiggly flip graph
\newcommand{\wigglyLattice}{\mathrm{WL}} % wiggly lattice
\newcommand{\wigglyFan}{\mathrm{WF}} % wiggly fan
\newcommand{\wigglyhedron}{\polytope{W}} % wigglyhedron

% formating the table of contents
\setcounter{tocdepth}{4}
\makeatletter
\def\l@part{\@tocline{1}{8pt}{0pc}{}{}}
\def\l@section{\@tocline{1}{4pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\sc\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}
\let\oldtocsubsubsection=\tocsubsubsection
\renewcommand{\tocsubsubsection}[2]{\quad\oldtocsubsubsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Wigglyhedra}

\thanks{VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}

\author{Asilata Bapat}
\address{The Australian National University}
\email{asilata.bapat@anu.edu.au}
\urladdr{\url{https://asilata.github.io}}

\author{Vincent Pilaud}
\address{Universitat de Barcelona}
\email{vincent.pilaud@ub.edu}
\urladdr{\url{https://www.ub.edu/comb/vincentpilaud/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
\end{abstract}

\maketitle

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

This problem arose from recent discussions with Asilata Bapat~\cite{BapatPilaud}.
It was originally motivated by her joint work with Anand Deopurkar and Anthony Licata on categorical representation theory and stability conditions, but it can be stated in purely combinatorial terms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Wiggly pseudotriangulations and wiggly permutations}
\label{sec:combinatorics}

Fix an integer~$n \ge 1$.
In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points and the wiggly permutations of~$[2n]$, and we prove that they are in bijection.
These two perspectives enable us to endow this combinatorial families with additional structures : the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.

%%%%%%%%%%%%

\subsection{Wiggly pseudotriangulations and the wiggly complex}
\label{subsec:wigglyPseudotriangulations}

We start with wiggly pseudodissections of points on a line.
The following definitions are illustrated in \cref{fig:incompatible}.

\begin{definition}
A \defn{wiggly arc} is a quadruple $(i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~$\{i+1, \dots, j-1\}$.
We represent it by an $x$-monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~$\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])$ are called \defn{external}, all others are called \defn{internal}.
\end{definition}

\begin{definition}
Two wiggly arcs~$(i,j,A,B)$ and~$(i',j',A',B')$ are 
\begin{itemize}
\item \defn{non pointed} if~$i = j'$ or~$i' = j$,
\item \defn{crossing} if~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing \ne (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, that is, if the corresponding curves cross,
\item \defn{incompatible} if they are non pointed or crossing, and \defn{compatible} otherwise.
\end{itemize}
%
\begin{figure}[h]
\centerline{\includegraphics[scale=1.3]{incompatible}}
\caption{Some incompatible wiggly arcs: non pointed (left) and crossing (right).}
\label{fig:incompatible}
\end{figure}
\end{definition}

We consider sets of compatible wiggly arcs.
The following definitions are illustrated~in~\cref{fig:pseudodissections}.

\begin{definition}
A \defn{wiggly pseudodissection}~$D$ is a set of pairwise compatible wiggly arcs which contains the exterior wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$. We denote by~$D^\circ \eqdef D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.
%
\begin{figure}[b]
\centerline{\includegraphics[scale=1.3]{pseudodissections}}
\caption{Three wiggly pseudodissections. The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue). The other two have $7$ pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and blue pseudotriangles.}
\label{fig:pseudodissections}
\end{figure}
\end{definition}

\begin{definition}
A wiggly pseudodissection~$D$ decomposes the digon bounded by~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ into cells, that we call \defn{wiggly cells}.
The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
A point~$p$ on the external boundary of~$c$ is a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if~$c$ covers less (resp.~more) than half of any small disc centered at~$p$.
%The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
\end{definition}

\begin{remark}
\label{rem:degree}
Consider a wiggly cell~$c$ in a wiggly pseudodissection~$D$.
Note that~$\beta_c$ is always even as~$D$ is pointed, so that~$\beta_c/2$ is an integer.
Moreover, we have~$\beta_c \ge 2$ and~$\kappa_c \ge 1$, where at least one of the two inequalities is strict (as otherwise, the two wiggly arcs bounding~$c$ would coincide).
%We conclude that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$.
We thus obtain on the one hand that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$, and on the other hand that~$\beta_c/2+\kappa_c-1 \ge 2$.
\end{remark}

\begin{definition}
A \defn{wiggly pseudotriangle} (resp.~\defn{pseudoquadrangle}) is a wiggly cell of degree~$3$ (resp.~$4$).
\end{definition}

\begin{remark}
\label{rem:descriptionPseudotrianglesPseudoquadrangles}
As illustrated in \cref{fig:pseudotriangles}, a wiggly pseudotriangle~$t$ has no point in its interior and $4$ points on its boundary, $3$ corners and $1$ hinge.
%Hence, it has two corners oriented in the same direction, which we call the \defn{twin corners}.
As illustrated in \cref{fig:pseudoquadrangles}, a wiggly pseudoquadrangle~$q$ can have
\begin{enumerate}
\item either one point in its interior and~$2$ points on its boundary, both corners,
\item or no point in its interior and $6$ points on its boundary, $4$ corners and $2$ hinges. We then distinguish three situations, depending on the position of the two pairs~$p, p'$ of wiggly arcs incident to the two hinges of~$c$, as illustrated in \cref{fig:pseudoquadrangles} (where~$p$ and~$p'$ are colored in red and orange):
\begin{enumerate}[(a)]
\item those where $p$ and $p'$ are not consecutive along~$c$, and do not overlap vertically,
\item those where $p$ and $p'$ are not consecutive along~$c$, but overlap vertically.
\item those where~$p$ and~$p'$ are consecutive along~$c$,
\end{enumerate}
\end{enumerate}
%
\begin{figure}
\centerline{\includegraphics[scale=1.3]{pseudotriangles}}
\caption{Four wiggly pseudotriangles.}
\label{fig:pseudotriangles}
\end{figure}
%
\begin{figure}
\centerline{\includegraphics[scale=1.3]{pseudoquadrangles}}
\vspace{-.3cm}
\caption{Four types of wiggly pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
\label{fig:pseudoquadrangles}
\end{figure}
\end{remark}

\begin{proposition}
\label{prop:wigglyPseudotriangulations}
Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
Moreover, the following are equivalent:
\begin{enumerate}[(i)]
\item all wiggly cells of~$D$ are wiggly pseudotriangles,
\item $D$ contains~$n$ wiggly cells and is connected,
\item $D$ contains $2n-1$ internal wiggly arcs,
\item $D$ is an inclusion maximal wiggly pseudodissection.
\end{enumerate}
We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
\end{proposition}

\begin{proof}
Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$\gamma=\iota+\kappa-n$.
Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = \gamma+n$.
We conclude that~$\gamma \le n$ and~$\iota = \gamma-\kappa+n \le 2n-1$.

%Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
%Observe that~$\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and that~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
%As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus get~$2 \gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa$.
%As~$D$ is a planar graph with~$v = n+2$ vertices, $e = \iota+2$ edges, $f = 1+\gamma$ faces, and $\kappa$ connected components, Euler's formula~$1+\kappa = v-e+f$ yields~$2(1+\kappa) = 2(n+2)-2(\iota+2)+2(1+\gamma) \le 2n-2\iota+2+\iota+\kappa$, so that~$\iota \le 2n-\kappa \le 2n-1$ and~$\gamma \le (\iota+\kappa)/2 \le n$.

To prove the second part of the statement, we show that~(i) $\Rightarrow$ (ii) $\Rightarrow$ (iii) $\Rightarrow$ (iv) $\Rightarrow$ (i).

\para{(i) $\Rightarrow$ (ii)}
For any wiggly cell~$c$, we have~$\delta_c = 3$, so that~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}, hence~$2 = \beta_c/2+\kappa_c-1$.
Therefore~$\kappa = 1$ ($D$ is connected) and~$2\gamma = \iota+1 = \gamma+n$, so that~$\gamma=n$.

\para{(ii) $\Rightarrow$ (iii)}
As $\gamma=n$ and~$\kappa=1$, we have~$\iota = \gamma+n-\kappa = 2n-1$.

%\para{(i) $\Rightarrow$ (ii)}
%We have~$\delta_c = 3$ for any wiggly cell~$c$.
%Hence~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}.
%Therefore~$2\gamma = \iota+1$ and~$\kappa = 1$ (so that~$D$ is connected).
%Applying Euler's formula as before, we get~$2 = (n+2)-(\iota+2)+(1+\gamma) = n-\gamma+2$, so that~$\gamma=n$.
%
%\para{(ii) $\Rightarrow$ (iii)}
%As $\gamma=n$ and~$\kappa=1$, we have~$2n = 2\gamma \le \iota+\kappa = \iota+1$, so that~$\iota = 2n-1$.

\para{(iii) $\Rightarrow$ (iv)}
If~$D$ already contains~$2n-1$ internal wiggly arcs, it has maximal cardinality among all wiggly pseudodissections, hence it is certainly inclusion maximal.

\para{(iv) $\Rightarrow$ (i)}
We now consider a wiggly pseudodissection~$D$ containing a wiggly cell~$c$ which is not a wiggly pseudotriangle, and we prove that~$D$ is not inclusion maximal.
%
Assume first that the external boundary of~$c$ is a digon bounded by the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i, j, A', B')$.
Denote by~$m$ the maximum of the points~$(A \symdif A') \cup (B \symdif B')$ located inside this digon (where~$\symdif$ denotes the symmetric difference).
Then the wiggly arc~$\beta \eqdef \big( i, m, {]i,m[} \cap (A \cup A'), {]i,m[} \cap (B \cap B') \big)$ is compatible with~$D$ (any wiggly arc incompatible with~$\beta$ crosses~$\alpha$ or~$\alpha'$) and is not in~$D$ (it connects the boundary of~$c$ with one of its internal connected components).
%Indeed, for any wiggly arc~$\gamma \eqdef (k, \ell, X, Y)$ inside~$c$, we have
%\begin{itemize}
%\item $i < k < \ell \le m$ so that~$\beta$ and~$\gamma$ are pointed,
%\item $Y \subseteq {]i,m[} \cap B \cap B'$ so that~$\beta$ and~$\gamma$ are non-crossing.
%\end{itemize}

Assume now that the external boundary of~$c$ is a not digon.
Consider a hinge~$j$ of~$c$.
Assume by symmetry that the boundary of~$c$ contains the two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j, A', B')$, such that~$\alpha$ is below~$\alpha'$. % (\ie $k \in A'$ or~$k' \in B$).
Let~$\gamma \eqdef (k, \ell, X, Y)$ denote the uppermost wiggly arc of the boundary of~$c$ such that~$j \in Y$ (it exists since~$j$ is a  hinge of~$c$), and let~$X' \eqdef {]j,\ell[} \cap X$ and~$Y' \eqdef {]j,\ell[} \cap Y$.
Then the two wiggly arcs~$\beta \eqdef \big( i, \ell, A \cup X', B \cup \{j\} \cup Y')$ and~$\beta' \eqdef \big( i', \ell, A'  \cup \{j\} \cup X', B \cup Y')$ are both compatible with~$D$ (any arc incompatible with~$\beta$ is incompatible with~$\alpha$ or~$\gamma$, and similarly for~$\beta'$) and cannot both belong to~$D$ (otherwise, $c$ would be a wiggly pseudotriangle bounded by~$\alpha, \alpha', \gamma', \gamma$).
\end{proof}

\begin{remark}
Note that in the proof of \cref{prop:wigglyPseudotriangulations}, we actually obtained that
\[
\sum_{c \in C} (\delta_c-3) = \sum_{c \in D} \beta_c/2 + 2 \sum_{c \in D} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
\]
In other words, the number of wiggly arcs of~$D$ is $2n-1$ minus the number of wiggly cells of~$D$ which are not wiggly pseudotriangles.
\end{remark}

\begin{definition}
A \defn{wiggly diagonal} of a wiggly cell~$c$ is a wiggly arc inside~$c$ and compatible with~$c$.
\end{definition}

\begin{proposition}
\label{prop:diagonalsPseudoquadrangle}
Any wiggly pseudoquadrangle has exactly two wiggly diagonals.
Moreover, these two wiggly diagonals either cross precisely once, or are non pointed.
\end{proposition}

\begin{proof}
Depending on the four types of pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}:
\begin{enumerate}
\item the two diagonals are the two wiggly arcs inside~$q$, incident to the point in the interior~of~$q$,
\item[(2a)] the two diagonals connect the two pairs of opposite corners of~$q$,
\item[(2b)] one of two diagonals connects two opposite corners of~$q$ while the other connects the two hinges~of~$q$,
\item[(2c)] one of the diagonals connects two opposite corners of~$q$ while the other connects an hinge of~$q$ to a corner of~$q$.
\end{enumerate}
See \cref{fig:diagonalsPseudoquadrangles} where the two diagonals appear in red and orange.
%
\begin{figure}[h]
\centerline{\includegraphics[scale=1.3]{diagonalsPseudoquadrangles}}
\caption{The two diagonals in each of the four types of wiggly pseudoquadrangles.} % described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
\label{fig:diagonalsPseudoquadrangles}
\end{figure}
%Let~$q$ be a wiggly pseudoquadrangle.
%We distinguish two situations depending on~$\kappa(q)$:
%\begin{description}
%\item[$\kappa(q) = 1$] Then the boundary of~$c$ is a single wiggly hexagon, so that it has~$4$ concave points. We distinguish again two situations:
%	\begin{description}
%	\item 
%	\end{description}
%\item[$\kappa(q) = 2$] Then~$q$ is a digon bounded by two wiggly arcs~$(i, k, A, B \cup \{j\})$ and~$(i, k, A \cup \{j\}, B)$ for some~$1 < i < j < k \le n$ and~$A \sqcup B = {]i,j[} \cup{]j,k[}$. Hence, the only two wiggly arcs in the interior of~$q$ are~$(i, j, {]i,j[} \cap A, {]i,j[} \cap B)$ and~$(j, k, {]j,k[} \cap A, {]j,k[} \cap B)$, which are both compatible with~$q$ and are not pointed.
%\end{description}
\end{proof}

We are now ready to consider the wiggly flip graph and the wiggly complex.
The following definitions are illustrated in \cref{fig:wigglyComplex} when~$n = 2$.
%
\begin{figure}
\centerline{\includegraphics[scale=1.1]{wigglyComplex}}
\caption{The wiggly complex~$\wigglyComplex_2$ (left) and the wiggly flip graph~$\wigglyFlipGraph_2$ (right).}
\label{fig:wigglyComplex}
\end{figure}

\begin{definition}
The \defn{wiggly flip graph}~$\wigglyFlipGraph_n$ is the graph with a vertex for each wiggly pseudotriangulation, and with an edge between two wiggly pseudotriangulations~$T,T'$ if there are wiggly arcs~$\alpha \in T$ and~$\alpha' \in T'$ such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
\end{definition}

\begin{proposition}
\label{prop:wigglyFlipGraph}
The wiggly flip graph~$\wigglyFlipGraph_n$ is regular of degree~$2n-1$.
\end{proposition}

\begin{proof}
Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
Then~$Q \eqdef T \ssm \{\alpha\}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and an other one~$\alpha'$.
As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
\end{proof}

\begin{definition}
The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
\end{definition}

\begin{proposition}
The wiggly complex~$\wigglyComplex_n$ is a flag pure $(2n-1)$-dimensional pseudomanifold without boundary.
\end{proposition}

\begin{proof}
It is a flag simplicial complex because it is a clique complex.
It is pure of dimension $2n-1$ by the implication (iv) $\Rightarrow$ (iii) of \cref{prop:wigglyPseudotriangulations}.
Finally, it is a pseudomanifold without boundary by \cref{prop:wigglyFlipGraph}.
\end{proof}

\begin{remark}
$\wigglyComplex_1$ contains two isolated points.
$\wigglyComplex_2$ is a simplicial $3$-dimensional associahedron (this coincidence fails for~$n > 2$).
Here are the first few $f$-vectors:
\begin{align*}
f(\wigglyComplex_1) & = (1, 2), \\
f(\wigglyComplex_2) & = (1, 9, 21, 14), \\
f(\wigglyComplex_3) & = (1, 24, 154, 396, 440, 176), \\
f(\wigglyComplex_4) & = (1, 55, 729, 4002, 10930, 15684, 11312, 3232), \\
f(\wigglyComplex_5) & = (1, 118, 2868, 28110, 140782, 400374, 673274, 662668, 352728, 78384),
\intertext{and the first few $h$-vectors:}
h(\wigglyComplex_1) & = (1, 1), \\
h(\wigglyComplex_2) & = (1, 6, 6, 1), \\
h(\wigglyComplex_3) & = (1, 19, 68, 68, 19, 1), \\
h(\wigglyComplex_4) & = (1, 48, 420, 1147, 1147, 420, 48, 1), \\
h(\wigglyComplex_5) & = (1, 109, 1960, 11254, 25868, 25868, 11254, 1960, 109, 1).
\end{align*}
\end{remark}

\begin{remark}
Note that the number of vertices of~$\wigglyComplex_n$ is the number~$\sum_{j = 0}^n 2^j (n+1-j)$ of wiggly arcs on~$n+2$ points.
The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal arcs ending at the last point~$n+1$.
For instance,
\begin{align*}
	f_0(x) & = 1 \\
	f_1(x) & = x + 1 \\
	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2 \\
	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14
\end{align*}
We use this additional variable~$x$ to obtain a recursive formula for~$f_n(x)$, discussing on the wiggly pseudotriangle~$t_n$ with a hinge at~$n$.
Namely, there are two types of wiggly pseudotriangulations of~$n+2$ points:
\begin{itemize}
\item those with the arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
\item those without the arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
\end{itemize}
Hence we obtain for all~$n \ge 1$,
\[
f_{n}(x) = \frac{1}{(1 - x)^2} \big( f_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) f_{n-1}(x) + x^4 (x - 1) f_{n-1}’(x) \big).
\]
This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
\[
\sum_{n \ge 0} f(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
\dots
\]
\end{remark}

Finally, we will need the following observation, illustrated in \cref{fig:incompatible2}.

\begin{proposition}
\label{prop:uerp}
Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
\begin{itemize}
\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$.
(In other words, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
\end{itemize}
See \cref{fig:incompatible2} for illustrations.
%
\begin{figure}
\centering
\includegraphics[scale=1.3]{incompatible2}
\caption{The arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
\label{fig:incompatible2}
\end{figure}
%
(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
\end{proposition}

\begin{proof}
Any wiggly arc non pointed with~$\beta$ would be non pointed with~$\alpha$ or~$\alpha'$ (as the endpoints of~$\beta$ are endpoints of~$\alpha$ or~$\alpha'$).
Any wiggly arc crossing~$\beta$ would be either non pointed or crossing~$\alpha$ or~$\alpha'$ (as~$\beta$ follows~$\alpha$ or~$\alpha'$, except at the point~$j = i'$ in the first situation).
\end{proof}

%%%%%%%%%%%%

\subsection{Wiggly permutations and the wiggly lattice}
\label{subsec:wigglyPermutations}

We now consider wiggly permutations, defined as follows.

\begin{definition}
A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
\begin{itemize}
\item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
\item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
\end{itemize}
\end{definition}

\begin{example}
The wiggly permutations of~$[2]$ are~$12$ and~$21$.
The wiggly permutations of~$[4]$ are
\[
1234, 2134, 1342, 1243, 3421, 2143, 3412, 1432, 1423, 4321, 4213, 4312, 4132, 4123.
\]
%The wiggly permutations of~$[6]$ are
%\begin{gather*}
%123456, 213456, 134256, 124356, 123564, 123465, 342156, 214356, 213564, 213465, 341256, 143256, \\
%134562, 134265, 142356, 125643, 124365, 135642, 125634, 123654, 123645, 432156, 345621, 342165, \\
%421356, 215643, 214365, 356421, 215634, 213654, 213645, 431256, 341562, 341265, 413256, 143562, \\
%143265, 134652, 134625, 412356, 156423, 142365, 156243, 126543, 126435, 356412, 156342, 136542, \\
%156234, 126534, 126354, 136425, 126345, 435621, 432165, 346521, 346215, 564213, 421365, 562143, \\
%216543, 216435, 563421, 365421, 562134, 216534, 216354, 364215, 216345, 431562, 431265, 345612, \\
%341652, 341625, 413562, 413265, 156432, 143652, 143625, 136452, 564123, 412365, 561423, 165423, \\
%164235, 561243, 165243, 162543, 162435, 563412, 365412, 561342, 165342, 163542, 561234, 165234, \\
%162534, 162354, 364125, 163425, 162345, 564321, 436521, 436215, 364521, 654213, 642135, 652143, \\
%621543, 621435, 653421, 635421, 652134, 621534, 621354, 634215, 621345, 435612, 431652, 431625, \\
%346512, 346152, 346125, 564132, 413652, 413625, 561432, 165432, 164352, 164325, 364152, 163452, \\
%654123, 641235, 651423, 615423, 614235, 651243, 615243, 612543, 612435, 653412, 564312, 635412, \\
%651342, 615342, 613542, 651234, 615234, 612534, 612354, 634125, 613425, 612345, 654321, 643521, \\
%643215, 634521, 436512, 436152, 436125, 364512, 654132, 641352, 641325, 651432, 615432, 614352, \\
%614325, 634152, 613452, 654312, 643125, 643512, 643152, 634512.
%\end{gather*}
\end{example}

\begin{remark}
The numbers of wiggly permutations are given by
\[
\begin{array}{c|ccccccccc}
n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
\hline
|\wigglyLattice_n| & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
\end{array}
\]
\end{remark}

Recall that the \defn{inversion set} of a permutation~$\sigma$ of~$[2n]$ is the set
\[
\inv(\sigma) \eqdef \set{(\sigma_i, \sigma_j)}{1 \le i < j \le 2n \text{ and } \sigma_i > \sigma_j}.
\]
We denote by~$\ninv(\sigma)$ the non-inversions of~$\sigma$, that is the complement of~$\inv(\sigma)$.
Note that~$\inv(\sigma)$ and~$\ninv(\sigma)$ are transitive: $\{(k,j), (j,i)\} \subseteq \inv(\sigma)$ implies~$(k,i) \in \inv(\sigma)$ for all~${1 \le i < j < k \le 2n}$, and similarly for~$\ninv$.
The inversion sets of wiggly permutations are characterized as follows.

\begin{lemma}
\label{lem:inversionSetsWigglyPermutations}
A permutation~$\sigma$ of~$[2n]$ is a wiggly permutation if and only if for all~$j \in [n]$,
\begin{itemize}
\item $(2j-1, i) \in \inv(\sigma)$ implies $(2j, i) \in \inv(\sigma)$ for all~$i < 2j-1$, and
\item $(k, 2j-1) \in \inv(\sigma)$ implies $(k, 2j) \in \inv(\sigma)$ for all~$k > 2j$.
\end{itemize}
A similar characterization holds for~$\ninv(\sigma)$ by exchanging~$2j-1$ and~$2j$.
\end{lemma}

\begin{proof}
Immediate as it precisely corresponds to the pattern avoidance description.
\end{proof}

The (left) \defn{weak order} on permutations of~$[2n]$ is defined as the inclusion order of their inversion sets.
Its cover relations are given by the exchanges of two entries at consecutive positions.
It is a (congruence uniform) lattice, and the join and meet satisfy
\[
\inv(\sigma \join \tau) = \big( \inv(\sigma) \cup \inv(\tau) \big)^\textrm{tc}
\qquad\text{and}\qquad
\ninv(\sigma \meet \tau) = \big( \ninv(\sigma) \cup \ninv(\tau) \big)^\textrm{tc}
\]
where~$X^\mathrm{tc}$ denotes the transitive closure of~$X$.

%The following statements are illustrated on \cref{fig:wigglyLattice}\,(right) when~${n = 2}$.
%
\begin{figure}
\centering
\includegraphics[scale=1]{wigglyFlipGraph}
\caption{The wiggly lattice~$\wigglyLattice_2$ on wiggly pseudotriangulations (left) and on wiggly permutations (right).}
\label{fig:wigglyLattice}
\end{figure}

\begin{proposition}
The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, that we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
\end{proposition}

\begin{proof}
Consider two wiggly permutations~$\rho, \sigma$ of~$[2n]$, and let~$\tau = \rho \join \sigma$.
Assume that there is~$1 \le i < 2j-1 < 2n$ such that~$(2j-1, i) \in \inv(\tau)$.
As $\inv(\tau) = \big( \inv(\rho) \cup \inv(\sigma) \big)^\textrm{tc}$, there exist~$i \le i' < 2j-1$ such that~$(i', i) \in \inv(\tau)$ and~$(2j-1, i') \in \inv(\rho) \cup \inv(\sigma)$.
Since~$\rho$ and~$\sigma$ are wiggly permutations, we obtain by \cref{lem:inversionSetsWigglyPermutations} that~$(2j, i') \in \inv(\rho) \cup \inv(\sigma) \subseteq \inv(\tau)$.
As~$(i', i) \in \inv(\tau)$ and~$(2j, i') \in \inv(\tau)$ and~$\inv(\tau)$ is transitive, we conclude that~$(2j,i) \in \inv(\tau)$.
A similar argument shows that~$(k, 2j-1) \in \inv(\tau)$ implies~$(k, 2j) \in \inv(\tau)$ for all~$1 < 2j < k \le 2n$.
By \cref{lem:inversionSetsWigglyPermutations}, we conclude that~$\tau = \rho \join \sigma$ is a wiggly permutation.
The proof is similar for~$\rho \meet \sigma$, using $\ninv$ instead of~$\inv$.
\end{proof}

Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$i$ such that~$\sigma_i < \sigma_{i+1}$ (resp.~$\sigma_i > \sigma_{i+1}$).

\begin{proposition}
Each wiggly permutation~$\sigma$ covers (resp.~is covered by) as many wiggly permutations as its number of descents (resp.~ascents), so that the cover graph of~$\wigglyLattice_n$ is regular of degree~$2n-1$.
\end{proposition}

\begin{proof}
%For a descent~$i$, consider...
\vincent{todo}
\end{proof}

We close this section by the following conjecture (checked computationally up to~$n = 4$).

\begin{conjecture}
\label{conj:Hamiltonian}
The cover graph of the wiggly lattice~$\wigglyLattice_n$ is Hamiltonian.
\end{conjecture}

Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).

%%%%%%%%%%%%

\subsection{Bijection}
\label{subsec:bijection}

We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
The following two definitions are illustrated in \cref{fig:wigglyLattice,fig:bijection}.

\begin{figure}
\centerline{\includegraphics[scale=1.7]{bijection}}
\caption{The bijection between wiggly pseudotriangulations and wiggly permutations.}
\label{fig:bijection}
\end{figure}

\begin{definition}
\label{def:bijection1}
Consider a wiggly pseudotriangulation~$T$.
Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabeled).
We define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
\end{definition}

\begin{definition}
\label{def:bijection2}
For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef \big( i, j, {]i,j[} \cap \sigma([k]), {]i,j[} \ssm \sigma([k]) \big)$ with
\[
i \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i} 
\;\text{and}\;
j \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1} \!.
\]
\end{definition}

\begin{proposition}
The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a graph isomorphism between the wiggly flip graph~$\wigglyFlipGraph_n$ and the cover graph of the wiggly lattice~$\wigglyLattice_n$.
\end{proposition}

\begin{proof}
%We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
\vincent{todo}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Wiggly fan and wigglyhedron}
\label{sec:geometry}

%%%%%%%%%%%%

\subsection{Polyhedral geometry}
\label{subsec:polyhedralGeometry}

We refer to \cite{Ziegler-polytopes} for a reference on polyhedral geometry, and only remind the basic notions needed later in the paper.

A (polyhedral) \defn{cone} is the positive span~$\R_{\ge 0}\b{R}$ of a finite set~$\b{R}$ of vectors of~$\R^d$ or equivalently, the intersection of finitely many closed linear half-spaces of~$\R^d.$ 
The \defn{faces} of a cone are its intersections with its supporting hyperplanes. 
The \defn{rays} (resp.~\defn{facets}) are the faces of dimension~$1$ (resp.~ codimension~$1$).
A cone is \defn{simplicial} if its rays are linearly independent.
A (polyhedral) \defn{fan}~$\Fan$ is a set of cones such that any face of a cone of~$\Fan$ belongs to~$\Fan$, and any two cones of~$\Fan$ intersect along a face of both. 
A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^d$, and \defn{simplicial} if all its cones are simplicial.

Note that a simplicial fan defines a simplicial complex on its rays (the simplices of the simplicial complex are the subsets of rays which span a cone of the fan).
Conversely, given a simplicial complex~$\Delta$ with ground set~$V$, one can try to realize it geometrically by associating a ray~$\b{r}_v$ of~$\R^d$ to each~$v \in V$, and the cone~$\R_{\ge 0}\b{R}_\triangle$ generated by the set~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ to each~$\triangle \in \Delta$.
To show that the resulting cones indeed form a fan, we will need the following statement, which can be seen as a reformulation of~\cite[Coro.~4.5.20]{DeLoeraRambauSantos}.

\begin{proposition}
\label{prop:characterizationFan}
Consider a closed simplicial pseudomanifold~$\Delta$ with ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
Then the collection of cones~$\set{\R_{\ge 0}\b{R}_\triangle}{\triangle \in \Delta}$ forms a complete simplicial fan of~$\R^d$ if and~only~if
\begin{itemize}
\item there exists a vector~$\b{v}$ of~$\R^d$ contained in only one of the cones~$\R_{\ge 0}\b{R}_\triangle$ for~$\triangle \in \Delta$,
\item for any two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have~$\lambda_v \lambda_{v'} > 0$~where
\[
\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
\]
denotes the unique (up to rescaling) linear dependence on~$\b{R}_{\triangle \cup \triangle'}$.
\end{itemize}
\end{proposition}

A \defn{polytope} is the convex hull of finitely many points of~$\R^d$ or equivalently, a bounded intersection of finitely many closed affine half-spaces of~$\R^d$.
The \defn{faces} of a polytope are its intersections with its supporting hyperplanes.
The \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) are the faces of dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$).

The \defn{normal cone} of a face~$\polytope{F}$ of a polytope~$\polytope{P}$ is the cone generated by the normal vectors to the supporting hyperplanes of~$\polytope{P}$ containing~$\polytope{F}$.
Said differently, it is the cone of vectors~$\b{c}$ of~$\R^d$ such that the linear form~$\b{x} \mapsto \dotprod{\b{c}}{\b{x}}$ on~$\polytope{P}$ is maximized by all points of the face~$\polytope{F}$.
The \defn{normal fan} of~$\polytope{P}$ is the set of normal cones of all its faces.

Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
To realize the fan~$\Fan$, one can try to pick a height vector~$\b{h} \eqdef (h_v)_{v \in V} \in \R^V$ and consider the polytope
\(
\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}.
\)
The following classical statement characterizes the height vectors~$\b{h}$ for which the fan~$\Fan$ is the normal fan of this polytope~$\polytope{P}_{\b{h}}$.
We borrow the formulation from~\cite[Lem.~2.1]{ChapotonFominZelevinsky}.

\begin{proposition}
\label{prop:characterizationPolytopalFan}
Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~$\triangle \in \Delta$.
Then the following are equivalent for any height vector~$\b{h} \in \R^V$:
\begin{itemize}
\item The fan~$\Fan$ is the normal fan of the polytope~$\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}$.
\item For two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, the height vector~$\b{h}$ satisfies the \defn{wall crossing inequality}
\[
\lambda_v \, h_v + \lambda_{v'} \, h_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, h_w > 0
\]
where
\[
\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
\]
denotes the unique linear dependence on~$\b{R}_{\triangle \cup \triangle'}$ such that~$\lambda_v + \lambda_{v'} = 2$.
\end{itemize}
\end{proposition}

We denote by~$(\b{e}_i)_{i \in [d]}$ the standard basis of~$\R^d$.
For~$I \subseteq [d]$, we define~$\one_I \eqdef \sum_{i \in I} \b{e}_i$, and we often shorten~$\one_{[d]}$ by~$\one_d$.
We denote by~$\HH_d$ the hyperplane of~$\R^d$ defined by the equation~$\dotprod{\b{x}}{\one_d} = 0$, and we denote by~$\pi : \R^d \to \HH$ the orthogonal projection on~$\HH_d$, that is~$\pi(\b{x}) \eqdef \b{x} - (\dotprod{\b{x}}{\one_d} / d) \one_d$.

%%%%%%%%%%%%

\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
\label{subsec:gcvectors}

We now define two families of vectors.
%
\begin{figure}
\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
\caption{The $\b{g}$-matrix and $\b{c}$-matrix of a wiggly pseudotriangulation~$T$. The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top). The colors of the columns match the colors of the wiggly arcs.}
\label{fig:pseudotriangulationMatrices}
\end{figure}

\begin{definition}
\label{def:gvectors}
The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
\begin{align*}
\alpha^+ & \eqdef \big(\{2i-1, 2j\} \ssm \{-1, 2n+2\} \big) \cup \set{2a-1}{a \in A} \cup \set{2a}{a \in A},
\\
\alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
\end{align*}
If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
We define~$\b{g}(D) \eqdef \set{\b{g}(\alpha)}{\alpha \in D^\circ}$ for a set~$D$ of wiggly arcs.
\end{definition}

\begin{definition}
\label{def:cvectors}
Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
\begin{itemize}
\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
\end{itemize}
Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
\end{definition}

\begin{proposition}
\label{prop:dualBases}
For any wiggly pseudotriangulation~$T$, the sets~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases~of~$\HH_{2n}$.
\end{proposition}

\begin{proof}
We first prove that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
\vincent{todo}

Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
Hence, we obtain that~$\dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \dotprod{\pi(\hat{\b{g}}(\alpha))}{\b{c}(\alpha', T)} = \dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$.
We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
\end{proof}

%%%%%%%%%%%%

\subsection{Wiggly fan}
\label{subsec:wigglyFan}

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$.

\begin{theorem}
\label{thm:wigglyFan}
The collection of cones~$\R_{\ge 0} \langle \b{g}(A) \rangle$ for all~$A$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called \defn{wiggly fan}~$\wigglyFan_n$.
\end{theorem}

To prove \cref{thm:wigglyFan}, we just need to check the conditions of \cref{prop:characterizationFan}.
We first find a vector contained in the cone~$\R_{\ge 0} \langle \b{g}(T) \rangle$ for a single wiggly pseudotriangulation~$T$.

\begin{lemma}
\label{lem:-+...-+}
Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$ for all~${i \in [n]}$.
Then~$\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \langle \b{g}(T) \rangle$.
\end{lemma}

\begin{proof}
Observe first that, for any wiggly arc~$\alpha \eqdef (i, j, A, B)$ and any~$k \in [n]$, we have
%\begin{itemize}
%\item $\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = 1$ if~$k = i$, $-1$ if~$k = j$, and~$0$ otherwise,
%\item $\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = 2$ if~$k \in A$, $-2$ if~$k \in B$, and~$0$ otherwise.
%\end{itemize}
\[
\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 1 & \text{if~$k = i$,} \\ -1 & \text{if~$k = j$,} \\ 0 & \text{otherwise}, \end{cases}
\qquad\text{and}\qquad
\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 2 & \text{if~$k \in A$,} \\ -2 & \text{if~$k \in B$,} \\ 0 & \text{otherwise}. \end{cases}
\]

Assume now that~$\b{v} = \sum_\alpha \lambda_\alpha \, \hat{\b{g}}(\alpha)$ where the sum ranges over all wiggly arcs~$\alpha$ for some positive scalars~$\lambda_\alpha \ge 0$ such that~$\lambda_\alpha \cdot \lambda_{\alpha'} = 0$ for all incompatible wiggly arcs~$\alpha$ and~$\alpha'$.
For~$k \in [n]$, let~$\underline{\Lambda}_k$ (resp.~$\overline{\Lambda}_k$) denote the sum of~$\lambda_\alpha$ over the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$k \in A$ (resp.~$k \in B$).
Note that~$\underline{\Lambda}_k = \overline{\Lambda}_k$ since~$0 = \b{v}_{2k-1} + \b{v}_{2k} = \sum_\alpha \lambda_\alpha \big( \hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} \big) = 2\underline{\Lambda}_k - 2\overline{\Lambda}_k$.

As~$\b{v}_1 - \b{v}_2 = -2$ and~$\hat{\b{g}}(\alpha)_1 - \hat{\b{g}}(\alpha)_2 \ge 0$ except if~$\alpha = \alpha_0$, we have~$\lambda_{\alpha_0} > 0$, and thus~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$1$.
%As~$\b{g}(\alpha)_1 - \b{g}(\alpha)_2 = 0$ for all wiggly arcs~$\alpha$ with no endpoint at~$1$, we thus obtain that~$\lambda_{\alpha_0} = 1$.
We then prove by induction on~$i \in [n-1]$ that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$ and that~$\lambda_\alpha = 0$ for all wiggly arcs starting at~$i+1$.
Consider~$i \in [n-1]$ and assume that we proved it for~$i-1$.
As~$\smash{\lambda_{\underline{\alpha}_{i-1}} \cdot \lambda_{\overline{\alpha}_{i-1}} > 0}$, we already have~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ ending at~$i+1$, except if~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
As~$\b{v}_{2i+1} - \b{v}_{2i+2} = -2$, this implies that~$\smash{\lambda_{\underline{\alpha}_i} + \lambda_{\overline{\alpha}_i} = 1}$.
This already implies that~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$i+1$.
Moreover, assume for instance that~$\lambda_{\overline{\alpha}_i} > 0$.
Hence, $\lambda_\alpha = 0$ for all wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$i \in A$ and~$i+1 \in B$.
We thus obtain that~$\underline{\Lambda}_i - \lambda_{\underline{\alpha}_i} \le \underline{\Lambda}_{i+1}$ and~$\overline{\Lambda}_i - \lambda_{\overline{\alpha}_i} \ge \overline{\Lambda}_{i+1}$.
As~$\underline{\Lambda}_i = \overline{\Lambda}_i$ and~$\underline{\Lambda}_{i+1} = \overline{\Lambda}_{i+1}$, we thus obtain that~$\lambda_{\underline{\alpha}_i} \ge \lambda_{\overline{\alpha}_i} > 0$, hence that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$.
We conclude that~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ except if~$\alpha = \alpha_0$ or~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$ for some~$i \in [n]$.

Consider now a wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \langle \b{g}(T) \rangle$.
Write~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \b{g}(\alpha)$ with~$\lambda_\alpha \ge 0$ for all~$\alpha \in T^\circ$.
Let~$\mu \eqdef \sum_{\alpha \in T^\circ} \lambda_\alpha \dotprod{\hat{\b{g}}(\alpha)}{\one_{2n}}$.
As~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \hat{\b{g}}(\alpha) - \mu \, \one_{2n}$ and~$\one_{2n} = \hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)$, we thus conclude from the previous paragraph that~$T = \{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
\end{proof}

We now describe the unique linear dependence between the $\b{g}$-vectors of two adjacent facets of the wiggly complex~$\wigglyComplex_n$.
The following statement is illustrated in \cref{fig:linearDependences}.

\begin{lemma}
\label{lem:linearDependences}
Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
Then~$\{\beta, \beta'\} \in T \cap T'$ and
\begin{itemize}
\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$,
\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
\end{itemize}
%Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs, and let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
%Then
%\begin{description}
%\item[if $\alpha$ and~$\alpha'$ are not pointed] Assume without loss of generality that~$i' = j$, and consider %the wiggly arcs~
%$\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$.
%(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
%Then~$\{\beta, \beta'\} \in T \cap T'$ and~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$.
%\item[if~$\alpha$ and~$\alpha'$ are crossing] Assume without loss of generality that~$i \in A'$ or~$i' \in B$, and consider %the wiggly arcs~
%$\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$. \linebreak
%(In other words, if~$p$ denotes the crossing point of~$\alpha$ and~$\alpha'$, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows~$\alpha$ on~$]i,p[$ and~$\alpha'$ on~$]p,j'[$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows~$\alpha$ on~$]i',p[$ and~$\alpha$ on~$]p,j[$.)
%Then~${\{\beta, \beta'\} \in T \cap T'}$ and~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
%\end{description}
\end{lemma}

\begin{proof}
In both situations, we will just prove that the same linear dependence holds on the vectors~$\hat{\b{g}}(\alpha), \hat{\b{g}}(\alpha'), \hat{\b{g}}(\beta), \hat{\b{g}}(\beta')$, which will imply the statement as~$\pi$ is a linear map.

If~$\alpha$ and~$\alpha'$ are non pointed with~$i' = j$, then we have
\[
\alpha^+ \sqcup \alpha'^+ = \beta^+ \sqcup \{2j-1, 2j\} = \beta'^+
\qquad\text{and}\qquad 
\alpha^- \sqcup \alpha'^- = \beta^- = \beta'^- \sqcup \{2j-1, 2j\}.
\]
We thus obtain that
\[
\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\beta^+} + \b{e}_{2j-1} + \b{e}_{2j} = \one_{\beta'^+}
\qquad\text{and}\qquad 
\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} = \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}.
\]
hence
\begin{align*}
2 \big( \hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') \big)
& = 2(\one_{\alpha^+} - \one_{\alpha^-}) + 2(\one_{\alpha'^+} - \one_{\alpha'^-})
= 2(\one_{\alpha^+} + \one_{\alpha'^+}) - 2(\one_{\alpha^-} + \one_{\alpha'^-}) \\
& = (\one_{\beta^+} + \one_{\beta'^+} + \b{e}_{2j-1} + \b{e}_{2j}) - (\one_{\beta^-} + \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}) \\
& = (\one_{\beta^+} + \one_{\beta'^+}) - (\one_{\beta^-} + \one_{\beta'^-})
= (\one_{\beta^+} - \one_{\beta^-}) + (\one_{\beta^-} + \one_{\beta'^-})
= \hat{\b{g}}(\beta) + \hat{\b{g}}(\beta').
\end{align*}

If~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$, then we have
\begin{gather*}
\alpha^+ \cup \alpha'^+ = \beta^+ \cup \beta'^+ \qquad\text{and}\qquad \alpha^+ \cap \alpha'^+ = \beta^+ \cap \beta'^+, \\
\alpha^- \cup \alpha'^- = \beta^- \cup \beta'^- \qquad\text{and}\qquad \alpha^- \cap \alpha'^- = \beta^- \cap \beta'^-.
\end{gather*}
We thus obtain that
\[
\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\alpha^+ \cup \alpha'^+} + \one_{\alpha^+ \cap \alpha'^+} = \one_{\beta^+ \cup \beta'^+} + \one_{\beta^+ \cap \beta'^+} = \one_{\beta^+} + \one_{\beta'^+}
\]
and similarly~$\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} + \one_{\beta'^-}$, so that~$\hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') =\hat{\b{g}}(\beta) + \hat{\b{g}}(\beta')$.
\end{proof}

\begin{proof}[Proof of \cref{thm:wigglyFan}]
Directly follows from \cref{prop:characterizationFan,lem:-+...-+,lem:linearDependences}.
\end{proof}

\begin{remark}
The wiggly fan coarsens the $\b{c}$-vector fan.
\vincent{todo}
\end{remark}

%%%%%%%%%%%%

\subsection{Wigglyhedron}
\label{subsec:wigglyhedron}

We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
%
\begin{figure}[t]
\centering
\input{wigglyhedron}
\caption{The wigglyhedron~$\wigglyhedron_2$.}
\label{fig:wigglyhedron}
\end{figure}

\begin{definition}
\label{def:incompatibilityDegree}
The \defn{incompatibility degree}~$\delta(\alpha, \alpha')$ of two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ is given by
\begin{itemize}
\item $0$ if~$\alpha$ and~$\alpha'$ are pointed and non-crossing,
\item $1$ is~$\alpha$ and~$\alpha'$ are not pointed (\ie $i = j'$ or~$i' = j$),
\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing.
\vincent{give an equivalent definition with subsets...}
\end{itemize}
The \defn{incompatibility number} of a wiggly arc~$\alpha$ is~$\kappa(\alpha) \eqdef \sum_{\alpha'} \delta(\alpha, \alpha')$.
\end{definition}

\begin{remark}
This is indeed an incompatibility degree in the sense that
\begin{itemize}
\item $\alpha$ and~$\alpha'$ are compatible if and only if~$\delta(\alpha, \alpha') = 0$,
\item $\alpha$ and~$\alpha'$ are exchangeable if and only if~$\delta(\alpha, \alpha') = 1$.
\end{itemize}
\end{remark}

\begin{theorem}
\label{thm:wigglyhedron}
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \nu(\alpha)}$ for all internal wiggly arcs~$\alpha$,
\item the convex hull of the points~$\sum_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\end{theorem}

\begin{proof}
\vincent{todo}
\end{proof}

In fact, the wigglyhedron even recovers the wiggly lattice of \cref{subsec:wigglyPermutations}.

\begin{proposition}
The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in the direction~$\omega \eqdef (2n, \dots, 1) - (1, \dots, 2n)$.
\end{proposition}

\begin{proof}
\vincent{todo}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Wiggly pseudotriangulations of planar point sets}

We now extend \cref{thm:wigglyhedron,conj:Hamiltonian} to wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).

\begin{definition}
Fix a point set~$P$ of the plane, and an arbitrary total order~$<$ on~$P$.
A \defn{wiggly arc} is a quadruple~$(p,q,R,S)$ where~$p < q \in P$ and the sets~$R$ and~$S$ form a partition of the points of~$P$ located in the open segment joining~$p$ to~$q$.
Two wiggly arcs~$(p,q,R,S)$ and~$(p',q',R',S')$ are \defn{crossing} if 
\begin{itemize}
\item either the segments~$[p,q]$ and~$[p',q']$ cross, 
\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$,
\end{itemize}
A set~$X$ of wiggly arcs is \defn{pointed} if for any~$p \in P$, the wiggly arcs of~$X$ with an endpoint at~$p$ generate a pointed cone.
The \defn{wiggly complex}~$\wigglyComplex_P$ is the simplicial complex of pairwise pointed and non-crossing subsets of wiggly arcs.
Note that the boundary wiggly arcs are irrelevant, which allows us to consider a reduced wiggly complex~$\wigglyComplex_P$ induced by internal wiggly arcs.
A \defn{wiggly pseudotriangulation} of~$P$ is a facet of~$\wigglyComplex_P$.
The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
Note that, by construction, $\wigglyFlipGraph_P$ is regular.
See \cref{fig:wigglyComplexSquarre} for an illustration.
%
\begin{figure}[!h]
\centering
\includegraphics[scale=1]{wigglyComplexSquare}
\caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}
\label{fig:wigglyComplexSquarre}
\end{figure}
\end{definition}

\begin{conjecture}
\label{conj:polytopality}
For any point set~$P$ in the plane, the wiggly complex~$\wigglyComplex_P$ is the boundary complex of a simplicial polytope.
\end{conjecture}

Note that in \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope} (see also \cite{RoteSantosStreinu-pseudotriangulations} for a nice survey on pseudotriangulations).

\begin{conjecture}
\label{conj:Hamiltonian2}
For any point set~$P$ in the plane, the wiggly flip graph~$\wigglyFlipGraph_P$ is Hamiltonian.
\end{conjecture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Further questions}

A few additional questions to arouse your curiosity:
\begin{enumerate}
\item Can the construction of \cref{thm:wigglyhedron} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
\item What is the dual interpretation of wiggly pseudotriangulations as pseudoline arrangements? (see~\cite{PilaudPocchiola} for context) Can this interpretation be extended to other finite Coxeter groups? (see~\cite{CeballosLabbeStump} for context).
\item What is the multi wiggly complex?
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\clearpage
\addtocontents{toc}{ \vspace{.1cm} }
\bibliographystyle{alpha}
\bibliography{wigglyhedra}
\label{sec:biblio}

\end{document}

### 2024-02-22 programmation/wigglyPseudotriangulations.py

@@ -1,0 +1,605 @@
+from collections import defaultdict
+from functools import cmp_to_key
+
+### WIGGLY COMPLEX ON ARCS
+
+@cached_function
+def number_arcs(n):
+    r"""
+    Return the number of arcs on n+2 points.
+
+    EXAMPLES::
+        sage: [number_arcs(n) for n in range(10)]
+        [1, 4, 11, 26, 57, 120, 247, 502, 1013, 2036]
+    """
+    return add(2**j * (n+1-j) for j in range(n+1))
+
+def number_relevant_arcs(n):
+    r"""
+    Return the number of arcs on n+2 points.
+
+    EXAMPLES::
+        sage: [number_relevant_arcs(n) for n in range(10)]
+        [0, 2, 9, 24, 55, 118, 245, 500, 1011, 2034]
+    """
+    return max(0, number_arcs(n)-2)
+
+@cached_function
+def arcs(n):
+    r"""
+    Return all arcs on n+2 points.
+
+    EXAMPLES::
+        sage: arcs(2)
+        [(0, 1, {}, {}),
+         (0, 2, {}, {1}),
+         (0, 2, {1}, {}),
+         (1, 2, {}, {}),
+         (0, 3, {}, {1, 2}),
+         (0, 3, {1}, {2}),
+         (0, 3, {2}, {1}),
+         (0, 3, {1, 2}, {}),
+         (1, 3, {}, {2}),
+         (1, 3, {2}, {}),
+         (2, 3, {}, {})]
+    """
+    return [(i, j, A, Set(range(i+1, j)).difference(A)) for j in range(n+2) for i in range(j) for A in Subsets(range(i+1, j))]
+
+@cached_function
+def relevant_arcs(n):
+    r"""
+    Return all relevant arcs on n+2 points.
+
+    EXAMPLES::
+        sage: relevant_arcs(2)
+        [(0, 1, {}, {}),
+         (0, 2, {}, {1}),
+         (0, 2, {1}, {}),
+         (1, 2, {}, {}),
+         (0, 3, {1}, {2}),
+         (0, 3, {2}, {1}),
+         (1, 3, {}, {2}),
+         (1, 3, {2}, {}),
+         (2, 3, {}, {})]
+    """
[…]

### 2024-02-22 draft/wigglyhedra.tex
minor corrections

@@
 In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points and the wiggly permutations of~$[2n]$, and we prove that they are in bijection.
-These two perspectives enable us to endow this combinatorial families with additional structures : the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
+These two perspectives enable us to endow these combinatorial families with additional structures: the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
 
@@
 
-We start with wiggly pseudodissections of points on a line.
+We start with wiggly pseudodissections of $n+2$ points on a line.
 The following definitions are illustrated in \cref{fig:incompatible}.
@@
 \begin{figure}[b]
-\centerline{\includegraphics[scale=1.3]{pseudodissections}}
+\centerline{\includegraphics[scale=1.5]{pseudodissections}}
 \caption{Three wiggly pseudodissections.
@@
 \centering
-\includegraphics[scale=1]{wigglyFlipGraph}
+\includegraphics[scale=1.1]{wigglyFlipGraph}
 \caption{The wiggly lattice~$\wigglyLattice_2$ on wiggly pseudotriangulations (left) and on wiggly permutations (right).}
@@
 
-We close this section by the following conjecture (checked computationally up to~$n = 4$).
+We close this section by the following conjecture (checked computationally up to~$n = 3$).
 
@@
 \label{prop:characterizationFan}
-Consider a closed simplicial pseudomanifold~$\Delta$ with ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
+Consider a closed simplicial $(d-1)$-dimensional pseudomanifold~$\Delta$ with ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
 Then the collection of cones~$\set{\R_{\ge 0}\b{R}_\triangle}{\triangle \in \Delta}$ forms a complete simplicial fan of~$\R^d$ if and~only~if
@@
 
-We now define two families of vectors.
+We now define two families of vectors, illustrated in \cref{fig:pseudotriangulationMatrices}.
 %

### 2024-02-22 draft/wigglyhedra.tex
add proofs

@@
 
+\begin{lemma}
+\label{lem:wallCrossingInequalities}
+Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
+Then
+\begin{itemize}
+\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\kappa(\alpha) + \kappa(\alpha') > \big( \kappa(\beta) + \kappa(\beta') \big) / 2$,
+\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\kappa(\alpha) + \kappa(\alpha') > \kappa(\beta) + \kappa(\beta')}$.
+\end{itemize}
+\end{lemma}
+
+\begin{proof}
+Any crossing between a wiggly arc~$\gamma$ and~$\beta$ or~$\beta'$ translates to a crossing with~$\alpha$ or~$\alpha'$.
+When~$\alpha$ and~$\alpha'$ are not pointed, a crossing with~$\alpha$ or~$\alpha'$ can correspond to a crossing with~$\beta$ and a crossing with~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \big( \delta(\beta, \gamma) + \delta(\beta', \gamma) \big) / 2$.
+When~$\alpha$ and~$\alpha'$ are crossing, then there is a correspondence between the crossings with~$\alpha$ or~$\alpha'$ and the crossings with~$\beta$ or~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \delta(\beta, \gamma) + \delta(\beta', \gamma)$
+The result follows by summation, and since~$\delta(\alpha, \alpha') = 1$.
+\end{proof}
+
 \begin{theorem}
@@
 \begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \nu(\alpha)}$ for all internal wiggly arcs~$\alpha$,
-\item the convex hull of the points~$\sum_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
+\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
+\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
 \end{itemize}
@@
 \begin{proof}
-\vincent{todo}
+By \cref{prop:characterizationPolytopalFan,lem:linearDependences,lem:wallCrossingInequalities}, the wiggly fan is indeed the normal fan of the polytope~$\wigglyhedron_n$ defined by the inequalities~$\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$.
+For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\beta \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\beta, T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{prop:dualBases}.
+Hence, $\b{p}(T)$ is indeed the point of~$\wigglyhedron_n$ corresponding to~$T$, which is located at the intersection of the hyperplanes~$\dotprod{\b{g}(\alpha)}{\b{x}} = \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$ in~$T$.
 \end{proof}

### 2024-02-23 draft/wigglyhedra.tex
two minor improvements

@@
 
-\thanks{VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
+\thanks{VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
 
@@
 \[
-\inv(\sigma) \eqdef \set{(\sigma_i, \sigma_j)}{1 \le i < j \le 2n \text{ and } \sigma_i > \sigma_j}.
+\inv(\sigma) \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) > \sigma(j)}.
 \]
@@
 
-Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$i$ such that~$\sigma_i < \sigma_{i+1}$ (resp.~$\sigma_i > \sigma_{i+1}$).
+Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$j$ such that~$\sigma(j) < \sigma(j+1)$ (resp.~$\sigma(j) > \sigma(j+1)$).
 
@@
 \begin{proof}
-%For a descent~$i$, consider...
-\vincent{todo}
+Consider an ascent~$j$ of~$\sigma$.
+Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
+Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
+Let~$\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n)$.
+Then~$\sigma^j$ is the minimal wiggly permutation such that~$\inv(\sigma^j) \supseteq \inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\}$.
+Moreover,~$\sigma^j \ne \sigma^{j'}$ for distinct ascents~$j \ne j'$.
+As any permutation~$\sigma'$ larger than~$\sigma$ satisfies~${\inv(\sigma') \supseteq \inv(\sigma) \cup \{\sigma(j+1), \sigma(j)\}}$ for some ascent~$j$ of~$\sigma$, we thus obtain that~$j \to \sigma^j$ is a bijection from the ascents of~$\sigma$ to the wiggly permutations covering~$\sigma$.
+The proof is symmetrical for the bijection from descents of~$\sigma$ to wiggly permutations covered by~$\sigma$.
 \end{proof}
@@
 \item $1$ is~$\alpha$ and~$\alpha'$ are not pointed (\ie $i = j'$ or~$i' = j$),
-\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing.
-\vincent{give an equivalent definition with subsets...}
+\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing (\ie the number of~$p \in \{0, \dots, n\}$ with $p \in (A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\})$ and~$p+1 \in (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, or the opposite).
 \end{itemize}

### 2024-02-23 draft/wigglyhedra.tex
minor corrrections

@@
 \begin{definition}
-A \defn{wiggly arc} is a quadruple $(i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~$\{i+1, \dots, j-1\}$.
-We represent it by an $x$-monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
-The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~$\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])$ are called \defn{external}, all others are called \defn{internal}.
+A \defn{wiggly arc} is a quadruple $\alpha \eqdef (i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~${]i,j[} \eqdef \{i+1, \dots, j-1\}$.
+We represent $\alpha$ by an $x$-monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
+The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~$\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])$ are called \defn{external}, all other wiggly arcs are called \defn{internal}.
 \end{definition}
@@
 \end{definition}
+
+\vincent{Here, I am using the fact that a set of pairwise non-crossing arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
 
@@
 \item those where $p$ and $p'$ are not consecutive along~$c$, and do not overlap vertically,
-\item those where $p$ and $p'$ are not consecutive along~$c$, but overlap vertically.
-\item those where~$p$ and~$p'$ are consecutive along~$c$,
+\item those where $p$ and $p'$ are not consecutive along~$c$, but overlap vertically,
+\item those where~$p$ and~$p'$ are consecutive along~$c$.
 \end{enumerate}
@@
 Consider a hinge~$j$ of~$c$.
-Assume by symmetry that the boundary of~$c$ contains the two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j, A', B')$, such that~$\alpha$ is below~$\alpha'$.
+Assume by symmetry that the boundary of~$c$ contains two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j, A', B')$, such that~$\alpha$ is below~$\alpha'$.
 % (\ie $k \in A'$ or~$k' \in B$).
@@
 \]
-In other words, the number of wiggly arcs of~$D$ is $2n-1$ minus the number of wiggly cells of~$D$ which are not wiggly pseudotriangles.
 \end{remark}
@@
 The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
-For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal arcs ending at the last point~$n+1$.
+For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal wiggly arcs ending at the last point~$n+1$.
 For instance,
 \begin{align*}
-	f_0(x) & = 1 \\
-	f_1(x) & = x + 1 \\
-	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2 \\
-	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14
+	f_0(x) & = 1, \\
+	f_1(x) & = x + 1, \\
+	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
+	f_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
 \end{align*}
@@
 Finally, we will need the following observation, illustrated in \cref{fig:incompatible2}.
-
-\begin{proposition}
-\label{prop:uerp}
-Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
-Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
-\begin{itemize}
-\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
-(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$.
-(In other words, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
-\end{itemize}
-See \cref{fig:incompatible2} for illustrations.
 %
@@
 \end{figure}
-%
+
+\begin{proposition}
+\label{prop:uerp}
+Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
+Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
+\begin{itemize}
+\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
+(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
+\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$.
+(In other words, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
+\end{itemize}
+%See \cref{fig:incompatible2} for illustrations.
 (By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
@@
 
-We now consider wiggly permutations, defined as follows.
+We now consider wiggly permutations of~$[2n]$, defined as follows.
 
@@
 
+We now aim at describing the cover relations of the wiggly lattice.
 Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$j$ such that~$\sigma(j) < \sigma(j+1)$ (resp.~$\sigma(j) > \sigma(j+1)$).
+
+\begin{lemma}
+Consider an ascent~$j$ of a wiggly permutation~$\sigma$ of~$[2n]$.
+Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
+Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
+Then
+\[
+\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n).
+\]
+is the minimal wiggly permutation such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\sigma^j)$.
+\end{lemma}
+
+\begin{proof}
+We start with a few observations.
+Let~$i < p \le j$ (resp.~$j+1 \le q < k$).
+As~$\sigma$ is a wiggly permutation, we have~$\sigma(p) < \sigma(i)$ (resp.~$\sigma(q) > \sigma(k)$).
+Hence~$\big( \sigma(i), \sigma(p) \big)$ (resp.~$\big( \sigma(q), \sigma(k) \big)$) belongs to~$\inv(\sigma)$.
+Moreover, since~$j$ is an ascent of~$\sigma$, we obtain that~$\sigma(p) < \sigma(q)$ for all~${i \le p \le j < q \le k}$.
+Hence, $\inv(\sigma^j) = \inv(\sigma) \cup \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}$.
+
+We now prove that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$.
+We consider~$v \in [n]$ and~$u < 2v-1$ such that~$(2v-1, u) \in \inv(\sigma^j)$, and we show that~$(2v, u) \in \inv(\sigma^j)$.
+If~$(2v, u) \in \inv(\sigma)$, we are done as~$\inv(\sigma) \subset \inv(\sigma^j)$.
+If~$(2v, u) \not\in \inv(\sigma)$, then~$(2v-1, u) \not\in \inv(\sigma)$ by \cref{lem:inversionSetsWigglyPermutations}, and~$i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v-1) \le k$ since~${\inv(\sigma^j) \ssm \inv(\sigma) = \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}}$.
+We have~$\sigma^{-1}(2v) \le k$ since~$\sigma$ is a wiggly permutation.
+As~$(2v, u) \not\in \inv(\sigma)$ and~$\sigma(p) < \sigma(q)$ for all~$i \le p \le j < q \le k$, we conclude that~$j < \sigma^{-1}(2v) < k$.
+Hence, we obtain that ${i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v) \le k}$, so that~$(2v,u) \in \inv(\sigma^j)$.
+Similarly~${(w, 2v-1) \in \inv(\sigma^j)}$ implies~$(w, 2v) \in \inv(\sigma^j)$ for all~$v \in [n]$ and~$w > 2v$.
+We conclude that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$ by \cref{lem:inversionSetsWigglyPermutations}.
+
+Consider now any wiggly transposition~$\tau$ such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\tau)$.
+By \cref{lem:inversionSetsWigglyPermutations}, we obtain that~$\inv(\tau)$ also contains % both~$\big( \sigma(j+1), \sigma(i) \big)$ and~$\big( \sigma(k), \sigma(j) \big)$, hence also~
+$\big( \sigma(k), \sigma(i) \big)$.
+Since~$\inv(\sigma) \subset \inv(\tau)$ and~$\inv(\sigma)$ contains~$\big( \sigma(i), \sigma(p) \big)$ and~$\big( \sigma(q), \sigma(k) \big)$ for all~$i < p \le j$ and~$j+1 \le q < k$, we conclude by transitivity that~$\inv(\tau)$ contains~$\big( \sigma(q), \sigma(p) \big)$ for all~$i \le p \le j < q \le k$.
+\end{proof}
 
@@
 \begin{proof}
-Consider an ascent~$j$ of~$\sigma$.
-Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
-Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
-Let~$\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n)$.
-Then~$\sigma^j$ is the minimal wiggly permutation such that~$\inv(\sigma^j) \supseteq \inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\}$.
-Moreover,~$\sigma^j \ne \sigma^{j'}$ for distinct ascents~$j \ne j'$.
+%Consider an ascent~$j$ of~$\sigma$.
+%Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
+%Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
+%Let~$\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n)$.
+%Then~$\sigma^j$ is the minimal wiggly permutation such that~$\inv(\sigma^j) \supseteq \inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\}$.
+Observe that~$\sigma^j \ne \sigma^{j'}$ for distinct ascents~$j \ne j'$.
 As any permutation~$\sigma'$ larger than~$\sigma$ satisfies~${\inv(\sigma') \supseteq \inv(\sigma) \cup \{\sigma(j+1), \sigma(j)\}}$ for some ascent~$j$ of~$\sigma$, we thus obtain that~$j \to \sigma^j$ is a bijection from the ascents of~$\sigma$ to the wiggly permutations covering~$\sigma$.

### 2024-02-26 draft/wigglyhedra.tex
added definition of increasing flip graph, automorphisms, and started Cambrian considerations

@@
 \newcommand{\wigglyFlipGraph}{\mathrm{WFG}} % wiggly flip graph
+\newcommand{\wigglyIncreasingFlipGraph}{\mathrm{WIFG}} % wiggly increasing flip graph
 \newcommand{\wigglyLattice}{\mathrm{WL}} % wiggly lattice
@@
 \end{proof}
+
+The following definition is illustrated in \cref{fig:incompatible2}.
+%
+\begin{figure}
+\centering
+\includegraphics[scale=1.3]{incompatible2}
+\caption{The arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
+\label{fig:incompatible2}
+\end{figure}
+
+\begin{definition}
+\label{def:wigglyIncreasingFlipGraph}
+Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two wiggly arcs and~$T$ and~$T'$ be two wiggly pseudotriangulations, such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
+We say that the flip from~$T$ to~$T'$ is \defn{increasing} if 
+\begin{itemize}
+\item $\alpha$ starts where~$\alpha'$ ends (that is, $i = j'$), or 
+\item $\alpha$ crosses~$\alpha'$ from north-west to south-east (that is, there exists~$k \in [n-1]$ such that $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$).
+\end{itemize}
+The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and a edge for each increasing~flip.
+\end{definition}
 
@@
 
-Finally, we will need the following observation, illustrated in \cref{fig:incompatible2}.
+\begin{remark}
+\label{rem:wigglyComplexAutomorphism}
+The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
+Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
+\end{remark}
+
+Finally, we will need the following observation, illustrated in \cref{fig:incompatible3}.
 %
@@
 \centering
-\includegraphics[scale=1.3]{incompatible2}
+\includegraphics[scale=1.3]{incompatible3}
 \caption{The arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
-\label{fig:incompatible2}
+\label{fig:incompatible3}
 \end{figure}
@@
 (In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$.
-(In other words, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
-\end{itemize}
-%See \cref{fig:incompatible2} for illustrations.
+\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ such that~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
+(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
+\end{itemize}
+%See \cref{fig:incompatible3} for illustrations.
 (By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
@@
 
+\begin{remark}
+\label{rem:wigglyLatticeAntiIsomorphism}
+The map~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_n)$ obviously provides an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$.
+\end{remark}
+
 We now aim at describing the cover relations of the wiggly lattice.
@@
 \begin{proposition}
-The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a graph isomorphism between the wiggly flip graph~$\wigglyFlipGraph_n$ and the cover graph of the wiggly lattice~$\wigglyLattice_n$.
+The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a directed graph isomorphism between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
 \end{proposition}
@@
 \end{proof}
+
+\begin{remark}
+The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
+\end{remark}
 
@@
 \label{lem:-+...-+}
-Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$ for all~${i \in [n]}$.
+Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and for~${i \in [n]}$, let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$.
 Then~$\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \langle \b{g}(T) \rangle$.
@@
 \end{itemize}
-%Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs, and let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-%Then
-%\begin{description}
-%\item[if $\alpha$ and~$\alpha'$ are not pointed] Assume without loss of generality that~$i' = j$, and consider %the wiggly arcs~
-%$\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$.
-%(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-%Then~$\{\beta, \beta'\} \in T \cap T'$ and~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$.
-%\item[if~$\alpha$ and~$\alpha'$ are crossing] Assume without loss of generality that~$i \in A'$ or~$i' \in B$, and consider %the wiggly arcs~
-%$\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$. \linebreak
-%(In other words, if~$p$ denotes the crossing point of~$\alpha$ and~$\alpha'$, then~$\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows~$\alpha$ on~$]i,p[$ and~$\alpha'$ on~$]p,j'[$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows~$\alpha$ on~$]i',p[$ and~$\alpha$ on~$]p,j[$.)
-%Then~${\{\beta, \beta'\} \in T \cap T'}$ and~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
-%\end{description}
 \end{lemma}
@@
 
-If~$\alpha$ and~$\alpha'$ are crossing with~$i \in A'$ or~$i' \in B$, then we have
+If~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ with $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$, then we have
 \begin{gather*}
@@
 \begin{remark}
-This is indeed an incompatibility degree in the sense that
+Note that~$\delta$ is indeed an incompatibility degree in the sense that
 \begin{itemize}
@@
 \end{itemize}
+Observe also that~$\delta$ (and thus~$\kappa$) is preserved by the automorphisms of \cref{rem:wigglyComplexAutomorphism}.
 \end{remark}
+
+\begin{example}
+Observe that
+$\kappa \big( (0, j, {[1,j[}, \varnothing) \big) 
+= \kappa \big( (0, j, \varnothing, {[1,j[}) \big) 
+%= \kappa \big( (n+1-j, n+1, {]n+1-j, n]}, \varnothing) \big) 
+%= \kappa \big( (n+1-j, n+1, \varnothing, {]n+1-j, n]}) \big) 
+= (2^j-1)(2^{n+1-j}-1)$.
+\end{example}
 
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Cambrian considerations}
+
+In this section, we fix a signature~$\delta \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
+
+\begin{definition}
+The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point at abscissa~$i$ and ordinate of the sign of~$\delta_i$  for all~$0 \le i \le n+1$
+A \defn{$\delta$-triangulation} is a set of ordered pairs~$(i,j)$ which are the internal diagonals of a triangulation of the $\delta$-gon.
+The \defn{$\delta$-triangulation lattice} is the transitive closure of the slope increasing flip graph on $\delta$-triangulations.
+%If~$T$ and~$T'$ are two $\delta$-triangulations with~$T \ssm \{d\} = T' \ssm \{d'\}$, then the flip from~$T$ to~$T'$ is \defn{increasing} if the slope of~$d$ is smaller than the slope of~$d'$.
+\end{definition}
+
+\begin{definition}
+A \defn{$\delta$-permutation} is a permutation of~$[n]$ which avoids~$\cdots ik \cdots j \cdots$ with~$i < j < k$ and~$\delta_j = -$, and~$\cdots j \cdots ik \cdots$ with~$i < j < k$ and~$\delta_j = +$.
+The \defn{$\delta$-permutation lattice} is the sublattice of the weak order induced by $\delta$-permutations.
+\end{definition}
+
+\begin{definition}
+\label{def:CambrianWigglyPseudotriangulations}
+The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j > 0$ and~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j < 0$.
+A \defn{$\delta$-wiggly pseudotriangulation} is a wiggly pseudotriangulation containing all $\delta$-wiggly arcs.
+The \defn{$\delta$-wiggly pseudotriangulation lattice} is the transitive closure of the increasing flip graph on $\delta$-wiggly pseudotriangulations.
+\end{definition}
+
+\begin{definition}
+\label{def:CambrianWigglyPermutations}
+A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ such that
+% for all~$j \in [n]$, we have~ and~$\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$i \in [2j-2]$.
+%\begin{itemize}
+%\item $\sigma^{-1}(2j-1) > \sigma^{-1}(2j)$ for all~$j \in [n]$,
+%\item $\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$j \in [n]$ and~$i \in [2j-2]$.
+%\end{itemize}
+\[
+\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
+\qquad\text{and}\qquad
+\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)
+\]
+%$\delta_j > 0 \implies \sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ and~$\delta_j < 0 \implies \sigma^{-1}(i) \ge \sigma^{-1}(2j)$
+for all~$1 \le i \le 2j \le 2n$.
+The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly permutation lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
+\end{definition}
+
+\begin{proposition}
+\label{prop:CambrianIntervals}
+For any signature~$\delta \in \{+,-\}^n$, the $\delta$-triangulation lattice, $\delta$-permutation lattice, \mbox{$\delta$-wiggly} pseudotriangulation lattice, and $\delta$-wiggly permutation lattice are all isomorphic, and are known as the \defn{$\delta$-Cambrian lattice}~\cite{Reading-CambrianLattices}.
+\end{proposition}
+
+\begin{proof}
+\vincent{todo}
+\end{proof}
+
+\begin{remark}
+We had to make a choice in \cref{def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations}.
+For~$\delta_j = {+}$, we could replace ``$(0, j, {[1,j[}, \varnothing)$'' by~``$(j, n+1, {]j,n]}, \varnothing)$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
+Independently, for~$\delta_j = {-}$, we could replace ``$(0, j, \varnothing, {[1,j[})$'' by~``$(j, n+1, \varnothing, {]j,n]})$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(2j) \le \sigma^{-1}(i)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(2j-1) \le \sigma^{-1}(i)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
+%\end{itemize}
+\end{remark}
+
+\vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
 

### 2024-02-26 programmation/wigglyPseudotriangulations.py

@@ -569,6 +569,66 @@ def wigglyhedron(n, method='inequalities'):
     if method == 'vertices': return wigglyhedron_from_vertices(n)
     print('method should be inequalities or vertices')
 
+### CAMBRIAN LATTICES
+
+@cached_function
+def cambrian_face(signature):
+    r"""
+    Return a collection of wiggly arcs corresponding to a given signature.
+    """
+    n = len(signature)
+    return Set([(0, i+1, tuple([]), tuple(range(1,i+1))) for i in range(n) if signature[i] < 0] + [(0, i+1, tuple(range(1,i+1)), tuple([])) for i in range(n) if signature[i] > 0]) # left - left
+    # return Set([(i+1, n+1, tuple([]), tuple(range(i+2,n+1))) for i in range(n) if signature[i] < 0] + [(0, i+1, tuple(range(1,i+1)), tuple([])) for i in range(n) if signature[i] > 0]) # right - left
+    # return Set([(0, i+1, tuple([]), tuple(range(1,i+1))) for i in range(n) if signature[i] < 0] + [(i+1, n+1, tuple(range(i+2,n+1)), tuple([])) for i in range(n) if signature[i] > 0]) # left - right
+    # return Set([(i+1, n+1, tuple([]), tuple(range(i+2,n+1))) for i in range(n) if signature[i] < 0] + [(i+1, n+1, tuple(range(i+2,n+1)), tuple([])) for i in range(n) if signature[i] > 0]) # right - right
+
+@cached_function
+def cambrian_complex(signature):
+    r"""
+    Return the subcomplex of the wiggly complex corresponding to the given Cambrian associahedron.
+    """
+    return wiggly_complex(len(signature)).link(cambrian_face(signature))
+
+@cached_function
+def cambrian_wiggly_permutations(signature):
+    r"""
+    Return the set of Cambrian wiggly permutations for the given signature.
+    """
+    n = len(signature)
+    return [wp for wp in wiggly_permutations(n) if all(wp.inverse()(2*j+2) < wp.inverse()(i+1) for j in range(n) if signature[j] < 0 for i in range(2*j+1)) and all(wp.inverse()(i+1) <= wp.inverse()(2*j+1) for j in range(n) if signature[j] > 0 for i in range(2*j+2))] # left - left
[…]

### 2024-02-26 draft/wigglyhedra.tex
minor corrections, Cambrian fan, associahedron

@@
 \newcommand{\polytope}[1]{\mathds{#1}} % font polytope
-\newcommandx{\Zono}[1][1=D]{\polytope{Z}_{#1}} % zonotope
-\newcommandx{\Asso}[1][1=n]{\polytope{A}_{#1}} % associahedron
 
@@
 \newcommand{\wigglyhedron}{\polytope{W}} % wigglyhedron
+\newcommand{\Asso}{\polytope{A}\mathsf{sso}} % associahedron
 
@@
 
-If~$\alpha$ and~$\alpha'$ are non pointed with~$i' = j$, then we have
+If~$\alpha$ and~$\alpha'$ are non pointed, then we have
 \[
@@
 
-If~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ with $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$, then we have
+If~$\alpha$ and~$\alpha'$ cross, then we have
 \begin{gather*}
@@
 \begin{definition}
-The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point at abscissa~$i$ and ordinate of the sign of~$\delta_i$  for all~$0 \le i \le n+1$
-A \defn{$\delta$-triangulation} is a set of ordered pairs~$(i,j)$ which are the internal diagonals of a triangulation of the $\delta$-gon.
+The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point with abscissa~$i$ and with ordinate of the same sign as~$\delta_i$  for all~$0 \le i \le n+1$.
+A \defn{$\delta$-triangulation} is a triangulation of the $\delta$-gon.
 The \defn{$\delta$-triangulation lattice} is the transitive closure of the slope increasing flip graph on $\delta$-triangulations.
@@
 \label{def:CambrianWigglyPseudotriangulations}
-The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j > 0$ and~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j < 0$.
+The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j = {+}$ and~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j = {-}$.
 A \defn{$\delta$-wiggly pseudotriangulation} is a wiggly pseudotriangulation containing all $\delta$-wiggly arcs.
@@
 
-\begin{proposition}
-\label{prop:CambrianIntervals}
-For any signature~$\delta \in \{+,-\}^n$, the $\delta$-triangulation lattice, $\delta$-permutation lattice, \mbox{$\delta$-wiggly} pseudotriangulation lattice, and $\delta$-wiggly permutation lattice are all isomorphic, and are known as the \defn{$\delta$-Cambrian lattice}~\cite{Reading-CambrianLattices}.
-\end{proposition}
-
-\begin{proof}
-\vincent{todo}
-\end{proof}
-
 \begin{remark}
@@
 Independently, for~$\delta_j = {-}$, we could replace ``$(0, j, \varnothing, {[1,j[})$'' by~``$(j, n+1, \varnothing, {]j,n]})$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(2j) \le \sigma^{-1}(i)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(2j-1) \le \sigma^{-1}(i)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
-%\end{itemize}
+\cref{prop:CambrianLattice,prop:CambrianFan} would still hold.
 \end{remark}
 
+\begin{proposition}
+\label{prop:CambrianLattice}
+For any signature~$\delta \in \{+,-\}^n$, the $\delta$-triangulation lattice, $\delta$-permutation lattice, \mbox{$\delta$-wiggly} pseudotriangulation lattice, and $\delta$-wiggly permutation lattice are all isomorphic, and are known as the \defn{$\delta$-Cambrian lattice}~\cite{Reading-CambrianLattices}.
+\end{proposition}
+
+\begin{proof}
+\vincent{todo}
+\end{proof}
+
+Recall that the $\delta$-Cambrian lattice can be realized by the $\delta$-Cambrian fan~\cite{ReadingSpeyer} and the $\delta$-associahedron of~\cite{HohlwegLange}.
+Namely, to each diagonal~$(i,j)$ of the $\delta$-gon, we associate the subset~$X(\delta)$ of points of the $\delta$-gon distinct from~$0$ and~$n+1$, and located below the line~$(i,j)$, including~$i$ if and only if~$\delta_i = {+}$ and~$j$ if and only if~$\delta_j = {+}$.
+The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
+The \defn{$\delta$-associahedron} is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \le \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
+
+\begin{proposition}
+\label{prop:CambrianFan}
+The $\delta$-associahedron~$\Asso_\delta$ is normally equivalent to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly arcs.
+\end{proposition}
+
+\begin{proof}
+The maps of \cref{prop:CambrianLattice} preserve the $\b{g}$-vector linear dependences.
+\vincent{explain}
+\end{proof}
+
 \vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
+\vincent{todo: add picture}
 

### 2024-02-27 draft/wigglyhedra.tex
improve Cambrian

@@
 %\usepackage{tikz-qtree}
-\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
+\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles, cd}
 \usepackage[external]{forest}
@@
 \begin{figure}
-\centering
-\includegraphics[scale=1.3]{incompatible2}
+\centerline{\includegraphics[scale=1.3]{incompatible2}}
 \caption{The arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
@@
 \begin{figure}
-\centering
-\includegraphics[scale=1.3]{incompatible3}
+\centerline{\includegraphics[scale=1.3]{incompatible3}}
 \caption{The arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
@@
 \begin{figure}
-\centering
-\includegraphics[scale=1.1]{wigglyFlipGraph}
+\centerline{\includegraphics[scale=1.1]{wigglyFlipGraph}}
 \caption{The wiggly lattice~$\wigglyLattice_2$ on wiggly pseudotriangulations (left) and on wiggly permutations (right).}
@@
 \begin{figure}[t]
-\centering
-\input{wigglyhedron}
+\centerline{\input{wigglyhedron}}
 \caption{The wigglyhedron~$\wigglyhedron_2$.}
@@
 In this section, we fix a signature~$\delta \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
-
-\begin{definition}
+We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice of \cref{sec:combinatorics} and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron of \cref{sec:geometry}.
+\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.
+
+\begin{figure}
+\centerline{\includegraphics[scale=1.1]{wigglyCambrian1}}
+\vspace{-.3cm}
+\centerline{\includegraphics[scale=1.1]{wigglyCambrian2}}
+\vspace{-.5cm}
+\centerline{\includegraphics[scale=1.1]{wigglyCambrian3}}
+\caption{Cambrian lattices as intervals of wiggly lattices.}
+\label{fig:wigglyCambrian}
+\end{figure}
+
+\begin{definition}
+\label{def:CambrianTriangulations}
 The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point with abscissa~$i$ and with ordinate of the same sign as~$\delta_i$  for all~$0 \le i \le n+1$.
@@
 \begin{definition}
-A \defn{$\delta$-permutation} is a permutation of~$[n]$ which avoids~$\cdots ik \cdots j \cdots$ with~$i < j < k$ and~$\delta_j = -$, and~$\cdots j \cdots ik \cdots$ with~$i < j < k$ and~$\delta_j = +$.
+\label{def:CambrianPermutations}
+A \defn{$\delta$-permutation} is a permutation of~$[n]$ which avoids~$\cdots ik \cdots j \cdots$ with~$i < j < k$ and~$\delta_j = -$, and~$\cdots j \cdots ki \cdots$ with~$i < j < k$ and~$\delta_j = +$.
 The \defn{$\delta$-permutation lattice} is the sublattice of the weak order induced by $\delta$-permutations.
@@
 \begin{proof}
-\vincent{todo}
+We only describe the following bijections
+\begin{center}
+\begin{tikzcd}[column sep=3cm]
+\text{$\delta$-triangulations} \arrow[d] & \text{$\delta$-permutations} \arrow[l] \\
+\text{$\delta$-wiggly pseudotriangulations} \arrow[r] & \text{$\delta$-wiggly permutations} \arrow[u]
+%\text{$\delta$-triangulations} \arrow[d, "\lambda"'] & \text{$\delta$-permutations} \arrow[l, "\zeta"'] \\
+%\text{$\delta$-wiggly pseudotriangulations} \arrow[r, "\mu"'] & \text{$\delta$-wiggly permutations} \arrow[u, "\nu"']
+\end{tikzcd}
+\end{center}
+illustrated in \cref{fig:wigglyCambrian}.
+We let the readers convince themselves that they are well-defined, that they compose to the identity, and that they preserve the flip structure.
+(We also invite the reader to work out the explicit description of the 8 missing arrows.)
+For~$I \subseteq [n]$, we set~$I^+ \eqdef \set{i \in I}{\delta_i = {+}}$ and~$I^- \eqdef \set{i \in I}{\delta_i = {-}}$.
+
+\para{From $\delta$-triangulations to $\delta$-wiggly pseudotriangulations}
+Replace each diagonal~$(i,j)$ of the $\delta$-gon by the wiggly arc~$(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
+
+\para{From $\delta$-wiggly pseudotriangulations to $\delta$-wiggly permutations}
+Already described in \cref{def:bijection1}.
+
+\para{From $\delta$-wiggly permutations to $\delta$-permutations}
+For all~$j \in [n]$, erase~$2j-1$ and replace~$2j$ by~$j$ if~$\delta_j = {+}$, and erase~$2j$ and replace~$2j-1$ by~$j$ if~$\delta_j = {-}$.
+
+\para{From $\delta$-permutations to $\delta$-triangulations}
+Already described in~\cite{Reading-CambrianLattices}.
+Given a permutation~$\pi$, construct the union of the upper hulls of the point sets~$[n]^- \symdif \pi([j])$ for all~$j \in \{0, \dots, n\}$.
 \end{proof}
@@
 \begin{figure}[!h]
-\centering
-\includegraphics[scale=1]{wigglyComplexSquare}
+\centerline{\includegraphics[scale=1]{wigglyComplexSquare}}
 \caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}

### 2024-02-27 programmation/wigglyPseudotriangulations.py

@@ -463,6 +463,12 @@ def wp2wpt(wp):
 
 ### WIGGLYHEDRON
 
+def basis_vector(i,m):
+    r"""
+    Return the i-th vector of the standard basis.
+    """
+    return vector([0]*(i-1) + [1] + [0]*(m-i))
+
 def g_vector(arc, n, essential=True):
     r"""
     Return the g-vector of an arc.

### 2024-02-27 draft/wigglyhedra.tex
wrapping up Cambrian considerations

@@
 \para{From $\delta$-wiggly pseudotriangulations to $\delta$-wiggly permutations}
-Already described in \cref{def:bijection1}.
+Specialization of \cref{def:bijection1}.
 
@@
 \begin{proof}
-The maps of \cref{prop:CambrianLattice} preserve the $\b{g}$-vector linear dependences.
-\vincent{explain}
-\end{proof}
-
-\vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
-\vincent{todo: add picture}
+Following the proof of \cref{prop:CambrianLattice}, consider the map~$\zeta$ sending a diagonal~$(i,j)$ of the $\delta$-gon to the wiggly arc $(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
+Let~$a \eqdef (i,j)$ and~$a' \eqdef (i',j')$ be two crossing diagonals of the~$\delta$-gon.
+Then any $\delta$-triangulations~$T$ and~$T'$ with~$T \ssm \{a\} = T' \ssm \{a'\}$ contain the diagonals~$b \eqdef (i',j)$ and~$b' \eqdef (i,j')$ of the $\delta$-gon, and~$\b{g}(a) + \b{g}(a') = \b{g}(b) + \b{g}(b')$.
+Moreover, if~$\alpha \eqdef \zeta(a)$, $\alpha' \eqdef \zeta(a')$, $\beta \eqdef \zeta(b)$ and~$\beta' \eqdef \zeta(b')$, then~$\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')$.
+We thus conclude that $\zeta$ preserves the linear dependences among $\b{g}$-vectors.
+Hence, there is a linear map~$Z : \HH_n \to \HH_{2n}$ such that~$Z \big( \b{g}(d) \big) = \b{g} \big( \zeta(d) \big)$ for all diagonals~$d$ of the $\delta$-gon.
+This map is a normal equivalence from $\delta$-associahedron~$\Asso_\delta$ to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly~arcs.
+\end{proof}
+
+%\vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
 
@@
 
-We now extend \cref{thm:wigglyhedron,conj:Hamiltonian} to wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).
+We now consider \cref{thm:wigglyhedron,conj:Hamiltonian} for wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).
 

### 2024-02-27 draft/wigglyhedra.tex
directed skeleton

@@
 We now describe the unique linear dependence between the $\b{g}$-vectors of two adjacent facets of the wiggly complex~$\wigglyComplex_n$.
-The following statement is illustrated in \cref{fig:linearDependences}.
+The following statement is illustrated in \cref{fig:incompatible3}.
 
@@
 \begin{proposition}
-The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in the direction~$\omega \eqdef (2n, \dots, 1) - (1, \dots, 2n)$.
+The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in the direction
+\(
+\b{\omega} \eqdef \sum_{i \in [n]} 4ni (\b{e}_{2i-1} + \b{e}_{2i}) + \sum_{j \in [2n]} j \b{e}_j.
+\)
 \end{proposition}
@@
 \begin{proof}
-\vincent{todo}
+Consider an increasing flip~$T \to T'$ between two wiggly pseudotriangulations~$T$ and~$T'$ with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
+Denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$ in the corner labeling of~$T$ described in \cref{def:bijection1}, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
+We have~$u < v$ because the flip~$T \to T'$ is increasing, so that~$\bar u \le \bar v$.
+
+Observe now that~${\b{p}(T') - \b{p}(T)}$ is orthogonal to the $(2n-2)$-dimensional cone of the wiggly fan generated by the $\b{g}$-vectors of the wiggly arcs in~$T \cap T'$, and points from the side containing~$\b{g}(\alpha)$ to the side containing~$\b{g}(\alpha')$.
+Hence, $\b{p}(T') - \b{p}(T)$ is a positive multiple of~$-\b{c}(\alpha, T)$.
+From \cref{def:cvectors}, we observe that
+\begin{itemize}
+\item $\dotprod{\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} = 1/2$ if~$i = \bar u \ne \bar v$, $-1/2$ if~$i = \bar v \ne \bar u$, and $0$ otherwise,
+\item $\dotprod{\b{c}(\alpha, T)}{\b{e}_j}| \le 1/2$ for all~$j \in [2n]$.
+\end{itemize}
+We now distinguish two situations.
+If~$\bar u \ne \bar v$, then
+\[
+\dotprod{-\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} \ge 2n(\bar v - \bar u) + n > 0.
+\]
+If~$\bar u = \bar v$, then~$u = 2k-1$ and~$v = 2k$ for some~$k \in [n]$, and we have
+\[
+\dotprod{\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} = 1/2 > 0.
+\]
+We conclude in both cases that~$\dotprod{\b{c}(\alpha, T)}{\b{\omega}} > 0$, so that we recover the increasing flip graph by orienting the graph of the wigglyhedron~$\wigglyhedron_n$ in direction~$\b{\omega}$.
 \end{proof}

### 2024-02-27 programmation/wigglyPseudotriangulations.py

@@ -522,7 +522,7 @@ def wiggly_fan(n):
     return Fan(cones = [[arc_dict[arc] for arc in f] for f in wiggly_complex(n).faces()[2*n-2]], rays = [g_vector(arc, n) for arc in arcs(n)])
 
 @cached_function
-def wigglyhedron_from_inequalities(n):
+def wigglyhedron_from_inequalities(n, essential=True):
     r"""
     Return the wigglyhedron.
     Here, it is constructed using its inequality description.
@@ -537,26 +537,21 @@ def wigglyhedron_from_inequalities(n):
         A 5-dimensional polyhedron in QQ^5 defined as the convex hull of 176 vertices
         sage: wigglyhedron_from_inequalities(4)
         A 7-dimensional polyhedron in QQ^7 defined as the convex hull of 3232 vertices
-
-        sage: directed_skeleton(wigglyhedron(3)).is_isomorphic(wiggly_permutations_digraph(3))
-        True
-        sage: directed_skeleton(wigglyhedron(4)).is_isomorphic(wiggly_permutations_digraph(4))
-        True
     """
     m = len(relevant_arcs(n))
-    return Polyhedron(ieqs = [[incompatibility_numbers_dictionary(n)[tuplize(arc)]] + list(-g_vector(arc, n)) for arc in relevant_arcs(n)])
+    return Polyhedron(ieqs = [[incompatibility_numbers_dictionary(n)[tuplize(arc)]] + list(-g_vector(arc, n, essential=essential)) for arc in relevant_arcs(n)])
 
-def wiggly_vertex(pt):
+def wiggly_vertex(pt, essential=True):
     r"""
     Return the vertex corresponding to the wiggly pseudotriangulation pt.
     """
     pt = ordered_arcs(pt)
     n = (len(pt)+1)//2
-    cvect = c_vectors(wpt2wp(pt))
+    cvect = c_vectors(wpt2wp(pt), essential=essential)
     return add([incompatibility_numbers_dictionary(n)[tuplize(pt[i])] * cvect[i] for i in range(len(pt))])
 
 @cached_function
-def wigglyhedron_from_vertices(n):
+def wigglyhedron_from_vertices(n, essential=True):
     r"""
     Return the wigglyhedron.
     Here, it is constructed using its vertex description.
@@ -564,16 +559,35 @@ def wigglyhedron_from_vertices(n):
 
     EXAMPLES::
     """
-    return Polyhedron([wiggly_vertex(pt) for pt in wiggly_complex(n).facets()])
[…]

### 2024-02-28 draft/wigglyhedra.tex
Updated arc construction in inverse bijection.
A couple of minor questions/corrections.

@@
 \newcommand{\vincent}[1]{\todo[color=blue!30]{\rm #1 \\ \hfill --- V.}}
+\newcommand{\asilata}[2][]{\todo[size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- A.}}
 
@@
 We consider sets of compatible wiggly arcs.
-The following definitions are illustrated~in~\cref{fig:pseudodissections}.
+The following definitions are illustrated~in~\cref{fig:pseudodissections}.\asilata{It looks like the degree of the green cell is 6 in the figure, not 8.}
 
@@
 Then~$Q \eqdef T \ssm \{\alpha\}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
-By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and an other one~$\alpha'$.
+By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and another one~$\alpha'$.
 As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
@@
 \]
+\asilata[inline]{I think the correct definition of \(\alpha(\sigma,k)\) is as follows.
+  \[\alpha(\sigma,k) = \big(i,j, {]i,j[} \cap \tau(k), {]i,j[} \ssm \tau(k)\big),\]
+  where
+  \[\tau(k) = \{l \in [n] \mid 2l - 1 \in \sigma([k])\text{ and } 2l \in \sigma([k])\}.\]
+}
+
 \end{definition}

### 2024-02-28 draft/wigglyhedra.tex
Half a proof.

@@
   \vincent{todo}
+  Let us first prove that for any wiggly permutation \(\sigma\), the set \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
+  By~\cref{prop:wigglyPseudotriangulations}, it suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
+  \(\alpha(\sigma,k)\) and \(\alpha(\sigma,k')\) are distinct and compatible.
+  First suppose that \(k \leq k'\) and \(\alpha(\sigma,k) = \alpha(\sigma,k') = (i,j,A,B)\).
+  It is easy to see that for any \(l \in [n]\), we have \(2l \in \sigma([k']) \ssm \sigma([k])\) if and only if \(2l -1 \in \sigma([k']) \ssm \sigma([k])\).
+  If \(2l \in \sigma([k']) \ssm \sigma([k])\); equivalently \(2l - 1 \in \sigma([k']) \ssm \sigma([k])\), it is easy to check that
+  \[i < l < j.\]
+  \asilata[inline]{Fix definitions to check distinctness.}
+  We check compatibility.
+  Suppose that
+  \[\alpha(\sigma,k) = (i,j,A,B) \text{ and }\alpha(\sigma,k') = (i',j',A',B').\]
+  It is clear from the definition that \(i \neq j'\), as the sets over which we take the max and min to define \(i\) and \(j'\) respectively are disjoint.
+  Similarly, we have \(j \neq i'\).
+  Therefore the two arcs are pointed.
+  To check that the arcs are non-crossing, we must show that the sets
+  \[(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \text{ and } (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})\]
+  are both empty.
+  We check the first; the second is similar.
+  \asilata[inline]{Fix definitions to check non-crossing-ness.}
+
 \end{proof}

### 2024-02-28 draft/wigglyhedra.tex
minor changes
fix Definition 31 + remark universal associahedra

--- 2024-02-27 draft/wigglyhedra.tex
@@
 
+Analogies to cluster algebras and gentle algebras.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{def:bijection2}
-For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef \big( i, j, {]i,j[} \cap \sigma([k]), {]i,j[} \ssm \sigma([k]) \big)$ with
-\[
-i \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i} 
-\;\text{and}\;
-j \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1} \!.
-\]
+For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
+\begin{align*}
+i & \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i}, \\
+j & \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1}, \\
+A & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \subseteq \sigma([k])}, \\
+B & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) = \varnothing}.
+\end{align*}
 \end{definition}
@@
 \item $\dotprod{\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} = 1/2$ if~$i = \bar u \ne \bar v$, $-1/2$ if~$i = \bar v \ne \bar u$, and $0$ otherwise,
-\item $\dotprod{\b{c}(\alpha, T)}{\b{e}_j}| \le 1/2$ for all~$j \in [2n]$.
+\item $|\dotprod{\b{c}(\alpha, T)}{\b{e}_j}| \le 1/2$ for all~$j \in [2n]$.
 \end{itemize}
@@
 \[
-\dotprod{-\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} \ge 2n(\bar v - \bar u) + n > 0.
+\dotprod{-\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} \ge 2n(\bar v - \bar u) - n > 0.
 \]
@@
 \[
-\dotprod{\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} = 1/2 > 0.
+\dotprod{\b{c}(\alpha, T)}{\b{\omega}} = \!\!
+\sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \!\!
+\sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} = \frac{2k}{2}-\frac{2k-1}{2} = 1/2 > 0.
 \]
@@
 
+\begin{remark}
+In their work on polytopal realizations of $\b{g}$-vector fans of finite type cluster algebras~\cite{HohlwegPilaudStella}, C.~Hohlweg, V.~Pilaud and S.~Stella already constructed a \defn{universal associahedron}~$\polytope{U}_n$ which somehow contains all Cambrian fans (actually all $\b{g}$-vector fans from any initial cluster seed).
+More precisely, the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$  appears as a section of the normal fan of the universal associahedron~$\polytope{U}_n$, which is a $(n^2+n-4)/2$-dimensional polytope.
+In contrast, \cref{prop:CambrianFan} states that the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$ appears as a link of the normal fan of the wigglyhedron~$\wigglyhedron_n$, which is a $(2n-1)$-dimensional polytope.
+There seem to be no connection between these two universal polytopes.
+However, this certainly raises the question to construct analogues of the wigglyhedron for all finite Coxeter groups.
+\end{remark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-02-28 draft/wigglyhedra.tex
Added proof of well-definedness of bijections.

@@
 \begin{proof}
-%We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
-\vincent{todo}
+  % We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
+  We break the proof into several steps.
+  \subsection*{\(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).}
+  Let \(\sigma = \Phi(T)\), and for any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
+  Suppose that \(2j-1\) appears before \(2j\) in \(\sigma\) for some fixed \(j\).
+  This means that the pseudotriangle \(t_j\) has its unlabelled corner to the left of its labelled corners.
+  In other words, its hinge opens to the right (see, e.g., the triangle labelled by the \(2\)nd hinge in~\cref{fig:bijection}).
+
+  Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
+  This label belongs to some pseudotriangle \(t_h\), such that \(j\) is either a labelled or an unlabelled corner of \(t_h\).
+  Moreover, the corner angle of \(t_h\) is sandwiched within the convex angle at \(j\) formed by \(t_j\).
+  If \(j\) is an unlabelled corner of \(t_h\), then \(t_h\) also opens to the right at \(h\).
+  If \(j\) is a labelled corner of \(t_h\), then \(t_h\) opens to the left.
+  In both cases, it is clear that \(h > j\), and hence \(i > 2j-1\).
+  In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i > 2j-1\).
+
+  The other case (when \(2j\) appears before \(2j-1\) in \(\sigma\)) is similar.
+
+  \subsection*{\(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).}
+  By~\cref{prop:wigglyPseudotriangulations}, it suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
+  \(\alpha(\sigma,k)\) and \(\alpha(\sigma,k')\) are distinct and compatible.
+
+  To check distinctness, suppose that \(\alpha(\sigma,k) = (i,j,A,B)\) equals \((\sigma,k') = (i',j',A',B')\) for some \(k \leq k'\).
+  Note that \(i = i',j = j'\) are both in \(\sigma([k])\), and also \(\sigma([k]) \subseteq \sigma([k'])\).
+  For any \(l \in \sigma([k']) \ssm \sigma([k])\), the conditions on wiggly permutations imply that
+  \[i < \left\lceil \frac{l}{2} \right\rceil < j.\]
+  Furthermore, from the definitions of \(i\) and \(j\), we see that for any \(l \in \sigma([k']) \ssm \sigma([k])\), we have
+  \[2 \left\lceil \frac{l}{2} \right\rceil \in \sigma([k']) \text{ if and only if } 2\left\lceil \frac{l}{2} \right\rceil - 1 \in \sigma([k']).\]
+  Now it follows from the fact that \(A' = A\) that there is no element \(l \in \sigma([k']) \setminus \sigma([k])\); that is, \(k = k'\).
+
+  We check compatibility.
+  Suppose that for some \(k < k'\), we have 
+  \[\alpha(\sigma,k) = (i,j,A,B) \text{ and }\alpha(\sigma,k') = (i',j',A',B').\]
+  It is clear from the definition that \(i \neq j'\), as the sets over which we take the max and min to define \(i\) and \(j'\) respectively are disjoint.
+  Similarly, we have \(j \neq i'\).
+  Therefore the two arcs are pointed.
+  To check that the arcs are non-crossing, we must show that the sets
+  \[(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \text{ and } (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})\]
+  are both empty.
+  We check the first; the second is similar.
+  Recall that \(\sigma([k]) \subset \sigma([k'])\).
+  For any \(l \in B'\), we have \(2l, 2l-1 \notin \sigma([k'])\), and hence \(2l, 2l-1 \notin \sigma([k])\), which means that \(l \notin A\).
+  So \(A \cap B' = \emptyset\).
+  Since \(2i - 1, 2j \in \sigma([k]) \subset \sigma([k'])\), we see that \(\{i,j\} \cap B' = \emptyset\).
+  Since \(2i', 2j'-1 \notin \sigma([k'])\) hence not in \(\sigma([k])\), we see that \(A \cap \{i',j'\} = \emptyset\).
+  \subsection*{The maps \(\Phi\) and \(\Psi\) are inverse bijections that induce the directed graph isomorphism claimed in the statement.}
+  \asilata{Todo.}
+\item
+
 \end{proof}

### 2024-02-29 draft/wigglyhedra.tex
unsatisfying proof of dual bases

--- 2024-02-28 draft/wigglyhedra.tex
@@
 \item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
-\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
+\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
+\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
 \item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
@@
 \begin{proof}
-We first prove that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
-\vincent{todo}
-
+We claim that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
 Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
@@
 We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
+
+The proof of the claim is a boring case analysis.
+Let~$i < j$ be the endpoints of~$\alpha$, and let~$u$ and~$v$ the labels (in the corner labeling of~$T$) incident to~$\alpha'$ and respectively below and above~$\alpha'$, and~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
+By symmetry, we can assume that~$u < v$ so that~$\bar u \le \bar v$.
+Let us write~$\hat{\b{g}}(\alpha) \eqdef (g_1, \dots, g_{2n})$ and~$\b{c}(\alpha', T) \eqdef (c_1, \dots, c_{2n})$, and define~$gc_k \eqdef g_{2k-1}c_{2k-1} + g_{2k}c_{2k}$.
+Hence, we have~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \sum_{k \in [n]} gc_k = \sum_{k \in \{i, j, \bar u, \bar v\}} gc_k$.
+Indeed, the last equality holds since~$g_{2k-1} = g_{2k}$ for all~$k \in [n] \ssm \{i,j\}$ and~$c_{2k-1} = -c_{2k}$ for all~$k \in [n] \ssm \{\bar u, \bar v\}$.
+
+Assume first that~$\alpha = \alpha'$.
+Hence, we have~$i \le \bar u \le \bar v \le j$.
+We distinguish two cases:
+\begin{enumerate}
+\item If~$i = \bar u = \bar v < j$, then~$u = 2i-1$ and~$v = 2i$, so that~$gc_i = 1 \cdot 1/2 + (-1) \cdot (-1/2) = 1$ and~$gc_j = 0$, thus~$\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = gc_i + gc_j = 1$.
+\item Otherwise, $i \le \bar u < \bar v \le j$.
+If~$i = \bar u$, we have~$u = 2i-1$ so that~$gc_{\bar u} = 1 \cdot 1/2 + (-1) \cdot 0 = 1/2$.
+If~$i < \bar u$, we have~$gc_i = 0$ (since~$c_{2i-1} = c_{2i} = 0$) and~$gc_{\bar u} = 1/2$ (since~$g_{2\bar u-1} = g_{2\bar u} = 1$ and~${c_{2\bar u-1} + c_{2\bar u} = 1/2}$).
+In both cases, we get that~$\sum_{k \in \{i, \bar u\}} gc_k = 1/2$.
+By symmetric arguments, we conclude~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = \sum_{k \in \{i, \bar u\}} gc_k + \sum_{k \in \{j, \bar v\}} gc_k = 1/2 + 1/2 = 1}$.
+\end{enumerate}
+
+Assume now that~$\alpha \ne \alpha'$.
+\vincent{I am really unhappy with this proof. I can do the case analysis, but it is really unsatisfactory. I am waiting to see if I find another idea...}
+We distinguish ten cases:
+\begin{enumerate}
+\item If~$j < \bar u$, then~$c_{2i-1} = c_{2i} = c_{2j-1} = c_{2j} = 0$ and~$g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v} = 0$.
+\item If~$j = \bar u < \bar v$, then~$c_{2i-1} \! = \! c_{2i} \! = \! 0$, $g_{2j-1} \! = \! -g_{2j}$ and~$c_{2j-1} \! = \! c_{2j}$,  and~${g_{2 \bar v-1} \! = \! g_{2 \bar v} = 0}$.
+\item If~$i < \bar u < j < \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2 \bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$, and~$g_{2 \bar v-1} = g_{2 \bar v} = 0$.
+\item If~$i < \bar u < j = \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2\bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$.
+\item If~$i < \bar u \le \bar v < j$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v}$ and~$c_{2 \bar u-1} + c_{2\bar u} + c_{2j-1} + c_{2j} = 0$, and~$c_{2j-1} = c_{2j} = 0$.
+\item If~$i = \bar u < j < \bar v$, then \dots
+\item If~$i = \bar u < j = \bar v$, then \dots
+\item If~$i = \bar u < \bar v < j$, then \dots
+\item If~$\bar u < i < j < \bar v$, then \dots
+\item If~$\bar u < i < j = \bar v$, then \dots
+\item If~$\bar u < i < \bar v < j$, then \dots
+\item If~$\bar u < i = \bar v < j$, then \dots
+\item If~$\bar u < \bar v < i < j$, then \dots
+\end{enumerate}
+(Note that~$\bar u = \bar v$ implies that~$\{i,j\} \notin \bar u$.)
+In all cases, we check that~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = 0}$.
 \end{proof}
@@
 By \cref{prop:characterizationPolytopalFan,lem:linearDependences,lem:wallCrossingInequalities}, the wiggly fan is indeed the normal fan of the polytope~$\wigglyhedron_n$ defined by the inequalities~$\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$.
-For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\beta \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\beta, T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{prop:dualBases}.
+For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\alpha' \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{prop:dualBases}.
 Hence, $\b{p}(T)$ is indeed the point of~$\wigglyhedron_n$ corresponding to~$T$, which is located at the intersection of the hyperplanes~$\dotprod{\b{g}(\alpha)}{\b{x}} = \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$ in~$T$.

### 2024-02-29 programmation/wigglyPseudotriangulations.py

@@ -85,6 +85,12 @@ def tuplize(arc):
     """
     return (arc[0], arc[1], tuple(sorted(arc[2])), tuple(sorted(arc[3])))
 
+def are_non_pointed(arc1, arc2):
+    r"""
+    Check if two arcs arc1 and arc2 are non pointed.
+    """
+    return arc1[0] == arc2[1] or arc1[1] == arc2[0]
+
 def are_crossing(arc1, arc2):
     r"""
     Check if two arcs arc1 and arc2 are crossing.
@@ -99,9 +105,7 @@ def compatible(arc1, arc2):
     r"""
     Check if two arcs arc1 and arc2 are compatible.
     """
-    (i1, j1, A1, B1) = arc1
-    (i2, j2, A2, B2) = arc2
-    return arc1 != arc2 and i1 != j2 and j1 != i2 and not are_crossing(arc1, arc2)
+    return arc1 != arc2 and not are_non_pointed(arc1, arc2) and not are_crossing(arc1, arc2)
 
 def incompatibility_degree(arc1, arc2):
     r"""
@@ -671,9 +675,10 @@ def multi_wiggly_elements(n, k):
             if lt(arc, X[1]):
                 Y = (copy(X[0]), arc, copy(X[2]))
                 Y[0].append(arc)
-                for arcb in X[0]:
-                    if not compatible(arc, arcb):
-                        Y[2].add_edge(arc, arcb)
+                if not any(are_non_pointed(arc, arcb) for arcb in X[0]):
+                    for arcb in X[0]:
+                        if not compatible(arc, arcb):
+                            Y[2].add_edge(arc, arcb)
                 if Y[2].clique_number() < k+1:
                     res.append(Y)
         return res
@@ -682,4 +687,4 @@ def multi_wiggly_elements(n, k):
 
 @cached_function
 def multi_wiggly_complex(n, k):
-    return SimplicialComplex([x[0] for x in multiWigglyElements(n, k)])
+    return SimplicialComplex([x[0] for x in multi_wiggly_elements(n, k)])

### 2024-03-04 draft/wigglyhedra.tex
Added some more words in the bijection proof.

@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:wigglyCoverRelation}
 Consider an ascent~$j$ of a wiggly permutation~$\sigma$ of~$[2n]$.
@@
   We break the proof into several steps.
-  \subsection*{\(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).}
+
+  First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
   Let \(\sigma = \Phi(T)\), and for any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
@@
   In other words, its hinge opens to the right (see, e.g., the triangle labelled by the \(2\)nd hinge in~\cref{fig:bijection}).
-
   Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
@@
   In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i > 2j-1\).
-
-  The other case (when \(2j\) appears before \(2j-1\) in \(\sigma\)) is similar.
-
-  \subsection*{\(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).}
+  The other case (in which \(2j\) appears before \(2j-1\) in \(\sigma\)) is similar.
+
+  Next, we show that \(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).
   By~\cref{prop:wigglyPseudotriangulations}, it suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
@@
   Since \(2i', 2j'-1 \notin \sigma([k'])\) hence not in \(\sigma([k])\), we see that \(A \cap \{i',j'\} = \emptyset\).
-  \subsection*{The maps \(\Phi\) and \(\Psi\) are inverse bijections that induce the directed graph isomorphism claimed in the statement.}
-  \asilata{Todo.}
+
+  Finally, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
+  Let \(\sigma\) be a wiggly permutation, so that \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
+  The following are easy to check for any \(k \in [n]\).
+  Let \(m = \lceil \sigma(k)/2 \rceil\).
+  \begin{enumerate}
+  \item If both \(2m\) and \(2m -1\) appear in \(\sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) passes above the point \(m\).
+  \item If \(\sigma(k) = 2m\) and \(2m - 1 \notin \sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) has its right endpoint at \(m\).
+  \item If \(\sigma(k) = 2m - 1\) and \(2m \notin \sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) has its left endpoint at \(m\).
+  \end{enumerate}
+  It follows from the above that in the wiggly pseudotriangulation \(\Psi(\sigma)\), the arc \(\alpha(\sigma,k)\) is precisely the arc lying immediately above the angle \(\sigma(k)\), where we regard \(\alpha(\sigma,2n)\) to be the top irrelevant arc.
+  In other words, we have \(\Phi(\Psi(\sigma)) = \sigma\).
+
+  Similarly, let \(T\) be a wiggly pseudotriangulation so that \(\sigma = \Phi(T)\) is a wiggly permutation.
+  One can check that for any angle in \(T\), namely any \(l \in [2n]\), the arc immediately above \(l\) is precisely the one constructed as \(\alpha(\sigma,\sigma^{-1}(l))\).
+  This shows that \(\Psi(\Phi(T)) = T\).
+
+  Finally, one can check using~\cref{lem:wigglyCoverRelation} that increasing flips in triangulations correspond precisely to edges in the wiggly lattice.
+  \asilata{Todo: more details here?}
 \item

### 2024-03-18 draft/wigglyhedra.tex
Added small question (typo fix?)

@@
 \item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
+\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,\asilata{In this item, should ``or if \(\bar u\) and\dots'' be ``or if \(\bar v\) and \dots''?}
 \item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,

### 2024-04-08 draft/wigglyhedra.tex
Added some categorical context. Needs to be cleaned up.

@@
 \DeclareMathOperator{\Vol}{Vol} % (mixed) volume
+\DeclareMathOperator{\Hom}{Hom} % hom-spaces
 
@@
 Analogies to cluster algebras and gentle algebras.
+
+\subsection{Curves in a disk and a triangulated category associated to a quiver}
+There is an algebraic/categorical model of curves in a disk with marked points, due to Khovanov and Seidel~\cite{kho.sei:02}, which we describe in this section.
+This model identifies curves in a disk with objects in a certain triangulated category, and the correspondence has several useful features.
+For instance, the number of intersections between two curves is the number of morphisms in the category between the corresponding objects.
+Furthermore, the Artin braid group is the fundamental group of the unordered configuration space of points in a disk, and thus acts on the set of curves in the disk.
+The associated triangulated category also carries an action by the Artin braid group, and the Khovanov--Seidel map from curves to objects is equivariant with respect to this group action.
+
+We now give a concise account of this correspondence.
+We omit the details that do not play a starring role in the remainder of this paper, and direct the reader to the original references.
+Recall that the \emph{type \(A_m\)} Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connecting successive pairs of points as shown in~\cref{fig:a5-dynkin}.
+\begin{figure}[h]
+  \centering
+  \begin{tikzcd}
+    \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet
+  \end{tikzcd}
+  \caption{The type \(A_5\) Dynkin graph.}
+  \label{fig:a5-dynkin}
+\end{figure}
+Given an undirected graph as above, we can construct its \emph{doubled quiver}, which is a directed graph in which every undirected edge is replaced by a pair of oppositely oriented arrows, as shown in~\cref{fig:a5-doubled}.
+\begin{figure}[h]
+  \centering
+  \begin{tikzcd}
+    \bullet \arrow[bend left]{r}& \bullet \arrow[bend left]{r} \arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{l}
+  \end{tikzcd}
+  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
+  \label{fig:a5-doubled}
+\end{figure}
+The \emph{zig-zag algebra} of the doubled quiver of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).
+
+Then there is a triangulated category \(\mathcal{C}_m\) associated to the Dynkin graph of type \(A_m\), constructed as a differential graded version of the homotopy category of projective modules over the zig-zag algebra of the doubled quiver of type \(A_m\).
+The precise definition of this category appears in, e.g.,~\cite{sei.tho:01,tho:06} for type \(A_m\) and in~\cite{bap.deo.lic:20} for general undirected graphs.
+
+The category \(\mathcal{C}_m\) is linear over a fixed field \(k\), triangulated, and 2-Calabi--Yau.
+That is, for every pair of objects \(X\) and \(Y\) in \(\mathcal{C}_m\), we have
+\[\Hom_{\mathcal{C}_m}(X,Y[d]) \cong \Hom_{\mathcal{C}_m}(Y, X[2-d]),\]
+where \([1]\) denotes the triangulated shift.
+\asilata{Update these definitions to the bigraded version, not the 2-CY version.}
+Furthermore, \(\mathcal{C}_m\) is strongly generated by \(m\) objects denoted by \(P_1, \ldots, P_m\), which correspond to indecomposable projective modules over the zig-zag algebra.
+These objects satisfy:
+\begin{itemize}
+\item \(\Hom(P_i,P_i[d]) = 0\) if \(d \neq 0, 2\);
+\item \(\Hom(P_i,P_i[d]) = k\) if \(d = 0, 2\);
+\item \(\Hom(P_i, P_{i\pm1}[d]) = 0\) if \(d \neq 1\);
+\item \(\Hom(P_i, P_{i\pm1}[1]) = k\), and
+\item \(\Hom(P_i, P_j[d]) = 0 \) otherwise.
+\end{itemize}
+
+Now consider \(n+2\) marked points on a disk, arranged on a straight horizontal line, and labelled \(0,1, \ldots, n+1\).
+We will consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
+For convenience, we also refer to such an isotopy class as a \emph{curve}.
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+
+In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
+It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms between the associated objects.
+In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
+In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects (\cite[Lemma 4.11]{kho.sei:02}).
+\asilata{Now figure out what to say about \(t\)-structures, namely that wiggly arcs are exactly those whose associated complexes lie in the heart of the standard \(t\)-structure.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-04-17 draft/wigglyhedra.tex
change definition c-vectors

@@
 \label{def:cvectors}
-Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
-Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
+The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$ is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha)} = 1$ and~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha')} = 0$ for all interior wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
+In other words, $\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ is the dual basis of~$\b{g}(T)$ in~$\HH_{2n}$.
+\end{definition}
+
+\begin{remark}
+The $\b{c}$-vector~$\b{c}(\alpha, T)$ can also be described combinatorially.
+Namely, label the the corners of~$T$ as in \cref{def:bijection1}, and denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
+Then the $\b{c}$-vector~$\b{c}(\alpha, T)$ has coordinates
 \begin{itemize}
 \item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,\asilata{In this item, should ``or if \(\bar u\) and\dots'' be ``or if \(\bar v\) and \dots''?}
+\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
 \item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
@@
 \end{itemize}
-Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
-\end{definition}
-
-\begin{proposition}
-\label{prop:dualBases}
-For any wiggly pseudotriangulation~$T$, the sets~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases~of~$\HH_{2n}$.
-\end{proposition}
-
-\begin{proof}
-We claim that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
-Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
-Hence, we obtain that~$\dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \dotprod{\pi(\hat{\b{g}}(\alpha))}{\b{c}(\alpha', T)} = \dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$.
-We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
-
-The proof of the claim is a boring case analysis.
-Let~$i < j$ be the endpoints of~$\alpha$, and let~$u$ and~$v$ the labels (in the corner labeling of~$T$) incident to~$\alpha'$ and respectively below and above~$\alpha'$, and~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-By symmetry, we can assume that~$u < v$ so that~$\bar u \le \bar v$.
-Let us write~$\hat{\b{g}}(\alpha) \eqdef (g_1, \dots, g_{2n})$ and~$\b{c}(\alpha', T) \eqdef (c_1, \dots, c_{2n})$, and define~$gc_k \eqdef g_{2k-1}c_{2k-1} + g_{2k}c_{2k}$.
-Hence, we have~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \sum_{k \in [n]} gc_k = \sum_{k \in \{i, j, \bar u, \bar v\}} gc_k$.
-Indeed, the last equality holds since~$g_{2k-1} = g_{2k}$ for all~$k \in [n] \ssm \{i,j\}$ and~$c_{2k-1} = -c_{2k}$ for all~$k \in [n] \ssm \{\bar u, \bar v\}$.
-
-Assume first that~$\alpha = \alpha'$.
-Hence, we have~$i \le \bar u \le \bar v \le j$.
-We distinguish two cases:
-\begin{enumerate}
-\item If~$i = \bar u = \bar v < j$, then~$u = 2i-1$ and~$v = 2i$, so that~$gc_i = 1 \cdot 1/2 + (-1) \cdot (-1/2) = 1$ and~$gc_j = 0$, thus~$\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = gc_i + gc_j = 1$.
-\item Otherwise, $i \le \bar u < \bar v \le j$.
-If~$i = \bar u$, we have~$u = 2i-1$ so that~$gc_{\bar u} = 1 \cdot 1/2 + (-1) \cdot 0 = 1/2$.
-If~$i < \bar u$, we have~$gc_i = 0$ (since~$c_{2i-1} = c_{2i} = 0$) and~$gc_{\bar u} = 1/2$ (since~$g_{2\bar u-1} = g_{2\bar u} = 1$ and~${c_{2\bar u-1} + c_{2\bar u} = 1/2}$).
-In both cases, we get that~$\sum_{k \in \{i, \bar u\}} gc_k = 1/2$.
-By symmetric arguments, we conclude~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = \sum_{k \in \{i, \bar u\}} gc_k + \sum_{k \in \{j, \bar v\}} gc_k = 1/2 + 1/2 = 1}$.
-\end{enumerate}
-
-Assume now that~$\alpha \ne \alpha'$.
-\vincent{I am really unhappy with this proof. I can do the case analysis, but it is really unsatisfactory. I am waiting to see if I find another idea...}
-We distinguish ten cases:
-\begin{enumerate}
-\item If~$j < \bar u$, then~$c_{2i-1} = c_{2i} = c_{2j-1} = c_{2j} = 0$ and~$g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-\item If~$j = \bar u < \bar v$, then~$c_{2i-1} \! = \! c_{2i} \! = \! 0$, $g_{2j-1} \! = \! -g_{2j}$ and~$c_{2j-1} \! = \! c_{2j}$,  and~${g_{2 \bar v-1} \! = \! g_{2 \bar v} = 0}$.
-\item If~$i < \bar u < j < \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2 \bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$, and~$g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-\item If~$i < \bar u < j = \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2\bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$.
-\item If~$i < \bar u \le \bar v < j$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v}$ and~$c_{2 \bar u-1} + c_{2\bar u} + c_{2j-1} + c_{2j} = 0$, and~$c_{2j-1} = c_{2j} = 0$.
-\item If~$i = \bar u < j < \bar v$, then \dots
-\item If~$i = \bar u < j = \bar v$, then \dots
-\item If~$i = \bar u < \bar v < j$, then \dots
-\item If~$\bar u < i < j < \bar v$, then \dots
-\item If~$\bar u < i < j = \bar v$, then \dots
-\item If~$\bar u < i < \bar v < j$, then \dots
-\item If~$\bar u < i = \bar v < j$, then \dots
-\item If~$\bar u < \bar v < i < j$, then \dots
-\end{enumerate}
-(Note that~$\bar u = \bar v$ implies that~$\{i,j\} \notin \bar u$.)
-In all cases, we check that~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = 0}$.
-\end{proof}
+\end{remark}
+
+%\begin{definition}
+%\label{def:cvectors}
+%Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
+%Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
+%The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
+%\begin{itemize}
+%\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
+%\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
+%\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
+%\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
+%\end{itemize}
+%Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
+%\end{definition}
+%
+%\begin{proposition}
+%\label{prop:dualBases}
+%For any wiggly pseudotriangulation~$T$, the sets~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases~of~$\HH_{2n}$.
+%\end{proposition}
+%
+%\begin{proof}
+%We claim that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
+%Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
+%Hence, we obtain that~$\dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \dotprod{\pi(\hat{\b{g}}(\alpha))}{\b{c}(\alpha', T)} = \dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$.
+%We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
+%
+%The proof of the claim is a boring case analysis.
+%Let~$i < j$ be the endpoints of~$\alpha$, and let~$u$ and~$v$ the labels (in the corner labeling of~$T$) incident to~$\alpha'$ and respectively below and above~$\alpha'$, and~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
+%By symmetry, we can assume that~$u < v$ so that~$\bar u \le \bar v$.
+%Let us write~$\hat{\b{g}}(\alpha) \eqdef (g_1, \dots, g_{2n})$ and~$\b{c}(\alpha', T) \eqdef (c_1, \dots, c_{2n})$, and define~$gc_k \eqdef g_{2k-1}c_{2k-1} + g_{2k}c_{2k}$.
+%Hence, we have~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \sum_{k \in [n]} gc_k = \sum_{k \in \{i, j, \bar u, \bar v\}} gc_k$.
+%Indeed, the last equality holds since~$g_{2k-1} = g_{2k}$ for all~$k \in [n] \ssm \{i,j\}$ and~$c_{2k-1} = -c_{2k}$ for all~$k \in [n] \ssm \{\bar u, \bar v\}$.
+%
+%Assume first that~$\alpha = \alpha'$.
+%Hence, we have~$i \le \bar u \le \bar v \le j$.
+%We distinguish two cases:
+%\begin{enumerate}
+%\item If~$i = \bar u = \bar v < j$, then~$u = 2i-1$ and~$v = 2i$, so that~$gc_i = 1 \cdot 1/2 + (-1) \cdot (-1/2) = 1$ and~$gc_j = 0$, thus~$\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = gc_i + gc_j = 1$.
+%\item Otherwise, $i \le \bar u < \bar v \le j$.
+%If~$i = \bar u$, we have~$u = 2i-1$ so that~$gc_{\bar u} = 1 \cdot 1/2 + (-1) \cdot 0 = 1/2$.
+%If~$i < \bar u$, we have~$gc_i = 0$ (since~$c_{2i-1} = c_{2i} = 0$) and~$gc_{\bar u} = 1/2$ (since~$g_{2\bar u-1} = g_{2\bar u} = 1$ and~${c_{2\bar u-1} + c_{2\bar u} = 1/2}$).
+%In both cases, we get that~$\sum_{k \in \{i, \bar u\}} gc_k = 1/2$.
+%By symmetric arguments, we conclude~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = \sum_{k \in \{i, \bar u\}} gc_k + \sum_{k \in \{j, \bar v\}} gc_k = 1/2 + 1/2 = 1}$.
+%\end{enumerate}
+%
+%Assume now that~$\alpha \ne \alpha'$.
+%\vincent{I am really unhappy with this proof. I can do the case analysis, but it is really unsatisfactory. I am waiting to see if I find another idea...}
+%We distinguish ten cases:
+%\begin{enumerate}
+%\item If~$j < \bar u$, then~$c_{2i-1} = c_{2i} = c_{2j-1} = c_{2j} = 0$ and~$g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v} = 0$.
+%\item If~$j = \bar u < \bar v$, then~$c_{2i-1} \! = \! c_{2i} \! = \! 0$, $g_{2j-1} \! = \! -g_{2j}$ and~$c_{2j-1} \! = \! c_{2j}$,  and~${g_{2 \bar v-1} \! = \! g_{2 \bar v} = 0}$.
+%\item If~$i < \bar u < j < \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2 \bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$, and~$g_{2 \bar v-1} = g_{2 \bar v} = 0$.
+%\item If~$i < \bar u < j = \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2\bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$.
+%\item If~$i < \bar u \le \bar v < j$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v}$ and~$c_{2 \bar u-1} + c_{2\bar u} + c_{2j-1} + c_{2j} = 0$, and~$c_{2j-1} = c_{2j} = 0$.
+%\item If~$i = \bar u < j < \bar v$, then \dots
+%\item If~$i = \bar u < j = \bar v$, then \dots
+%\item If~$i = \bar u < \bar v < j$, then \dots
+%\item If~$\bar u < i < j < \bar v$, then \dots
+%\item If~$\bar u < i < j = \bar v$, then \dots
+%\item If~$\bar u < i < \bar v < j$, then \dots
+%\item If~$\bar u < i = \bar v < j$, then \dots
+%\item If~$\bar u < \bar v < i < j$, then \dots
+%\end{enumerate}
+%(Note that~$\bar u = \bar v$ implies that~$\{i,j\} \notin \bar u$.)
+%In all cases, we check that~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = 0}$.
+%\end{proof}
 
@@
 By \cref{prop:characterizationPolytopalFan,lem:linearDependences,lem:wallCrossingInequalities}, the wiggly fan is indeed the normal fan of the polytope~$\wigglyhedron_n$ defined by the inequalities~$\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$.
-For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\alpha' \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{prop:dualBases}.
+For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\alpha' \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{def:cvectors}.
 Hence, $\b{p}(T)$ is indeed the point of~$\wigglyhedron_n$ corresponding to~$T$, which is located at the intersection of the hyperplanes~$\dotprod{\b{g}(\alpha)}{\b{x}} = \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$ in~$T$.

### 2024-05-14 draft/wigglyhedra.tex
add acknowledgements
Added grant.

--- 2024-03-18 draft/wigglyhedra.tex
@@
 
-\thanks{VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
+\thanks{AB was partially supported by the Australin Research Council DECRA grant DE240100447. 
+  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
 

### 2024-05-14 draft/wigglyhedra.tex

--- 2024-04-17 draft/wigglyhedra.tex
@@
 
+\section*{Acknowledgements}
+
+This work started during the \emph{Winterbraids XIII: School on low dimensional topology, braid groups and interactions}.
+We are grateful to the organizers Bérénice Delcroix-Oger, Peter Feller, Vincent Florens, Hoel Queffelec for this fruitful event.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\clearpage

### 2024-05-24 draft/wigglyhedra.tex
minor changes

--- 2024-04-17 draft/wigglyhedra.tex
@@
 
+\vincent{Asilata has an alternative description of the flip...}
+
 We are now ready to consider the wiggly flip graph and the wiggly complex.
@@
 
+\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}
+
 \begin{example}

### 2024-05-28 draft/wigglyhedra.tex
Updated figure/intro writeup.

--- 2024-05-14 draft/wigglyhedra.tex
@@
 \subsection{Curves in a disk and a triangulated category associated to a quiver}
-There is an algebraic/categorical model of curves in a disk with marked points, due to Khovanov and Seidel~\cite{kho.sei:02}, which we describe in this section.
-This model identifies curves in a disk with objects in a certain triangulated category, and the correspondence has several useful features.
-For instance, the number of intersections between two curves is the number of morphisms in the category between the corresponding objects.
-Furthermore, the Artin braid group is the fundamental group of the unordered configuration space of points in a disk, and thus acts on the set of curves in the disk.
-The associated triangulated category also carries an action by the Artin braid group, and the Khovanov--Seidel map from curves to objects is equivariant with respect to this group action.
-
-We now give a concise account of this correspondence.
-We omit the details that do not play a starring role in the remainder of this paper, and direct the reader to the original references.
-Recall that the \emph{type \(A_m\)} Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connecting successive pairs of points as shown in~\cref{fig:a5-dynkin}.
+Curves up to isotopy in a disk with marked points constitute a geometric model of certain objects in a triangulated category.
+This correspondence, due to Khovanov--Seidel~\cite{kho.sei:02}, and will enable us to build categorical interpretations of the combinatorial results obtained in this paper.
+The aim of this section is to give a concise account of this correspondence and some of its useful features; we refer the reader to~\cite{kho.sei:02} for details.
+
+The triangulated category of interest will be the category \(\mathcal{C}_m = D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
+The algebra \(A_m\) is defined as the quotient of the path algebra of the quiver with \(m+1\) vertices depicted in~\cref{fig:am-quiver}.
+\begin{figure}[h]
+  \centering
+  \begin{tikzcd}
+    0 \arrow[bend left]{r}& 1 \arrow[bend left]{r} \arrow[bend left]{l}& 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
+  \end{tikzcd}
+  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
+  \label{fig:am-quiver}
+\end{figure}
+
+Recall that the type \(A_m\) Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connects successive pairs of points as shown in~\cref{fig:a5-dynkin}.
 \begin{figure}[h]
@@
 \end{figure}
-The \emph{zig-zag algebra} of the doubled quiver of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).
-
-Then there is a triangulated category \(\mathcal{C}_m\) associated to the Dynkin graph of type \(A_m\), constructed as a differential graded version of the homotopy category of projective modules over the zig-zag algebra of the doubled quiver of type \(A_m\).
+The \emph{zig-zag algebra} of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).
+
+Let \(Z_m\) be the zig-zag algebra of the type \(A_m\) graph.
+Let \(\mathcal{C}_m\) be \(K^b(Z-\text{proj})\), which is the bounded homotopy category of graded projective modules over \(Z_m\)
+The category \(\mathcal{C}_m\) is triangulated.
 The precise definition of this category appears in, e.g.,~\cite{sei.tho:01,tho:06} for type \(A_m\) and in~\cite{bap.deo.lic:20} for general undirected graphs.

### 2024-05-28 draft/wigglyhedra.tex
Added reference and some more writing about KS complexes.

@@
 
-The triangulated category of interest will be the category \(\mathcal{C}_m = D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-The algebra \(A_m\) is defined as the quotient of the path algebra of the quiver with \(m+1\) vertices depicted in~\cref{fig:am-quiver}.
+The category of interest is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
+That is, a subcategory of the bounded derived category of (finitely generated) \(A_m\)-modules.
+The algebra \(A_m\), called the \emph{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
 \begin{figure}[h]
@@
   \begin{tikzcd}
-    0 \arrow[bend left]{r}& 1 \arrow[bend left]{r} \arrow[bend left]{l}& 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
+    1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
   \end{tikzcd}
-  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
+  \caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
   \label{fig:am-quiver}
 \end{figure}
-
-Recall that the type \(A_m\) Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connects successive pairs of points as shown in~\cref{fig:a5-dynkin}.
-\begin{figure}[h]
-  \centering
-  \begin{tikzcd}
-    \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet
-  \end{tikzcd}
-  \caption{The type \(A_5\) Dynkin graph.}
-  \label{fig:a5-dynkin}
-\end{figure}
-Given an undirected graph as above, we can construct its \emph{doubled quiver}, which is a directed graph in which every undirected edge is replaced by a pair of oppositely oriented arrows, as shown in~\cref{fig:a5-doubled}.
-\begin{figure}[h]
-  \centering
-  \begin{tikzcd}
-    \bullet \arrow[bend left]{r}& \bullet \arrow[bend left]{r} \arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{l}
-  \end{tikzcd}
-  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
-  \label{fig:a5-doubled}
-\end{figure}
-The \emph{zig-zag algebra} of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).
-
-Let \(Z_m\) be the zig-zag algebra of the type \(A_m\) graph.
-Let \(\mathcal{C}_m\) be \(K^b(Z-\text{proj})\), which is the bounded homotopy category of graded projective modules over \(Z_m\)
-The category \(\mathcal{C}_m\) is triangulated.
-The precise definition of this category appears in, e.g.,~\cite{sei.tho:01,tho:06} for type \(A_m\) and in~\cite{bap.deo.lic:20} for general undirected graphs.
-
-The category \(\mathcal{C}_m\) is linear over a fixed field \(k\), triangulated, and 2-Calabi--Yau.
-That is, for every pair of objects \(X\) and \(Y\) in \(\mathcal{C}_m\), we have
-\[\Hom_{\mathcal{C}_m}(X,Y[d]) \cong \Hom_{\mathcal{C}_m}(Y, X[2-d]),\]
-where \([1]\) denotes the triangulated shift.
-\asilata{Update these definitions to the bigraded version, not the 2-CY version.}
-Furthermore, \(\mathcal{C}_m\) is strongly generated by \(m\) objects denoted by \(P_1, \ldots, P_m\), which correspond to indecomposable projective modules over the zig-zag algebra.
-These objects satisfy:
-\begin{itemize}
-\item \(\Hom(P_i,P_i[d]) = 0\) if \(d \neq 0, 2\);
-\item \(\Hom(P_i,P_i[d]) = k\) if \(d = 0, 2\);
-\item \(\Hom(P_i, P_{i\pm1}[d]) = 0\) if \(d \neq 1\);
-\item \(\Hom(P_i, P_{i\pm1}[1]) = k\), and
-\item \(\Hom(P_i, P_j[d]) = 0 \) otherwise.
-\end{itemize}
-
+Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
+Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i|j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
+A longer path, which is a composition of arrows, will be denoted by \((i_1|i_2|\cdots|i_n)\).
+
+The zigzag algebra \(A_m\) is the quotient of \(kQ_m\) by the following relations:
+\begin{itemize}
+\item set \((i|j|l) = 0\) whenever \(i \neq l\);
+\item set \((i|j|i) = (i|l|i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
+\end{itemize}
+See~\cite[Section 3]{hue.kho:01} for further details, and~\cite[Remark 6.6]{bap.deo.lic:20} for a more detailed discussion.
+Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
+For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
+Set \(\mathcal{C}_m\) to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion).
+
+The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
+For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{i,j}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of homological degree \(i\) and internal degree \(j\).
+In other words, we have
+\[\Hom^{i,j}(X,Y) = \Hom(X,Y\langle i \rangle[j]).\]
+Furthermore, for any integers \(a\) and \(b\), we have
+\[\Hom^{i,j}(X\langle a \rangle[b], Y\langle a \rangle[b]) = \Hom^{i,j}(X,Y).\]
+
+\begin{remark}\label{rem:generating-morphisms}
+  The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
+  \begin{itemize}
+  \item \(\Hom^{a,b}(P_i,P_i) = 0\) if \(b \neq 0\) and \(a \neq 0, 2\);
+  \item \(\Hom^{a,0}(P_i,P_i) = k\) if \(a = 0, 2\);
+  \item \(\Hom^{a,b}(P_i, P_{i\pm1}) = 0\) if \(b \neq 0\) and \(a \neq 1\);
+  \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
+  \item \(\Hom^{a,b}(P_i, P_j) = 0 \) otherwise.
+  \end{itemize}
+\end{remark}
+
+The category \(\mathcal{C}_m\) has a standard bounded \(t\)-structure, whose heart consists of the \emph{linear complexes}.
+\asilata{Say more about linear complexes.}
+
+\subsection{The Khovanov--Seidel curve model}
 Now consider \(n+2\) marked points on a disk, arranged on a straight horizontal line, and labelled \(0,1, \ldots, n+1\).
-We will consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
+We consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
 For convenience, we also refer to such an isotopy class as a \emph{curve}.
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading\asilata{Should this say homological?} shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
 
 In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
-It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms between the associated objects.
+It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms\asilata{Discuss (or choose to ignore) grading.} between the associated objects.
 In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
 In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects (\cite[Lemma 4.11]{kho.sei:02}).
+
+\begin{lemma}
+Every wiggly arc corresponds to an object in the heart of the standard \(t\)-structure.  
+\end{lemma}
+\begin{proof}
+  The procedure to build up the complex of projective modules from a curve explicitly describes the differentials.
+  Each component of these differentials is a map from a shift of \(P_i\) to a shift of \(P_j\).
+  It can be seen from~\cref{rem:generating-morphisms} that any component that maps from \(P_i\) to \(P_j\) for \(i \neq j\) keeps the complex linear; it is only when we have a looping map from \(P_i\) to \(P_i\langle 2 \rangle\) that we move out of the standard heart.
   \asilata{Now figure out what to say about \(t\)-structures, namely that wiggly arcs are exactly those whose associated complexes lie in the heart of the standard \(t\)-structure.}
+\end{proof}
 
@@
 \end{document}
+
+%%% Local variables:
+%%% TeX-command-extra-options: "-pvc"
+%%% End:

### 2024-05-31 draft/wigglyhedra.tex
Moved categorical section; started writing some propositions to prove.

@@
 
-\subsection{Curves in a disk and a triangulated category associated to a quiver}
-Curves up to isotopy in a disk with marked points constitute a geometric model of certain objects in a triangulated category.
-This correspondence, due to Khovanov--Seidel~\cite{kho.sei:02}, and will enable us to build categorical interpretations of the combinatorial results obtained in this paper.
-The aim of this section is to give a concise account of this correspondence and some of its useful features; we refer the reader to~\cite{kho.sei:02} for details.
-
-The category of interest is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-That is, a subcategory of the bounded derived category of (finitely generated) \(A_m\)-modules.
-The algebra \(A_m\), called the \emph{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
-\begin{figure}[h]
-  \centering
-  \begin{tikzcd}
-    1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
-  \end{tikzcd}
-  \caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
-  \label{fig:am-quiver}
-\end{figure}
-Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
-Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i|j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
-A longer path, which is a composition of arrows, will be denoted by \((i_1|i_2|\cdots|i_n)\).
-
-The zigzag algebra \(A_m\) is the quotient of \(kQ_m\) by the following relations:
-\begin{itemize}
-\item set \((i|j|l) = 0\) whenever \(i \neq l\);
-\item set \((i|j|i) = (i|l|i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
-\end{itemize}
-See~\cite[Section 3]{hue.kho:01} for further details, and~\cite[Remark 6.6]{bap.deo.lic:20} for a more detailed discussion.
-Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
-For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-Set \(\mathcal{C}_m\) to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion).
-
-The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
-For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{i,j}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of homological degree \(i\) and internal degree \(j\).
-In other words, we have
-\[\Hom^{i,j}(X,Y) = \Hom(X,Y\langle i \rangle[j]).\]
-Furthermore, for any integers \(a\) and \(b\), we have
-\[\Hom^{i,j}(X\langle a \rangle[b], Y\langle a \rangle[b]) = \Hom^{i,j}(X,Y).\]
-
-\begin{remark}\label{rem:generating-morphisms}
-  The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
-  \begin{itemize}
-  \item \(\Hom^{a,b}(P_i,P_i) = 0\) if \(b \neq 0\) and \(a \neq 0, 2\);
-  \item \(\Hom^{a,0}(P_i,P_i) = k\) if \(a = 0, 2\);
-  \item \(\Hom^{a,b}(P_i, P_{i\pm1}) = 0\) if \(b \neq 0\) and \(a \neq 1\);
-  \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
-  \item \(\Hom^{a,b}(P_i, P_j) = 0 \) otherwise.
-  \end{itemize}
-\end{remark}
-
-The category \(\mathcal{C}_m\) has a standard bounded \(t\)-structure, whose heart consists of the \emph{linear complexes}.
-\asilata{Say more about linear complexes.}
-
-\subsection{The Khovanov--Seidel curve model}
-Now consider \(n+2\) marked points on a disk, arranged on a straight horizontal line, and labelled \(0,1, \ldots, n+1\).
-We consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-For convenience, we also refer to such an isotopy class as a \emph{curve}.
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading\asilata{Should this say homological?} shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
-
-In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
-It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms\asilata{Discuss (or choose to ignore) grading.} between the associated objects.
-In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
-In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects (\cite[Lemma 4.11]{kho.sei:02}).
-
-\begin{lemma}
-Every wiggly arc corresponds to an object in the heart of the standard \(t\)-structure.  
-\end{lemma}
-\begin{proof}
-  The procedure to build up the complex of projective modules from a curve explicitly describes the differentials.
-  Each component of these differentials is a map from a shift of \(P_i\) to a shift of \(P_j\).
-  It can be seen from~\cref{rem:generating-morphisms} that any component that maps from \(P_i\) to \(P_j\) for \(i \neq j\) keeps the complex linear; it is only when we have a looping map from \(P_i\) to \(P_i\langle 2 \rangle\) that we move out of the standard heart.
-  \asilata{Now figure out what to say about \(t\)-structures, namely that wiggly arcs are exactly those whose associated complexes lie in the heart of the standard \(t\)-structure.}
-\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{definition}
+\begin{definition}\label{def:compatible}
 Two wiggly arcs~$(i,j,A,B)$ and~$(i',j',A',B')$ are 
@@
 
+\section{Categorical interpretation of wiggly pseudotriangulations}
+The aim of this section is to explain a categorical interpretation of wiggly arcs.
+We recall results of Khovanov--Seidel~\cite{kho.sei:02} that realise wiggly arcs as objects of a triangulated category, such that intersections between wiggly arcs correspond to morphism in this category.
+We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible}.
+
+% Curves up to isotopy in a disk with marked points constitute a geometric model of certain objects in a triangulated category.
+% This correspondence, due to Khovanov--Seidel~\cite{kho.sei:02}, and will enable us to build categorical interpretations of the combinatorial results obtained in this paper.
+% The aim of this section is to give a concise account of this correspondence and some of its useful features; we refer the reader to~\cite{kho.sei:02} for details.
+
+\subsection{A triangulated category associated to a quiver}
+We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
+That is, a subcategory of the bounded derived category of (finitely generated) \(A_m\)-modules.
+The algebra \(A_m\), called the \emph{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
+\begin{figure}[h]
+  \centering
+  \begin{tikzcd}
+    1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
+  \end{tikzcd}
+  \caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
+  \label{fig:am-quiver}
+\end{figure}
+Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
+Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i|j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
+A longer path, which is a composition of arrows, will be denoted by \((i_1|i_2|\cdots|i_n)\).
+
+\begin{definition}
+  The zigzag algebra \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the following relations:
+  \begin{itemize}
+  \item \((i|j|l) = 0\) whenever \(i \neq l\);
+  \item \((i|j|i) = (i|l|i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
+  \end{itemize}
+\end{definition}
+
+See~\cite[Section 3]{hue.kho:01} for further details on the definition, and~\cite[Remark 6.6]{bap.deo.lic:20} for more discussion.
+Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
+For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
+Set \(\mathcal{C}_m\) to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion on the construction).
+
+The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
+For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{i,j}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of homological degree \(i\) and internal degree \(j\).
+In other words, we have
+\[\Hom^{i,j}(X,Y) = \Hom(X,Y\langle i \rangle[j]).\]
+Furthermore, for any integers \(a\) and \(b\), we have
+\[\Hom^{i,j}(X\langle a \rangle[b], Y\langle a \rangle[b]) = \Hom^{i,j}(X,Y).\]
+
+\begin{remark}\label{rem:generating-morphisms}
+  The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
+  \begin{itemize}
+  \item \(\Hom^{a,b}(P_i,P_i) = 0\) if \(b \neq 0\) and \(a \neq 0, 2\);
+  \item \(\Hom^{a,0}(P_i,P_i) = k\) if \(a = 0, 2\);
+  \item \(\Hom^{a,b}(P_i, P_{i\pm1}) = 0\) if \(b \neq 0\) and \(a \neq 1\);
+  \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
+  \item \(\Hom^{a,b}(P_i, P_j) = 0 \) otherwise.
+  \end{itemize}
+\end{remark}
+
+The category \(\mathcal{C}_m\) has a standard bounded \(t\)-structure, whose heart consists of the \emph{linear complexes}.
+\asilata{Say more about linear complexes.}
+
+\subsection{The Khovanov--Seidel curve model}
+In this section we briefly recall the procedure to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
+In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
+All the results of this section are due to Khovanov and Seidel~\cite{kho.sei:02}.
+
+Consider \(n+2\) points arranged in a straight horizontal line, and labelled \(0,1, \ldots, n+1\) as in~\cref{sec:combinatorics}.
+In addition to the wiggly arcs, consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
+For convenience, we refer to such an isotopy class as an \emph{arc}.
+
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading\asilata{Should this say homological?} shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+
+In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
+It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms\asilata{Discuss (or choose to ignore) grading.} between the associated objects.
+In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
+In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects (\cite[Lemma 4.11]{kho.sei:02}).
+
+\begin{lemma}
+Every wiggly arc corresponds to an object in the heart of the standard \(t\)-structure.  
+\end{lemma}
+\begin{proof}
+  The procedure to build up the complex of projective modules from a curve explicitly describes the differentials.
+  Each component of these differentials is a map from a shift of \(P_i\) to a shift of \(P_j\).
+  It can be seen from~\cref{rem:generating-morphisms} that any component that maps from \(P_i\) to \(P_j\) for \(i \neq j\) keeps the complex linear; it is only when we have a looping map from \(P_i\) to \(P_i\langle 2 \rangle\) that we move out of the standard heart.
+  \asilata{Now figure out what to say about \(t\)-structures, namely that wiggly arcs are exactly those whose associated complexes lie in the heart of the standard \(t\)-structure.}
+\end{proof}
+
+\subsection{Categorical conditions on compatibility of arcs}
+
+\begin{proposition}
+  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
+  Consider its cohomology filtration
+  \[
+    \begin{tikzcd}[column sep=0.3cm]
+      0 = X_0 \arrow{rr} && X_1 \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{k-1} \arrow{rr} \arrow{dl} && X_k = X \arrow{dl}\\
+      & H^1(X) \arrow[dashed]{ul}{+1} && H^2(X) \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X) \arrow[dashed]{ul}{+1}
+    \end{tikzcd}
+  \]
+  Consider the set of objects \(\{H^j(X)\}\) taken without multiplicity, and let \(T\) be corresponding set of wiggly curves.
+  We have the following results.
+  \begin{enumerate}
+  \item 
+    \(T\) is a subset of a wiggly pseudotriangulation.
+  \item \(T\) contains at most one of the two irrelevant arcs.
+  \end{enumerate}
+\end{proposition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section*{Acknowledgements}

### 2024-06-07 draft/wigglyhedra.tex
Updated categorical constraints (lots of todos still).

@@
 \newtheorem{assumption}[theorem]{Assumption}
+\newtheorem{defprop}[theorem]{Definition/Proposition}
 \crefname{notation}{Notation}{Notations}
@@
 \DeclareMathOperator{\Hom}{Hom} % hom-spaces
+\DeclareMathOperator{\Ext}{Ext} % extensions
 
@@
 
-See~\cite[Section 3]{hue.kho:01} for further details on the definition, and~\cite[Remark 6.6]{bap.deo.lic:20} for more discussion.
+\begin{remark}
+  The definition of the zigzag algebra as used here originally appeared in~\cite[Section 3]{hue.kho:01}.
+  This is an ``un-signed'' version of the zigzag algebra.
+  It is technically better to use a ``signed'' version of the zigzag algebra, and the comparison between the two is discussed in~\cite[Remark 6.6]{bap.deo.lic:20}.
+  As the two versions are isomorphic in our example, we ignore this technicality and use the easier definition.
+\end{remark}
+
 Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
 For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-Set \(\mathcal{C}_m\) to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion on the construction).
+Let \(\mathcal{C}_m\) be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion on the construction).
 
 The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
-For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{i,j}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of homological degree \(i\) and internal degree \(j\).
+For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{g,h}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of internal degree \(g\) and homological degree \(h\).
 In other words, we have
-\[\Hom^{i,j}(X,Y) = \Hom(X,Y\langle i \rangle[j]).\]
+\[\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).\]
 Furthermore, for any integers \(a\) and \(b\), we have
-\[\Hom^{i,j}(X\langle a \rangle[b], Y\langle a \rangle[b]) = \Hom^{i,j}(X,Y).\]
+\[\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).\]
 
 \begin{remark}\label{rem:generating-morphisms}
-  The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
-  \begin{itemize}
-  \item \(\Hom^{a,b}(P_i,P_i) = 0\) if \(b \neq 0\) and \(a \neq 0, 2\);
-  \item \(\Hom^{a,0}(P_i,P_i) = k\) if \(a = 0, 2\);
-  \item \(\Hom^{a,b}(P_i, P_{i\pm1}) = 0\) if \(b \neq 0\) and \(a \neq 1\);
+  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
+  \begin{itemize}
+  \item \(\Hom^{g,h}(P_i,P_i) = 0\) if \(g \neq 0, 2\) and \(h \neq 0\);
+  \item \(\Hom^{g,0}(P_i,P_i) = k\) if \(g = 0, 2\);
+  \item \(\Hom^{g,h}(P_i, P_{i\pm1}) = 0\) if \(g \neq 1\) and \(h \neq 0\);
   \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
-  \item \(\Hom^{a,b}(P_i, P_j) = 0 \) otherwise.
-  \end{itemize}
-\end{remark}
-
-The category \(\mathcal{C}_m\) has a standard bounded \(t\)-structure, whose heart consists of the \emph{linear complexes}.
-\asilata{Say more about linear complexes.}
+  \item \(\Hom^{g,h}(P_i, P_j) = 0 \) otherwise.
+  \end{itemize}
+\end{remark}
+
+We now describe the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\).
+It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
+as bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
+More precisely, we can write
+\[P^{\bullet} = \bigoplus M_i\langle g \rangle[h],\]
+where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
+each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
+
+Recall that an object of the form \(M_i[h]\) is placed in homological degree \(-h\);
+since the differential \(d\) raises the homological degree by one, it \emph{lowers} the homological shift by one.
+That is, we have
+\[d \colon M_i\langle g \rangle[h] \to \bigoplus M_{i'}\langle g' \rangle[h-1].\]
+In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
+\begin{definition}\label{def:linear-complex}
+  Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
+  \[P^{\bullet} = \bigoplus M_i\langle g \rangle[h]\]
+  together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet + 1}\).
+  We say that \(P^{\bullet}\) has \emph{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
+  We say that \(P^{\bullet}\) is \emph{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
+
+\end{definition}
+Let \(\mathcal{A}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) that is closed under isomorphism, which contains all the linear complexes.
+\begin{proposition}\label{prop:standard-heart}
+  The category \(\mathcal{A}_m\) is abelian.
+  Furthermore, it is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\), which we call the \emph{standard \(t\)-structure} on \(\mathcal{C}_m\).
+\end{proposition}
+\asilata{Find a reference for this and possibly a cleaner statement.}
+
+Also recall the following statements for future use.
+\begin{defprop}\label{defprop:cohomology}
+  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a bounded \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart \(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
+  For each integer \(i\), we have the \(i\)th truncation functors
+  \[\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i}\]
+  and
+  \[\tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},\]
+  which are left and right adjoint respectively\asilata{Check left vs right.} to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
+  The \(i\)th cohomology functor is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
+  It is equal to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
+\end{defprop}
+In the presence of a bounded \(t\)-structure, every object of \(\mathcal{C}\) has a canonical filtration whose factors are shifts of its cohomology objects.
+\begin{defprop}\label{defprop:cohomology-filtration}
+  Let \(\mathcal{C}\) be any triangulated category, and \(\mathcal{A} \subset \mathcal{C}\) the heart of a bounded \(t\)-structure on \(\mathcal{C}\).
+  Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(l\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^{l}(X)\) are non-zero.
+  \asilata{Find references for cohomology and cohomology filtration.}
+  Then \(X\) has a unique filtration of the form
+  \[
+    \begin{tikzcd}[column sep=0.1cm]
+      0  \arrow{rr} && X_{-l} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k+1} \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
+      & H^l(X)[-l] \arrow[dashed]{ul}{+1} && H^{l+1}(X)[-l-1] \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X)[-k] \arrow[dashed]{ul}{+1}
+    \end{tikzcd}
+  \]  
+\end{defprop}
 
 \subsection{The Khovanov--Seidel curve model}
-In this section we briefly recall the procedure to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
+In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
 In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
@@
 \begin{lemma}
-Every wiggly arc corresponds to an object in the heart of the standard \(t\)-structure.  
+  Every wiggly arc corresponds to an object in the heart \(\mathcal{A}_m\) of the standard \(t\)-structure on \(\mathcal{C}_m\).
 \end{lemma}
 \begin{proof}
+  Let \(P^{\bullet}\) be the complex built from an arbitrary (not necessarily wiggly) arc.
   The procedure to build up the complex of projective modules from a curve explicitly describes the differentials.
-  Each component of these differentials is a map from a shift of \(P_i\) to a shift of \(P_j\).
-  It can be seen from~\cref{rem:generating-morphisms} that any component that maps from \(P_i\) to \(P_j\) for \(i \neq j\) keeps the complex linear; it is only when we have a looping map from \(P_i\) to \(P_i\langle 2 \rangle\) that we move out of the standard heart.
-  \asilata{Now figure out what to say about \(t\)-structures, namely that wiggly arcs are exactly those whose associated complexes lie in the heart of the standard \(t\)-structure.}
-\end{proof}
-
-\subsection{Categorical conditions on compatibility of arcs}
-
+
+  Each component of these differentials is a map of the form
+  \[P_i\langle g \rangle[h] \to P_j\langle g' \rangle[h-1].\]
+  First consider a component of the differential from some \(P_i\langle g \rangle\) to some \(P_j\langle g' \rangle\) for \(i \neq j\).
+  We see from~\cref{rem:generating-morphisms} that any such map must take \(P_i\langle g \rangle\) to \(P_j \langle g+1 \rangle\).
+  In other words, the differentials has the form
+  \[P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\]
+  if \(i \neq j\).
+  Since \(P_i\langle g \rangle[h]\) and \(P_j\langle g+1 \rangle[h-1]\) have the same level, any differential from a graded shift of \(P_i\) to a graded shift of \(P_j\) keeps the level unchanged.
+  The other possibility is a map from \(P_i\langle g \rangle\) to \(P_i\langle g' \rangle\).
+  Once again, it is clear from~\cref{rem:generating-morphisms} that such differentials have the form
+  \[P_i \langle g \rangle[h] \to P_i\langle g' \rangle[h-1],\]
+  where \(g'\) is either \(g\) or \(g + 2\).
+  Any component of the form
+  \[P_i \langle g \rangle[h] \to P_i\langle g \rangle[h-1]\]
+  is necessarily a multiple of the identity map, and identity maps do not appear in the Khovanov--Seidel complex.
+  Hence the only possibility is multiples of the loop map, which have the form
+  \[P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1].\]  
+  Therefore any portion of the differential from a graded shift of a \(P_i\) to another graded shift of itself raises the level by one.
+
+  Computing the \(j\)th cohomology of \(P^{\bullet}\) simply amounts to truncating the complex to level \(j\).
+  The object \(P^{\bullet}\) is in the heart if and only if it is concentrated in a single cohomological degree, which means that its differential has no components of the form
+  \[P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1].\]
+  This is the case if and only if the corresponding curve does not loop back around any point; that is, if and only if it is \(x\)-monotone.
+  The lemma is proved.
+\end{proof}
+
+\subsection{Cohomology filtrations of spherical objects}
+In this section we explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of spherical objects of \(\mathcal{C}_m\).
+
+Recall from~\cref{defprop:cohomology-filtration} that any object \(X\) of \(\mathcal{C}_m\) has a canonical cohomology filtration whose factors are homological shifts of objects in \(\mathcal{A}_m\).
+For general \(X\), the cohomology filtration can be arbitrary.
+However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations, as explained in the following proposition.
 \begin{proposition}
@@
     \begin{tikzcd}[column sep=0.3cm]
-      0 = X_0 \arrow{rr} && X_1 \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{k-1} \arrow{rr} \arrow{dl} && X_k = X \arrow{dl}\\
-      & H^1(X) \arrow[dashed]{ul}{+1} && H^2(X) \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X) \arrow[dashed]{ul}{+1}
+      0 \arrow{rr} && X_{-l} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
+      & H^l(X)[-l] \arrow[dashed]{ul}{+1} && H^{l+1}(X)[-l-1] \arrow[dashed]{ul}{+1} & \cdots & H^k(X)[-k] \arrow[dashed]{ul}{+1}
     \end{tikzcd}
   \]
-  Consider the set of objects \(\{H^j(X)\}\) taken without multiplicity, and let \(T\) be corresponding set of wiggly curves.
+  Consider the set of all nonzero objects \(\{H^j(X)\}\) taken without multiplicity, and let \(T\) be corresponding set of wiggly curves.
   We have the following results.
@@
 \end{proposition}
+\begin{proof}
+  The proof of this proposition is an easy consequence of analysing cohomology filtration from the point of view of arcs on the disk with marked points.
+  \asilata{TODO.}
+\end{proof}
+
+\subsection{Categorical constraints on compatibility of curves}
+In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
+As such, this section is somewhat dual to the previous section --- our criterion determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
+\begin{proposition}
+  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
+  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X\langle g \rangle, X\langle g' \rangle) = 0\) for any two integers \(g\) and \(g'\).
+\end{proposition}
+\begin{remark}
+  This proposition is similar to the condition of being compatible in a cluster-tilting object.
+  \asilata{Expand and make precise.}
+\end{remark}
+\begin{remark}
+  As stated, this proposition is not expected to be true in greater generality.
+  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
+  \asilata{Decide what to say here, because the forthcoming work is far from complete, although I do have counterexamples in type \(D_4\).
+Discussing how to interpret these counterexamples may not involve too much more work?}
+\end{remark}
+\begin{question}
+  How to best relate this section to the previous one purely categorically?
+  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
+  \asilata{Make more precise.}
+\end{question}
 

### 2024-06-07 draft/wigglyhedra.tex
Added comment; also typo fixes and readability.

@@
 \label{thm:wigglyFan}
-The collection of cones~$\R_{\ge 0} \langle \b{g}(A) \rangle$ for all~$A$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called \defn{wiggly fan}~$\wigglyFan_n$.
+The collection of cones~$\R_{\ge 0} \langle \b{g}(A) \rangle$ for all~$A$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called the \defn{wiggly fan}~$\wigglyFan_n$.
 \end{theorem}
@@
 However, this certainly raises the question to construct analogues of the wigglyhedron for all finite Coxeter groups.
+\asilata{I can come up with a possible categorical pathway towards the wiggly flip graph for arbitrary finite Coxeter groups, related to~\cref{prop:hn-filtration}.
+But I have no idea how to construct the polytope!}
 \end{remark}
@@
 \begin{definition}
-  The zigzag algebra \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the following relations:
+  The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the following relations:
   \begin{itemize}
@@
   The definition of the zigzag algebra as used here originally appeared in~\cite[Section 3]{hue.kho:01}.
-  This is an ``un-signed'' version of the zigzag algebra.
-  It is technically better to use a ``signed'' version of the zigzag algebra, and the comparison between the two is discussed in~\cite[Remark 6.6]{bap.deo.lic:20}.
+  This is the ``un-signed'' zigzag algebra.
+  It is technically better to use a ``signed'' zigzag algebra, and the comparison between the two is discussed in~\cite[Remark 6.6]{bap.deo.lic:20}.
   As the two versions are isomorphic in our example, we ignore this technicality and use the easier definition.
@@
   together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet + 1}\).
-  We say that \(P^{\bullet}\) has \emph{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
-  We say that \(P^{\bullet}\) is \emph{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
+  We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
+  We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
 
@@
   which are left and right adjoint respectively\asilata{Check left vs right.} to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
-  The \(i\)th cohomology functor is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
+  The \(i\)th \defn{cohomology functor} is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
   It is equal to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
@@
   \asilata{Find references for cohomology and cohomology filtration.}
-  Then \(X\) has a unique filtration of the form
+  Then \(X\) has a unique \defn{cohomology filtration}, which is the unique filtration of the form
   \[
@@
 However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations, as explained in the following proposition.
-\begin{proposition}
+\begin{proposition}\label{prop:hn-filtration}
   Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
@@
 In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
-As such, this section is somewhat dual to the previous section --- our criterion determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
+As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
 \begin{proposition}
@@
 \end{proposition}
+\begin{proof}
+  \asilata{TODO.}
+\end{proof}
 \begin{remark}

### 2024-06-09 draft/wigglyhedra.tex
Started writing about t-structure.

@@
 Let \(\mathcal{A}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) that is closed under isomorphism, which contains all the linear complexes.
+For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq N\).
+For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq N\).
+Observe that if \(P^{\cdot}\) has level \(\ell\), then \(P^{\cdot}[1]\) has level \(\ell + 1\), and that \(P^{\cdot}[-1]\) has level \(\ell - 1\).
+\asilata{The directions of the shifts are a mess.}
 \begin{proposition}\label{prop:standard-heart}

### 2024-06-11 draft/wigglyhedra.tex
Some more writing.

@@
 \newtheorem{defprop}[theorem]{Definition/Proposition}
+\newtheorem{warning}[theorem]{Warning}
 \crefname{notation}{Notation}{Notations}
@@
 For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-Let \(\mathcal{C}_m\) be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\) (see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22} for further discussion on the construction).
-
+There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
+In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).
+\begin{definition}
+  The category \(\mathcal{C}_m\) is defined to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
+\end{definition}
+For further discussion on the construction, see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22}.
 The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
@@
 More precisely, we can write
-\[P^{\bullet} = \bigoplus M_i\langle g \rangle[h],\]
+\[P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],\]
 where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
 each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
-
-Recall that an object of the form \(M_i[h]\) is placed in homological degree \(-h\);
-since the differential \(d\) raises the homological degree by one, it \emph{lowers} the homological shift by one.
+Set \(P^h\) to be the direct sum of all summands that have homological grading shift \(h\).
+That is, in the notation above, we have
+\[P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].\]
+
+\begin{warning}
+  By convention, if \(M_i\) is an \(A_m\)-module, then the object \(M_i[h]\) is placed in homological degree \(-h\).
+  Since the differential \(d\) raises the homological degree by one, it lowers the homological shift by one.
   That is, we have
-\[d \colon M_i\langle g \rangle[h] \to \bigoplus M_{i'}\langle g' \rangle[h-1].\]
+  \[d \colon M_i\langle g \rangle[h] \to \bigoplus_{g',i'} M_{i'}\langle g' \rangle[h-1].\]
   In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
+\end{warning}
 \begin{definition}\label{def:linear-complex}
@@
   \[P^{\bullet} = \bigoplus M_i\langle g \rangle[h]\]
-  together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet + 1}\).
+  together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
   We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).

### 2024-06-11 draft/wigglyhedra.tex
Added references and more writing.

@@
 
-We now describe the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\).
+We now describe the \(t\)-structure induced by the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\); a variant of this construction is described in~\cite[Section 2.5]{lic.que:21}.
 It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
@@
 \end{definition}
-Let \(\mathcal{A}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) that is closed under isomorphism, which contains all the linear complexes.
-For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq N\).
-For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq N\).
-Observe that if \(P^{\cdot}\) has level \(\ell\), then \(P^{\cdot}[1]\) has level \(\ell + 1\), and that \(P^{\cdot}[-1]\) has level \(\ell - 1\).
-\asilata{The directions of the shifts are a mess.}
-\begin{proposition}\label{prop:standard-heart}
-  The category \(\mathcal{A}_m\) is abelian.
-  Furthermore, it is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\), which we call the \emph{standard \(t\)-structure} on \(\mathcal{C}_m\).
+For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq -N\).
+For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq -N\).
+
+We refer the reader to e.g.~\cite[1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
+The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
+\begin{proposition}
+  The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
 \end{proposition}
-\asilata{Find a reference for this and possibly a cleaner statement.}
-
-Also recall the following statements for future use.
+We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
+Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\); this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
+It follows that \(\mathcal{A}_m\) is abelian.
+
+Also record the following statements for future use; the first may be found in~\cite[1.3]{bel.ber.del:82}
 \begin{defprop}\label{defprop:cohomology}
-  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a bounded \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart \(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
+  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart \(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
   For each integer \(i\), we have the \(i\)th truncation functors
-  \[\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i}\]
-  and
-  \[\tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},\]
-  which are left and right adjoint respectively\asilata{Check left vs right.} to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
+  \[\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i} \quad\text{and}\quad \tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},\]
+  which are right and left adjoint respectively to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
   The \(i\)th \defn{cohomology functor} is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
-  It is equal to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
+  It is canonically isomorphic to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
 \end{defprop}
-In the presence of a bounded \(t\)-structure, every object of \(\mathcal{C}\) has a canonical filtration whose factors are shifts of its cohomology objects.
+The next statement, which is easy to check from the definitions, is mentioned in~\cite[Section 3.3]{bayer2011tour}.
 \begin{defprop}\label{defprop:cohomology-filtration}
@@
   Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(l\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^{l}(X)\) are non-zero.
-  \asilata{Find references for cohomology and cohomology filtration.}
   Then \(X\) has a unique \defn{cohomology filtration}, which is the unique filtration of the form

### 2024-06-12 draft/wigglyhedra.tex
Minor readability updates.

@@
 
-We now describe the \(t\)-structure induced by the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\); a variant of this construction is described in~\cite[Section 2.5]{lic.que:21}.
+We now describe the \(t\)-structure induced by the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\); a variant of this construction is also described in~\cite[Section 2.5]{lic.que:21}.
 It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
@@
 
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading\asilata{Should this say homological?} shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
 
@@
 
+Let us first characterise wiggly arcs in terms of objects of \(\mathcal{C}_m\).
 \begin{lemma}
-  Every wiggly arc corresponds to an object in the heart \(\mathcal{A}_m\) of the standard \(t\)-structure on \(\mathcal{C}_m\).
+  Every wiggly arc corresponds, up to grading shift, to an indecomposable spherical object in the heart \(\mathcal{A}_m\) of the standard \(t\)-structure on \(\mathcal{C}_m\).
 \end{lemma}
@@
   Let \(P^{\bullet}\) be the complex built from an arbitrary (not necessarily wiggly) arc.
-  The procedure to build up the complex of projective modules from a curve explicitly describes the differentials.
-
+  The results of~\cite{kho.sei:02} imply that \(P^{\bullet}\) is spherical and indecomposable; we now show that it belongs to \(\mathcal{A}_m\) up to grading shift if and only if the arc is a wiggly arc.
+
+  Recall that the procedure to build up the complex of projective modules from an arc explicitly describes the differentials.    
   Each component of these differentials is a map of the form
@@
 For general \(X\), the cohomology filtration can be arbitrary.
-However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations, as explained in the following proposition.
+However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
 \begin{proposition}\label{prop:hn-filtration}
@@
   \]
-  Consider the set of all nonzero objects \(\{H^j(X)\}\) taken without multiplicity, and let \(T\) be corresponding set of wiggly curves.
+  Consider the set of all possible indecomposable summands of the cohomology objects \(\{H^j(X)\}\) taken without multiplicity.
+  Let \(T\) be corresponding set of wiggly curves.
   We have the following results.

### 2024-06-12 draft/wigglyhedra.tex
More writing.

@@
 
-Let us first characterise wiggly arcs in terms of objects of \(\mathcal{C}_m\).
-\begin{lemma}
-  Every wiggly arc corresponds, up to grading shift, to an indecomposable spherical object in the heart \(\mathcal{A}_m\) of the standard \(t\)-structure on \(\mathcal{C}_m\).
-\end{lemma}
-\begin{proof}
-  Let \(P^{\bullet}\) be the complex built from an arbitrary (not necessarily wiggly) arc.
-  The results of~\cite{kho.sei:02} imply that \(P^{\bullet}\) is spherical and indecomposable; we now show that it belongs to \(\mathcal{A}_m\) up to grading shift if and only if the arc is a wiggly arc.
-
-  Recall that the procedure to build up the complex of projective modules from an arc explicitly describes the differentials.    
+\begin{proposition}\label{prop:cohomology-pieces}
+  Let \(\alpha\) be any arc, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
+  Recall that for any integer \(j\), the cohomology object \(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
+  \begin{enumerate}
+  \item The object \(X\) is an indecomposable spherical object of \(\mathcal{A}_m\) up to shift if and only if \(\alpha\) is a wiggly arc.
+    In this case, \(H^j(X) \neq 0\) for exactly one \(j\), such that \(X \cong H^j(X)[-j]\).
+  \item If \(\alpha\) is a general arc, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical indecomposable object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
+  \end{enumerate}
+\end{proposition}
+\begin{proof}
+  Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) arc \(\alpha\).
+  The results of~\cite{kho.sei:02} imply that \(X\) is spherical and indecomposable.
+  Let us now analyse the indecomposable summands of its cohomology objects.
+
+  Recall that the procedure to build up \(X\) from \(\alpha\) explicitly describes the differentials.    
   Each component of these differentials is a map of the form
   \[P_i\langle g \rangle[h] \to P_j\langle g' \rangle[h-1].\]
-  First consider a component of the differential from some \(P_i\langle g \rangle\) to some \(P_j\langle g' \rangle\) for \(i \neq j\).
-  We see from~\cref{rem:generating-morphisms} that any such map must take \(P_i\langle g \rangle\) to \(P_j \langle g+1 \rangle\).
-  In other words, the differentials has the form
-  \[P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\]
-  if \(i \neq j\).
-  Since \(P_i\langle g \rangle[h]\) and \(P_j\langle g+1 \rangle[h-1]\) have the same level, any differential from a graded shift of \(P_i\) to a graded shift of \(P_j\) keeps the level unchanged.
-  The other possibility is a map from \(P_i\langle g \rangle\) to \(P_i\langle g' \rangle\).
-  Once again, it is clear from~\cref{rem:generating-morphisms} that such differentials have the form
-  \[P_i \langle g \rangle[h] \to P_i\langle g' \rangle[h-1],\]
-  where \(g'\) is either \(g\) or \(g + 2\).
-  Any component of the form
-  \[P_i \langle g \rangle[h] \to P_i\langle g \rangle[h-1]\]
-  is necessarily a multiple of the identity map, and identity maps do not appear in the Khovanov--Seidel complex.
-  Hence the only possibility is multiples of the loop map, which have the form
-  \[P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1].\]  
-  Therefore any portion of the differential from a graded shift of a \(P_i\) to another graded shift of itself raises the level by one.
-
-  Computing the \(j\)th cohomology of \(P^{\bullet}\) simply amounts to truncating the complex to level \(j\).
-  The object \(P^{\bullet}\) is in the heart if and only if it is concentrated in a single cohomological degree, which means that its differential has no components of the form
-  \[P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1].\]
-  This is the case if and only if the corresponding curve does not loop back around any point; that is, if and only if it is \(x\)-monotone.
-  The lemma is proved.
+  Let us see how these maps interact with the level.
+
+  First consider a non-zero component \(P_i\langle g \rangle[h] \to P_j\langle g' \rangle[h-1]\) for \(i \neq j\).
+  We see from~\cref{rem:generating-morphisms} that \(g' = g+1\).
+  In other words, this component has the form
+  \(P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\),
+  and hence does not change the level.
+
+  Now consider a non-zero component \(P_i\langle g \rangle[h] \to P_i\langle g' \rangle[h-1]\).
+  Once again, it is clear from~\cref{rem:generating-morphisms} that we either have \(g' = g\) or \(g' = g + 2\).
+  Any component of the form \(P_i \langle g \rangle[h] \to P_i\langle g \rangle[h-1]\)
+  is necessarily a multiple of the identity map, which do not appear in the Khovanov--Seidel complex.
+  The only remaining possibility is a ``loop'' map \(P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1]\), which raises the level by one.
+
+  Computing the \(j\)th cohomology \(H^j(X)\) simply amounts to truncating the complex to level \(j\).
+  Explicitly, the truncation is a new chain complex in which we only keep the terms of \(X\) that have level \(j\), together with all maps between them, and forget all the other terms.
+  From the calculation above, we see that the resulting complex only has components in its differential of the form \(P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\) for \(i \neq j\); in particular, we kill all the ``loop'' components.
+  The resulting chain complex breaks up into indecomposable summands, each of which is an object of \(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
+
+  The object \(X\) is in the heart up to shift if and only if it is concentrated in a single cohomological degree \(j\).
+  Truncating to level \(j\) as described above, we do not delete any of the terms of \(X\).
+  This can happen if and only if the differential of \(X\) contains no loop components,
+  which appear in the complex if and only if \(\alpha\) loops around a point.
+  Thus \(X\) is in the heart up to shift if and only if \(\alpha\) is  \(x\)-monotone.
+  This proves the first part of the proposition.
+
+  More generally, consider the indecomposable pieces of the level-\(j\) truncations of \(X\) for various \(j\), up to shift.
+  As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve \(\alpha\) into \(x\)-monotone portions.
+  More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by bending around a point \(p_1\).
+  In this case, we take the portion of \(\alpha\) between \(p_0\) and \(p_1\), calling it \(\alpha_1\), and setting its endpoints to be \(p_0\) and \(p_1\) respectively.
+  Note that \(p_0 \neq p_1\) because \(\alpha\) is \(x\)-monotone between \(p_0\) and \(p_1\).
+  We continue with the remainder of \(\alpha\) starting at \(p_1\), greedily taking the maximal \(x\)-monotone portion each time, to obtain pieces \(\alpha_1,\alpha_2, \ldots, \alpha_k\), which are all wiggly arcs.
+  These wiggly arcs correspond to complexes \(X_1, \ldots, X_k\), which are indecomposable spherical objects of \(\mathcal{A}_m\), up to shift.
+  It is clear from the construction of the associated complex that these objects, up to shift, are exactly the indecomposable pieces of the cohomology truncations \(H^j(X)\) for various \(j\).
+  This argument proves the second part of the proposition.
 \end{proof}
@@
 
-Recall from~\cref{defprop:cohomology-filtration} that any object \(X\) of \(\mathcal{C}_m\) has a canonical cohomology filtration whose factors are homological shifts of objects in \(\mathcal{A}_m\).
-For general \(X\), the cohomology filtration can be arbitrary.
+For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
 However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
@@
   Consider the set of all possible indecomposable summands of the cohomology objects \(\{H^j(X)\}\) taken without multiplicity.
-  Let \(T\) be corresponding set of wiggly curves.
+  Let \(T\) be corresponding set of wiggly arcs, as explained in~\cref{prop:cohomology-pieces}.
   We have the following results.
@@
 \begin{proof}
-  The proof of this proposition is an easy consequence of analysing cohomology filtration from the point of view of arcs on the disk with marked points.
-  \asilata{TODO.}
+  The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of arcs on the disk with marked points.
+  Let \(X_1, \ldots, X_k\) be the objects in \(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
+  Let \(\beta = (i,j,A,B)\) and \(\beta' = (i',j', A',B')\) be two distinct wiggly arcs among \(\{\alpha_1, \ldots,\alpha_k\}\).
+  We check that \(\beta\) and \(\beta'\) are compatible in the sense of~\cref{def:compatible}.
+
+  Recall that \(\beta\) and \(\beta'\) are two pieces of the arc \(\alpha\).
+  Therefore \(\beta\) and \(\beta'\) cannot cross, because \(\alpha\) does not cross itself.
+  Suppose that \(\beta\) and \(\beta'\) are non-pointed, and without loss of generality, suppose that \(i' = j\).
+  This means that the piece \(\beta\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the right of the point \(i'\).
+  Moreover, if \(i'\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(i'\) lies to the left of \(i'\).
+
+  Similarly, the piece \(\beta'\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the left of the point \(j\).
+  Moreover, if \(j\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(j\) lies to the right of \(j\).
+
+  We have four possible combinations:
+  \begin{enumerate}
+  \item \(i' = j\) is an endpoint such that \(\alpha\) goes left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) goes right starting at \(j\);
+  \item \(i' = j\) is an endpoint such that \(\alpha\) goes left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
+  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) goes right starting at \(j\); 
+  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
+  \end{enumerate}
+  It is clear that none of these possibilities can occur within the arc \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
+  Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.
+
+  \(T\) cannot contain both external edges because otherwise, the curve \(\alpha\) will not be able to have a second endpoint.\asilata{I am struggling to explain this, even though it should be obvious.}
 \end{proof}

### 2024-06-12 draft/wigglyhedra.tex
very minor cleaning changes

@@
 That is, a subcategory of the bounded derived category of (finitely generated) \(A_m\)-modules.
-The algebra \(A_m\), called the \emph{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
+The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
 \begin{figure}[h]
@@
   \item \((i|j|i) = (i|l|i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
+  \vincent{why not write $i-1$ and~$i+1$?}
   \end{itemize}
@@
 \begin{remark}
-  The definition of the zigzag algebra as used here originally appeared in~\cite[Section 3]{hue.kho:01}.
+  The definition of the zigzag algebra as used here originally appeared in~\cite[Sect.~3]{hue.kho:01}.
   This is the ``un-signed'' zigzag algebra.
-  It is technically better to use a ``signed'' zigzag algebra, and the comparison between the two is discussed in~\cite[Remark 6.6]{bap.deo.lic:20}.
+  It is technically better to use a ``signed'' zigzag algebra, and the comparison between the two is discussed in~\cite[Rem.~6.6]{bap.deo.lic:20}.
   As the two versions are isomorphic in our example, we ignore this technicality and use the easier definition.
@@
 Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
-For any integer \(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
+For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
 There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
@@
 \end{definition}
-For further discussion on the construction, see, e.g.,~\cite[Section 2.3.3]{bap.deo.lic:22}.
+For further discussion on the construction, see, e.g.,~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
 The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
@@
   \begin{itemize}
-  \item \(\Hom^{g,h}(P_i,P_i) = 0\) if \(g \neq 0, 2\) and \(h \neq 0\);
-  \item \(\Hom^{g,0}(P_i,P_i) = k\) if \(g = 0, 2\);
-  \item \(\Hom^{g,h}(P_i, P_{i\pm1}) = 0\) if \(g \neq 1\) and \(h \neq 0\);
+  \item \(\Hom^{g,h}(P_i,P_i) = 0\) if \(g \neq 0, 2\) and \(h \neq 0\),
+  \item \(\Hom^{g,0}(P_i,P_i) = k\) if \(g = 0, 2\),
+  \item \(\Hom^{g,h}(P_i, P_{i\pm1}) = 0\) if \(g \neq 1\) and \(h \neq 0\),
   \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
@@
 
-We now describe the \(t\)-structure induced by the full subcategory of \emph{linear complexes} of \(\mathcal{C}_m\); a variant of this construction is also described in~\cite[Section 2.5]{lic.que:21}.
+We now describe the \(t\)-structure induced by the full subcategory of \defn{linear complexes} of \(\mathcal{C}_m\).
+A variant of this construction is also described in~\cite[Sect.~2.5]{lic.que:21}.
 It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
@@
   together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
-  We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some \(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
+  We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some~\(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
   We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
@@
 Also record the following statements for future use; the first may be found in~\cite[1.3]{bel.ber.del:82}
+\vincent{is that a section?}
 \begin{defprop}\label{defprop:cohomology}
-  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart \(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
+  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart~\(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
   For each integer \(i\), we have the \(i\)th truncation functors
@@
 \end{defprop}
-The next statement, which is easy to check from the definitions, is mentioned in~\cite[Section 3.3]{bayer2011tour}.
+The next statement, easy to check from the definitions, is mentioned in~\cite[Sect.~3.3]{bayer2011tour}.
 \begin{defprop}\label{defprop:cohomology-filtration}
@@
 In addition to the wiggly arcs, consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-For convenience, we refer to such an isotopy class as an \emph{arc}.
-
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of \(\mathcal{C}_{n+1}\) (up to grading shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+For convenience, we refer to such an isotopy class as an \defn{arc}.
+
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to grading shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
 
@@
 In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
-In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects (\cite[Lemma 4.11]{kho.sei:02}).
+In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects~\cite[Lem.~4.11]{kho.sei:02}.
 
@@
   From the calculation above, we see that the resulting complex only has components in its differential of the form \(P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\) for \(i \neq j\); in particular, we kill all the ``loop'' components.
-  The resulting chain complex breaks up into indecomposable summands, each of which is an object of \(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
+  The resulting chain complex breaks up into indecomposable summands, each of which is an object of~\(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
 
@@
 
-  More generally, consider the indecomposable pieces of the level-\(j\) truncations of \(X\) for various \(j\), up to shift.
-  As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve \(\alpha\) into \(x\)-monotone portions.
+  More generally, consider the indecomposable pieces of the level-\(j\) truncations of \(X\) for various~\(j\), up to shift.
+  As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve~\(\alpha\) into \(x\)-monotone portions.
   More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by bending around a point \(p_1\).
@@
   Recall that \(\beta\) and \(\beta'\) are two pieces of the arc \(\alpha\).
-  Therefore \(\beta\) and \(\beta'\) cannot cross, because \(\alpha\) does not cross itself.
+  Therefore \(\beta\) and \(\beta'\) cannot cross, because~\(\alpha\) does not cross itself.
   Suppose that \(\beta\) and \(\beta'\) are non-pointed, and without loss of generality, suppose that \(i' = j\).
@@
 
-  Similarly, the piece \(\beta'\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the left of the point \(j\).
+  Similarly, the piece \(\beta'\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because~\(\alpha\) loops around the left of the point \(j\).
   Moreover, if \(j\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(j\) lies to the right of \(j\).

### 2024-06-12 draft/wigglyhedra.tex
minor changes

@@
 Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
-Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i|j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
-A longer path, which is a composition of arrows, will be denoted by \((i_1|i_2|\cdots|i_n)\).
-
-\begin{definition}
-  The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the following relations:
-  \begin{itemize}
-  \item \((i|j|l) = 0\) whenever \(i \neq l\);
-  \item \((i|j|i) = (i|l|i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
-  \vincent{why not write $i-1$ and~$i+1$?}
-  \end{itemize}
+Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
+A longer path, which is a composition of arrows, will be denoted by \((i_1, i_2, \dots, i_n)\).
+
+\begin{definition}
+  The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations: \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
+%  \begin{itemize}
+%  \item \((i-1, i, i+1) = (i+1, i, i-1\) for all~\(1 < i < m\),
+%  \item \((i, i-1, i) = (i, i+1, i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
+%  \end{itemize}
 \end{definition}
@@
   \end{itemize}
+\end{remark}
+
+\vincent{What about this remark instead?}
+\begin{remark}\label{rem:generating-morphisms}
+  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
 \end{remark}
@@
 
-We refer the reader to e.g.~\cite[1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
+We refer the reader to e.g.~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
 The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
@@
 
-Also record the following statements for future use; the first may be found in~\cite[1.3]{bel.ber.del:82}
-\vincent{is that a section?}
+Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}
 \begin{defprop}\label{defprop:cohomology}
@@
   As stated, this proposition is not expected to be true in greater generality.
+  For instance, it does not hold for the zigzag algebra of Dynkin type~$D_4$.
   However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.

### 2024-06-12 draft/wigglyhedra.tex
Updates following conversation.

--- 2024-06-12 draft/wigglyhedra.tex
@@
 However, this certainly raises the question to construct analogues of the wigglyhedron for all finite Coxeter groups.
-\asilata{I can come up with a possible categorical pathway towards the wiggly flip graph for arbitrary finite Coxeter groups, related to~\cref{prop:hn-filtration}.
-But I have no idea how to construct the polytope!}
 \end{remark}
@@
 In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects~\cite[Lem.~4.11]{kho.sei:02}.
+\asilata{Add picture of curve cutting.}
 
@@
   Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X\langle g \rangle, X\langle g' \rangle) = 0\) for any two integers \(g\) and \(g'\).
+  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
 \end{proposition}
@@
 
+\asilata{Write something about \(g\)-vectors.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-06-12 draft/wigglyhedra.tex
Kept second version of remark + cleaning.

@@
 \begin{remark}\label{rem:generating-morphisms}
-  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy the following:
-  \begin{itemize}
-  \item \(\Hom^{g,h}(P_i,P_i) = 0\) if \(g \neq 0, 2\) and \(h \neq 0\),
-  \item \(\Hom^{g,0}(P_i,P_i) = k\) if \(g = 0, 2\),
-  \item \(\Hom^{g,h}(P_i, P_{i\pm1}) = 0\) if \(g \neq 1\) and \(h \neq 0\),
-  \item \(\Hom^{1,0}(P_i, P_{i\pm1}) = k\), and
-  \item \(\Hom^{g,h}(P_i, P_j) = 0 \) otherwise.
-  \end{itemize}
-\end{remark}
-
-\vincent{What about this remark instead?}
-\begin{remark}\label{rem:generating-morphisms}
-  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
+  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
 \end{remark}
@@
 We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
-Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\); this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
+Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
 It follows that \(\mathcal{A}_m\) is abelian.
@@
 In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
-All the results of this section are due to Khovanov and Seidel~\cite{kho.sei:02}.
 

### 2024-06-12 draft/wigglyhedra.tex
Updated Remark 73.

@@
 \begin{remark}
-  As stated, this proposition is not expected to be true in greater generality.
-  For instance, it does not hold for the zigzag algebra of Dynkin type~$D_4$.
+  As stated, this proposition in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
+  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two indecomposable spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
   However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
-  \asilata{Decide what to say here, because the forthcoming work is far from complete, although I do have counterexamples in type \(D_4\).
-Discussing how to interpret these counterexamples may not involve too much more work?}
 \end{remark}

### 2024-06-12 draft/wigglyhedra.tex
improve proof bijection

--- 2024-06-12 draft/wigglyhedra.tex
@@
 
-\vincent{Here, I am using the fact that a set of pairwise non-crossing arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
+%\vincent{Here, I am using the fact that a set of pairwise non-crossing arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
 
@@
 
-\vincent{Asilata has an alternative description of the flip...}
+%\vincent{Asilata has an alternative description of the flip...}
 
@@
 \begin{definition}
+\label{def:wigglyPermutation}
 A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
@@
 
-Recall that the \defn{inversion set} of a permutation~$\sigma$ of~$[2n]$ is the set
-\[
-\inv(\sigma) \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) > \sigma(j)}.
-\]
-We denote by~$\ninv(\sigma)$ the non-inversions of~$\sigma$, that is the complement of~$\inv(\sigma)$.
-Note that~$\inv(\sigma)$ and~$\ninv(\sigma)$ are transitive: $\{(k,j), (j,i)\} \subseteq \inv(\sigma)$ implies~$(k,i) \in \inv(\sigma)$ for all~${1 \le i < j < k \le 2n}$, and similarly for~$\ninv$.
+Recall that the \defn{inversion set} and \defn{non-inversion set} of a permutation~$\sigma$ of~$[2n]$ are the sets
+\begin{align*}
+\inv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) > \sigma(j)}, \\
+\ninv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) < \sigma(j)}.
+\end{align*}
+Note that~$\inv(\sigma)$ and~$\ninv(\sigma)$ are transitive: $\{(c,b), (b,a)\} \subseteq \inv(\sigma)$ implies~$(c,a) \in \inv(\sigma)$ for all~${1 \le a < b < c \le 2n}$, and similarly for~$\ninv$.
 The inversion sets of wiggly permutations are characterized as follows.
@@
 Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
+\vincent{Ask Aaron what he prefers here...}
 
@@
 Consider a wiggly pseudotriangulation~$T$.
-Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabeled).
+Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
 We define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
@@
 \begin{proof}
+\vincent{I disagree with some points in this proof, so I put an alternative one below...}
   % We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
@@
   Finally, one can check using~\cref{lem:wigglyCoverRelation} that increasing flips in triangulations correspond precisely to edges in the wiggly lattice.
-  \asilata{Todo: more details here?}
-\item
-
+\end{proof}
+
+\begin{proof}
+First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
+Observe first that~\(\Phi(T)\) is by construction a permutation~$\sigma$ of~$[2n]$.
+For any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
+Suppose that \(2j-1\) appears before \(2j\) in \(\sigma\) for some fixed \(j \in [n]\).
+This means that the pseudotriangle~\(t_j\) has its unlabelled corner to the left of its labelled corners.
+In other words, its hinge opens to the right (see \eg $t_2$ in~\cref{fig:bijection}).
+Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
+This label belongs to some pseudotriangle \(t_h\) with~$h > j$.
+In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i < 2j-1\).
+The other case (in which \(2j\) appears before \(2j-1\) in \(\sigma\)) is symmetric.
+
+Next, we show that \(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).
+Observe first that for any~$1 \le u < v \le n$, we cannot see~$\{2u, 2v-1\}$ before~$\{2u-1, 2v\}$ in~$\sigma$ as it contains no forbidden pattern of \cref{def:wigglyPermutation}.
+Using the notations of \cref{def:bijection2}, this implies that~$i < j$ and that~${]i,j[} = A \sqcup B$, so that~$\alpha(\sigma,k) \eqdef (i, j, A, B)$ is indeed a wiggly arc for each~$k \in [2n-1]$.
+By~\cref{prop:wigglyPseudotriangulations}, it thus suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
+\(\alpha(\sigma,k)\) and~\(\alpha(\sigma,k')\) are distinct and compatible.
+\begin{enumerate}
+\item \textbf{Distinctness.}
+Suppose by contradiction that \(\alpha(\sigma,k) = (i,j,A,B) = \alpha(\sigma,k')\) for some~\({k < k'}\).
+Let~${\ell \in \sigma([k'] \ssm [k])}$ and~$\bar\ell \eqdef \lceil \ell/2 \rceil$.
+As~$\ell \notin \sigma([k])$, we have~$\bar\ell \notin A$.
+As~$\ell \in \sigma([k'])$, we have~$\bar\ell \notin B$.
+As~$\{2i-1, 2j\} \subseteq \sigma([k])$ and~$\{2i, 2j-1\} \cap \sigma([k']) = \varnothing$ and~$\sigma$ avoids the forbidden pattern of \cref{def:wigglyPermutation}, we have~$2i < \ell < 2j-1$, so that~$i < \bar\ell < j$.
+This contradicts the fact that~${]i,j[} = A \sqcup B$.
+
+\item \textbf{Compatibility.}
+Let $\alpha(\sigma, k) = (i,j,A,B)$ and $\alpha(\sigma, k') = (i',j',A',B')$ for some \(k < k'\).
+It is clear from the definition that \(i \neq j'\), as the sets over which we take the $\max$ and $\min$ to define \(i\) and \(j'\) respectively are disjoint.
+Similarly, \(j \neq i'\).
+Hence, the two arcs are pointed.
+To check that the arcs are non-crossing, we show $(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) = \varnothing$.
+Indeed~$A \cap B' = \varnothing$ since~$A \subseteq A'$ because~$\sigma([k]) \subseteq \sigma([k'])$.
+Moreover, \(\{i,j\} \cap B' = \emptyset\) since~\(\{2i - 1, 2j\} \subseteq \sigma([k]) \subseteq \sigma([k'])\).
+Finally, \(A \cap \{i',j'\} = \emptyset\) since~\(\{2i', 2j'-1\} \cap \sigma([k]) \subseteq \{2i', 2j'-1\} \cap \sigma([k']) = \varnothing\).
+\end{enumerate}
+
+\vincent{I am working here...}
+Next, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
+Let \(\sigma\) be a wiggly permutation, so that \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
+Let~$k \in [2n-1]$ and~$m \eqdef \lceil \sigma(k)/2 \rceil$.
+Then observe that
+\begin{itemize}
+\item if $\{2m, 2m-1\} \subseteq \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ passes above the point~$m$,
+\item if~$\sigma(k) = 2m$ and~$2m-1 \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has right endpoint~$m$,
+\item if~$\sigma(k) = 2m-1$ and~$2m \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has left endpoint~$m$.
+\end{itemize}
+It follows that in the wiggly pseudotriangulation~\(\Psi(\sigma)\), the arc \(\alpha(\sigma, k)\) is precisely the arc lying immediately above the angle labelled by~\(\sigma(k)\).
+Therefore, we have~\(\Phi(\Psi(\sigma)) = \sigma\).
+
+Conversely, let \(T\) be a wiggly pseudotriangulation, so that \(\sigma = \Phi(T)\) is a wiggly permutation.
+Then for any \(k \in [2n-1]\), the arc immediately above the angle of~$T$ labelled by~$\sigma(k)$ is precisely the one constructed as~\(\alpha(\sigma, k)\).
+This shows that \(\Psi(\Phi(T)) = T\).
+
+Finally, one can check using~\cref{lem:wigglyCoverRelation} that increasing flips in triangulations correspond precisely to edges in the wiggly lattice.
+\vincent{Indeed, we need more here. Todo.}
 \end{proof}
@@
 We now define two families of vectors, illustrated in \cref{fig:pseudotriangulationMatrices}.
+\vincent{Move that to the corresponding sections, and delete this section.}
 %
@@
 A few additional questions to arouse your curiosity:
+\vincent{Integrate that to the previous section}
 \begin{enumerate}
@@
 \end{definition}
-For further discussion on the construction, see, e.g.,~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
+For further discussion on the construction, see \eg~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
 The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
@@
 
-We refer the reader to e.g.~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
+We refer the reader to \eg~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
 The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
@@
 \subsection{The Khovanov--Seidel curve model}
+\vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}
 In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
@@
 In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects~\cite[Lem.~4.11]{kho.sei:02}.
-\asilata{Add picture of curve cutting.}
 
@@
   Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
+  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X\langle g \rangle, X\langle g' \rangle) = 0\) for any two integers \(g\) and \(g'\).
 \end{proposition}
@@
 
-\asilata{Write something about \(g\)-vectors.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-06-12 draft/wigglyhedra.tex
improve proof bijection

@@
 
-\vincent{I am working here...}
 Next, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
@@
 
-Finally, one can check using~\cref{lem:wigglyCoverRelation} that increasing flips in triangulations correspond precisely to edges in the wiggly lattice.
-\vincent{Indeed, we need more here. Todo.}
+Finally, consider a cover relation~$\sigma \lessdot \sigma^j$ in the wiggly lattice~$\wigglyLattice_n$ as described in~\cref{lem:wigglyCoverRelation}.
+Using the notations of~\cref{lem:wigglyCoverRelation}, bserve that
+\begin{itemize}
+\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell)$ for all~$\ell < i$ or~$\ell > k$,
+\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell+k-j)$ for all~$i \le \ell < j$, and
+\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell-j+i-1)$ for all~$j < \ell \le k$.
+\end{itemize}
+Hence, $\Psi(\sigma) \ssm \{\alpha(\sigma, j)\} = \Psi(\sigma^j) \ssm \{\alpha(\sigma^j, j)\}$.
+This implies that~$\Psi$ is a morphism of directed graph from the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ to the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$.
+As the underlying undirected graphs are both regular of degree~$2n-1$, we conclude that~$\Phi$ and~$\Psi$ induce directed graph isomorphisms between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
 \end{proof}

### 2024-06-13 draft/wigglyhedra.tex
improve proof bijection
add many examples

@@
 
-\begin{definition}\label{def:compatible}
+\begin{definition}
+\label{def:compatible}
 Two wiggly arcs~$(i,j,A,B)$ and~$(i',j',A',B')$ are 
@@
 \begin{figure}[b]
-\centerline{\includegraphics[scale=1.5]{pseudodissections}}
-\caption{Three wiggly pseudodissections.
+\centerline{\includegraphics[scale=1.5]{wigglyPseudodissections}}
+\caption{Three wiggly pseudodissections for~$n = 7$.
 The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue).
-The other two have $7$ pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and blue pseudotriangles.}
+The other two have $7$ pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and dark blue pseudotriangles.}
 \label{fig:pseudodissections}
@@
 
+\begin{example}
+For~$n = 1$, the $2$ wiggly pseudotriangulations of $3$ points are \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation1}}} and \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation2}}}.
+For~${n = 2}$, the $14$ wiggly pseudotriangulations of $4$ points are \\[.2cm]
+\centerline{\includegraphics[scale=.8]{wigglyPseudotriangulations}}
+\end{example}
+
+\begin{example}
+\label{exm:specialWigglyPseudotriangulations}
+\begin{figure}
+\centerline{\includegraphics[scale=1.3]{specialWigglyPseudotriangulations}}
+\caption{The wiggly pseudotriangulations~$T_\downarrow$ (left), $T_\uparrow$ (middle left), $T_\leftarrow$ (middle right), and $T_\rightarrow$ (right) of \cref{exm:specialWigglyPseudotriangulations} for~$n = 7$.}
+\label{fig:specialWigglyPseudotriangulations}
+\end{figure}
+The following wiggly pseudotriangulations are illustrated in \cref{fig:specialWigglyPseudotriangulations}:
+\begin{align*}
+T_\downarrow & \eqdef \set{(i-1, n+1, \varnothing, {[i,n]})}{i \in [n+1]} \cup \set{(0, n+1, [i], {]i,n]})}{i \in [n]}, \\
+T_\uparrow & \eqdef \set{(0, i, \varnothing, {[i-1]})}{i \in [n+1]} \cup \set{(0, n+1, {]i,n]}, [i])}{i \in [n]}, \\
+T_\leftarrow & \eqdef \{(0, 1, \varnothing, \varnothing)\} \cup \set{(0, i+1, \varnothing, [i])}{i \in [n]} \cup \set{(0, i+1, [i], \varnothing)}{i \in [n]}, \\
+T_\rightarrow & \eqdef \{(n, n+1, \varnothing, \varnothing)\} \cup \set{(i-1, n+1, \varnothing, [i,n])}{i \in [n]} \cup \set{(i-1, n+1, [i,n], \varnothing)}{i \in [n]}.
+\end{align*}
+\end{example}
+
 \begin{definition}
@@
 %
-\begin{figure}[h]
+\begin{figure}
 \centerline{\includegraphics[scale=1.3]{diagonalsPseudoquadrangles}}
@@
 \begin{definition}
+\label{def:wigglyFlipGraph}
 The \defn{wiggly flip graph}~$\wigglyFlipGraph_n$ is the graph with a vertex for each wiggly pseudotriangulation, and with an edge between two wiggly pseudotriangulations~$T,T'$ if there are wiggly arcs~$\alpha \in T$ and~$\alpha' \in T'$ such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
@@
 \begin{definition}
+\label{def:wigglyComplex}
 The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
@@
 \[
-1234, 2134, 1342, 1243, 3421, 2143, 3412, 1432, 1423, 4321, 4213, 4312, 4132, 4123.
+1234, 1243, 1342, 1423, 1432, 2134, 2143, 3412, 3421, 4123, 4132, 4213, 4312, 4321.
 \]
@@
 
+\begin{example}
+\label{exm:specialWigglyPermutations}
+The permutations
+\[
+\sigma_\downarrow \eqdef 1 2 \cdots (2n),
+\quad
+\sigma_\uparrow \eqdef (2n) \cdots 2 1,
+\quad
+\sigma_\leftarrow \eqdef (2n) \cdots 2 1 \cdots (2n-1),
+\quad
+\sigma_\rightarrow \eqdef 1 \cdots (2n-1) (2n) \cdots 2
+\]
+are wiggly permutations of~$[2n]$.
+\end{example}
+
 \begin{remark}
@@
 
+\begin{example}
+The map~$\Phi$ sends the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} to the wiggly permutations of \cref{exm:specialWigglyPermutations}.
+Namely, $\Phi(T_\downarrow) = \sigma_\downarrow$, $\Phi(T_\uparrow) = \sigma_\uparrow$, $\Phi(T_\leftarrow) = \sigma_\leftarrow$, and~$\Phi(T_\rightarrow) = \sigma_\rightarrow$.
+\end{example}
+
 \begin{definition}
@@
 
+\begin{example}
+The map~$\Psi$ sends the wiggly permutations of \cref{exm:specialWigglyPermutations} to the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
+Namely, $\Psi(\sigma_\downarrow) = T_\downarrow$, $\Psi(\sigma_\uparrow) = T_\uparrow$, $\Psi(\sigma_\leftarrow) = T_\leftarrow$, and~$\Psi(\sigma_\rightarrow) = T_\rightarrow$.
+\end{example}
+
 \begin{proposition}
@@
 \begin{proof}
-\vincent{I disagree with some points in this proof, so I put an alternative one below...}
+\vincent{I disagree with (or want to make more precise) some points in this proof, so I put an alternative one below...}
   % We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
@@
 \begin{remark}
+Transporting the wiggly lattice~$\wigglyLattice_n$ via the map~$\Psi$ to the wiggly pseudotriangulation, note that the minimal wiggly pseudotriangulation is~$\Psi(\sigma_\downarrow) = T_\downarrow$ while the maximal wiggly pseudotriangulation is~$\Psi(\sigma_\uparrow) = T_\uparrow$.
+See \cref{exm:specialWigglyPseudotriangulations,fig:specialWigglyPseudotriangulations} for illustrations.
+\end{remark}
+
+\begin{remark}
 The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
@@
 \label{sec:geometry}
+
+In this section, we define the wiggly fan and the wigglyhedron, which provide geometric realizations of the wiggly complex and of the wiggly lattice.
 
@@
 We now define two families of vectors, illustrated in \cref{fig:pseudotriangulationMatrices}.
-\vincent{Move that to the corresponding sections, and delete this section.}
 %
@@
 \centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\b{g}$-matrix and $\b{c}$-matrix of a wiggly pseudotriangulation~$T$.
+\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
 The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
@@
 
+\begin{example}
+\label{exm:specialGMatrices}
+\cref{table:specialGMatrices} gathers the $\b{g}$-matrices (\ie matrices whose columns are the $\b{g}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
+
+\begin{table}
+	\begingroup
+	\setlength\arraycolsep{2pt}
+	\begin{alignat*}{3}
+%	\b{g}(T_\downarrow) & = \begin{pmatrix}
+%		1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
+%		-1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
+%		-1 & 1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
+%		-1 & -1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
+%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
+%		-1 & -1 & \dots & 1 & 0 & -1 & -1 & \dots & -1 & 1 \\
+%		-1 & -1 & \dots & -1 & 0 & -1 & -1 & \dots & -1 & 1 \\
+%		-1 & -1 & \dots & -1 & 1 & -1 & -1 & \dots & -1 & -1 \\
+%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
+%	\end{pmatrix}
+%	\qquad &
+	\b{g}(T_\downarrow) & = \begin{pmatrix}
+		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
+		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
+		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
+		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
+	\end{pmatrix}
+	\qquad &
+%	\b{g}(T_\leftarrow) & = \begin{pmatrix}
+%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
+%		1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
+%		0 & -1 & \dots & -1 & -1 & -1 & 1 & \dots & 1 & 1 \\
+%		0 & 1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
+%		0 & 0 & \dots & -1 & -1 & 0 & -1 & \dots & 1 & 1 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & 1 & 1 \\
+%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & -1 & 1 \\
+%		0 & 0 & \dots & 1 & -1 & 0 & 0 & \dots & 1 & 1 \\
+%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & 0 & -1 \\
+%		0 & 0 & \dots & 0 & 1 & 0 & 0 & \dots & 0 & 1 \\
+%	\end{pmatrix}
+%	\qquad &
+	\b{g}(T_\leftarrow) & = \begin{pmatrix}
+		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
+		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
+		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
+	\end{pmatrix}
+	\\[.3cm]
+%	\b{g}(T_\uparrow) & = \begin{pmatrix}
+%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
+%		1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
+%		0 & -1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
+%		0 & 1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
+%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
+%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & -1 \\
+%		0 & 0 & \dots & 1 & -1 & 1 & 1 & \dots & 1 & -1 \\
+%		0 & 0 & \dots & 0 & -1 & 1 & 1 & \dots & 1 & 1 \\
+%		0 & 0 & \dots & 0 & 1 & 1 & 1 & \dots & 1 & 1 \\
+%	\end{pmatrix}
+%	\qquad &
+	\b{g}(T_\uparrow) & = \begin{pmatrix}
+		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
+		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
+		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
+		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
+		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
+		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
+		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
+		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
+	\end{pmatrix}
+	\qquad &
+%	\b{g}(T_\rightarrow) & = \begin{pmatrix}
+%		1 & 0 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
+%		-1 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
+%		-1 & 1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
+%		-1 & -1 & \dots & 0 & 0 & 1 & -1 & \dots & 0 & 0 \\
+%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & -1 & 0 \\
+%		-1 & -1 & \dots & 1 & 0 & 1 & 1 & \dots & 1 & 1 \\
+%		-1 & -1 & \dots & -1 & 0 & 1 & 1 & \dots & 1 & -1 \\
+%		-1 & -1 & \dots & -1 & 1 & 1 & 1 & \dots & 1 & 1 \\
+%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
+%	\end{pmatrix}
+%	\qquad &
+	\b{g}(T_\rightarrow) & = \begin{pmatrix}
+		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
+		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
+		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots  & \ddots & \vdots & \vdots \\
+		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
+		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
+	\end{pmatrix}
+	\end{alignat*}
+	\endgroup
+	\caption{The $\b{g}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
+The $i$th column of~$\b{g}(T)$ is the $\b{g}$-vector~$\b{g}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+}
+	\label{table:specialGMatrices}
+\end{table}
+\end{example}
+
+Observe that the $\b{g}$-matrices of \cref{exm:specialGMatrices} have full rank.
+More generally, we will see in \cref{coro:basis} that~$\b{G}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis.
+
 \begin{definition}
@@
 \end{itemize}
+The tedious proof of this description is not needed in this paper.
 \end{remark}
+
+\begin{example}
+\label{exm:specialCMatrices}
+\cref{table:specialCMatrices} gathers the $\b{c}$-matrices (\ie matrices whose columns are the $\b{c}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
+
+\begin{table}
+	\begingroup
+	\setlength\arraycolsep{1.1pt}
+	\begin{alignat*}{3}
+%	4\b{c}(T_\downarrow) & = \begin{pmatrix}
+%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
+%		-2 & 0 & \dots & 0 & 0 & 2 & 0 & \dots & 0 & 0 \\
+%		0 & 2 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
+%		0 & -2 & \dots & 0 & 0 & -1 & 2 & \dots & 0 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & 0 & -1 & \dots & 0 & 0 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 2 & 0 \\
+%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & -1 & 0 \\
+%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & -1 & 2 \\
+%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & -1 \\
+%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & -1 \\
+%	\end{pmatrix}
+%	\qquad &
+	4\b{c}(T_\downarrow) & = \begin{pmatrix}
+		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
+		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
+		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
+		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
+		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
+		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
+		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
+		0 & 0 & 0& 0 & \dots & 2 & 0 & 0 \\
+		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
+		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
+		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
+	\end{pmatrix}
+	\qquad &
+%	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
+%		-2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
+%		2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & -2 & 1 & \dots & 0 & 0 \\
+%		0 & 2 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & 0 & -2 & \dots & 0 & 0 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & -1 & 0 & 0 & 0 & \dots & 1 & 0 \\
+%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & -2 & 1 \\
+%		0 & 0 & \dots & 2 & -1 & 0 & 0 & \dots & 0 & 1 \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & -2 \\
+%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
+%	\end{pmatrix}
+%	\qquad &
+	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
+		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
+		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
+		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
+		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
+		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
+		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
+		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
+	\end{pmatrix}
+	\\[.3cm]
+%	4\b{c}(T_\uparrow) & = \begin{pmatrix}
+%		-2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
+%		2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
+%		0 & -2 & \dots & 0 & 0 & 2 & -1 & \dots & -1 & 2 \\
+%		0 & 2 & \dots & 0 & 0 & 0 & -1 & \dots & -1 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 2 & \dots & 2 & 0 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -1 & 0 \\
+%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & 2 & -1 \\
+%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 0 & -1 \\
+%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & 2 \\
+%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
+%	\end{pmatrix}
+%	\qquad &
+	4\b{c}(T_\uparrow) & = \begin{pmatrix}
+		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
+		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
+		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
+		0 & 0 & 0 & 0 & \dots & 2 & 0 & 0 \\
+		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
+		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
+		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
+		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
+		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
+		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
+		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
+	\end{pmatrix}
+	\qquad &
+%	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
+%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & -2 & 0 & \dots & 0 & 0 \\
+%		-1 & 2 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
+%		-1 & 0 & \dots & 0 & 0 & 1 & -2 & \dots & 0 & 0 \\
+%		0 & -1 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
+%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -2 & 0 \\
+%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 1 & 0 \\
+%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 1 & -2 \\
+%		0 & 0 & \dots & -1 & 2 & 0 & 0 & \dots & 0 & 1 \\
+%		0 & 0 & \dots & -1 & -2 & 0 & 0 & \dots & 0 & 1 \\
+%	\end{pmatrix}
+%	\qquad &
+	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
+		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
+		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
+		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
+		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
+		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
+		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
+		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
+		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
+	\end{pmatrix}
+	\end{alignat*}
+	\endgroup
+	\caption{The $\b{c}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
+The $i$th column of~$\b{c}(T)$ is the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).}
+	\label{table:specialCMatrices}
+\end{table}
+\end{example}
 
@@
 
+\begin{corollary}
+\label{coro:basis}
+For any wiggly pseudotriangulation~$T$, the set~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ is a basis of~$\HH_{2n}$.
+\end{corollary}
+
+\begin{proof}
+Observe that the $\b{g}$-matrix~$\b{g}(T_\leftarrow)$ presented in \cref{exm:specialGMatrices} has full rank (it is very easy to check for~$\b{g}(T_\leftarrow)$, but any other would do).
+The statement thus follows from \cref{lem:linearDependences} and the connectedness of the flip graph on wiggly pseudotriangulations.
+\end{proof}
+
+Finally, we wrap up \cref{thm:wigglyFan}.
+
 \begin{proof}[Proof of \cref{thm:wigglyFan}]
@@
 \begin{remark}
-The wiggly fan coarsens the $\b{c}$-vector fan.
-\vincent{todo}
+By definition, each wall of the wiggly fan is normal to a $\b{c}$-vector.
+Hence, the wiggly fan coarsens the \defn{$\b{c}$-vector fan}, defined by the arrangement of hyperplanes~$\set{\b{x} \in \HH_{2n}}{\dotprod{\b{x}}{\b{c}(\alpha, T}}$ for all arcs~$\alpha$ and wiggly pseudotriangulations~$T$ with~$\alpha \in T$.
 \end{remark}
@@
 
-\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}
+%\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}
 
@@
 
-\section{Cambrian considerations}
+\section{Further topics}
+\label{sec:furtherTopics}
+
+In this section, we explore two further topics on the wigglyhedron.
+In \cref{subsec:CambrianConsiderations}, we observe that any (type~$A$) Cambrian associahedron~\cite{Reading-CambrianLattices,HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$.
+In \cref{subsec:planarPointSets}, we raise the question to extend our construction to wiggly complexes of arbitrary planar point sets.
+
+%%%%%%%%%%%%
+
+\subsection{Cambrian considerations}
+\label{subsec:CambrianConsiderations}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Wiggly pseudotriangulations of planar point sets}
+%%%%%%%%%%%%
+
+\subsection{Wiggly pseudotriangulations of planar point sets}
+\label{subsec:planarPointSets}
 
@@
 \begin{definition}
+\label{def:wigglyComplexPointSet}
 Fix a point set~$P$ of the plane, and an arbitrary total order~$<$ on~$P$.
@@
 The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
-Note that, by construction, $\wigglyFlipGraph_P$ is regular.
+%Note that, by construction, $\wigglyFlipGraph_P$ is regular.
 See \cref{fig:wigglyComplexSquarre} for an illustration.
@@
 
+Note that \cref{def:wigglyComplexPointSet} recovers two specific situations:
+\begin{itemize}
+\item \cref{def:wigglyComplex,def:wigglyFlipGraph} in the case of aligned points, and
+\item the pseudodissection complex of~$P$ and pseudotriangulation flip graph of~$P$ in the case of points~$P$ in general position.
+We refer to the original article of M.~Pocchiola and G.~Vegter~\cite{PocchiolaVegter} and to the nice survey of G.~Rote, F.~Santos and I.~Streinu~\cite{RoteSantosStreinu-pseudotriangulations}.
+\end{itemize}
+
+Note that it is not even clear from \cref{def:wigglyComplexPointSet} that the wiggly complex~$\wigglyComplex_P$ is a pure pseudomanifold (hence that the wiggly flip graph~$\wigglyFlipGraph_P$ is well-defined).
+However, we make the following ambitious conjecture.
+
 \begin{conjecture}
@@
 
-Note that in \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope} (see also \cite{RoteSantosStreinu-pseudotriangulations} for a nice survey on pseudotriangulations).
-
-\begin{conjecture}
-\label{conj:Hamiltonian2}
-For any point set~$P$ in the plane, the wiggly flip graph~$\wigglyFlipGraph_P$ is Hamiltonian.
-\end{conjecture}
+Note that in \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
+This raises in particular the following question.
+
+\begin{question}
+Can the construction of \cref{thm:wigglyhedron} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (\aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
+\end{question}
+
+Using the duality between lines in the plane and points in the M\"obius strip, the pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations} were interpreted in~\cite{PilaudPocchiola} as pseudoline arrangements on sorting networks.
+It is natural to look for the analogue of this interpretation in the wiggly setting.
+
+\begin{question}
+Is there a dual interpretation of wiggly pseudotriangulations as some sort of pseudoline arrangements? 
+\end{question}
+
+This dual interpretation enables \cite{PilaudPocchiola} to consider the pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations} and the multitriangulations of~\cite{PilaudSantos-multitriangulations} under the same roof, and to define multi-pseudo-triangulations.
+The extension to the wiggly case is a natural question.
+
+\begin{question}
+Is there a multi wiggly complex?
+\end{question}
+
+Moreover, pseudoline arrangements on sorting networks can also be interpreted as (type~$A$) subword complexes of~\cite{KnutsonMiller-subwordComplex}, which in turn extend to arbitrary finite Coxeter group.
+See \cite{Stump, CeballosLabbeStump} for the study of subword complexes corresponding to cluster complexes and multi-cluster complexes.
+
+\begin{question}
+Can the wiggly complex be extended to arbitrary finite Coxeter groups?
+\end{question}
+
+%\begin{question}
+%\begin{itemize}
+%\item Is there a dual interpretation of wiggly pseudotriangulations as some sort of pseudoline arrangements? 
+%\item Is there a multi wiggly complex?
+%\item Can this interpretation be extended to other finite Coxeter groups?
+%\end{itemize}
+%\end{question}
+
+Finally, it is natural to consider the extension of \cref{conj:Hamiltonian}.
+
+\begin{question}
+\label{qu:Hamiltonian}
+Is the wiggly flip graph~$\wigglyFlipGraph_P$ is Hamiltonian for any point set~$P$ in the plane?
+\end{question}
 
@@
 
-\section{Further questions}
-
-A few additional questions to arouse your curiosity:
-\vincent{Integrate that to the previous section}
-\begin{enumerate}
-\item Can the construction of \cref{thm:wigglyhedron} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
-\item What is the dual interpretation of wiggly pseudotriangulations as pseudoline arrangements?
-(see~\cite{PilaudPocchiola} for context) Can this interpretation be extended to other finite Coxeter groups?
-(see~\cite{CeballosLabbeStump} for context).
-\item What is the multi wiggly complex?
-\end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Categorical interpretation of wiggly pseudotriangulations}
+\label{sec:categoricalInterpretation}
+
 The aim of this section is to explain a categorical interpretation of wiggly arcs.
-We recall results of Khovanov--Seidel~\cite{kho.sei:02} that realise wiggly arcs as objects of a triangulated category, such that intersections between wiggly arcs correspond to morphism in this category.
+We recall results of Khovanov--Seidel~\cite{kho.sei:02} that realise wiggly arcs as objects of a triangulated category, such that intersections between wiggly arcs correspond to morphisms in this category.
 We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible}.
@@
 
+%%%%%%%%%%%%
+
 \subsection{A triangulated category associated to a quiver}
+
 We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
@@
 
+%%%%%%%%%%%%
+
 \subsection{The Khovanov--Seidel curve model}
+
 \vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}
@@
 
+%%%%%%%%%%%%
+
 \subsection{Cohomology filtrations of spherical objects}
+
 In this section we explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of spherical objects of \(\mathcal{C}_m\).
@@
 
+%%%%%%%%%%%%
+
 \subsection{Categorical constraints on compatibility of curves}
+
 In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.

### 2024-06-14 draft/wigglyhedra.tex
Merged proof of Prop 37.

@@
 \end{proposition}
-
-\begin{proof}
-\vincent{I disagree with (or want to make more precise) some points in this proof, so I put an alternative one below...}
-  % We first have to prove that~$\Phi$ and~$\Psi$ are well-defined.
-  We break the proof into several steps.
-
-  First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
-  Let \(\sigma = \Phi(T)\), and for any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
-  Suppose that \(2j-1\) appears before \(2j\) in \(\sigma\) for some fixed \(j\).
-  This means that the pseudotriangle \(t_j\) has its unlabelled corner to the left of its labelled corners.
-  In other words, its hinge opens to the right (see, e.g., the triangle labelled by the \(2\)nd hinge in~\cref{fig:bijection}).
-  Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
-  This label belongs to some pseudotriangle \(t_h\), such that \(j\) is either a labelled or an unlabelled corner of \(t_h\).
-  Moreover, the corner angle of \(t_h\) is sandwiched within the convex angle at \(j\) formed by \(t_j\).
-  If \(j\) is an unlabelled corner of \(t_h\), then \(t_h\) also opens to the right at \(h\).
-  If \(j\) is a labelled corner of \(t_h\), then \(t_h\) opens to the left.
-  In both cases, it is clear that \(h > j\), and hence \(i > 2j-1\).
-  In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i > 2j-1\).
-  The other case (in which \(2j\) appears before \(2j-1\) in \(\sigma\)) is similar.
-
-  Next, we show that \(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).
-  By~\cref{prop:wigglyPseudotriangulations}, it suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
-  \(\alpha(\sigma,k)\) and \(\alpha(\sigma,k')\) are distinct and compatible.
-
-  To check distinctness, suppose that \(\alpha(\sigma,k) = (i,j,A,B)\) equals \((\sigma,k') = (i',j',A',B')\) for some \(k \leq k'\).
-  Note that \(i = i',j = j'\) are both in \(\sigma([k])\), and also \(\sigma([k]) \subseteq \sigma([k'])\).
-  For any \(l \in \sigma([k']) \ssm \sigma([k])\), the conditions on wiggly permutations imply that
-  \[i < \left\lceil \frac{l}{2} \right\rceil < j.\]
-  Furthermore, from the definitions of \(i\) and \(j\), we see that for any \(l \in \sigma([k']) \ssm \sigma([k])\), we have
-  \[2 \left\lceil \frac{l}{2} \right\rceil \in \sigma([k']) \text{ if and only if } 2\left\lceil \frac{l}{2} \right\rceil - 1 \in \sigma([k']).\]
-  Now it follows from the fact that \(A' = A\) that there is no element \(l \in \sigma([k']) \setminus \sigma([k])\); that is, \(k = k'\).
-
-  We check compatibility.
-  Suppose that for some \(k < k'\), we have 
-  \[\alpha(\sigma,k) = (i,j,A,B) \text{ and }\alpha(\sigma,k') = (i',j',A',B').\]
-  It is clear from the definition that \(i \neq j'\), as the sets over which we take the max and min to define \(i\) and \(j'\) respectively are disjoint.
-  Similarly, we have \(j \neq i'\).
-  Therefore the two arcs are pointed.
-  To check that the arcs are non-crossing, we must show that the sets
-  \[(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \text{ and } (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})\]
-  are both empty.
-  We check the first; the second is similar.
-  Recall that \(\sigma([k]) \subset \sigma([k'])\).
-  For any \(l \in B'\), we have \(2l, 2l-1 \notin \sigma([k'])\), and hence \(2l, 2l-1 \notin \sigma([k])\), which means that \(l \notin A\).
-  So \(A \cap B' = \emptyset\).
-  Since \(2i - 1, 2j \in \sigma([k]) \subset \sigma([k'])\), we see that \(\{i,j\} \cap B' = \emptyset\).
-  Since \(2i', 2j'-1 \notin \sigma([k'])\) hence not in \(\sigma([k])\), we see that \(A \cap \{i',j'\} = \emptyset\).
-
-  Finally, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
-  Let \(\sigma\) be a wiggly permutation, so that \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
-  The following are easy to check for any \(k \in [n]\).
-  Let \(m = \lceil \sigma(k)/2 \rceil\).
-  \begin{enumerate}
-  \item If both \(2m\) and \(2m -1\) appear in \(\sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) passes above the point \(m\).
-  \item If \(\sigma(k) = 2m\) and \(2m - 1 \notin \sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) has its right endpoint at \(m\).
-  \item If \(\sigma(k) = 2m - 1\) and \(2m \notin \sigma([k])\), then \(k\) is the smallest number for which \(\alpha(\sigma,k)\) has its left endpoint at \(m\).
-  \end{enumerate}
-  It follows from the above that in the wiggly pseudotriangulation \(\Psi(\sigma)\), the arc \(\alpha(\sigma,k)\) is precisely the arc lying immediately above the angle \(\sigma(k)\), where we regard \(\alpha(\sigma,2n)\) to be the top irrelevant arc.
-  In other words, we have \(\Phi(\Psi(\sigma)) = \sigma\).
-
-  Similarly, let \(T\) be a wiggly pseudotriangulation so that \(\sigma = \Phi(T)\) is a wiggly permutation.
-  One can check that for any angle in \(T\), namely any \(l \in [2n]\), the arc immediately above \(l\) is precisely the one constructed as \(\alpha(\sigma,\sigma^{-1}(l))\).
-  This shows that \(\Psi(\Phi(T)) = T\).
-
-  Finally, one can check using~\cref{lem:wigglyCoverRelation} that increasing flips in triangulations correspond precisely to edges in the wiggly lattice.
-\end{proof}
 

### 2024-06-14 draft/wigglyhedra.tex
add remarks on symmetries

--- 2024-06-13 draft/wigglyhedra.tex
@@
 \thanks{AB was partially supported by the Australin Research Council DECRA grant DE240100447. 
-  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
+  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}
 
@@
 \begin{abstract}
+Motivated by categorical representation theory and stability conditions, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
+The wiggly complex is a pure pseudomanifold, whose facets are wiggly pseudotriangulations.
+We show that wiggly pseudotriangulations are in bijection with wiggly permutations, which are permutations of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
+These permutations define the wiggly lattice, an induced sublattice of the weak order.
+We then prove that the wiggly complex is isomorphic to the boundary complex of the polar of the wigglyhedron, for which we give explicit and simple vertex and facet descriptions.
+Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
+Finally, we develop the connections with categorical representation theory and stability conditions.
 \end{abstract}
@@
 \maketitle
+
+\centerline{\includegraphics[scale=1.6]{wigglyFlipGraph}}
 
@@
 Fix an integer~$n \ge 1$.
-In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points and the wiggly permutations of~$[2n]$, and we prove that they are in bijection.
+In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points (\cref{subsec:wigglyPseudotriangulations}) and the wiggly permutations of~$[2n]$ (\cref{subsec:wigglyPermutations}), and we prove that they are in bijection (\cref{subsec:bijection}).
 These two perspectives enable us to endow these combinatorial families with additional structures: the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
@@
 \begin{figure}
-\centerline{\includegraphics[scale=1.1]{wigglyFlipGraph}}
+\centerline{\includegraphics[scale=1.1]{wigglyLattice}}
 \caption{The wiggly lattice~$\wigglyLattice_2$ on wiggly pseudotriangulations (left) and on wiggly permutations (right).}
@@
 
-In this section, we define the wiggly fan and the wigglyhedron, which provide geometric realizations of the wiggly complex and of the wiggly lattice.
+In this section, we use $\b{g}$- and $\b{c}$-vectors (\cref{subsec:gcvectors}) to define the wiggly fan (\cref{subsec:wigglyFan}) and the wigglyhedron (\cref{subsec:wigglyhedron}), which provide geometric realizations of the wiggly complex and of the wiggly lattice.
 
@@
 
+\begin{remark}
+\label{rem:gcvectorsSymmetries}
+Following \cref{rem:wigglyComplexAutomorphism}, note that the vertical and horizontal symmetries on wiggly arcs translate on $\b{g}$- and $\b{c}$-vectors to the isometries sending~$(x_1, x_2, \dots, x_{2n-1}, x_{2n}) \in \HH_{2n}$ to~$(x_{2n}, x_{2n-1}, \dots, x_2, x_1)$ and to~$(-x_2, -x_1, \dots, -x_{2n}, -x_{2n-1})$ respectively.
+\end{remark}
+
 %%%%%%%%%%%%
@@
 \begin{remark}
+\label{rem:wigglyFanSymmetries}
+Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define linear automorphisms of the wiggly fan~$\wigglyFan_n$.
+\end{remark}
+
+\begin{remark}
 By definition, each wall of the wiggly fan is normal to a $\b{c}$-vector.
@@
 
+\begin{remark}
+\label{rem:wigglyhedronSymmetries}
+Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define isometries of the wigglyhedron~$\wigglyhedron_n$.
+\end{remark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In this section, we explore two further topics on the wigglyhedron.
-In \cref{subsec:CambrianConsiderations}, we observe that any (type~$A$) Cambrian associahedron~\cite{Reading-CambrianLattices,HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$.
-In \cref{subsec:planarPointSets}, we raise the question to extend our construction to wiggly complexes of arbitrary planar point sets.
+We first observe that any (type~$A$) Cambrian associahedron~\cite{Reading-CambrianLattices,HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$ (\cref{subsec:CambrianConsiderations}).
+We then raise the question to extend our construction to wiggly complexes of arbitrary planar point sets (\cref{subsec:planarPointSets}).
 
@@
 \cref{prop:CambrianLattice,prop:CambrianFan} would still hold.
+\end{remark}
+
+\begin{remark}
+\label{rem:CambrianSymmetries}
+Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries,rem:wigglyhedronSymmetries}, note that the vertical and horizontal symmetries send $\delta$ to~$\delta_n \cdots \delta_1$ and $(-\delta_1) \cdots (-\delta_n)$ respectively.
 \end{remark}
@@
 \label{qu:Hamiltonian}
-Is the wiggly flip graph~$\wigglyFlipGraph_P$ is Hamiltonian for any point set~$P$ in the plane?
+Is the wiggly flip graph~$\wigglyFlipGraph_P$ Hamiltonian for any point set~$P$ in the plane?
 \end{question}

### 2024-06-14 draft/wigglyhedra.tex
start intro

@@
 \newtheorem*{theorem*}{Theorem}%[section]
+\newtheorem*{proposition*}{Proposition}%[section]
+\newtheorem*{conjecture*}{Conjecture}%[section]
 
@@
 
-This problem arose from recent discussions with Asilata Bapat~\cite{BapatPilaud}.
-It was originally motivated by her joint work with Anand Deopurkar and Anthony Licata on categorical representation theory and stability conditions, but it can be stated in purely combinatorial terms.
-
-Analogies to cluster algebras and gentle algebras.
+%This problem arose from recent discussions with Asilata Bapat~\cite{BapatPilaud}.
+%It was originally motivated by her joint work with Anand Deopurkar and Anthony Licata on categorical representation theory and stability conditions, but it can be stated in purely combinatorial terms.
+
+\vincent{Start with one or two paragraphs on motivation from categories}
+
+\para{Combinatorics}
+Fix $n \ge 2$ and consider the~$n+2$ points on the horizontal axis at abscissa~${0, \dots, n+1}$.
+A \defn{wiggly arc} is an abscissa monotone curve starting at some point~$i$, ending at some point~$j$ (with~${0 \le i < j \le n+1}$), and passing above or below each point~$i+1, \dots, j-1$.
+Two wiggly arcs are \defn{compatible} if they are pointed (the left endpoint of one is not the right endpoint of the other) and non-crossing (the interior of the curve are disjoint).
+A \defn{wiggly dissection} is a collection of pairwise compatible wiggly arcs, and a \defn{wiggly pseudotriangulation} is an inclusion maximal wiggly dissection.
+The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of wiggly dissections (minus their external wiggly arcs).
+We first establish the following result.
+
+\begin{proposition*}
+The wiggly complex~$\wigglyComplex_n$ is a pure closed pseudomanifold of dimension~$2n-1$.
+\end{proposition*}
+
+In particular, all wiggly pseudotriangulations have $2n-1$ internal wiggly arcs, each of which can be \defn{flipped}.
+We actually describe the flip in terms of wiggly diagonals in wiggly pseudoquadrangles.
+We also orient this flip graph in a canonical way, which we call the \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$.
+The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper.
+
+We then make a small detour to permutations.
+A \defn{wiggly permutation} is a permutation of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
+Our main result on wiggly permutations is the following.
+
+\begin{proposition*}
+The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, which we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
+Moreover, its Hasse diagram is regular of degree~$2n-1$.
+\end{proposition*}
+
+We then connect wiggly pseudotriangulations to wiggly permutations.
+
+\begin{proposition*}
+The increasing flip graph on wiggly pseudotriangulations~$\wigglyIncreasingFlipGraph_n$ is isomorphic to the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
+In particular, the wiggly pseudotriangulations admit a lattice structure.
+\end{proposition*}
+
+\para{Polyhedral geometry}
+We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
+Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinski-clusterAlgebrasI,FominZelevinski-clusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon}.
+Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.
+
+\begin{theorem*}
+The cones generated by the $\b{g}$-vectors of wiggly pseudodissections form a complete simplicial fan, called \defn{wiggly fan}~$\wigglyFan_n$, realizing the wiggly complex~$\wigglyComplex_n$.
+\end{theorem*}
+
+The proof of this result is based on a fine understanding of the linear dependences between $\b{g}$-vectors.
+We use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
+Analogously to cluster algebras and gentle algebras, this height function is obtained by summing some compatibility degrees of wiggly arcs.
+Using the $\b{c}$-vectors of each pseudotriangulation, defined to form the dual basis of the $\b{g}$-vectors, we obtain our main result.
+
+\begin{theorem*}
+The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
+\begin{itemize}
+\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
+\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
+\end{itemize}
+\end{theorem*}
+
+Moreover, as for the classical permutahedron and associahedron, we recover our lattice structure by a suitable linear orientation of the graph of the wigglyhedron.
+
+\begin{proposition*}
+The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ (or equivalently, the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$) is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in a suitable direction.
+\end{proposition*}
+
+\para{Further topics}
+The wigglyhedron has interesting connections in lattice theory and discrete geometry.
+We first connect the wigglyhedron to the (type~$A$) Cambrian world.
+
+\begin{theorem*}
+For any~$\delta \in \{-,+\}^n$,
+\begin{itemize}
+\item the $\delta$-Cambrian lattice of~\cite{Reading-CambrianLattices} is an interval in the wiggly lattice~$\wigglyLattice_n$,
+\item the $\delta$-Cambrian fan of~\cite{ReadingSpeyer} is a link in the wiggly fan~$\wigglyFan_n$,
+\item the $\delta$-associahedron of~\cite{HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$.
+\end{itemize}
+\end{theorem*}
+
+We then define the wiggly complex~$\wigglyComplex_P$ of an arbitrary planar point set~$P$ (not necessarily along the horizontal axis, nor necessarily in general position).
+Our definition recovers:
+\begin{itemize}
+\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ colinear points,
+\item the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
+\end{itemize}
+
+\begin{conjecture*}
+For any point set~$P$ in the plane, the wiggly complex~$\wigglyComplex_P$ is the boundary complex of a simplicial polytope.
+\end{conjecture*}
+
+We also present a few open questions related to this conjecture, concerning in particular the possible interpretation of the wiggly complex~$\wigglyComplex_P$ in terms of dual pseudoline arrangements, and the extension to multi wiggly complexes and arbitrary finite Coxeter groups.
+
+\para{Categorical representation and stability conditions}
+
+\vincent{Asilata, the floor is yours...}
 
@@
 \end{definition}
+
+\begin{remark}
+\vincent{todo}
+\end{remark}
 
@@
 Hence, there is a linear map~$Z : \HH_n \to \HH_{2n}$ such that~$Z \big( \b{g}(d) \big) = \b{g} \big( \zeta(d) \big)$ for all diagonals~$d$ of the $\delta$-gon.
-This map is a normal equivalence from $\delta$-associahedron~$\Asso_\delta$ to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly~arcs.
+This map is a normal equivalence from the $\delta$-associahedron~$\Asso_\delta$ to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly~arcs.
 \end{proof}
@@
 
-Note that \cref{def:wigglyComplexPointSet} recovers two specific situations:
+Note that \cref{def:wigglyComplexPointSet} recovers two specific situations, namely
 \begin{itemize}
@@
 
-Note that it is not even clear from \cref{def:wigglyComplexPointSet} that the wiggly complex~$\wigglyComplex_P$ is a pure pseudomanifold (hence that the wiggly flip graph~$\wigglyFlipGraph_P$ is well-defined).
+Observe that it is not even clear from \cref{def:wigglyComplexPointSet} that the wiggly complex~$\wigglyComplex_P$ is a pure pseudomanifold (hence that the wiggly flip graph~$\wigglyFlipGraph_P$ is well-defined).
 However, we make the following ambitious conjecture.
@@
 
-Note that in \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
+In \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
 This raises in particular the following question.

### 2024-06-14 draft/wigglyhedra.tex
one more remark and some bibentries missing

@@
 We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
-Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinski-clusterAlgebrasI,FominZelevinski-clusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon}.
+Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
 Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.
@@
 
-\begin{remark}
-\vincent{todo}
-\end{remark}
-
 We consider sets of compatible wiggly arcs.
@@
 \end{definition}
+
+\begin{remark}
+We want to stress out the important difference between our wiggly dissections and the noncrossing arc diagrams of~\cite{Reading-arcDiagrams}.
+Our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
+However, for two arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints, while N.~Reading does the opposite in~\cite{Reading-arcDiagrams}.
+This results in very different objects.
+\end{remark}
 

### 2024-06-19 draft/wigglyhedra.tex
Updated abstract and intro.

@@
 \begin{abstract}
-Motivated by categorical representation theory and stability conditions, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
+  Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
 The wiggly complex is a pure pseudomanifold, whose facets are wiggly pseudotriangulations.
@@
 Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
-Finally, we develop the connections with categorical representation theory and stability conditions.
+Finally, we recall the correspondence of wiggly arcs with objects in a category.
+We develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
 \end{abstract}
@@
 
-\vincent{Start with one or two paragraphs on motivation from categories}
+In this paper we consider wiggly pseudotriangulations, which are built from arcs on a linear configuration of points.
+We study their combinatorics in detail, and interpret it in terms of categorical representation theory.
 
@@
 \begin{itemize}
-\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ colinear points,
+\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ collinear points,
 \item the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
@@
 
-\para{Categorical representation and stability conditions}
-
-\vincent{Asilata, the floor is yours...}
+\para{Categorical interpretation}
+Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the arcs.
+In fact, this correspondence holds for more general arcs, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
+
+A general arc can be decomposed into wiggly arcs simply by cutting along U-turns.
+We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
+\begin{proposition*}
+  Consider the set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc.
+  This set is contained in a face of the wiggly complex.
+\end{proposition*}
+Furthermore, we characterise categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
+\begin{proposition*}
+  Consider two wiggly arcs, and their corresponding objects in the abelian category.
+  The wiggly arcs are compatible if and only if there are no extensions between the corresponding objects.
+\end{proposition*}
 

### 2024-06-26 draft/wigglyhedra.tex
Finished proof of why both outside edges don't appear.

@@
 
-  \(T\) cannot contain both external edges because otherwise, the curve \(\alpha\) will not be able to have a second endpoint.\asilata{I am struggling to explain this, even though it should be obvious.}
+  Now suppose for contradiction that \(T\) contains both external edges.
+  Then some portion of \(\alpha\) curves around each of the extreme endpoints \(0\) and \(n+1\).
+  Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
+  These must then connect to each other, resulting in \(\alpha\) having a separate component that winds around the outside of the \(n+2\) points.
+  This is not possible because \(\alpha\) is a connected curve with two endpoints.
+  Therefore \(T\) cannot contain both external edges.
 \end{proof}

### 2024-06-26 draft/wigglyhedra.tex
Wrote a chunk of the proof of Ext-1 compatibility.

@@
 
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to grading shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
-
+The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to an overall grading and homological shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
 In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
-It is easy to check that the (minimal) intersection numbers between any two such segments counts the number of morphisms\asilata{Discuss (or choose to ignore) grading.} between the associated objects.
-In particular, the self-intersection number of a single segment is computed to be \(2\), as the second copy of the segment can be slightly deformed to be disjoint from the first copy except at the two endpoints.
-In fact, it is true for any pair of curves that its minimal intersection number is the number of morphisms between the associated objects~\cite[Lem.~4.11]{kho.sei:02}.
+Moreover, the minimal intersection number between any pair of curves is the number of morphisms between the associated objects~\cite[Prop.~4.9]{kho.sei:02}.
+In fact, the proposition in~\cite{kho.sei:02} is a stronger result: by considering \emph{bigraded curves}, we obtain \emph{bigraded intersection numbers} between the two associated objects.
+
 \asilata{Add picture of curve cutting.}
@@
 \begin{proof}
+  The proof follows from a specialisation of the bigraded intersection number calculations that appear in Sections 3 and 4 of~\cite{kho.sei:02}.
+  Let \(X\) and \(X'\) be objects in the standard heart that correspond to wiggly arcs \(\alpha\) and \(\alpha'\).
+  The bigraded intersection number as defined in~\cite[Sect.~3d]{kho.sei:02} between the curves \(\alpha\) and \(\alpha'\) is a polynomial in the variables \(q_1^{\pm}\), \(q_2^{\pm}\).
+  It follows from~\cite[Prop.~4.9]{kho.sei:02} that this bigraded intersection number equals
+  \begin{equation}
+    \label{eq:bigraded-homs}
+  \sum_{s_1,s_2}\dim(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1]))q_1^{s_1}q_2^{s_2}.    
+  \end{equation}
+  Note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes the object \(X\) in level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) in level \(s_1 - s_2\).
+  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\cref{eq:bigraded-homs}.
+
+  The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
   \asilata{TODO.}

### 2024-06-26 draft/wigglyhedra.tex
pictures curves

--- 2024-06-19 draft/wigglyhedra.tex
@@
 %\tikzexternalize
-\graphicspath{{figures/}{figures/nodes/}}
+\graphicspath{{figures/}}
 \makeatletter\def\input@path{{figures/}}\makeatother
@@
 \begin{abstract}
-  Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
+Motivated by categorical representation theory and stability conditions, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
 The wiggly complex is a pure pseudomanifold, whose facets are wiggly pseudotriangulations.
@@
 Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
-Finally, we recall the correspondence of wiggly arcs with objects in a category.
-We develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
+Finally, we develop the connections with categorical representation theory and stability conditions.
 \end{abstract}
@@
 
-In this paper we consider wiggly pseudotriangulations, which are built from arcs on a linear configuration of points.
-We study their combinatorics in detail, and interpret it in terms of categorical representation theory.
+In this paper, we introduce the wiggly complex and study it from different perspectives.
 
@@
 \begin{itemize}
-\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ collinear points,
+\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ colinear points,
 \item the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
@@
 
-\para{Categorical interpretation}
-Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the arcs.
-In fact, this correspondence holds for more general arcs, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
-
-A general arc can be decomposed into wiggly arcs simply by cutting along U-turns.
-We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
-\begin{proposition*}
-  Consider the set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc.
-  This set is contained in a face of the wiggly complex.
-\end{proposition*}
-Furthermore, we characterise categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
-\begin{proposition*}
-  Consider two wiggly arcs, and their corresponding objects in the abelian category.
-  The wiggly arcs are compatible if and only if there are no extensions between the corresponding objects.
-\end{proposition*}
+\para{Categorical representation and stability conditions}
+
+\vincent{Asilata, the floor is yours...}
 
@@
 
+\begin{figure}
+\centerline{
+	\includegraphics[scale=1.3]{curve1}
+	\qquad
+	\includegraphics[scale=1.3]{curve2}
+	\qquad
+	\includegraphics[scale=1.3]{curve3}
+}
+\caption{An illustration of the Khovanov--Seidel curve model.}
+\label{fig:curveModel}
+\end{figure}
+
 \vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}

### 2024-06-26 draft/wigglyhedra.tex
cleaning + some pagebreaks

--- 2024-06-26 draft/wigglyhedra.tex
@@
 
-%This problem arose from recent discussions with Asilata Bapat~\cite{BapatPilaud}.
-%It was originally motivated by her joint work with Anand Deopurkar and Anthony Licata on categorical representation theory and stability conditions, but it can be stated in purely combinatorial terms.
-
 In this paper we consider wiggly pseudotriangulations, which are built from arcs on a linear configuration of points.
-We study their combinatorics in detail, and interpret it in terms of categorical representation theory.
-
+We study their combinatorics in detail, construct polyhedral realizations of their flip graph, and interpret them in terms of categorical representation theory.
+
+\bigskip
 \para{Combinatorics}
@@
 
+\pagebreak
 We then connect wiggly pseudotriangulations to wiggly permutations.
@@
 
+\pagebreak
 \para{Categorical interpretation}
@@
 
-\newpage
 \section{Wiggly pseudotriangulations and wiggly permutations}
@@
 %
-\begin{figure}[h]
+\begin{figure}[b]
 \centerline{\includegraphics[scale=1.3]{incompatible}}
@@
 %
-\begin{figure}[b]
+\begin{figure}
 \centerline{\includegraphics[scale=1.5]{wigglyPseudodissections}}
@@
 
+\pagebreak
 \begin{remark}
@@
 \label{exm:specialWigglyPseudotriangulations}
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{specialWigglyPseudotriangulations}}
-\caption{The wiggly pseudotriangulations~$T_\downarrow$ (left), $T_\uparrow$ (middle left), $T_\leftarrow$ (middle right), and $T_\rightarrow$ (right) of \cref{exm:specialWigglyPseudotriangulations} for~$n = 7$.}
-\label{fig:specialWigglyPseudotriangulations}
-\end{figure}
 The following wiggly pseudotriangulations are illustrated in \cref{fig:specialWigglyPseudotriangulations}:
@@
 \end{align*}
+%
+\begin{figure}[h]
+\centerline{\includegraphics[scale=1.3]{specialWigglyPseudotriangulations}}
+\caption{The wiggly pseudotriangulations~$T_\downarrow$ (left), $T_\uparrow$ (middle left), $T_\leftarrow$ (middle right), and $T_\rightarrow$ (right) of \cref{exm:specialWigglyPseudotriangulations} for~$n = 7$.}
+\label{fig:specialWigglyPseudotriangulations}
+\end{figure}
 \end{example}
@@
 
+\pagebreak
 \begin{proposition}
@@
 
+\pagebreak
 \begin{proof}
@@
 
-\begin{table}
+\begin{table}[p]
 	\begingroup
+	\fontsize{10}{10.5}\selectfont
 	\setlength\arraycolsep{2pt}
@@
 	\begingroup
+	\fontsize{10}{10.5}\selectfont
 	\setlength\arraycolsep{1.1pt}
@@
 		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
+		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
 		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
@@
 
+\pagebreak
 \subsection{Wiggly fan}
@@
 %
-\begin{figure}[t]
+\afterpage{
+\begin{figure}
 \centerline{\input{wigglyhedron}}
@@
 \end{figure}
+}
 
@@
 
+\pagebreak
 \begin{theorem}
@@
 \subsection{The Khovanov--Seidel curve model}
+
+\begin{figure}
+\centerline{
+	\includegraphics[scale=1.3]{curve1}
+	\qquad
+	\includegraphics[scale=1.3]{curve2}
+	\qquad
+	\includegraphics[scale=1.3]{curve3}
+}
+\caption{An illustration of the Khovanov--Seidel curve model.}
+\label{fig:curveModel}
+\end{figure}
 

### 2024-06-27 draft/wigglyhedra.tex
More updates.

@@
 As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
-\begin{proposition}
+\begin{proposition}\label{prop:ext1}
   Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
   Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
+  More generally, the incompatibility degree \(\delta(\alpha,\alpha')\) as in~\cref{def:incompatibilityDegree} is the dimension of \(\Ext^1(X,X')\).
 \end{proposition}
@@
   The bigraded intersection number as defined in~\cite[Sect.~3d]{kho.sei:02} between the curves \(\alpha\) and \(\alpha'\) is a polynomial in the variables \(q_1^{\pm}\), \(q_2^{\pm}\).
-  It follows from~\cite[Prop.~4.9]{kho.sei:02} that this bigraded intersection number equals
+  It follows from~\cite[Prop.~4.9]{kho.sei:02} that this bigraded intersection number equals the Poincar{\'e} polynomial of the morphisms between \(X\) and \(X'\), namely the expression
   \begin{equation}
@@
   We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\cref{eq:bigraded-homs}.
-
     The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
-  \asilata{TODO.}
+
+However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
+So we must modify their argument slightly.
+In particular, the table in~\cite[Lemma 3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lemma 4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
+  \asilata{TODO: this is very tedious; how much to write it?}
 \end{proof}
 \begin{remark}
-  This proposition is similar to the condition of being compatible in a cluster-tilting object.
-  \asilata{Expand and make precise.}
+  \cref{prop:ext1} is very similar to the condition of being compatible in a cluster-tilting object of a cluster category (see, e.g.~\cite[Cor.~4.3]{bua.mar.rei.ea:06}).
+  However, it depends on shifting the objects \(X\) and \(X'\) so that they both lie in the standard heart, which is an auxiliary step that is not required in the case of cluster algebras.
 \end{remark}
 \begin{remark}
-  As stated, this proposition in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
+  As stated,~\cref{prop:ext1} in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
   For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two indecomposable spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
@@
 \begin{question}
-  How to best relate this section to the previous one purely categorically?
-  That is, given the categorical constraint on compatibility of arcs, is it also clear that it gives a constraint on objects appearing in the cohomology filtration?
-  \asilata{Make more precise.}
+  Suppose we have a collection of spherical objects in the standard heart \(\mathcal{A}_m\) that satisfy the compatibility condition of~\cref{prop:ext1}.
+  That is, the \(\Ext^1\) between any pair of objects in this collection is zero.
+  \begin{enumerate}
+  \item Can we prove properties about a maximal such collection without reference to arcs?
+  \item In particular, can we understand the combinatorics of maximal such collections without reference to arcs?
+  \item Given a maximal compatible collection of objects, can we always find a larger spherical object such that the factors of the cohomology filtration of that object are precisely shifts of the objects in the given collection?
+  \end{enumerate}
 \end{question}

### 2024-06-27 draft/wigglyhedra.tex
picture

@@
 \centerline{
+	\begin{tabular}{c@{\qquad}c@{\qquad}c}
+		Bounded homotopy category 
+		&
+		&
+		\\
+		of graded projective modules 
+		&
+		$\smash{\xrightarrow[\quad\text{combinatorial model}\quad]{}}$
+		&
+		curves
+		\\
+		over the zigzag algebra
+		&
+		&
+		\\
+		COMPLEX
+		&
+		&
 		\includegraphics[scale=1.3]{curve1}
-	\qquad
+		\\[.5cm]
+		cohomology $\Bigg\downarrow$ filtration
+		&
+		&
+		$\Bigg\downarrow$ cut
+		\\[.5cm]
+		Heart of the standard $t$-structure
+		&
+		$\xrightarrow[\quad\text{combinatorial model}\quad]{}$
+		&
+		wiggly arcs
+		\\
+		COMPLEX1
+		&
+		&
 		\includegraphics[scale=1.3]{curve2}
-	\qquad
+		\\
+		COMPLEX2
+		&
+		&
 		\includegraphics[scale=1.3]{curve3}		
+	\end{tabular}
 }
-\caption{An illustration of the Khovanov--Seidel curve model.}
+\caption{An illustration of the Khovanov--Seidel curve model and \cref{prop:cohomology-pieces}.}
 \label{fig:curveModel}
@@
 In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
-In fact, the procedure works on more general arcs as well --- namely, those that are not necessarily \(x\)-monotone.
+In fact, the procedure works on more general curves as well --- namely, those that are not necessarily \(x\)-monotone.
 
@@
 
+\begin{remark}
+Note that in \cref{def:wigglyComplex}, we adopted the convention that the faces of the wiggly complex contain none of the two external wiggly arcs.
+In contrast, the wiggly dissections of \cref{prop:hn-filtration} contain at most one of the two external wiggly arcs.
+Combinatorially, this is just the Cartesian product of the wiggly complex with an edge.
+\end{remark}
+
 %%%%%%%%%%%%
@@
 \begin{remark}
-  \cref{prop:ext1} is very similar to the condition of being compatible in a cluster-tilting object of a cluster category (see, e.g.~\cite[Cor.~4.3]{bua.mar.rei.ea:06}).
-  However, it depends on shifting the objects \(X\) and \(X'\) so that they both lie in the standard heart, which is an auxiliary step that is not required in the case of cluster algebras.
+  \cref{prop:ext1} is very similar to the condition of being compatible in a cluster-tilting object of a cluster category (see, \eg~\cite[Cor.~4.3]{bua.mar.rei.ea:06}) or in a $\tau$-tilting object (see, \eg~\cite{AdachiIyamaReiten}).
+  The condition in terms of crossings of curves already appears for some specializations (see, \eg~\cite{FominShapiroThurston, PaluPilaudPlamondon-surfaces}).
+  However, in \cref{prop:ext1}, it depends on shifting the objects~\(X\) and~\(X'\) so that they both lie in the standard heart, which is an auxiliary step that is not required in cluster-tilting and $\tau$-tilting theory.
 \end{remark}

### 2024-06-28 draft/wigglyhedra.tex
Updated figure and writeup about arcs.

@@
 Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the arcs.
-In fact, this correspondence holds for more general arcs, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
-
-A general arc can be decomposed into wiggly arcs simply by cutting along U-turns.
+In fact, this correspondence holds for more general curves, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
+
+A general curve can be decomposed into wiggly arcs simply by cutting along U-turns.
 We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
@@
 	\begin{tabular}{c@{\qquad}c@{\qquad}c}
-		Bounded homotopy category 
+		Spherical objects in bounded 
 		&
@@
 		\\
-		of graded projective modules 
+		homotopy category of graded projective 
 		&
@@
 		&
-		curves
+		Curves
 		\\
-		over the zigzag algebra
+		modules over the zigzag algebra
 		&
@@
                 \\
-		COMPLEX
+          \begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
+                                  \&           \& P_3 \langle -1 \rangle\arrow{dr} \& \\
+                                  \&           \&                      \& P_2\\
+            P_1\langle -5 \rangle\arrow{r}    \& P_1\langle -3 \rangle\arrow{r}   \& P_1 \langle -1 \rangle\arrow{ur} \& 
+          \end{tikzcd}
 		&
@@
 		\\[.5cm]
-		cohomology $\Bigg\downarrow$ filtration
+		{\scriptsize cohomology} $\Bigg\downarrow$ {\scriptsize filtration}
 		&
 		&
-		$\Bigg\downarrow$ cut
+		$\Bigg\downarrow$ {\scriptsize cut}
 		\\[.5cm]
@@
 		&
-		wiggly arcs
+		Wiggly arcs
 		\\
-		COMPLEX1
+          \begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
+            P_1\langle -1 \rangle \arrow{dr}\& \\
+            \& P_2 \\
+            P_3 \langle -1 \rangle \arrow{ur}
+          \end{tikzcd}
 		&
@@
           \\
-		COMPLEX2
+          \(P_1\)
+
 		&
@@
 In addition to the wiggly arcs, consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-For convenience, we refer to such an isotopy class as an \defn{arc}.
+For convenience, we refer to such an isotopy class as a \defn{curve}.
 
@@
 \begin{proposition}\label{prop:cohomology-pieces}
-  Let \(\alpha\) be any arc, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
+  Let \(\alpha\) be any curve, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
   Recall that for any integer \(j\), the cohomology object \(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
@@
     In this case, \(H^j(X) \neq 0\) for exactly one \(j\), such that \(X \cong H^j(X)[-j]\).
-  \item If \(\alpha\) is a general arc, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical indecomposable object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
+  \item If \(\alpha\) is a general curve, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical indecomposable object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
   \end{enumerate}
@@
 \begin{proof}
-  Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) arc \(\alpha\).
+  Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) curve \(\alpha\).
   The results of~\cite{kho.sei:02} imply that \(X\) is spherical and indecomposable.
@@
 \begin{proof}
-  The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of arcs on the disk with marked points.
+  The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of curves on the disk with marked points.
   Let \(X_1, \ldots, X_k\) be the objects in \(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
@@
 
-  Recall that \(\beta\) and \(\beta'\) are two pieces of the arc \(\alpha\).
+  Recall that \(\beta\) and \(\beta'\) are two pieces of the curve \(\alpha\).
   Therefore \(\beta\) and \(\beta'\) cannot cross, because~\(\alpha\) does not cross itself.
@@
   \end{enumerate}
-  It is clear that none of these possibilities can occur within the arc \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
+  It is clear that none of these possibilities can occur within the curve \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
   Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.
@@
   \begin{enumerate}
-  \item Can we prove properties about a maximal such collection without reference to arcs?
-  \item In particular, can we understand the combinatorics of maximal such collections without reference to arcs?
+  \item Can we prove properties about a maximal such collection without reference to curves?
+  \item In particular, can we understand the combinatorics of maximal such collections without reference to curves?
   \item Given a maximal compatible collection of objects, can we always find a larger spherical object such that the factors of the cohomology filtration of that object are precisely shifts of the objects in the given collection?
@@
 
-%%% Local variables:
-%%% TeX-command-extra-options: "-pvc"
-%%% End:
+% Local Variables:
+% TeX-command-extra-options: "-pvc"
+% End:

### 2024-07-02 draft/wigglyhedra.tex
Finished categorical section, more or less.

@@
 \end{proof}
-
 %%%%%%%%%%%%
@@
 
-\begin{remark}
+\begin{remark}\label{rem:incompatibility-deg}
 Note that~$\delta$ is indeed an incompatibility degree in the sense that
@@
 
-\vincent{Add a picture summarizing this section... Asilata drafts it, I will make it.}
 In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
@@
 The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to an overall grading and homological shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
+We illustrate this correspondence and~\cref{prop:cohomology-pieces} in~\cref{fig:curveModel}.
 In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
@@
 In fact, the proposition in~\cite{kho.sei:02} is a stronger result: by considering \emph{bigraded curves}, we obtain \emph{bigraded intersection numbers} between the two associated objects.
-
-\asilata{Add picture of curve cutting.}
 
@@
 However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
-So we must modify their argument slightly.
+So we have to modify the gradings when we construct the complexes, and thus the morphisms that now have level one change as well.
 In particular, the table in~\cite[Lemma 3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lemma 4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
-  \asilata{TODO: this is very tedious; how much to write it?}
+
+It can be checked that under the modified grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non-pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
+Morphisms arising from other intersections do not contribute to \(\Ext^1\).
+This calculation proves the proposition.
 \end{proof}
@@
 \end{remark}
+
+Recall from~\cref{rem:incompatibility-deg} that two arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
+Recall from~\cref{prop:uerp} the arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
+Finally, recall from~\cref{lem:linearDependences} that the \(g\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
+Let us interpret this dependince categorically.
+
+Let \(X\) and \(X'\) be spherical objects in the standard heart that correspond to \(\alpha\) and \(\alpha'\) respectively.
+First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
+Next, let us understand \(\beta\) and \(\beta'\) categorically.
+\begin{proposition}\label{prop:extensions}
+  Let \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\) be as just discussed.
+  Let \(Y\) and \(Y'\) be the objects in the standard heart corresponding to \(\beta\) and \(\beta'\) respectively.
+\begin{itemize}
+\item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
+  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0.\]
+\item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
+  \[0 \to X' \to (Y \oplus Y') \to X \to 0.\]
+\end{itemize}
+\end{proposition}
+\begin{proof}
+  The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
+  We do not reproduce the proof here, as the argument is contained in the proof of Theorem 5.5 in~\cite{tho:06}.
+  (See also~\cite[Figure 4]{tho:06}.)
+\end{proof}
+Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(g\)-vectors in~\cref{lem:linearDependences}.
+More precisely, we have that
+\begin{itemize}
+\item if \(\alpha\) and \(\alpha'\) are not pointed, then
+  \([Y] = [X] + [X'] = [Y']\),
+  from which we see \([X] + [X'] = ([Y] + [Y'])/2\);
+\item if \(\alpha\) and \(\alpha'\) are crossing, then
+  \([X] + [X'] = [Y] + [Y'].\)
+\end{itemize}
+This suggests that there should be a way to construct the \(g\)-vectors categorically in such a way that the \(g\)-vectors also map to the Grothendieck group of the category.
+At the moment, we do not have a concise construction of the \(g\)-vectors purely categorically, and it would be interesting to find this.
+
 \begin{question}
@@
 We are grateful to the organizers Bérénice Delcroix-Oger, Peter Feller, Vincent Florens, Hoel Queffelec for this fruitful event.
+We thank Anand Deopurkar and Anthony M. Licata for many useful conversations and ideas.
 

### 2024-07-04 draft/wigglyhedra.tex
minor changes

@@
 \label{conj:Hamiltonian}
-The cover graph of the wiggly lattice~$\wigglyLattice_n$ is Hamiltonian.
+The cover graph of the wiggly lattice~$\wigglyLattice_n$ admits an Hamiltonian path (or even cycle).
 \end{conjecture}
@@
 Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
-\vincent{Ask Aaron what he prefers here...}
 
@@
 
+\afterpage{
 \begin{figure}
@@
 		&
-		\includegraphics[scale=1.3]{curve1}
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve1}}
 		\\[.5cm]
@@
           	&
-		\includegraphics[scale=1.3]{curve2}
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve2}}
 		\\
 		\(P_1\)
-
 		&
 		&
-		\includegraphics[scale=1.3]{curve3}		
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve3}	}
 	\end{tabular}
@@
   Note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes the object \(X\) in level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) in level \(s_1 - s_2\).
-  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\cref{eq:bigraded-homs}.
+  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\ref{eq:bigraded-homs}.
     The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
@@
 First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
-Next, let us understand \(\beta\) and \(\beta'\) categorically.
+Next, let us understand~\(\beta\) and \(\beta'\) categorically.
 \begin{proposition}\label{prop:extensions}

### 2024-07-08 draft/wigglyhedra.tex
change g- to \b{g}-

@@
 Recall from~\cref{prop:uerp} the arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
-Finally, recall from~\cref{lem:linearDependences} that the \(g\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
+Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
 Let us interpret this dependince categorically.
@@
 \end{proof}
-Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(g\)-vectors in~\cref{lem:linearDependences}.
+Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(\b{g}\)-vectors in~\cref{lem:linearDependences}.
 More precisely, we have that
@@
 \end{itemize}
-This suggests that there should be a way to construct the \(g\)-vectors categorically in such a way that the \(g\)-vectors also map to the Grothendieck group of the category.
-At the moment, we do not have a concise construction of the \(g\)-vectors purely categorically, and it would be interesting to find this.
+This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
+At the moment, we do not have a concise construction of the \(\b{g}\)-vectors purely categorically, and it would be interesting to find this.
 

### 2024-07-10 draft/wigglyhedra.tex
minor corrections introduction

@@
 
-\thanks{AB was partially supported by the Australin Research Council DECRA grant DE240100447. 
+\thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
   VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}
@@
 Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
-Finally, we recall the correspondence of wiggly arcs with objects in a category.
-We develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
+Finally, we recall the correspondence of wiggly arcs with objects in a category, and we develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
 \end{abstract}
@@
 \para{Combinatorics}
-Fix $n \ge 2$ and consider the~$n+2$ points on the horizontal axis at abscissa~${0, \dots, n+1}$.
+Fix $n \ge 1$ and consider the~$n+2$ points on the horizontal axis labelled~${0, \dots, n+1}$.
 A \defn{wiggly arc} is an abscissa monotone curve starting at some point~$i$, ending at some point~$j$ (with~${0 \le i < j \le n+1}$), and passing above or below each point~$i+1, \dots, j-1$.
-Two wiggly arcs are \defn{compatible} if they are pointed (the left endpoint of one is not the right endpoint of the other) and non-crossing (the interior of the curve are disjoint).
+Two wiggly arcs are \defn{compatible} if they are pointed (the left endpoint of one is not the right endpoint of the other) and non-crossing (the interiors of the curves are disjoint).
 A \defn{wiggly dissection} is a collection of pairwise compatible wiggly arcs, and a \defn{wiggly pseudotriangulation} is an inclusion maximal wiggly dissection.
@@
 \begin{proposition*}
-The wiggly complex~$\wigglyComplex_n$ is a pure closed pseudomanifold of dimension~$2n-1$.
+The wiggly complex~$\wigglyComplex_n$ is a $(2n-1)$-dimensional pseudomanifold without boundary.
 \end{proposition*}
@@
 We also orient this flip graph in a canonical way, which we call the \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$.
-The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper.
+The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper (throughout the paper, we implicitly orient the graphs from bottom to top).
 
@@
 We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
-Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} for finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
+Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing} of support $\tau$-tilting complexes~\cite{AdachiIyamaReiten} on gentle algebras~\cite{ButlerRingel}.
 Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.
@@
 The proof of this result is based on a fine understanding of the linear dependences between $\b{g}$-vectors.
-We use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
-Analogously to cluster algebras and gentle algebras, this height function is obtained by summing some compatibility degrees of wiggly arcs.
+We further use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
+Without entering the details of its definition of~$\kappa$, let us just mention that it is obtained by summing some compatibility degrees of wiggly arcs, analogously to the constructions for cluster algebras~\cite{HohlwegPilaudStella} and gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
 Using the $\b{c}$-vectors of each pseudotriangulation, defined to form the dual basis of the $\b{g}$-vectors, we obtain our main result.
@@
 We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
+
 \begin{proposition*}
-  Consider the set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc.
-  This set is contained in a face of the wiggly complex.
+The set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc is a face of the wiggly complex.
 \end{proposition*}
-Furthermore, we characterise categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
+
+Furthermore, we characterize categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
+
 \begin{proposition*}
-  Consider two wiggly arcs, and their corresponding objects in the abelian category.
-  The wiggly arcs are compatible if and only if there are no extensions between the corresponding objects.
+Two wiggly arcs are compatible if and only if there are no extensions between the corresponding objects in the abelian category.
 \end{proposition*}

### 2024-07-10 draft/wigglyhedra.tex
proofreading and improving Section 2

@@
 \begin{abstract}
-  Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on the horizontal axis, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
-The wiggly complex is a pure pseudomanifold, whose facets are wiggly pseudotriangulations.
+  Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on a line, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
+The wiggly complex is a $(2n-1)$-dimensional pseudomanifold, whose facets are wiggly pseudotriangulations.
 We show that wiggly pseudotriangulations are in bijection with wiggly permutations, which are permutations of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
@@
 
-In this paper we consider wiggly pseudotriangulations, which are built from arcs on a linear configuration of points.
+In this paper we consider wiggly pseudotriangulations, which are built from arcs wiggling around points on a line.
 We study their combinatorics in detail, construct polyhedral realizations of their flip graph, and interpret them in terms of categorical representation theory.
@@
 
-\pagebreak
 We then connect wiggly pseudotriangulations to wiggly permutations.
@@
 \para{Categorical interpretation}
-Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the arcs.
+Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the wiggly arcs.
 In fact, this correspondence holds for more general curves, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
@@
 
+\enlargethispage{.5cm}
 Fix an integer~$n \ge 1$.
@@
 We start with wiggly pseudodissections of $n+2$ points on a line.
-The following definitions are illustrated in \cref{fig:incompatible}.
+The following two definitions are illustrated in \cref{fig:incompatible}.
 
@@
 \end{definition}
+
+\begin{remark}
+\label{rem:numberWigglyArcs}
+The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell)$.
+\end{remark}
 
@@
 
-We consider sets of compatible wiggly arcs.
-The following definitions are illustrated~in~\cref{fig:pseudodissections}.
+\begin{remark}
+We want to stress out that our notion of compatibility on wiggly arcs of \cref{def:compatible} fundamentally differs from the notion of compatibility used by N.~Reading to define noncrossing arc diagrams~\cite{Reading-arcDiagrams}.
+Namely, our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
+However, for two wiggly arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints, while N.~Reading does precisely the opposite in~\cite{Reading-arcDiagrams}.
+This results in very different objects.
+\end{remark}
+
+We consider pairwise compatible sets of wiggly arcs.
+The following two definitions are illustrated~in~\cref{fig:pseudodissections}.
 
@@
 
-\begin{remark}
-We want to stress out the important difference between our wiggly dissections and the noncrossing arc diagrams of~\cite{Reading-arcDiagrams}.
-Our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
-However, for two arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints, while N.~Reading does the opposite in~\cite{Reading-arcDiagrams}.
-This results in very different objects.
-\end{remark}
-
-%\vincent{Here, I am using the fact that a set of pairwise non-crossing arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
+%\vincent{Here, I am using the fact that a set of pairwise non-crossing wiggly arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
 
@@
 A wiggly pseudodissection~$D$ decomposes the digon bounded by~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ into cells, that we call \defn{wiggly cells}.
-The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
-A point~$p$ on the external boundary of~$c$ is a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if~$c$ covers less (resp.~more) than half of any small disc centered at~$p$.
+The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of wiggly arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
+Two consecutive wiggly arcs along the boundary of~$c$ define a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$.
 %The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
@@
 Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
-Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$\gamma=\iota+\kappa-n$.
+Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$n - \iota + \gamma = \kappa$.
 Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = \gamma+n$.
-We conclude that~$\gamma \le n$ and~$\iota = \gamma-\kappa+n \le 2n-1$.
+As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
+We conclude that~$\gamma \le n$ and~$\iota = n+\gamma-\kappa \le 2n-1$.
 
@@
 For any wiggly cell~$c$, we have~$\delta_c = 3$, so that~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}, hence~$2 = \beta_c/2+\kappa_c-1$.
-Therefore~$\kappa = 1$ ($D$ is connected) and~$2\gamma = \iota+1 = \gamma+n$, so that~$\gamma=n$.
+Therefore~$\kappa = 1$ ($D$ is connected) and~$2\gamma = \iota+1 = n+\gamma$, so that~$\gamma=n$.
 
 \para{(ii) $\Rightarrow$ (iii)}
-As $\gamma=n$ and~$\kappa=1$, we have~$\iota = \gamma+n-\kappa = 2n-1$.
+As $\gamma=n$ and~$\kappa=1$, we have~$\iota = n+\gamma-\kappa = 2n-1$.
 
@@
 Let~$\gamma \eqdef (k, \ell, X, Y)$ denote the uppermost wiggly arc of the boundary of~$c$ such that~$j \in Y$ (it exists since~$j$ is a  hinge of~$c$), and let~$X' \eqdef {]j,\ell[} \cap X$ and~$Y' \eqdef {]j,\ell[} \cap Y$.
-Then the two wiggly arcs~$\beta \eqdef \big( i, \ell, A \cup X', B \cup \{j\} \cup Y')$ and~$\beta' \eqdef \big( i', \ell, A'  \cup \{j\} \cup X', B \cup Y')$ are both compatible with~$D$ (any arc incompatible with~$\beta$ is incompatible with~$\alpha$ or~$\gamma$, and similarly for~$\beta'$) and cannot both belong to~$D$ (otherwise, $c$ would be a wiggly pseudotriangle bounded by~$\alpha, \alpha', \gamma', \gamma$).
+Then the two wiggly arcs~$\beta \eqdef \big( i, \ell, A \cup X', B \cup \{j\} \cup Y')$ and~$\beta' \eqdef \big( i', \ell, A'  \cup \{j\} \cup X', B \cup Y')$ are both compatible with~$D$ (any wiggly arc incompatible with~$\beta$ is incompatible with~$\alpha$ or~$\gamma$, and similarly for~$\beta'$) and cannot both belong to~$D$ (otherwise, $c$ would be a wiggly pseudotriangle bounded by~$\alpha, \alpha', \gamma', \gamma$).
 \end{proof}
@@
 \begin{example}
+\label{exm:allSmallWigglyPseudotriangulations}
 For~$n = 1$, the $2$ wiggly pseudotriangulations of $3$ points are \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation1}}} and \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation2}}}.
@@
 \end{example}
+
+\begin{remark}
+\label{rem:numberWigglyPseudotriangulations}
+The number~$wp_n$ of wiggly pseudotriangulations of~$n+2$ points is given by
+\[
+\begin{array}{c|ccccccccc}
+n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
+\hline
+wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
+\end{array}
+\]
+To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ \defn{final} internal wiggly arcs (\ie ending at the last point~$n+1$).
+For instance,
+\begin{align*}
+%	wp_0(x) & = 1, \\
+	wp_1(x) & = x + 1, \\
+	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
+	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
+\end{align*}
+We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPseudotriangulations}.
+We use this additional variable~$x$ to obtain a recursive formula for~$wp_n(x)$.
+%Indeed, any wiggly pseudotriangulation on~$n+1$ points can be obtained from a wiggly pseudotriangulation on~$n+2$ points by collapsing the points~$n$ and~$n+1$.
+Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting its wiggly pseudotriangle with a hinge at~$n$.
+%There are two kinds of wiggly pseudotriangulations of~$n+2$ points:
+%\begin{itemize}
+%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
+%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
+%\end{itemize}
+Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to
+\begin{itemize}
+\item $i+2$ wiggly pseudotriangulations of~$n+2$ points with $i+2$ final internal wiggly arcs, containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,
+\item $j+1$ wiggly pseudotriangulations of~$n+2$ points with $j$ final internal wiggly arcs, not containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,  for all~$0 \le j \le i+1$.
+\end{itemize}
+\pagebreak
+This translates to the recursive formula %for all~$n \ge 1$,
+\begin{align*}
+wp_{n}(x) & = \overbracket[.5pt]{x \cdot \frac{\partial}{\partial x} \big( x^2 wp_{n-1}(x) \big)}^{\substack{\text{wiggly pseudotriangulations} \\ \text{containing } (n, n+1, \varnothing, \varnothing)}} + \overbracket[.5pt]{\frac{\partial}{\partial x}\Big( \smash{\frac{wp_{n-1}(1)-x^3wp_{n-1}(x)}{1-x}} \Big)}^{\substack{\qquad\; \text{wiggly pseudotriangulations} \qquad\;  \\ \text{not containing } (n, n+1, \varnothing, \varnothing)}} \\
+& = \frac{1}{(1 - x)^2} \big( wp_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) wp_{n-1}(x) + x^4 (x - 1) wp_{n-1}’(x) \big).
+\end{align*}
+This enables to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
+%This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
+%\[
+%\sum_{n \ge 0} wp_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
+%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
+%\dots
+%\]
+\end{remark}
+
+Our next statement prepares for the definition of flips in wiggly pseudotriangulations.
 
@@
 \label{def:wigglyFlipGraph}
-The \defn{wiggly flip graph}~$\wigglyFlipGraph_n$ is the graph with a vertex for each wiggly pseudotriangulation, and with an edge between two wiggly pseudotriangulations~$T,T'$ if there are wiggly arcs~$\alpha \in T$ and~$\alpha' \in T'$ such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
+The \defn{wiggly flip graph}~$\wigglyFlipGraph_n$ is the graph with a vertex for each wiggly pseudotriangulation, and with an edge between two wiggly pseudotriangulations~$T$ and~$T'$ if there are wiggly arcs~$\alpha \in T$ and~$\alpha' \in T'$ such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
 \end{definition}
 
-\pagebreak
 \begin{proposition}
 \label{prop:wigglyFlipGraph}
-The wiggly flip graph~$\wigglyFlipGraph_n$ is regular of degree~$2n-1$.
+The wiggly flip graph~$\wigglyFlipGraph_n$ is regular of degree~$2n-1$ and connected.
 \end{proposition}
@@
 We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
+This shows that any internal wiggly arc in any wiggly pseudotriangulation can be flipped, hence that the wiggly flip graph is regular of degree~$2n-1$ by \cref{prop:wigglyPseudotriangulations}\,(iii).
+
+There are various possible proofs for the connectiveness.
+For instance, it will follow easily from \cref{prop:bijection}.
+To avoid to rely on this forward reference, we sketch an alternative direct proof by induction on~$n$.
+We claim that if a wiggly pseudotriangulation has some final internal wiggly arcs (\ie ending at the last point~$n+1$), then at least one of them can be flipped to a non-final wiggly arc.
+This implies that any wiggly pseudotriangulation can be transformed by flips to a wiggly pseudotriangulation with no final internal wiggly arc.
+The wiggly pseudotriangulations with no final internal wiggly arc all contain the arcs~$(0,n,\varnothing,[n-1])$ and~$(0,n,[n-1],\varnothing)$ (as the latter are compatible with all internal wiggly arcs but the final ones),
+Hence, they induce a subgraph of~$\wigglyFlipGraph_n$ isomorphic to~$\wigglyFlipGraph_{n-1}$, which is connected by induction.
+We conclude that~$\wigglyFlipGraph_n$ is itself connected.
+
+To see the claim, 
+\vincent{todo}
 \end{proof}
@@
 \centerline{\includegraphics[scale=1.3]{incompatible2}}
-\caption{The arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
+\caption{The wiggly arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
 \label{fig:incompatible2}
@@
 \end{itemize}
-The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and a edge for each increasing~flip.
+The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and an edge for each increasing~flip.
 \end{definition}
@@
 \begin{proposition}
-The wiggly complex~$\wigglyComplex_n$ is a flag pure $(2n-1)$-dimensional pseudomanifold without boundary.
+The wiggly complex~$\wigglyComplex_n$ is a flag $(2n-1)$-dimensional pseudomanifold without boundary.
 \end{proposition}
@@
 \end{align*}
-\end{remark}
-
-\begin{remark}
-Note that the number of vertices of~$\wigglyComplex_n$ is the number~$\sum_{j = 0}^n 2^j (n+1-j)$ of wiggly arcs on~$n+2$ points.
-The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
-For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal wiggly arcs ending at the last point~$n+1$.
-For instance,
-\begin{align*}
-	f_0(x) & = 1, \\
-	f_1(x) & = x + 1, \\
-	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-	f_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-\end{align*}
-We use this additional variable~$x$ to obtain a recursive formula for~$f_n(x)$, discussing on the wiggly pseudotriangle~$t_n$ with a hinge at~$n$.
-Namely, there are two types of wiggly pseudotriangulations of~$n+2$ points:
-\begin{itemize}
-\item those with the arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
-\item those without the arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
-\end{itemize}
-Hence we obtain for all~$n \ge 1$,
-\[
-f_{n}(x) = \frac{1}{(1 - x)^2} \big( f_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) f_{n-1}(x) + x^4 (x - 1) f_{n-1}’(x) \big).
-\]
-This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
-\[
-\sum_{n \ge 0} f(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
-% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
-\dots
-\]
-\end{remark}
+Note that the number of vertices and facets of~$\wigglyComplex_n$ were already discussed in \cref{rem:numberWigglyArcs,rem:numberWigglyPseudotriangulations}.
+\end{remark}
+
+%\begin{remark}
+%Note that the number of vertices of~$\wigglyComplex_n$ is the number~$\sum_{j = 0}^n 2^j (n+1-j)$ of wiggly arcs on~$n+2$ points.
+%The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
+%For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal wiggly arcs ending at the last point~$n+1$.
+%For instance,
+%\begin{align*}
+%	f_0(x) & = 1, \\
+%	f_1(x) & = x + 1, \\
+%	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+%	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
+%	f_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
+%\end{align*}
+%We use this additional variable~$x$ to obtain a recursive formula for~$f_n(x)$, discussing on the wiggly pseudotriangle~$t_n$ with a hinge at~$n$.
+%Namely, there are two types of wiggly pseudotriangulations of~$n+2$ points:
+%\begin{itemize}
+%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
+%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
+%\end{itemize}
+%Hence we obtain for all~$n \ge 1$,
+%\[
+%f_{n}(x) = \frac{1}{(1 - x)^2} \big( f_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) f_{n-1}(x) + x^4 (x - 1) f_{n-1}’(x) \big).
+%\]
+%This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
+%\[
+%\sum_{n \ge 0} f_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
+%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
+%\dots
+%\]
+%\end{remark}
 
@@
 \centerline{\includegraphics[scale=1.3]{incompatible3}}
-\caption{The arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
+\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
 \label{fig:incompatible3}
@@
 \begin{example}
-The wiggly permutations of~$[2]$ are~$12$ and~$21$.
-The wiggly permutations of~$[4]$ are
+\label{exm:allSmallWigglyPermutations}
+For~$n = 1$, the $2$ wiggly permutations of~$[2]$ are~$12$ and~$21$.
+For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
 \[
@@
 \begin{remark}
-The numbers of wiggly permutations are given by
+\label{re:nuberWigglyPermutations}
+The number~$wp_n$ of wiggly permutations of~$[2n]$ is given by
 \[
@@
 \hline
-|\wigglyLattice_n| & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
+wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
 \end{array}
 \]
+To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ with~$2j$ before~$\gamma$ before~$2j-1$).
+For instance,
+\begin{align*}
+%	wp_0(x) & = 1, \\
+	wp_1(x) & = x + 1, \\
+	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
+	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
+\end{align*}
+We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPermutations}.
+Any wiggly permutation of~$[2n]$ can be obtained from a wiggly permutation of~$[2n-2]$ by inserting the last values~$2n-1$ and~$2n$.
+Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to
+\begin{itemize}
+\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps where~$2j-1$ appears before~$2j$ (they must appear consecutively),
+\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs where $2j$ appears before~$2j-1$, for all~$0 \le j \le i+1$.
+\end{itemize}
+We thus obtain the same recursive equation on~$wp_n(x)$ as in \cref{rem:numberWigglyPseudotriangulations}.
 \end{remark}
@@
 \begin{proof}
-Immediate as it precisely corresponds to the pattern avoidance description.
+Immediate as it corresponds to the pattern avoidance description of \cref{def:wigglyPermutation}.
 \end{proof}
@@
 
-\pagebreak
 \begin{proof}
-Consider two wiggly permutations~$\rho, \sigma$ of~$[2n]$, and let~$\tau = \rho \join \sigma$.
+Consider two wiggly permutations~$\rho$ and~$\sigma$ of~$[2n]$, and let~$\tau = \rho \join \sigma$.
 Assume that there is~$1 \le i < 2j-1 < 2n$ such that~$(2j-1, i) \in \inv(\tau)$.
@@
 \begin{proposition}
-Each wiggly permutation~$\sigma$ covers (resp.~is covered by) as many wiggly permutations as its number of descents (resp.~ascents), so that the cover graph of~$\wigglyLattice_n$ is regular of degree~$2n-1$.
+Each wiggly permutation~$\sigma$ covers (resp.~is covered by) as many wiggly permutations as its number of descents (resp.~ascents).
+Hence, the cover graph of~$\wigglyLattice_n$ is regular of degree~$2n-1$ and connected.
 \end{proposition}
@@
 
-We close this section by the following conjecture (checked computationally up to~$n = 3$).
-
-\begin{conjecture}
-\label{conj:Hamiltonian}
-The cover graph of the wiggly lattice~$\wigglyLattice_n$ admits an Hamiltonian path (or even cycle).
-\end{conjecture}
-
-Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
-
 %%%%%%%%%%%%
@@
 \begin{proposition}
+\label{prop:bijection}
 The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a directed graph isomorphism between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
@@
 Using the notations of \cref{def:bijection2}, this implies that~$i < j$ and that~${]i,j[} = A \sqcup B$, so that~$\alpha(\sigma,k) \eqdef (i, j, A, B)$ is indeed a wiggly arc for each~$k \in [2n-1]$.
-By~\cref{prop:wigglyPseudotriangulations}, it thus suffices to check that for each \(k \neq k'\) in \([2n-1]\), the arcs 
+By~\cref{prop:wigglyPseudotriangulations}, it thus suffices to check that for each \(k \neq k'\) in \([2n-1]\), the wiggly arcs 
 \(\alpha(\sigma,k)\) and~\(\alpha(\sigma,k')\) are distinct and compatible.
@@
 Similarly, \(j \neq i'\).
-Hence, the two arcs are pointed.
-To check that the arcs are non-crossing, we show $(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) = \varnothing$.
+Hence, the two wiggly arcs are pointed.
+To check that the wiggly arcs are non-crossing, we show that~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) = \varnothing$.
 Indeed~$A \cap B' = \varnothing$ since~$A \subseteq A'$ because~$\sigma([k]) \subseteq \sigma([k'])$.
@@
 \end{itemize}
-It follows that in the wiggly pseudotriangulation~\(\Psi(\sigma)\), the arc \(\alpha(\sigma, k)\) is precisely the arc lying immediately above the angle labelled by~\(\sigma(k)\).
+It follows that in the wiggly pseudotriangulation~\(\Psi(\sigma)\), the wiggly arc \(\alpha(\sigma, k)\) is precisely the wiggly arc lying immediately above the angle labelled by~\(\sigma(k)\).
 Therefore, we have~\(\Phi(\Psi(\sigma)) = \sigma\).
@@
 Conversely, let \(T\) be a wiggly pseudotriangulation, so that \(\sigma = \Phi(T)\) is a wiggly permutation.
-Then for any \(k \in [2n-1]\), the arc immediately above the angle of~$T$ labelled by~$\sigma(k)$ is precisely the one constructed as~\(\alpha(\sigma, k)\).
+Then for any \(k \in [2n-1]\), the wiggly arc immediately above the angle of~$T$ labelled by~$\sigma(k)$ is precisely the one constructed as~\(\alpha(\sigma, k)\).
 This shows that \(\Psi(\Phi(T)) = T\).
@@
 Finally, consider a cover relation~$\sigma \lessdot \sigma^j$ in the wiggly lattice~$\wigglyLattice_n$ as described in~\cref{lem:wigglyCoverRelation}.
-Using the notations of~\cref{lem:wigglyCoverRelation}, bserve that
+Using the notations of~\cref{lem:wigglyCoverRelation}, observe that
 \begin{itemize}
@@
 Hence, $\Psi(\sigma) \ssm \{\alpha(\sigma, j)\} = \Psi(\sigma^j) \ssm \{\alpha(\sigma^j, j)\}$.
-This implies that~$\Psi$ is a morphism of directed graph from the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ to the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$.
+This implies that~$\Psi$ is a directed graph morphism from the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ to the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$.
 As the underlying undirected graphs are both regular of degree~$2n-1$, we conclude that~$\Phi$ and~$\Psi$ induce directed graph isomorphisms between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
@@
 \end{remark}
+
+\begin{remark}
+The map~$\Phi$ sends wiggly pseudotriangulations with $i$ internal wiggly arcs adjacent to the last point~$n+1$ to wiggly permutations with $i$ admissible gaps, explaining the similarities in the counting arguments of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
+\end{remark}
+
+%%%%%%%%%%%%
+
+\subsection{Graph properties}
+\label{subsec:graphProperties}
+
+We close this section by the following conjecture (checked computationally up to~$n = 3$).
+
+\begin{conjecture}
+\label{conj:Hamiltonian}
+The cover graph of the wiggly lattice~$\wigglyLattice_n$ admits an Hamiltonian path (or even cycle).
+\end{conjecture}
+
+Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
 
@@
 \label{prop:characterizationFan}
-Consider a closed simplicial $(d-1)$-dimensional pseudomanifold~$\Delta$ with ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
+Consider a simplicial $(d-1)$-dimensional pseudomanifold~$\Delta$ without boundary on a ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
 Then the collection of cones~$\set{\R_{\ge 0}\b{R}_\triangle}{\triangle \in \Delta}$ forms a complete simplicial fan of~$\R^d$ if and~only~if
@@
 \centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $4$ times the $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
+The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
 The colors of the columns match the colors of the wiggly arcs.}
@@
 	\begingroup
-	\fontsize{10}{10.5}\selectfont
+	\fontsize{10}{10}\selectfont
 	\setlength\arraycolsep{2pt}
@@
 \end{itemize}
-The tedious proof of this description is not needed in this paper.
+The tedious proof of this description is not needed in this paper as we will only use the dual basis property.
 \end{remark}
@@
 	\begingroup
-	\fontsize{10}{10.5}\selectfont
+	\fontsize{10}{10}\selectfont
 	\setlength\arraycolsep{1.1pt}
@@
 	\endgroup
-	\caption{The $\b{c}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\b{c}(T)$ is the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).}
+	\caption{$4$ times the $\b{c}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
+The $i$th column of~$\b{c}(T)$ is $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).}
 	\label{table:specialCMatrices}
@@
 
-\pagebreak
 \subsection{Wiggly fan}
@@
 \label{thm:wigglyFan}
-The collection of cones~$\R_{\ge 0} \langle \b{g}(A) \rangle$ for all~$A$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called the \defn{wiggly fan}~$\wigglyFan_n$.
+The collection of cones~$\R_{\ge 0} \b{g}(D) $ for all wiggly dissections~$D$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called the \defn{wiggly fan}~$\wigglyFan_n$.
 \end{theorem}
@@
 To prove \cref{thm:wigglyFan}, we just need to check the conditions of \cref{prop:characterizationFan}.
-We first find a vector contained in the cone~$\R_{\ge 0} \langle \b{g}(T) \rangle$ for a single wiggly pseudotriangulation~$T$.
+We first find a vector contained in the cone~$\R_{\ge 0} \b{g}(T)$ for a single wiggly pseudotriangulation~$T$.
 
@@
 Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and for~${i \in [n]}$, let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$.
-Then~$\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \langle \b{g}(T) \rangle$.
+Then~$T_\leftarrow \eqdef \{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
 \end{lemma}
@@
 
-Consider now a wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \langle \b{g}(T) \rangle$.
+Consider now a wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
 Write~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \b{g}(\alpha)$ with~$\lambda_\alpha \ge 0$ for all~$\alpha \in T^\circ$.
 Let~$\mu \eqdef \sum_{\alpha \in T^\circ} \lambda_\alpha \dotprod{\hat{\b{g}}(\alpha)}{\one_{2n}}$.
-As~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \hat{\b{g}}(\alpha) - \mu \, \one_{2n}$ and~$\one_{2n} = \hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)$, we thus conclude from the previous paragraph that~$T = \{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
+As~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \hat{\b{g}}(\alpha) - \mu \, \one_{2n}$ and~$\one_{2n} = \hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)$, we thus conclude from the previous paragraph that~$T = T_\leftarrow$.
+%\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
 \end{proof}
@@
 By definition, each wall of the wiggly fan is normal to a $\b{c}$-vector.
-Hence, the wiggly fan coarsens the \defn{$\b{c}$-vector fan}, defined by the arrangement of hyperplanes~$\set{\b{x} \in \HH_{2n}}{\dotprod{\b{x}}{\b{c}(\alpha, T}}$ for all arcs~$\alpha$ and wiggly pseudotriangulations~$T$ with~$\alpha \in T$.
+Hence, the wiggly fan coarsens the \defn{$\b{c}$-vector fan}, defined by the arrangement of hyperplanes~$\set{\b{x} \in \HH_{2n}}{\dotprod{\b{x}}{\b{c}(\alpha, T}}$ for all wiggly arcs~$\alpha$ and wiggly pseudotriangulations~$T$ with~$\alpha \in T$.
 \end{remark}
@@
 When~$\alpha$ and~$\alpha'$ are not pointed, a crossing with~$\alpha$ or~$\alpha'$ can correspond to a crossing with~$\beta$ and a crossing with~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \big( \delta(\beta, \gamma) + \delta(\beta', \gamma) \big) / 2$.
-When~$\alpha$ and~$\alpha'$ are crossing, then there is a correspondence between the crossings with~$\alpha$ or~$\alpha'$ and the crossings with~$\beta$ or~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \delta(\beta, \gamma) + \delta(\beta', \gamma)$
-The result follows by summation, and since~$\delta(\alpha, \alpha') = 1$.
+When~$\alpha$ and~$\alpha'$ are crossing, then there is a correspondence between the crossings with~$\alpha$ or~$\alpha'$ and the crossings with~$\beta$ or~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \delta(\beta, \gamma) + \delta(\beta', \gamma)$.
+Moreover, both inequalities are strict for~$\gamma = \alpha'$ since~$\delta(\alpha,\alpha') = 1$ while~$\delta(\beta, \alpha') = \delta(\beta, \alpha') = 0$.
+The result thus follows by summation.
 \end{proof}
 
-\pagebreak
 \begin{theorem}
@@
 
-In this section, we fix a signature~$\delta \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
+In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
 We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice of \cref{sec:combinatorics} and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron of \cref{sec:geometry}.
@@
 \label{rem:CambrianSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries,rem:wigglyhedronSymmetries}, note that the vertical and horizontal symmetries send $\delta$ to~$\delta_n \cdots \delta_1$ and $(-\delta_1) \cdots (-\delta_n)$ respectively.
-\end{remark}
-
-\pagebreak
+Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries,rem:wigglyhedronSymmetries}, note that the vertical and horizontal symmetries send $\delta \eqdef \delta_1 \dots \delta_n$ to~$\delta_n \cdots \delta_1$ and $(-\delta_1) \cdots (-\delta_n)$ respectively.
+\end{remark}
+
 \begin{proposition}
@@
 We let the readers convince themselves that they are well-defined, that they compose to the identity, and that they preserve the flip structure.
-(We also invite the reader to work out the explicit description of the 8 missing arrows.)
+We also invite the reader to work out the explicit description of the 8 missing arrows.
 For~$I \subseteq [n]$, we set~$I^+ \eqdef \set{i \in I}{\delta_i = {+}}$ and~$I^- \eqdef \set{i \in I}{\delta_i = {-}}$.
@@
 The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
-The \defn{$\delta$-associahedron} is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \le \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
+The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \le \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
 
@@
     \(T\) is a subset of a wiggly pseudotriangulation.
-  \item \(T\) contains at most one of the two irrelevant arcs.
+  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
   \end{enumerate}
@@
 
-Recall from~\cref{rem:incompatibility-deg} that two arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
-Recall from~\cref{prop:uerp} the arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
-Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
+Recall from~\cref{rem:incompatibility-deg} that two wiggly arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
+Recall from~\cref{prop:uerp} the wiggly arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
+Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the wiggly arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
 Let us interpret this dependince categorically.

### 2024-07-11 draft/wigglyhedra.tex
some more proofreading

@@
 We also orient this flip graph in a canonical way, which we call the \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$.
-The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper (throughout the paper, we implicitly orient the graphs from bottom to top).
+The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper (throughout the paper, we implicitly orient the graphs and posets from bottom to top).
 
@@
 We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
-Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing} of support $\tau$-tilting complexes~\cite{AdachiIyamaReiten} on gentle algebras~\cite{ButlerRingel}.
-Namely, we first construct a fan supported by certain $\b{g}$-vectors of the wiggly arcs.
+Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing} of support \mbox{$\tau$-tilting} complexes~\cite{AdachiIyamaReiten} on gentle algebras~\cite{ButlerRingel}.
+Namely, we first construct a fan supported by certain $\b{g}$-vectors associated to the wiggly arcs.
 
@@
 
-The proof of this result is based on a fine understanding of the linear dependences between $\b{g}$-vectors.
+The proof of this result is based on a fine understanding of the linear dependences between \mbox{$\b{g}$-vectors}.
 We further use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
-Without entering the details of its definition of~$\kappa$, let us just mention that it is obtained by summing some compatibility degrees of wiggly arcs, analogously to the constructions for cluster algebras~\cite{HohlwegPilaudStella} and gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
+Without entering the details of the definition of~$\kappa$ at the moment, let us just mention that it is obtained by summing some compatibility degrees of wiggly arcs, analogously to the constructions for cluster algebras~\cite{HohlwegPilaudStella} and gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
 Using the $\b{c}$-vectors of each pseudotriangulation, defined to form the dual basis of the $\b{g}$-vectors, we obtain our main result.
@@
 
-We then define the wiggly complex~$\wigglyComplex_P$ of an arbitrary planar point set~$P$ (not necessarily along the horizontal axis, nor necessarily in general position).
+We then define the wiggly complex~$\wigglyComplex_P$ of an arbitrary planar point set~$P$ (not necessarily aligned along the horizontal axis, nor necessarily in general position).
 Our definition recovers:
 \begin{itemize}
-\item the wiggly complex~$\wigglyComplex_n$ considered in this paper when $P$ consists of $n+2$ collinear points,
-\item the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
+\item when $P$ consists of $n+2$ collinear points, the wiggly complex~$\wigglyComplex_n$ considered in this~paper,
+\item when~$P$ is in general position, the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
 \end{itemize}
+These two families of examples motivate the following conjecture.
 
@@
 
-A general curve can be decomposed into wiggly arcs simply by cutting along U-turns.
+A general curve can be decomposed into wiggly arcs simply by cutting along its U-turns.
 We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
@@
 
-\enlargethispage{.5cm}
 Fix an integer~$n \ge 1$.
@@
 These two perspectives enable us to endow these combinatorial families with additional structures: the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
+We conclude with a few questions and conjectures on graph properties of the wiggly flip graph (\cref{subsec:graphProperties}).
 
@@
 \begin{remark}
-We want to stress out that our notion of compatibility on wiggly arcs of \cref{def:compatible} fundamentally differs from the notion of compatibility used by N.~Reading to define noncrossing arc diagrams~\cite{Reading-arcDiagrams}.
+We want to stress out that our notion of compatibility on wiggly arcs of \cref{def:compatible} might seem similar to, but fundamentally differs from the notion of compatibility used by N.~Reading to define noncrossing arc diagrams~\cite{Reading-arcDiagrams}.
 Namely, our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
-However, for two wiggly arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints, while N.~Reading does precisely the opposite in~\cite{Reading-arcDiagrams}.
-This results in very different objects.
-\end{remark}
-
-We consider pairwise compatible sets of wiggly arcs.
+However, we forbid an arc to start where another arc ends but allow two arcs to start or end at the same point,
+%for two wiggly arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints,
+while N.~Reading does precisely the opposite in~\cite{Reading-arcDiagrams}.
+%This results in very different objects.
+\end{remark}
+
+We then consider pairwise compatible sets of wiggly arcs.
 The following two definitions are illustrated~in~\cref{fig:pseudodissections}.
@@
 \end{align*}
-This enables to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
-%This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
+This enables us to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
+%This enables us to quickly compute the generating series of the number of wiggly pseudotriangulations
 %\[
@@
 
-Our next statement prepares for the definition of flips in wiggly pseudotriangulations.
+Our next statement prepares for the definition of flips in wiggly pseudotriangulations, and is illustrated in \cref{fig:diagonalsPseudoquadrangles}.
 
@@
 We are now ready to consider the wiggly flip graph and the wiggly complex.
-The following definitions are illustrated in \cref{fig:wigglyComplex} when~$n = 2$.
+The following definition is illustrated in \cref{fig:wigglyComplex}\,(right) when~$n = 2$.
 %
@@
 Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
-Then~$Q \eqdef T \ssm \{\alpha\}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
-By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and another one~$\alpha'$.
+Then~${Q \eqdef T \ssm \{\alpha\}}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
+By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, namely $\alpha$ and another one~$\alpha'$.
 As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
@@
 This implies that any wiggly pseudotriangulation can be transformed by flips to a wiggly pseudotriangulation with no final internal wiggly arc.
-The wiggly pseudotriangulations with no final internal wiggly arc all contain the arcs~$(0,n,\varnothing,[n-1])$ and~$(0,n,[n-1],\varnothing)$ (as the latter are compatible with all internal wiggly arcs but the final ones),
+All wiggly pseudotriangulations with no final internal wiggly arc contain the arcs~$(0,n,\varnothing,[n-1])$ and~$(0,n,[n-1],\varnothing)$, since the latter are compatible with all internal wiggly arcs but the final ones.
 Hence, they induce a subgraph of~$\wigglyFlipGraph_n$ isomorphic to~$\wigglyFlipGraph_{n-1}$, which is connected by induction.
@@
 
-To see the claim, 
-\vincent{todo}
+To see the claim, let~$i$ be maximal such that~$T$ contains two distinct wiggly arcs starting at~$i$ and ending at~$n+1$ (it is well-defined as we have the external wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ for~$i = 0$).
+Consider a final internal wiggly arc~$\alpha$ of~$T$ starting weakly after~$i$, and let~$\alpha'$ be the wiggly arc obtained by flipping~$\alpha$ in~$T$.
+If~$\alpha'$ is final, then at least one pseudotriangle~$t$ of~$T$ incident to~$\alpha$ has two corners at~$n+1$.
+Let~$h$ be the hinge of~$t$ and~$\beta, \beta'$ be the two wiggly arcs of~$t$ joining~$h$ to~$n+1$.
+As~$i < h \le n$ the maximality of~$i$ imposes that~$\beta = \beta'$.
+Flipping $\beta = \beta'$ in~$T$ thus yields a wiggly arc ending at~$h \le n$, hence a non-final arc.
 \end{proof}
 
+We will even consider an oriented version of the wiggly flip graph~$\wigglyFlipGraph_n$.
 The following definition is illustrated in \cref{fig:incompatible2}.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{incompatible2}}
-\caption{The wiggly arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
-\label{fig:incompatible2}
-\end{figure}
 
@@
 The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and an edge for each increasing~flip.
+%
+\begin{figure}
+\centerline{\includegraphics[scale=1.3]{incompatible2}}
+\caption{The wiggly arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
+\label{fig:incompatible2}
+\end{figure}
 \end{definition}
+
+\pagebreak
+We will also need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
+
+\begin{proposition}
+\label{prop:uerp}
+Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
+Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
+\begin{itemize}
+\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
+(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
+\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ such that~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
+(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
+\end{itemize}
+%See \cref{fig:incompatible3} for illustrations.
+(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
+%
+\begin{figure}
+\centerline{\includegraphics[scale=1.3]{incompatible3}}
+\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
+\label{fig:incompatible3}
+\end{figure}
+\end{proposition}
+
+\begin{proof}
+Any wiggly arc non pointed with~$\beta$ would be non pointed with~$\alpha$ or~$\alpha'$ (as the endpoints of~$\beta$ are endpoints of~$\alpha$ or~$\alpha'$).
+Any wiggly arc crossing~$\beta$ would be either non pointed or crossing~$\alpha$ or~$\alpha'$ (as~$\beta$ follows~$\alpha$ or~$\alpha'$, except at the point~$j = i'$ in the first situation).
+\end{proof}
+
+Finally, we are define the wiggly complex~$\wigglyComplex_n$, illustrated in \cref{fig:wigglyComplex}\,(left) when~$n = 2$.
 
@@
 
-Finally, we will need the following observation, illustrated in \cref{fig:incompatible3}.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{incompatible3}}
-\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
-\label{fig:incompatible3}
-\end{figure}
-
-\begin{proposition}
-\label{prop:uerp}
-Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
-Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
-\begin{itemize}
-\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
-(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ such that~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
-(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
-\end{itemize}
-%See \cref{fig:incompatible3} for illustrations.
-(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
-\end{proposition}
-
-\begin{proof}
-Any wiggly arc non pointed with~$\beta$ would be non pointed with~$\alpha$ or~$\alpha'$ (as the endpoints of~$\beta$ are endpoints of~$\alpha$ or~$\alpha'$).
-Any wiggly arc crossing~$\beta$ would be either non pointed or crossing~$\alpha$ or~$\alpha'$ (as~$\beta$ follows~$\alpha$ or~$\alpha'$, except at the point~$j = i'$ in the first situation).
-\end{proof}
 %%%%%%%%%%%%
@@
 \begin{remark}
-\label{re:nuberWigglyPermutations}
+\label{rem:numberWigglyPermutations}
 The number~$wp_n$ of wiggly permutations of~$[2n]$ is given by
@@
 \]
-To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ with~$2j$ before~$\gamma$ before~$2j-1$).
+To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ such that the value~$2j$ appears before the gap~$\gamma$ while the value~$2j-1$ appears after the gap~$\gamma$).
 For instance,
@@
 \begin{itemize}
-\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps where~$2j-1$ appears before~$2j$ (they must appear consecutively),
-\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs where $2j$ appears before~$2j-1$, for all~$0 \le j \le i+1$.
+\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps and where~$2n-1$ appears before~$2n$ (they must appear consecutively),
+\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
 \end{itemize}
@@
 
-The (left) \defn{weak order} on permutations of~$[2n]$ is defined as the inclusion order of their inversion sets.
+The (left) \defn{weak order} on permutations of~$[2n]$ is defined as the inclusion order of their inversion sets (or equivalently, the reverse inclusion of their non-inversion sets).
 Its cover relations are given by the exchanges of two entries at consecutive positions.
@@
 
-%The following statements are illustrated on \cref{fig:wigglyLattice}\,(right) when~${n = 2}$.
+The following statements are illustrated on \cref{fig:wigglyLattice}\,(right) when~${n = 2}$.
 %
@@
 
+\enlargethispage{.3cm}
 We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
@@
 Let~$k \in [2n-1]$ and~$m \eqdef \lceil \sigma(k)/2 \rceil$.
-Then observe that
+Then observe~that
 \begin{itemize}
@@
 \begin{remark}
-The map~$\Phi$ sends wiggly pseudotriangulations with $i$ internal wiggly arcs adjacent to the last point~$n+1$ to wiggly permutations with $i$ admissible gaps, explaining the similarities in the counting arguments of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
+The map~$\Phi$ sends wiggly pseudotriangulations with $i$ final internal wiggly arcs to wiggly permutations with $i$ admissible gaps, explaining the similarities of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
 \end{remark}
@@
 
-We close this section by the following conjecture (checked computationally up to~$n = 3$).
+We conclude this combinatorial section with two open questions and a conjecture on graphical properties of the wiggly flip graph~$\wigglyFlipGraph_n$ (or equivalently of the cover graph of the wiggly lattice~$\wigglyLattice_n$), motivated by the relevance of similar questions for the associahedron.
+
+First, we are interested in the graph diameter~$\delta_n$ of~$\wigglyFlipGraph_n$.
+It is clearly bounded below by~$2n-1$ (as~$T_\leftarrow \cap T_\rightarrow = \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$, all $2n-1$ internal wiggly arcs must sometimes be flipped at least once) and above by~$\binom{2n}{2}$ (as we have a sublattice of the weak order on permutations of~$[2n]$).
+The first few values of~$\delta_n$ are
+\[
+\begin{array}{c|ccccccccc}
+n & 1 & 2 & 3 & 4 & 5 & \dots \\
+\hline
+\delta_n & 1 & 4 & 8 & 14 & 20 & \dots
+\end{array}
+\]
+but they might be misleading as for the associahedron~\cite{Pournin}.
+This raises the following question.
+
+\begin{question}
+Compute (or estimate) the diameter~$\delta_n$ of the wiggly flip graph~$\wigglyFlipGraph_n$.
+\end{question}
+
+Related to the estimation of the diameter~$\delta_n$ is the study of the properties of the geodesic paths in~$\wigglyFlipGraph_n$.
+We refer to~\cite{CeballosPilaud-diameterDAssociahedron} for a discussion on geodesic properties in a polytope, in connection to the revisiting path property and the complexity of the simplex algorithm~\cite{Santos-surveyHirsch,Santos-Hirsch}.
+
+\begin{question}
+Does the wiggly complex has the non-leaving face property of~\cite{CeballosPilaud-diameterDAssociahedron}?
+\end{question}
+
+Finally, we checked the following conjecture computationally up to~$n = 3$.
 
@@
 \label{conj:Hamiltonian}
-The cover graph of the wiggly lattice~$\wigglyLattice_n$ admits an Hamiltonian path (or even cycle).
+The wiggly flip graph~$\wigglyFlipGraph_n$ admits an Hamiltonian path (or even cycle).
 \end{conjecture}
@@
 
+\enlargethispage{.5cm}
 Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
@@
 \[
-\lambda_v \, h_v + \lambda_{v'} \, h_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, h_w > 0
+\lambda_v \, h_v + \lambda_{v'} \, h_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, h_w > 0,
 \]
@@
 The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$ is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha)} = 1$ and~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha')} = 0$ for all interior wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
-In other words, $\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ is the dual basis of~$\b{g}(T)$ in~$\HH_{2n}$.
+In other words, $\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ is the dual basis of~$\b{g}(T)$~in~$\HH_{2n}$.
 \end{definition}
@@
 \end{itemize}
-The tedious proof of this description is not needed in this paper as we will only use the dual basis property.
+The tedious proof of this description is not needed here as we only use the dual basis property.
 \end{remark}
@@
 The aim of this section is to explain a categorical interpretation of wiggly arcs.
-We recall results of Khovanov--Seidel~\cite{kho.sei:02} that realise wiggly arcs as objects of a triangulated category, such that intersections between wiggly arcs correspond to morphisms in this category.
-We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible}.
-
-% Curves up to isotopy in a disk with marked points constitute a geometric model of certain objects in a triangulated category.
-% This correspondence, due to Khovanov--Seidel~\cite{kho.sei:02}, and will enable us to build categorical interpretations of the combinatorial results obtained in this paper.
-% The aim of this section is to give a concise account of this correspondence and some of its useful features; we refer the reader to~\cite{kho.sei:02} for details.
+We first present a particular triangulated category (\cref{subsec:category}), and recall results of Khovanov--Seidel~\cite{kho.sei:02} (\cref{subsec:KSCurveModel}) that interpret the objects of this category as wiggly arcs, such that intersections between wiggly arcs correspond to morphisms in this category.
+We then explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition (\cref{subsec:cohomologyFiltrations}).
+We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible} (\cref{subsec:categoricalCompatibility}).
 
@@
 \subsection{A triangulated category associated to a quiver}
+\label{subsec:category}
 
@@
 The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
-\begin{figure}[h]
+Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
+Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
+A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).
+
+\begin{figure}
 	\centering
@@
 \end{figure}
-Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
-Let \(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
-A longer path, which is a composition of arrows, will be denoted by \((i_1, i_2, \dots, i_n)\).
 
 \begin{definition}
-  The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations: \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
-%  \begin{itemize}
-%  \item \((i-1, i, i+1) = (i+1, i, i-1\) for all~\(1 < i < m\),
-%  \item \((i, i-1, i) = (i, i+1, i)\) for every \(j\) and \(l\) such that there are arrows between \(i\) and \(j\) and between \(i\) and \(l\).
-%  \end{itemize}
+The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
 \end{definition}
@@
 In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).
+
 \begin{definition}
@@
 \end{definition}
+
 For further discussion on the construction, see \eg~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
@@
 In other words, we have
-\[\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).\]
+\[
+\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).
+\]
 Furthermore, for any integers \(a\) and \(b\), we have
-\[\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).\]
-
-\begin{remark}\label{rem:generating-morphisms}
-  It is easy to check that the generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
+\[
+\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).
+\]
+
+\begin{remark}
+\label{rem:generating-morphisms}
+The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
 \end{remark}
@@
 A variant of this construction is also described in~\cite[Sect.~2.5]{lic.que:21}.
-It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\)
-as bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
+It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\) as a bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
 More precisely, we can write
-\[P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],\]
+\[
+P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],
+\]
 where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
@@
 That is, in the notation above, we have
-\[P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].\]
+\[
+P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].
+\]
 
@@
 \end{warning}
-\begin{definition}\label{def:linear-complex}
+
+\begin{definition}
+\label{def:linear-complex}
 Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
-  \[P^{\bullet} = \bigoplus M_i\langle g \rangle[h]\]
+\[
+P^{\bullet} = \bigoplus M_i\langle g \rangle[h]
+\]
 together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
@@
 We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
-
 \end{definition}
+
 For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq -N\).
@@
 The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
+
 \begin{proposition}
@@
 \end{proposition}
+
 We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
-Set \(\mathcal{A}_m = \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
+Set \(\mathcal{A}_m \eqdef \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
 It follows that \(\mathcal{A}_m\) is abelian.
@@
 Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}
-\begin{defprop}\label{defprop:cohomology}
-  Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart~\(\mathcal{A} = \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
+
+\begin{defprop}
+\label{defprop:cohomology}
+Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart~\(\mathcal{A} \eqdef \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
 For each integer \(i\), we have the \(i\)th truncation functors
-  \[\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i} \quad\text{and}\quad \tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},\]
+\[
+\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i} \quad\text{and}\quad \tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},
+\]
 which are right and left adjoint respectively to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
@@
 \end{defprop}
+
 The next statement, easy to check from the definitions, is mentioned in~\cite[Sect.~3.3]{bayer2011tour}.
-\begin{defprop}\label{defprop:cohomology-filtration}
+
+\begin{defprop}
+\label{defprop:cohomology-filtration}
 Let \(\mathcal{C}\) be any triangulated category, and \(\mathcal{A} \subset \mathcal{C}\) the heart of a bounded \(t\)-structure on \(\mathcal{C}\).
-  Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(l\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^{l}(X)\) are non-zero.
+Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(\ell\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^\ell(X)\) are non-zero.
 Then \(X\) has a unique \defn{cohomology filtration}, which is the unique filtration of the form
@@
 \begin{tikzcd}[column sep=0.1cm]
-      0  \arrow{rr} && X_{-l} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k+1} \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-      & H^l(X)[-l] \arrow[dashed]{ul}{+1} && H^{l+1}(X)[-l-1] \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X)[-k] \arrow[dashed]{ul}{+1}
+	0  \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k+1} \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
+	& H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X)[-k] \arrow[dashed]{ul}{+1}
 \end{tikzcd}
@@
 \subsection{The Khovanov--Seidel curve model}
+\label{subsec:KSCurveModel}
 
@@
 In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
-In fact, the procedure works on more general curves as well --- namely, those that are not necessarily \(x\)-monotone.
+In fact, the procedure works on more general curves as well (namely, those that are not necessarily \(x\)-monotone).
 
@@
 
-\begin{proposition}\label{prop:cohomology-pieces}
+\begin{proposition}
+\label{prop:cohomology-pieces}
 Let \(\alpha\) be any curve, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
@@
 \end{proposition}
+
 \begin{proof}
@@
 \subsection{Cohomology filtrations of spherical objects}
+\label{subsec:cohomologyFiltrations}
 
@@
 However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
-\begin{proposition}\label{prop:hn-filtration}
+
+\begin{proposition}
+\label{prop:hn-filtration}
   Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
@@
     \begin{tikzcd}[column sep=0.3cm]
-      0 \arrow{rr} && X_{-l} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-      & H^l(X)[-l] \arrow[dashed]{ul}{+1} && H^{l+1}(X)[-l-1] \arrow[dashed]{ul}{+1} & \cdots & H^k(X)[-k] \arrow[dashed]{ul}{+1}
+      0 \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
+      & H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} & \cdots & H^k(X)[-k] \arrow[dashed]{ul}{+1}
     \end{tikzcd}
@@
   Consider the set of all possible indecomposable summands of the cohomology objects \(\{H^j(X)\}\) taken without multiplicity.
-  Let \(T\) be corresponding set of wiggly arcs, as explained in~\cref{prop:cohomology-pieces}.
-  We have the following results.
+  Let \(T\) be corresponding set of wiggly arcs, as explained in~\cref{prop:cohomology-pieces}.~Then
   \begin{enumerate}
   \item 
-    \(T\) is a subset of a wiggly pseudotriangulation.
+    \(T\) is a subset of a wiggly pseudotriangulation,
   \item \(T\) contains at most one of the two irrelevant wiggly arcs.
@@
 \subsection{Categorical constraints on compatibility of curves}
+\label{subsec:categoricalCompatibility}
 
 In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
-As such, this section is somewhat dual to the previous section --- the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
-\begin{proposition}\label{prop:ext1}
+As such, this section is somewhat dual to the previous section: the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
+
+\begin{proposition}
+\label{prop:ext1}
   Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
@@
   Note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes the object \(X\) in level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) in level \(s_1 - s_2\).
-  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\ref{eq:bigraded-homs}.
+  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
     The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
@@
 So we have to modify the gradings when we construct the complexes, and thus the morphisms that now have level one change as well.
-In particular, the table in~\cite[Lemma 3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lemma 4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
+In particular, the table in~\cite[Lem.~3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lem.~4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
 
@@
 \end{proof}
+
 \begin{remark}
@@
 \end{remark}
+
 \begin{remark}
@@
 
+\pagebreak
 Recall from~\cref{rem:incompatibility-deg} that two wiggly arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
@@
 Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the wiggly arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
-Let us interpret this dependince categorically.
-
-Let \(X\) and \(X'\) be spherical objects in the standard heart that correspond to \(\alpha\) and \(\alpha'\) respectively.
+Let us interpret this dependence categorically.
+
+Let \(X\), \(X'\), \(Y\) and~\(Y'\) be spherical objects in the standard heart that correspond to \(\alpha\), \(\alpha'\), \(\beta\) and~\(\beta'\) respectively.
 First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
-Next, let us understand~\(\beta\) and \(\beta'\) categorically.
+Next, let us understand~\(Y\) and \(Y'\) categorically.
+
 \begin{proposition}\label{prop:extensions}
-  Let \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\) be as just discussed.
-  Let \(Y\) and \(Y'\) be the objects in the standard heart corresponding to \(\beta\) and \(\beta'\) respectively.
+For \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\), \(Y\), \(Y'\) as just discussed,
 \begin{itemize}
 \item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
-  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0.\]
+  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0,\]
 \item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
@@
 \end{proposition}
+
 \begin{proof}
   The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
-  We do not reproduce the proof here, as the argument is contained in the proof of Theorem 5.5 in~\cite{tho:06}.
-  (See also~\cite[Figure 4]{tho:06}.)
+  We do not reproduce the proof here, as the argument is contained in the proof of~\cite[Thm.~5.5]{tho:06}.
+  (See also~\cite[Fig.~4]{tho:06}.)
 \end{proof}

### 2024-07-12 draft/wigglyhedra.tex
maximise front page picture size
Several updates (some in progress).

@@
 
-\centerline{\includegraphics[scale=1.6]{wigglyFlipGraph}}
+\centerline{\includegraphics[scale=1.75]{wigglyFlipGraph}}
 
@@
 %Indeed, any wiggly pseudotriangulation on~$n+1$ points can be obtained from a wiggly pseudotriangulation on~$n+2$ points by collapsing the points~$n$ and~$n+1$.
-Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting its wiggly pseudotriangle with a hinge at~$n$.
+Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting a single wiggly pseudotriangle with a hinge at~$n$.
 %There are two kinds of wiggly pseudotriangulations of~$n+2$ points:
@@
 %\end{itemize}
-Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to
+Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to:
 \begin{itemize}
@@
 
-There are various possible proofs for the connectiveness.
+There are various possible proofs for the connectedness.
 For instance, it will follow easily from \cref{prop:bijection}.
-To avoid to rely on this forward reference, we sketch an alternative direct proof by induction on~$n$.
-We claim that if a wiggly pseudotriangulation has some final internal wiggly arcs (\ie ending at the last point~$n+1$), then at least one of them can be flipped to a non-final wiggly arc.
+To avoid relying on this forward reference, we sketch an alternative direct proof by induction on~$n$.
+We claim that if a wiggly pseudotriangulation has a non-zero number of final internal wiggly arcs (\ie ending at the last point~$n+1$), then at least one of them can be flipped to a non-final wiggly arc.
 This implies that any wiggly pseudotriangulation can be transformed by flips to a wiggly pseudotriangulation with no final internal wiggly arc.
@@
 Consider a final internal wiggly arc~$\alpha$ of~$T$ starting weakly after~$i$, and let~$\alpha'$ be the wiggly arc obtained by flipping~$\alpha$ in~$T$.
-If~$\alpha'$ is final, then at least one pseudotriangle~$t$ of~$T$ incident to~$\alpha$ has two corners at~$n+1$.
+If~$\alpha'$ is final, then by~\cref{prop:diagonalsPseudoquadrangle}, at least one pseudotriangle~$t$ of~$T$ incident to~$\alpha$ has two corners at~$n+1$.
 Let~$h$ be the hinge of~$t$ and~$\beta, \beta'$ be the two wiggly arcs of~$t$ joining~$h$ to~$n+1$.
@@
 
-We will even consider an oriented version of the wiggly flip graph~$\wigglyFlipGraph_n$.
+We will also consider an oriented version of the wiggly flip graph~$\wigglyFlipGraph_n$.
 The following definition is illustrated in \cref{fig:incompatible2}.
@@
 \pagebreak
-We will also need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
+We will need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
 
@@
 The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
-Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
+Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).\asilata{Check, is the horizontal reflection nothing at all?
+Is it actually an automorphism?}
 \end{remark}
@@
 Any wiggly permutation of~$[2n]$ can be obtained from a wiggly permutation of~$[2n-2]$ by inserting the last values~$2n-1$ and~$2n$.
-Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to
+Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to:
 \begin{itemize}
@@
 We first present a particular triangulated category (\cref{subsec:category}), and recall results of Khovanov--Seidel~\cite{kho.sei:02} (\cref{subsec:KSCurveModel}) that interpret the objects of this category as wiggly arcs, such that intersections between wiggly arcs correspond to morphisms in this category.
-We then explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition (\cref{subsec:cohomologyFiltrations}).
+We then explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of objects (\cref{subsec:cohomologyFiltrations}).
 We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible} (\cref{subsec:categoricalCompatibility}).
@@
 We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-That is, a subcategory of the bounded derived category of (finitely generated) \(A_m\)-modules.
+That is, a subcategory of the bounded derived category of finitely generated \(A_m\)-modules.
 The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
@@
 \]
-where \(g\) is the internal grading shift, and \(h\) is the homological grading shift, and 
+where \(g\) is the internal grading shift, \(h\) is the homological grading shift, and 
 each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
@@
 
-The next statement, easy to check from the definitions, is mentioned in~\cite[Sect.~3.3]{bayer2011tour}.
+The next statement, easy to check from the definitions, is mentioned \eg in~\cite[Sect.~3.3]{bayer2011tour}.
 
@@
 
+Any object \(X\) obtained via the Khovanov--Seidel correspondence is~\defn{spherical}; that is, \(\Hom^{g,0}(X,X)\) is \(k\) when \(g = 0,2\), and \(\Hom^{g,h}(X,X) = 0\) in all other cases.
+A spherical object \(X\) is necessarily indecomposable as \(\Hom^{0,0}(X,X) = k\).
+
 \begin{proposition}
@@
 \begin{enumerate}
-\item The object \(X\) is an indecomposable spherical object of \(\mathcal{A}_m\) up to shift if and only if \(\alpha\) is a wiggly arc.
+\item The object \(X\) is a (spherical) object of \(\mathcal{A}_m\) up to shift if and only if \(\alpha\) is a wiggly arc.
 In this case, \(H^j(X) \neq 0\) for exactly one \(j\), such that \(X \cong H^j(X)[-j]\).
-\item If \(\alpha\) is a general curve, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical indecomposable object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
+\item If \(\alpha\) is a general curve, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
 \end{enumerate}
@@
   Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) curve \(\alpha\).
-  The results of~\cite{kho.sei:02} imply that \(X\) is spherical and indecomposable.
+  Recall from~\cite{kho.sei:02} that \(X\) is spherical, and hence indecomposable.
   Let us now analyse the indecomposable summands of its cohomology objects.
 
-  Recall that the procedure to build up \(X\) from \(\alpha\) explicitly describes the differentials.    
-  Each component of these differentials is a map of the form
-  \[P_i\langle g \rangle[h] \to P_j\langle g' \rangle[h-1].\]
-  Let us see how these maps interact with the level.
-
-  First consider a non-zero component \(P_i\langle g \rangle[h] \to P_j\langle g' \rangle[h-1]\) for \(i \neq j\).
-  We see from~\cref{rem:generating-morphisms} that \(g' = g+1\).
-  In other words, this component has the form
-  \(P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\),
-  and hence does not change the level.
-
-  Now consider a non-zero component \(P_i\langle g \rangle[h] \to P_i\langle g' \rangle[h-1]\).
-  Once again, it is clear from~\cref{rem:generating-morphisms} that we either have \(g' = g\) or \(g' = g + 2\).
-  Any component of the form \(P_i \langle g \rangle[h] \to P_i\langle g \rangle[h-1]\)
-  is necessarily a multiple of the identity map, which do not appear in the Khovanov--Seidel complex.
-  The only remaining possibility is a ``loop'' map \(P_i \langle g \rangle[h] \to P_i\langle g+2 \rangle[h-1]\), which raises the level by one.
+  We recall that the procedure to build up \(X\) from \(\alpha\) explicitly describes the differential.
+  We analyse the possible non-zero components of the differential, checking how each interacts with the level.
+  The only two possibilities are as follows:
+  \begin{enumerate}
+  \item a map \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\), namely multiplication on the right by the path \((i,i\pm1)\), which does not change the level; or
+  \item a map \(P_i\langle g \rangle[h] \to P_{i}\langle g+2 \rangle[h-1]\), namely multiplication on the right by the ``loop'' path \((i,i\pm1, i)\), which raises the level by one.
+  \end{enumerate}
+  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the \(i-1\)th point.
+  The second possibility appears each time the curve makes a \(U\)-turn around the \(i\)th or \(i-1\)th point.
 
@@
   Explicitly, the truncation is a new chain complex in which we only keep the terms of \(X\) that have level \(j\), together with all maps between them, and forget all the other terms.
-  From the calculation above, we see that the resulting complex only has components in its differential of the form \(P_i\langle g \rangle[h] \to P_j\langle g+1 \rangle[h-1]\) for \(i \neq j\); in particular, we kill all the ``loop'' components.
+  From the calculation above, we see that the resulting complex only has components in its differential of the first type, namely \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\) where \(g + h = j\).
+  We kill all components of the second type (the ``loop'' components).
   The resulting chain complex breaks up into indecomposable summands, each of which is an object of~\(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
 
-  The object \(X\) is in the heart up to shift if and only if it is concentrated in a single cohomological degree \(j\).
+  The object \(X\) is in the heart up to shift if and only if it is concentrated in a single level \(j\).
   Truncating to level \(j\) as described above, we do not delete any of the terms of \(X\).
   This can happen if and only if the differential of \(X\) contains no loop components,
-  which appear in the complex if and only if \(\alpha\) loops around a point.
+  which appear in the complex if and only if \(\alpha\) makes a U-turn around one of the \(n+2\) points.
   Thus \(X\) is in the heart up to shift if and only if \(\alpha\) is  \(x\)-monotone.
@@
   We continue with the remainder of \(\alpha\) starting at \(p_1\), greedily taking the maximal \(x\)-monotone portion each time, to obtain pieces \(\alpha_1,\alpha_2, \ldots, \alpha_k\), which are all wiggly arcs.
-  These wiggly arcs correspond to complexes \(X_1, \ldots, X_k\), which are indecomposable spherical objects of \(\mathcal{A}_m\), up to shift.
+  These wiggly arcs correspond to complexes \(X_1, \ldots, X_k\), which are spherical objects of \(\mathcal{A}_m\), up to shift.
   It is clear from the construction of the associated complex that these objects, up to shift, are exactly the indecomposable pieces of the cohomology truncations \(H^j(X)\) for various \(j\).
@@
   Therefore \(\beta\) and \(\beta'\) cannot cross, because~\(\alpha\) does not cross itself.
-  Suppose that \(\beta\) and \(\beta'\) are non-pointed, and without loss of generality, suppose that \(i' = j\).
+  Suppose that \(\beta\) and \(\beta'\) are non pointed, and without loss of generality, suppose that \(i' = j\).
   This means that the piece \(\beta\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the right of the point \(i'\).
@@
 
-It can be checked that under the modified grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non-pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
+It can be checked that under the modified grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
 Morphisms arising from other intersections do not contribute to \(\Ext^1\).
@@
   As stated,~\cref{prop:ext1} in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
-  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two indecomposable spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
+  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
   However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.

### 2024-07-12 draft/wigglyhedra.tex
More updates (some in progress).

@@
   \end{enumerate}
-  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the \(i-1\)th point.
-  The second possibility appears each time the curve makes a \(U\)-turn around the \(i\)th or \(i-1\)th point.
+  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the \((i-1)\)th point.
+  The second possibility appears each time the curve makes a U-turn around the right of \(i\)th or the left of the \((i-1)\)th point.
 
@@
   Truncating to level \(j\) as described above, we do not delete any of the terms of \(X\).
-  This can happen if and only if the differential of \(X\) contains no loop components,
+  This can happen if and only if the differential of \(X\) contains no ``loop'' components,
   which appear in the complex if and only if \(\alpha\) makes a U-turn around one of the \(n+2\) points.
@@
   As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve~\(\alpha\) into \(x\)-monotone portions.
-  More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by bending around a point \(p_1\).
+  More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by making a U-turn around a point \(p_1\).
   In this case, we take the portion of \(\alpha\) between \(p_0\) and \(p_1\), calling it \(\alpha_1\), and setting its endpoints to be \(p_0\) and \(p_1\) respectively.
@@
   \begin{enumerate}
-  \item \(i' = j\) is an endpoint such that \(\alpha\) goes left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) goes right starting at \(j\);
-  \item \(i' = j\) is an endpoint such that \(\alpha\) goes left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
-  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) goes right starting at \(j\); 
+  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\);
+  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
+  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\); 
   \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
@@
   Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
-  These must then connect to each other, resulting in \(\alpha\) having a separate component that winds around the outside of the \(n+2\) points.
+  These must then connect to each other, resulting in \(\alpha\) having a separate closed component that winds around the outside of the \(n+2\) points.
   This is not possible because \(\alpha\) is a connected curve with two endpoints.
@@
 This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
-At the moment, we do not have a concise construction of the \(\b{g}\)-vectors purely categorically, and it would be interesting to find this.
+The \(\b{g}\)-vector of an object \(X\) corresponding to a wiggly arc \(\alpha\) can, of course, be reconstructed from \(\alpha\).
+However, at the moment we do not have a purely categorical construction of the \(\b{g}\)-vector of \(X\) that does not refer to \(\alpha\), and it would be interesting to find this.
 

### 2024-07-14 draft/wigglyhedra.tex
Edited categorical section.

@@
 
+Recall that two wiggly arcs \(\alpha\) and \(\alpha'\) are said to be compatible (as in~\cref{def:compatible}) if they are non-crossing and pointed.
+The incompatibility degree of \(\alpha\) and \(\alpha'\) (as in~\cref{def:incompatibilityDegree}) is \(1\) if \(\alpha\) and \(\alpha'\) are non pointed, and the number of crossings of \(\alpha\) and \(\alpha'\) otherwise.
 \begin{proposition}
 \label{prop:ext1}
-  Consider two wiggly arcs \(\alpha\) and \(\alpha'\), and let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible in the sense of~\cref{def:compatible} if and only if \(\Ext^1(X, X') = 0\).
-  More generally, the incompatibility degree \(\delta(\alpha,\alpha')\) as in~\cref{def:incompatibilityDegree} is the dimension of \(\Ext^1(X,X')\).
+Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
+  Then \(\alpha\) and \(\alpha'\) are compatible if and only if \(\Ext^1(X, X') = 0\).
+  More generally, the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext^1(X,X')\).
 \end{proposition}
@@
   The proof follows from a specialisation of the bigraded intersection number calculations that appear in Sections 3 and 4 of~\cite{kho.sei:02}.
-  Let \(X\) and \(X'\) be objects in the standard heart that correspond to wiggly arcs \(\alpha\) and \(\alpha'\).
   The bigraded intersection number as defined in~\cite[Sect.~3d]{kho.sei:02} between the curves \(\alpha\) and \(\alpha'\) is a polynomial in the variables \(q_1^{\pm}\), \(q_2^{\pm}\).
@@
 \end{equation}
-  Note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes the object \(X\) in level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) in level \(s_1 - s_2\).
-  We can obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
+However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
+So we have to modify the gradings when we construct the complexes.
+In particular, the table in~\cite[Lem.~3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lem.~4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
+
+With our path-length grading, note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes an object \(X\) of level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) of level \(s_1 - s_2\).
+  We can thus obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
     The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
 
-However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
-So we have to modify the gradings when we construct the complexes, and thus the morphisms that now have level one change as well.
-In particular, the table in~\cite[Lem.~3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lem.~4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
-
-It can be checked that under the modified grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
+It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
 Morphisms arising from other intersections do not contribute to \(\Ext^1\).

### 2024-07-14 draft/wigglyhedra.tex
Removed a todo.

@@
 The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
-Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).\asilata{Check, is the horizontal reflection nothing at all?
-Is it actually an automorphism?}
+Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
 \end{remark}

### 2024-10-08 exposeBerlin2410/exposeBerlin2410.tex
start presentation Berlin

\documentclass[12pt,titlepage,landscape,a4paper]{article}

%QUELQUES PACKAGES PLUS OU MOINS UTILES
\special{landscape}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amssymb, amsthm, mathtools}
\usepackage{aeguill}
\usepackage{graphics, graphicx}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{paralist}
\usepackage{multido,ifthen}
\usepackage{tikz}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles, snakes}
\usepackage[external]{forest}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{movie15}
\usepackage[abs]{overpic}
\usepackage{xargs}
\usepackage{extarrows}
\usepackage{shuffle}
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{dsfont}
\usepackage{pifont}
\usepackage{array, blkarray}
\usepackage{multicol, multirow}
\usepackage{ulem}
\usepackage{xifthen}

% ZONE DE TEXTE ET POLICE
\setlength{\topmargin}{-2.8cm}
\setlength{\textheight}{19cm}
\setlength{\oddsidemargin}{-1cm}
\setlength{\textwidth}{26.8cm}
\newcommand{\textenormal}{\fontsize{22}{28}\selectfont}
\newcommand{\textemoyen}{\fontsize{23}{27}\selectfont}
\newcommand{\textegrand}{\fontsize{55}{48}\selectfont}

% COMMANDE DE NOUVELLE PAGE
\newenvironment{slide}[1]
{
\newpage
\begin{center}
{\blue \textemoyen \uppercase{#1}}\\
\end{center}
\vspace{-1cm}
\rule{\textwidth}{0.5 pt}\\
\vspace{-.8cm}
}
{\vspace*{-3cm}}

% COMMANDE DE PARTIE
%\newcounter{partie}
%\setcounter{partie}{1}
%\newcommand{\thePartie}{Part \arabic{partie}}
\newcommand{\partie}[1]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.9\textwidth}{0.5 pt} \\[.5cm]
\fontsize{30}{30}\selectfont {\blue\uppercase{#1}} \\[-.35cm]
\rule{.9\textwidth}{0.5 pt} \\
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE D'EXPOSE
\newcommand{\expose}[2]
{
\newpage
\vspace*{0pt plus 1 fill}
\begin{center}
%\thePartie \\[-.75cm]
\rule{.8\textwidth}{0.5 pt} \\[.5cm]
\fontsize{35}{35}\selectfont {\red\uppercase{#1}} \\[-.35cm]
\rule{.8\textwidth}{0.5 pt} \\
\vspace{1cm}
\textemoyen #2
\end{center}
\vspace*{0pt plus 1.2 fill}
%\addtocounter{partie}{1}
}

% COMMANDE POUR LES BOITES
% centre
\newcommand{\cboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
\begin{center} #1 \end{center}
\vspace*{-.1cm}
\end{minipage}
}
}
% alignement gauche
\newcommand{\gboite}[1]
{
\vspace*{.5cm}
\fcolorbox{blue}{grisclair}{
\begin{minipage}{.97\linewidth}
\vspace*{.3cm}
#1
\vspace{.3cm}
\end{minipage}
}
}

\newcommand{\chapitre}[1]{{\blue \fontsize{23}{25}\selectfont {Chap\,#1}}}

% AUTRES COMMANDES
% quelques couleurs manquantes
\newcommand{\orange}{\color{orange}} % couleur orange
\newcommand{\green}{\color{green}} % couleur verte
\newcommand{\violet}{\color{violet}} % couleur violet
\newcommand{\blue}{\color{blue}} % couleur bleu
\newcommand{\red}{\color{red}} % couleur rouge
\definecolor{violet}{rgb}{.5,.1,.9}
\definecolor{orange}{rgb}{.94,.57,0}
\definecolor{green}{rgb}{0.2,0.6,0.2}
\definecolor{grisclair}{gray}{1}
\definecolor{grisfonce}{gray}{.1}
\definecolor{bblue}{rgb}{.8,.8,1}
% maths
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % ensemble
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % ensemble
\newcommand{\biggset}[2]{\bigg\{ #1 \;\bigg|\; #2 \bigg\}} % ensemble
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % ensemble
\newcommand{\dotprod}[2]{\left\langle\; #1 \;\middle|\; #2 \;\right\rangle} % produit scalaire
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\symdif}{\triangle} % symmetric difference
\newcommand{\eqdef}{\mbox{\,\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.3ex}{\normalsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\Fracfloor}[2]{\left\lfloor \frac{#1}{#2} \right\rfloor} % floor of a fraction
\newcommand{\one}{1\!\!1} % one bold
\DeclareMathOperator{\conv}{conv} % enveloppe convexe
\DeclareMathOperator{\cone}{cone} % cone engendre
\DeclareMathOperator{\vol}{vol} % volume
\newcommand{\C}{\mathbb{C}} % complexes
\newcommand{\R}{\mathbb{R}} % reels
\newcommand{\Z}{\mathbb{Z}} % entiers
\newcommand{\N}{\mathbb{N}} % naturels
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\K}{\mathbb{K}} % field
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cF}{\mathcal{F}} % flip graph
\newcommand{\cN}{\mathcal{N}} % sorting network
\renewcommand{\b}[1]{\boldsymbol{#1}} % bold letters
\renewcommand{\c}[1]{\mathcal{#1}} % caligraphic letters
\newcommand{\f}[1]{\mathfrak{#1}} % frak letters
\newcommand{\bb}[1]{\mathbb{#1}} % bbold letters
% autres
\setlength{\parindent}{0pt} % aucune indentation dans tout le document
\graphicspath{{figures/}{figures/nodes/}} % les repertoires ou se trouvent les figures
\newcommand{\papier}[1]{{\violet\fontsize{15}{20}\selectfont #1}} % citation papier
\newcommand{\theo}[2]{\gboite{{\blue \fontsize{18}{25}\selectfont #1.} #2}}
\newcommand{\HUGE}[1]{{\fontsize{35}{33}\selectfont #1}}
\newcommand{\esperluette}{ \\ --- \& --- \\ } % esperluette stylisée nouvelle ligne
\DeclareRobustCommand{\verylongrightarrow}{\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\relbar\joinrel\rightarrow}
\renewcommand{\emph}[1]{\uline{#1}}

% specific wiggly
\newcommand{\polytope}[1]{\mathds{#1}} % font polytope
\newcommand{\wigglyComplex}{\mathrm{WC}} % wiggly complex
\newcommand{\wigglyFlipGraph}{\mathrm{WFG}} % wiggly flip graph
\newcommand{\wigglyIncreasingFlipGraph}{\mathrm{WIFG}} % wiggly increasing flip graph
\newcommand{\wigglyLattice}{\mathrm{WL}} % wiggly lattice
\newcommand{\wigglyFan}{\mathrm{WF}} % wiggly fan
\newcommand{\wigglyhedron}{\polytope{W}} % wigglyhedron
\newcommand{\Asso}{\polytope{A}\mathsf{sso}} % associahedron

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\titre}{From permutahedra to associahedra, a walk through geometric and algebraic combinatorics}
\newcommand{\auteur}{Vincent Pilaud}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\fontshape{sf}\fontsize{22}{28}\selectfont % police par defaut
\sf
\pagestyle{empty} % bas de page par defaut

\vspace*{-1cm}
\begin{center}
{\blue \fontsize{60}{60}\selectfont
\uppercase{Wigglyhedra}

}

\vspace{.8cm}

A. BAPAT
(The Australian National University)

V. PILAUD
(Universitat de Barcelona)

\href{https://arxiv.org/abs/2407.11632}{\texttt{arxiv:2407.11632}}

\vspace{.2cm}
\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}\quad\includegraphics[scale=1.7]{wigglyLattice}}

\vspace{.3cm}

DMG Seminar Berlin --- October 9, 2024

\vspace*{-.6cm}

\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Triangulations \& associahedra}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Pseudotriangulations \& PPT polytope}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Wiggly pseudotriangulations \& wiggly complex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wiggly complex}

\emph{wiggly dissection} $=$ set of pairwise \emph{non-crossing} and \emph{pointed} wiggly arcs on $n+2$ points

\hspace{9.3cm}\includegraphics[scale=1.7]{incompatible}

\vspace{.2cm}
\emph{wiggly complex}~$\wigglyComplex_n$ $=$ simplicial complex of wiggly dissections

\vspace{.2cm}
\centerline{\includegraphics[scale=1.7]{wigglyComplex}}

%\theo{PROP}{The wiggly complex is a pure $(2n-1)$-dimensional pseudomanifold.}

\end{slide}

%%%

\begin{slide}{Wiggly complex}

\emph{wiggly dissection} $=$ set of pairwise \emph{non-crossing} and \emph{pointed} wiggly arcs on $n+2$ points

\hspace{9.3cm}\includegraphics[scale=1.7]{incompatible}

\vspace{.2cm}
\emph{wiggly complex}~$\wigglyComplex_n$ $=$ simplicial complex of wiggly dissections

\begin{align*}
f(\wigglyComplex_1) & = (1, 2) \\
f(\wigglyComplex_2) & = (1, 9, 21, 14) \\
f(\wigglyComplex_3) & = (1, 24, 154, 396, 440, 176) \\
f(\wigglyComplex_4) & = (1, 55, 729, 4002, 10930, 15684, 11312, 3232) \\
f(\wigglyComplex_5) & = (1, 118, 2868, 28110, 140782, 400374, 673274, 662668, 352728, 78384) \\[.8cm]
h(\wigglyComplex_1) & = (1, 1) \\
h(\wigglyComplex_2) & = (1, 6, 6, 1) \\
h(\wigglyComplex_3) & = (1, 19, 68, 68, 19, 1) \\
h(\wigglyComplex_4) & = (1, 48, 420, 1147, 1147, 420, 48, 1) \\
h(\wigglyComplex_5) & = (1, 109, 1960, 11254, 25868, 25868, 11254, 1960, 109, 1)
\end{align*}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wiggly pseudotriangulations}

$c$ cell in a wiggly dissection with boundary $\partial_c$ \\
\emph{degree} $\delta_c =  1/2 \, \# \text{arcs on } \partial_c + 2 \, \# \text{connected components of } \partial_c - 1$ \\
\emph{pseudotriangle} $=$ cell of degree $3$ \qquad \emph{pseudoquadragle} $=$ cell of degree $4$

\vspace{.4cm}
\centerline{\includegraphics[scale=3]{wigglyPseudodissections}}

\vspace{.1cm}
\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells.}

\vspace{.3cm}
%$wp_n = \#$wiggly pseudotriangulations
\[
\begin{array}{c|ccccccccc}
n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
\hline
wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
\end{array}
\]

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wiggly flip graph}

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed.}

\vspace{.1cm}
\centerline{\includegraphics[scale=2]{diagonalsPseudoquadrangles}}

\end{slide}

%%%

\begin{slide}{Wiggly flip graph}

\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed.}

\vspace{.1cm}
\centerline{\includegraphics[scale=2]{diagonalsPseudoquadrangles}}

\vspace{-.4cm}
\emph{wiggly flip graph} $\wigglyFlipGraph_n =$ \begin{tabular}[t]{|ll} a vertex for each wiggly pseudotriangulation \\ an edge between~$T$ and~$T'$ if~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$ \end{tabular}

\vspace{.3cm}
\centerline{\includegraphics[scale=3]{wigglyFlip}}

\end{slide}

%%%

\begin{slide}{Wiggly flip graph}

\vspace{.5cm}
\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected.}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.7]{wigglyComplex} \hspace{-2cm} \includegraphics[scale=1.7]{wigglyComplexDual}}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Wiggly permutations \& wiggly lattice}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wiggly permutations}

\vspace{1cm}
\hspace{13.5cm}
\includegraphics[scale=2]{wigglyLattice}

\vspace{-13.5cm}
\emph{wiggly permutation} = permutation of $2n$ avoiding
\begin{compactitem}
\item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
\item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
\end{compactitem}

\vspace{1cm}
\begin{minipage}{13.2cm}
\theo{PROP}{
The wiggly permutations induce a sublattice~$\wigglyLattice_n$ of the weak order on~$\f{S}_{2n}$.

}

\theo{PROP}{
The cover graph of the lattice~$\wigglyLattice_n$ is $(2n-1)$-regular and connected.
}
\end{minipage}

\vspace{5cm}
\[
\begin{array}{c|ccccccccc}
n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
\hline
wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
\end{array}
\]

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Bijection}

\vspace{1cm}
\centerline{\includegraphics[scale=1.42]{wigglyPseudotriangulations}}
\vspace{-.3cm}
\centerline{$
1234 \;\;\; 1243 \;\;\; 1342 \;\;\; 1423 \;\;\; 1432 \;\;\; 2134 \;\;\; 2143 \;\;\; 3412 \;\;\; 3421 \;\;\; 4123 \;\;\; 4132 \;\;\; 4213 \;\;\; 4312 \;\;\; 4321
$}

\vspace{1cm}
\theo{PROP}{The wiggly pseudotriangulations and wiggly permutations are in bijection.}

\vspace{.5cm}
\centerline{\includegraphics[scale=3]{bijection}}

\end{slide}

%%%

\begin{slide}{Bijection}

\theo{PROP}{This bijection induces a directed graph isomorphism between
\begin{compactitem}
\item the wiggly increasing flip graph on wiggly pseudotriangulations,
\item the Hasse diagram of the wiggly lattice on wiggly permutations.
\end{compactitem}
}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.8]{wigglyFlipGraph}\quad\raisebox{.5cm}{\includegraphics[scale=1.8]{wigglyLattice}}}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Wiggly fan}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{g- and c-vectors}

\emph{$\b{g}$-vector} of $\alpha =$ proj. on $\sum_{i = 1}^{2n} x_i = 0$ of \raisebox{-1.7cm}{\includegraphics[scale=4]{gvector}}

\vspace{-.5cm}
\emph{$\b{c}$-vector} of~$\alpha \in T = $ you don't want to know...

\vspace{.5cm}
\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases.}

\vspace{1cm}
\centerline{\raisebox{-4cm}{\includegraphics[scale=4]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{wiggly fan}

\emph{$\b{g}$-vector} of $\alpha =$ proj. on $\sum_{i = 1}^{2n} x_i = 0$ of \raisebox{-1.7cm}{\includegraphics[scale=4]{gvector}}

\vspace{.1cm}
\theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$).
}

\vspace{2cm}
Main observation:

\centerline{\includegraphics[scale=3.2]{incompatible2}}
\centerline{
${\red \b{g}(\alpha)} + {\orange \b{g}(\alpha')} = \big( {\green \b{g}(\beta)} + {\blue \b{g}(\beta')} \big) / 2$
\qquad
${\red \b{g}(\alpha)} + {\orange \b{g}(\alpha')} = {\green \b{g}(\beta)} + {\blue \b{g}(\beta')}$
}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Wigglyhedron}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wigglyhedron}

\emph{incompatibility degree}~$\delta(\alpha, \alpha') =$ 
\begin{compactitem}
\item $0$ if~$\alpha$ and~$\alpha'$ are pointed and non-crossing,
\item $1$ is~$\alpha$ and~$\alpha'$ are not pointed,
\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing.
\end{compactitem}

\vspace{.5cm}
$\kappa(\alpha) =$ \emph{incompatibility number} of~$\alpha = \sum_{\alpha'} \delta(\alpha, \alpha')$.

\vspace{2cm}
Main observation:

\centerline{\includegraphics[scale=3.2]{incompatible2}}
\centerline{
${\red \kappa(\alpha)} + {\orange \kappa(\alpha')} > \big( {\green \kappa(\beta)} + {\blue \kappa(\beta')} \big) / 2$
\qquad
${\red \kappa(\alpha)} + {\orange \kappa(\alpha')} > {\green \kappa(\beta)} + {\blue \kappa(\beta')}$
}

\vspace{1.5cm}
Hence, $\kappa$ satisfies all wall-crossing inequalities of the wiggly fan...

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Wigglyhedron}

\theo{THM}{
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \emph{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item intersection of the halfspaces~$\set{\b{x} \in \R^{2n}}{\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all wiggly arcs~$\alpha$,
\item convex hull of~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\vspace{-.5cm}
}

\vspace{1cm}
\centerline{\input{figures/wigglyhedron}}

\end{slide}

%%%

\begin{slide}{Wigglyhedron}

\theo{THM}{The wigglyhedron~$\wigglyhedron_n$ is a simple $(2n-1)$-dimensional polytope such that
\begin{compactitem}
\item the wiggly complex~$\wigglyComplex_n$ is the boundary complex of the polar of~$\wigglyhedron_n$,
\item the Hasse diagram of the wiggly lattice is a linear orientation of the graph of~$\wigglyhedron_n$.
\end{compactitem}
}

\vspace{1cm}
\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph} \quad \input{figures/wigglyhedron}}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Cambrian considerations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Cambrian considerations}

\theo{THM}{
For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
\begin{itemize}
\item \emph{$\delta$-triangulations} $=$ triangulation of the $\delta$-gon, whose vertex at abscissa $i$ has ordinate \\[-1cm]
\[
\text{positive if $\delta_j = {+}$
\qquad and \qquad
negative if $\delta_j = {-}$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-permutations} $=$ permutation of~$[n]$ avoiding for~$i < j < k$ \\[-1cm]
\[
\cdots j \cdots ki \cdots \text{ if~$\delta_j = +$}
\quad\text{and}\quad
\cdots ik \cdots j \cdots \text{ if~$\delta_j = -$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-wiggly pseudotriangulations} $=$ wiggly pseudotriangulation containing the arcs \\[-1cm]
\[
(0, j, {[1,j[}, \varnothing) \text{ for~$\delta_j = {+}$}
\qquad\text{and}\qquad
(0, j, \varnothing, {[1,j[}) \text{ for~$\delta_j = {-}$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-wiggly permutations} $=$ wiggly permutation~$\sigma$ of~$[2n]$ such that \\[-1cm]
\[
\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
\quad\text{and}\quad
\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)\quad\;\;
\]
\end{itemize}
\vspace{-.5cm}
}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.6]{wigglyCambrian1}}

\end{slide}

%%%

\begin{slide}{Cambrian considerations}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.6]{wigglyCambrian2}}

\end{slide}

%%%

\begin{slide}{Cambrian considerations}

\vspace{.5cm}
\centerline{\includegraphics[scale=1.6]{wigglyCambrian3}}

\end{slide}

%%%

\begin{slide}{Cambrian considerations}

\theo{THM}{
For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
\begin{itemize}
\item \emph{$\delta$-triangulations} $=$ triangulation of the $\delta$-gon, whose vertex at abscissa $i$ has ordinate \\[-1cm]
\[
\text{positive if $\delta_j = {+}$
\qquad and \qquad
negative if $\delta_j = {-}$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-permutations} $=$ permutation of~$[n]$ avoiding for~$i < j < k$ \\[-1cm]
\[
\cdots j \cdots ki \cdots \text{ if~$\delta_j = +$}
\quad\text{and}\quad
\cdots ik \cdots j \cdots \text{ if~$\delta_j = -$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-wiggly pseudotriangulations} $=$ wiggly pseudotriangulation containing the arcs \\[-1cm]
\[
(0, j, {[1,j[}, \varnothing) \text{ for~$\delta_j = {+}$}
\qquad\text{and}\qquad
(0, j, \varnothing, {[1,j[}) \text{ for~$\delta_j = {-}$}
\]
\vspace{-1.5cm}
\item \emph{$\delta$-wiggly permutations} $=$ wiggly permutation~$\sigma$ of~$[2n]$ such that \\[-1cm]
\[
\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
\quad\text{and}\quad
\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)\quad\;\;
\]
\end{itemize}
\vspace{-.5cm}
}

\vspace{.5cm}
\theo{PROP}{
The $\delta$-associahedron~$\Asso_\delta$ is normally equivalent to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly arcs.

}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\partie{Some open problems}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Open problem 1: graph properties of wigglyhedron}

\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}\quad\includegraphics[scale=1.7]{wigglyLattice}}

\theo{QU 1a}{Is the wiggly flip graph Hamiltonian?

\hfill \color{gray}{[NB: wiggly permutations do not form a zigzag language, right?]}
}

\theo{QU 1b}{What is the diameter of the wiggly flip graph?

%\hfill \color{gray}{[NB: $2n-1 \le \delta_n$]}
}

\end{slide}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{slide}{Open problem 2: wiggly pseudotriangulations of point sets}

$\b{P}$ arbitrary point set in the plane

\emph{wiggly complex}~$\wigglyComplex_{\b{P}}$ = simplicial complex of non-crossing and pointed wiggly edges

\vspace{-.5cm}\hspace{14.5cm}
\rotatebox{270}{\includegraphics[scale=1.1]{wigglyComplexSquare}}

\vspace*{-15cm}
\begin{minipage}{13cm}
\theo{Q2a}{Is~$\wigglyComplex_{\b{P}}$ the boundary complex of a simplicial polytope?

\color{gray}{
[NB: aligned points $\Rightarrow$ wigglyhedron \\
general position $\Rightarrow$ Rote--Santos--Streinu]
}

\vspace{.1cm}
}

\vspace{1cm}
\theo{Q2b}{Is the graph of~$\wigglyComplex_{\b{P}}$ Hamiltonian?}

\end{minipage}

\end{slide}

\end{document}

### 2024-10-08 exposeBerlin2410/exposeBerlin2410.tex
presentation Berlin

@@
 
-\vspace{.2cm}
-\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}\quad\includegraphics[scale=1.7]{wigglyLattice}}
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=1.8]{wigglyFlipGraph}\quad\raisebox{.5cm}{\includegraphics[scale=1.8]{wigglyLattice}}}
 
-\vspace{.3cm}
-
+\vspace{.1cm}
 DMG Seminar Berlin --- October 9, 2024
@@
 \partie{Pseudotriangulations \& PPT polytope}
+
+\begin{slide}{Three geometric structures}
+
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\begin{center}\includegraphics[scale=1.9]{geometricStructures0}\end{center}
+\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$
+
+\bigskip
+\begin{center}
+\begin{tabular}{rl}
+\emph{triangulation} & = maximal crossing-free set of edges \\
+\vspace{.3cm}
+\\
+
+\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
+\vspace{.3cm}
+\\
+
+\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
+\\
+\end{tabular}
+\end{center}
+\end{slide}
+
+\begin{slide}{Three geometric structures}
+
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\begin{center}\includegraphics[scale=1.9]{geometricStructures1}\end{center}
+\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$
+
+\bigskip
+\begin{center}
+\begin{tabular}{rl}
+\emph{triangulation} & = maximal crossing-free set of edges \\
+\vspace{.3cm}
+\\
+
+\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
+\vspace{.3cm}
+\\
+
+\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
+\\
+\end{tabular}
+\end{center}
+\end{slide}
+
+\begin{slide}{Three geometric structures}
+
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\begin{center}\includegraphics[scale=1.9]{geometricStructures2}\end{center}
+\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$
+
+\bigskip
+\begin{center}
+\begin{tabular}{rl}
+\emph{triangulation} & = maximal crossing-free set of edges \\
+\vspace{.3cm}
+& = decomposition into triangles \\
+
+\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
+\vspace{.3cm}
+& = decomposition into pseudotriangles \\
+
+\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
+& = decomposition into $k$-stars
+\end{tabular}
+\end{center}
+
+\vspace{.2cm}
+\papier{VP \& F. Santos, Multitriangulations as complexes of star polygons, 2009.}
+
+\vspace{-1cm}
+\end{slide}
+
+\begin{slide}{Three geometric structures}
+
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\begin{center}\includegraphics[scale=1.9]{geometricStructures3}\end{center}
+\vspace{-8cm} \hspace*{25.7cm} ${k=2}$
+
+\vspace{7cm}
+\begin{center}
+\emph{flip} = exchange an internal edge with the common bisector of the two adjacent cells
+\end{center}
+
+\vspace{-1cm}
+\end{slide}
+
+\begin{slide}{Three geometric structures}
+
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
+\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
+\begin{center}
+\begin{tabular}{r@{\quad $\longleftrightarrow$ \quad}l}
+\emph{associahedron} & crossing-free sets of internal edges \\
+\emph{pseudotriangulations polytope} & pointed crossing-free sets of internal edges \\
+{\red multiassociahedron} & $(k+1)$-crossing-free sets of $k$-internal edges
+\end{tabular}
+\end{center}
+
+\vspace{-1cm}
+\end{slide}
+
+%\begin{slide}{Three geometric structures}
+%\vspace{-.8cm}
+%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
+%\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
+%
+%\vspace{-.7cm}
+%\begin{flushright}
+%``Our main limits in understanding the combinatorial structure of polytopes still\\
+%lie in our ability to raise the good questions and in the \emph{lack of examples},\\
+%\emph{methods of constructing them}, and \emph{means of classifying them}.'' \\
+%\papier{G. Kalai, \emph{Handbook of Discrete \& Computational Geometry}.}
+%\end{flushright}
+%
+%\vspace{-2cm}
+%\end{slide}
+
+%%%%%%%
+
+\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}
+
+\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}
+
+\end{slide}
+
+%%%%%%%
+
+\multido{\n=0+1}{10}{%
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\vspace{-.5cm}\\
+\vspace*{-2cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
+\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+\end{slide}
+}
+
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\vspace{-.5cm}\\
+\vspace*{-2cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
+\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+\end{slide}
+
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\vspace{-.5cm}\\
+\vspace*{-2cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
+\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+\end{slide}
+
+\multido{\n=0+1}{10}{%
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\vspace{-.5cm}\\
+\vspace*{-2cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
+\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+\end{slide}
+}
+
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\vspace{-.5cm}\\
+\vspace*{-2cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
+\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+
+\vspace{7.6cm}
+\papier{VP \& M. Pocchiola, Multitriangulations, pseudotriangulations and primitive sorting networks, 2012.}
+
+\vspace*{-3cm}
+\end{slide}
+
+%%%%%%%%%
+
+\begin{slide}{Duality}
+\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
+
+\vspace{1.3cm}
+\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
+\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
+\end{slide}
 
@@
 \vspace{.5cm}
-\centerline{\includegraphics[scale=3]{bijection}}
+\centerline{\includegraphics[scale=3.3]{bijection}}
 
@@
 
-\theo{QU 1a}{Is the wiggly flip graph Hamiltonian?
+\theo{Q1a}{Is the wiggly flip graph Hamiltonian?
 
@@
 
-\theo{QU 1b}{What is the diameter of the wiggly flip graph?
+\theo{Q1b}{What is the diameter of the wiggly flip graph?
 
@@
 
-\begin{slide}{Open problem 2: wiggly pseudotriangulations of point sets}
+\begin{slide}{Open problem 2: wiggly pseudotriangulations and duality}
+%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+%\vspace{-.5cm}\\
+
+\vspace*{-.8cm}
+\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
+\vspace{-10.5cm} \\ \hspace*{25.7cm} ${k=2}$
+
+\vspace{7.8cm}
+\theo{Q2}{Is there a dual interpretation of wiggly pseudotriangulations?}
+
+\vspace*{-3cm}
+\end{slide}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{slide}{Open problem 3: wiggly pseudotriangulations of point sets}
 
@@
 \begin{minipage}{13cm}
-\theo{Q2a}{Is~$\wigglyComplex_{\b{P}}$ the boundary complex of a simplicial polytope?
+\theo{Q3a}{Is~$\wigglyComplex_{\b{P}}$ the boundary complex of a simplicial polytope?
 
@@
 \vspace{1cm}
-\theo{Q2b}{Is the graph of~$\wigglyComplex_{\b{P}}$ Hamiltonian?}
+\theo{Q3b}{Is the graph of~$\wigglyComplex_{\b{P}}$ Hamiltonian?}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+\vspace*{2cm}
+\centerline{\includegraphics[scale=1.8]{wigglyFlipGraph}\quad\raisebox{.5cm}{\includegraphics[scale=1.8]{wigglyLattice}}}
+
+\vspace*{.2cm}
+\centerline{\includegraphics[scale=4]{wigglyThankYou}}
+
 \end{document}

### 2024-10-09 draft/wigglyhedra.tex
minor
minor corrections
expose Berlin

@@
 \begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
+\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
 \item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
@@
 	\fontsize{10}{10}\selectfont
-	\setlength\arraycolsep{1.1pt}
+	\setlength\arraycolsep{2pt}
 	\begin{alignat*}{3}
@@
 	\end{pmatrix}
-	\qquad &
+	\quad &
 %	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
@@
 	\end{pmatrix}
+	\quad
 	\\[.3cm]
@@
 	\end{pmatrix}
-	\qquad &
+	\quad &
 %	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
@@
 \begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
+\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \! \le \! \kappa(\alpha)}$ for all internal wiggly~arcs~$\alpha$,
 \item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
@@
 The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
-The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \le \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
+The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \ge \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
 

### 2024-10-09 exposeBerlin2410/exposeBerlin2410.tex
expose Berlin

@@
 \rule{.9\textwidth}{0.5 pt} \\[.5cm]
-\fontsize{30}{30}\selectfont {\blue\uppercase{#1}} \\[-.35cm]
+\fontsize{30}{30}\selectfont {\blue \uppercase{#1}} \\[-.35cm]
 \rule{.9\textwidth}{0.5 pt} \\
@@
 \newcommand{\Asso}{\polytope{A}\mathsf{sso}} % associahedron
+\newcommand{\HH}{\mathbb{H}} % hyperplane
+\newcommand{\HS}{\b{H}^\ge} % half-space
 
@@
 
+\begin{slide}{ASSOCIAHEDRON}
+
+\gboite{
+\emph{Associahedron} = polytope whose face lattice is isomorphic to the lattice of crossing-free sets of internal diagonals of a convex $(n+3)$-gon, ordered by reverse inclusion
+}
+
+\vspace{.2cm}
+\centerline{\includegraphics[scale=3.1]{associahedron}}
+\vspace*{-3.5cm}
+\begin{tabular}{r@{ $\leftrightarrow$ }l}
+vertices & triangulations \\
+edges & flips \\
+faces & dissections
+\end{tabular}
+\hfill
+\begin{tabular}{r@{ $\leftrightarrow$ }l}
+vertices & binary trees \\
+edges & rotations \\
+faces & Schr\"oder trees
+\end{tabular}
+
+\end{slide}
+
+%%%%%%%%%%
+%
+%\begin{slide}{VARIOUS ASSOCIAHEDRA}
+%
+%\gboite{
+%\emph{Associahedron} = polytope whose face lattice is isomorphic to the lattice of crossing-free sets of internal diagonals of a convex $(n+3)$-gon, ordered by reverse inclusion
+%}
+%
+%\vspace{.5cm}
+%\centerline{\includegraphics[width=\textwidth]{manyAssociahedra1}}
+%\vspace{.5cm}
+%\centerline{\includegraphics[width=\textwidth]{manyAssociahedra2}}
+%
+%\vspace{-.2cm}
+%\hfill {\normalsize (Pictures by Ceballos-Santos-Ziegler)}
+%
+%\vspace{-.9cm}
+%\papier{
+%
+%Tamari ('51) --- Stasheff ('63) --- Haimann ('84) --- Lee ('89) --- \hspace*{12.5cm} \\[.2cm]
+%\dots --- Gel'fand-Kapranov-Zelevinski ('94) --- \dots --- Chapoton-Fomin-Zelevinsky ('02) --- \dots --- Loday ('04) --- \dots \hspace*{1.5cm} \\[.2cm]
+%--- Ceballos-Santos-Ziegler ('11)
+%
+%}
+%
+%\end{slide}
+
+%%%%%%%%%
+
+\begin{slide}{THREE FAMILIES OF REALIZATIONS}
+
+\vspace{-.25cm}
+\hspace{-1.2cm}
+\begin{tabular}{cc|ccc|cc}
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue SECONDARY} \\ {\blue POLYTOPE} \\[.5cm]
+\end{center}
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=1.5]{associahedron}}
+\vspace{.1cm}
+\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)
+
+}
+\vspace{8cm}
+\end{minipage}
+&&&
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue LODAY'S ASSOCIAHEDRON} \\[.5cm]
+\end{center}
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=.78]{associahedronLoday}}
+\vspace{-.4cm}
+\papier{Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--Pilaud--Stella ('18) \\ Pilaud--Santos--Ziegler ('24)
+
+}
+\end{minipage}
+&&&
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue CHAP.--FOM.--ZEL.'S ASSOCIAHEDRON} \\[.5cm]
+\end{center}
+\centerline{\input{figures/associahedronCFZ}}
+\vspace{-7.5cm}\hspace{5.3cm}
+{\normalsize (Pictures by CFZ)}
+\vspace{5.8cm}
+
+\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)
+
+}
+\end{minipage}
+\end{tabular}
+
+\end{slide}
+
+%%%%%%%%%
+
+\begin{slide}{THREE FAMILIES OF REALIZATIONS}
+
+\vspace{-.25cm}
+\hspace{-1.2cm}
+\begin{tabular}{cc|ccc|cc}
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue SECONDARY} \\ {\blue POLYTOPE} \\[.5cm]
+\end{center}
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=1.5]{associahedron}}
+\vspace{.1cm}
+\papier{Gelfand--Kapranov--Zelevinsky ('94) \\ Billera--Filliman--Sturmfels ('90)
+
+}
+\vspace{.1cm}
+\centerline{\includegraphics[scale=1.5]{secondaryPolytope}}
+\vspace{1cm}
+\end{minipage}
+&&&
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue LODAY'S ASSOCIAHEDRON} \\[.5cm]
+\end{center}
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=.78]{associahedronLoday}}
+\vspace{-.4cm}
+\papier{Loday ('04) \\ Hohlweg--Lange ('07) \\ Hohlweg--Lange--Thomas ('12) \\ Hohlweg--Pilaud--Stella ('18) \\ Pilaud--Santos--Ziegler ('24)
+
+}
+\vspace{.3cm}
+\hspace{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Hopf \\ algebra \\[-1.2cm] ~\end{center} \end{minipage}} \\[.2cm]
+\hspace*{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Cluster \\ algebras \\[-1.2cm] ~\end{center} \end{minipage}} \\
+\vspace{-4.7cm}
+\hspace*{3.5cm}\includegraphics[scale=.35]{associahedronTypeB}
+\vspace{-.2cm}
+\hspace*{2.5cm}\includegraphics[scale=.35]{associahedronTypeH}
+\end{minipage}
+&&&
+\begin{minipage}[t]{8.5cm}
+\begin{center}
+{\blue CHAP.--FOM.--ZEL.'S ASSOCIAHEDRON} \\[.5cm]
+\end{center}
+\centerline{\input{figures/associahedronCFZ}}
+\vspace{-7.5cm}\hspace{5.3cm}
+{\normalsize (Pictures by CFZ)}
+\vspace{5.8cm}
+
+\papier{Chapoton--Fomin--Zelevinsky ('02) \\ Ceballos--Santos--Ziegler ('11)
+
+}
+\vspace{1.2cm}
+\hspace{-.4cm}\boxed{\begin{minipage}{2.5cm} \smallskip \begin{center} \blue Cluster \\ algebras \\[-1.2cm] ~\end{center} \end{minipage}} \\
+\vspace{-3cm}
+\centerline{\hspace{2.5cm}\input{figures/cyclohedronCFZ}}
+
+\end{minipage}
+\end{tabular}
+
+\end{slide}
+
+%%%%%%%%%
+%
+%\begin{slide}{LODAY'S ASSOCIAHEDRON}
+%
+%\vspace{-.3cm}
+%\cboite{
+%\vspace{-.7cm}
+%\[
+%\Asso(n) \, \eqdef \, \conv \set{\b{L}(T)}{T \text{ binary tree}} \, = \, \HH \; \cap \!\!\!\!\!\! \bigcap_{1 \le i \le j \le n+1} \!\!\!  \HS(i,j)
+%\]
+%\vspace{-.3cm}
+%\[
+%\b{L}(T) \eqdef \big[ \ell(T, i) \cdot r(T, i) \big]_{i \in [n+1]}
+%\qquad
+%\HS(i,j) \eqdef \biggset{\b{x} \in \R^{n+1}}{\sum_{i \le k \le j} x_i \ge \binom{j-i+2}{2} \!\! }
+%\]
+%
+%\flushright{
+%\papier{
+%	Shnider-Sternberg, \textit{Quantum groups: From coalgebras to Drinfeld algebras} ('93) \\
+%	Loday, \textit{Realization of the Stasheff polytope} ('04)
+%	
+%}}
+%}
+%
+%\vspace{.3cm}
+%\centerline{\raisebox{1cm}{\includegraphics[scale=2.2]{LodayVector}} \qquad  \includegraphics[scale=1.15]{associahedronLoday}}
+%
+%\end{slide}
+%
+%%%%%%%%%
+
+\begin{slide}{LODAY'S ASSOCIAHEDRON}
+
+\vspace*{-1cm}
+\begin{align*}
+\text{\blue Loday's associahedron} \; & = \; \conv \set{L(T)}{T \text{ triangulation of the } (n+3)\text{-gon}} \\
+& = \; \HH \; \cap \!\!\!\!\! \bigcap_{\substack{\delta \text{ diagonal} \\ \text{of the } (n+3)\text{-gon}}} \!\!\!\!\!\!\!\!\!\! \HS(\delta)
+\end{align*}
+
+\vspace{-.5cm}
+\centerline{
+	\begin{overpic}[scale=2.5]{lodayTriangulation}
+		\put(30,90){$i$}
+		\put(175,0){$j$}
+		\put(345,175){$k$}
+		\put(53,23){$\ell(T,j)$}
+		\put(295,55){$r(T,j)$}
+		\put(560,140){$\delta$}
+		\put(595,5){$B(\delta)$}
+   \end{overpic}
+}
+\[
+\hspace{1.8cm}
+L(T) = \big(\ell(T,j) \, \cdot \, r(T,j)\big)_{j \in [n+1]}
+\hspace{1.7cm}
+\HS(\delta) = \biggset{\b{x} \in \R^{n+1}}{\sum_{j \in B(\delta)} x_j \ge \binom{|B(\delta)|+1}{2}}
+\]
+
+\vspace{.5cm}
+\papier{Loday ('04)}
+
+\end{slide}
+
+%%%%%%%%%
+
+\begin{slide}{HOHLWEG \& LANGE'S ASSOCIAHEDRA}
+
+Can also replace Loday's $(n+3)$-gon by others\dots
+
+\vspace{.2cm}
+\centerline{\includegraphics[width=\textwidth]{polygonsHohlwegLange}}
+
+\vspace{-.3cm}
+\dots to obtain different realizations of the associahedron
+
+\vspace{.1cm}
+\centerline{\includegraphics[scale=2]{associahedronLodayHL}}
+
+\vspace{-.6cm}
+\papier{Hohlweg--Lange ('07)}
+
+\end{slide}
+
+%%%%%%%%%
+
+\begin{slide}{HOHLWEG \& LANGE'S ASSOCIAHEDRA}
+
+\vspace*{-1cm}
+\[
+\Asso(P) \; = \; \conv \set{H\!L(T)}{T \text{ triangulation of } P} \; = \; \HH \; \cap \!\!\!\!\! \bigcap_{\delta \text{ diagonal of } P} \!\!\!\!\!\!\!\!\!\! \HS(\delta)
+\]
+
+\vspace{-.6cm}
+\centerline{
+	\begin{overpic}[scale=2.5]{hohlwegLange}
+		\put(30,85){$i$}
+		\put(85,325){$j$}
+		\put(255,30){$k$}
+		\put(-20,225){$\ell(T,j)$}
+		\put(275,290){$r(T,j)$}
+		\put(540,165){$\delta$}
+		\put(370,110){$B(\delta)$}
+   \end{overpic}
+}
+
+\vspace{-1.3cm}
+\[
+\hspace*{-1cm}
+H\!L(T)_j =
+\begin{cases}
+	\ell(T,j) \cdot r(T,j) & \text{if } j \text{ down} \\
+	n+2-\ell(T,j) \cdot r(T,j) & \text{if } j \text{ up}
+\end{cases}
+\hspace{1.4cm}
+\HS(\delta) = \biggset{\b{x}}{\sum_{j \in B(\delta)} x_j \ge \binom{|B(\delta)|+1}{2}}
+\]
+
+\papier{Hohlweg--Lange ('07)}
+
+\end{slide}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \partie{Pseudotriangulations \& PPT polytope}
@@
 
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \begin{center}\includegraphics[scale=1.9]{geometricStructures0}\end{center}
@@
 
-\bigskip
-\begin{center}
-\begin{tabular}{rl}
-\emph{triangulation} & = maximal crossing-free set of edges \\
-\vspace{.3cm}
-\\
-
-\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
-\vspace{.3cm}
-\\
-
-\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
-\\
-\end{tabular}
-\end{center}
-\end{slide}
+\hspace{1.7cm} 
+\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\  \end{tabular} 
+\hspace{3.4cm} 
+\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
+\hspace{2cm} 
+\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ \\  \end{tabular}
+
+\end{slide}
+
+%%%
 
@@
 
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \begin{center}\includegraphics[scale=1.9]{geometricStructures1}\end{center}
@@
 
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \begin{center}\includegraphics[scale=1.9]{geometricStructures2}\end{center}
@@
 
-\bigskip
-\begin{center}
-\begin{tabular}{rl}
-\emph{triangulation} & = maximal crossing-free set of edges \\
-\vspace{.3cm}
-& = decomposition into triangles \\
-
-\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
-\vspace{.3cm}
-& = decomposition into pseudotriangles \\
-
-\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
-& = decomposition into $k$-stars
-\end{tabular}
-\end{center}
-
-\vspace{.2cm}
-\papier{VP \& F. Santos, Multitriangulations as complexes of star polygons, 2009.}
-
-\vspace{-1cm}
-\end{slide}
+\hspace{1.7cm} 
+\begin{tabular}[t]{c} crossing-free \\ \\[-.3cm] \\ \\ triangles \end{tabular} 
+\hspace{3.4cm} 
+\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
+\hspace{2cm} 
+\begin{tabular}[t]{c} $(k+1)$-crossing-free \\ \papier{Capoyleas--Pach ('92)} \\[-.3cm] \papier{Jonsson ('05)} \\ \\ $k$-stars \\ \papier{P.--Santos ('09)} \end{tabular}
+
+\end{slide}
+
+%%%
 
@@
 
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \begin{center}\includegraphics[scale=1.9]{geometricStructures3}\end{center}
@@
 
-\vspace{-1cm}
-\end{slide}
+\end{slide}
+
+%%%
 
@@
 
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
 \begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
-\begin{center}
-\begin{tabular}{r@{\quad $\longleftrightarrow$ \quad}l}
-\emph{associahedron} & crossing-free sets of internal edges \\
-\emph{pseudotriangulations polytope} & pointed crossing-free sets of internal edges \\
-{\red multiassociahedron} & $(k+1)$-crossing-free sets of $k$-internal edges
-\end{tabular}
-\end{center}
+\hspace{1.5cm} associahedron \hspace{2.6cm} pseudotriangulation polytope \hspace{1.2cm} multiassociahedron
 
@@
 %\vspace{-.8cm}
-%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
+%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
 %\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
@@
 \begin{slide}{Duality}
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \vspace{-.5cm}\\
@@
 
+%%%
+
 \begin{slide}{Duality}
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \vspace{-.5cm}\\
@@
 
+%%%
+
 \multido{\n=0+1}{10}{%
 \begin{slide}{Duality}
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 \vspace{-.5cm}\\
@@
 \vspace{7.6cm}
-\papier{VP \& M. Pocchiola, Multitriangulations, pseudotriangulations and primitive sorting networks, 2012.}
+\papier{P.--Pocchiola ('12)}
 
@@
 
-%%%%%%%%%
-
-\begin{slide}{Duality}
-\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
-
-\vspace{1.3cm}
-\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
-\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
-\end{slide}
+%%%%%%%%%%
+%
+%\begin{slide}{Duality}
+%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations
+%
+%\vspace{1.3cm}
+%\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
+%\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
+%\end{slide}
 
@@
 \vspace{.1cm}
-\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells.}
+\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}}
 
@@
 
-\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed.}
+\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}}
 
@@
 \vspace{.5cm}
-\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected.}
+\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}}
 
@@
 
+\hfill \papier{Bapat--P. (24$^+$)}
 }
@@
 The cover graph of the lattice~$\wigglyLattice_n$ is $(2n-1)$-regular and connected.
+
+\hfill \papier{Bapat--P. (24$^+$)}
 }
@@
 
-\vspace{5cm}
+\vspace{3cm}
 \[
@@
 
-\begin{slide}{Bijection}
+\begin{slide}{Wiggly pseudotriangulations $\longleftrightarrow$ wiggly permutations}
 
@@
 \vspace{1cm}
-\theo{PROP}{The wiggly pseudotriangulations and wiggly permutations are in bijection.}
+\theo{PROP}{The wiggly pseudotriangulations and wiggly permutations are in bijection.
+
+\hfill \papier{Bapat--P. (24$^+$)}
+}
 
@@
 
-\end{slide}
-
-%%%
-
-\begin{slide}{Bijection}
+{\color{gray}
+permutation of $2n$ avoiding \begin{tabular}[t]{@{}l} $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$ \\ $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$ \end{tabular}}
+
+\end{slide}
+
+%%%
+
+\begin{slide}{Wiggly pseudotriangulations $\longleftrightarrow$ wiggly permutations}
 
@@
 \item the wiggly increasing flip graph on wiggly pseudotriangulations,
-\item the Hasse diagram of the wiggly lattice on wiggly permutations.
+\item the Hasse diagram of the wiggly lattice on wiggly permutations. \hfill \papier{Bapat--P. (24$^+$)}
 \end{compactitem}
@@
 \vspace{.5cm}
-\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases.}
+\theo{PROP}{For any wiggly pseudotriangulation~$T$, the $\b{g}$-vectors~$\set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and the $\b{c}$-vectors~$\set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases.
+\hfill \papier{Bapat--P.
+(24$^+$)}}
 
@@
 \theo{THM}{The cones~$\setangle{\b{g}(\alpha)}{\alpha \in D}$ for all wiggly dissections~$D$ form a complete simplicial fan~$\wigglyFan_n$ (in $\sum_{i = 1}^{2n} x_i = 0$).
+\hfill \papier{Bapat--P.
+(24$^+$)}
 }
@@
 \end{itemize}
-\vspace{-.5cm}
-}
-
-\vspace{1cm}
+
+\vspace{-.6cm}
+\hfill \papier{Bapat--P. (24$^+$)}
+}
+
+\vspace{.5cm}
 \centerline{\input{figures/wigglyhedron}}
@@
 \end{compactitem}
+
+\hfill \papier{Bapat--P. (24$^+$)}
 }
@@
 For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between
+
+\vspace{-.4cm}
 \begin{itemize}
@@
 \end{itemize}
+
 \vspace{-.5cm}
-}
-
-\vspace{.5cm}
+\hfill \papier{Bapat--P. (24$^+$)}
+}
+
+\vspace{.3cm}
 \centerline{\includegraphics[scale=1.6]{wigglyCambrian1}}
-
-\end{slide}
-
-%%%
-
-\begin{slide}{Cambrian considerations}
-
-\vspace{.5cm}
-\centerline{\includegraphics[scale=1.6]{wigglyCambrian2}}
-
-\end{slide}
-
-%%%
-
-\begin{slide}{Cambrian considerations}
-
-\vspace{.5cm}
-\centerline{\includegraphics[scale=1.6]{wigglyCambrian3}}
 
@@
 For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
-\begin{itemize}
-\item \emph{$\delta$-triangulations} $=$ triangulation of the $\delta$-gon, whose vertex at abscissa $i$ has ordinate \\[-1cm]
-\[
-\text{positive if $\delta_j = {+}$
-\qquad and \qquad
-negative if $\delta_j = {-}$}
-\]
-\vspace{-1.5cm}
-\item \emph{$\delta$-permutations} $=$ permutation of~$[n]$ avoiding for~$i < j < k$ \\[-1cm]
-\[
-\cdots j \cdots ki \cdots \text{ if~$\delta_j = +$}
-\quad\text{and}\quad
-\cdots ik \cdots j \cdots \text{ if~$\delta_j = -$}
-\]
-\vspace{-1.5cm}
-\item \emph{$\delta$-wiggly pseudotriangulations} $=$ wiggly pseudotriangulation containing the arcs \\[-1cm]
-\[
-(0, j, {[1,j[}, \varnothing) \text{ for~$\delta_j = {+}$}
-\qquad\text{and}\qquad
-(0, j, \varnothing, {[1,j[}) \text{ for~$\delta_j = {-}$}
-\]
-\vspace{-1.5cm}
-\item \emph{$\delta$-wiggly permutations} $=$ wiggly permutation~$\sigma$ of~$[2n]$ such that \\[-1cm]
-\[
-\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
-\quad\text{and}\quad
-\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)\quad\;\;
-\]
-\end{itemize}
-\vspace{-.5cm}
+\begin{compactitem}
+\item $\delta$-triangulations
+\item $\delta$-permutations
+\item $\delta$-wiggly pseudotriangulations
+\item $\delta$-wiggly permutations \hfill \papier{Bapat--P. (24$^+$)}
+\end{compactitem}
+}
+
+\vspace{.5cm}
+\centerline{\includegraphics[scale=1.5]{wigglyCambrian2}}
+
+\end{slide}
+
+%%%
+
+\begin{slide}{Cambrian considerations}
+
+\theo{THM}{
+For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
+\begin{compactitem}
+\item $\delta$-triangulations
+\item $\delta$-permutations
+\item $\delta$-wiggly pseudotriangulations
+\item $\delta$-wiggly permutations \hfill \papier{Bapat--P. (24$^+$)}
+\end{compactitem}
+}
+
+\vspace{-.2cm}
+\centerline{\includegraphics[scale=1.5]{wigglyCambrian3}}
+
+\end{slide}
+
+%%%
+
+\begin{slide}{Cambrian considerations}
+
+\theo{THM}{
+For $\delta = \delta_1 \dots \delta_n \in \{+,-\}^n$, there are lattice isomorphisms between 
+\begin{compactitem}
+\item $\delta$-triangulations
+\item $\delta$-permutations
+\item $\delta$-wiggly pseudotriangulations
+\item $\delta$-wiggly permutations \hfill \papier{Bapat--P. (24$^+$)}
+\end{compactitem}
 }
@@
 \begin{slide}{Open problem 2: wiggly pseudotriangulations and duality}
-%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
+%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
 %\vspace{-.5cm}\\

### 2024-10-11 FPSAC25/wigglyhedraFPSAC.tex
start FPSAC

--- 2024-10-09 draft/wigglyhedra.tex
@@
-\documentclass{amsart}
-
-\usepackage[T1]{fontenc}
-\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, shuffle, xargs, multicol, overpic, pdflscape, multirow, hvfloat, minibox, accents, array, multido, xifthen, a4wide, ae, aecompl, blkarray, pifont, mathtools, etoolbox, dsfont}
-\usepackage{marginnote}
-\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
-\usepackage[all]{xy}
-\usepackage[bottom]{footmisc}
-\usepackage{tikz}
-%\usepackage{tkz-graph}
-%\usepackage{tikz-qtree}
-\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles, cd}
-\usepackage[external]{forest}
-%\tikzexternalize
-\graphicspath{{figures/}}
-\makeatletter\def\input@path{{figures/}}\makeatother
-\usepackage{caption}
-\captionsetup{width=\textwidth}
-\renewcommand{\topfraction}{1} % possibility to have one page of pictures
-\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
-\usepackage[noabbrev,capitalise]{cleveref}
-\usepackage[export]{adjustbox}
-\usepackage{ulem}\normalem
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% if you are submitting an initial manuscript then you should have submission as an option here
+%% if you are submitting a revised manuscript then you should have revision as an option here
+%% otherwise options taken by the article class will be accepted
+\documentclass[submission]{FPSAC2025}
+%% but DO NOT pass any options (or change anything else anywhere) which alters page size / layout / font size etc
+
+%% note that the class file already loads {amsmath, amsthm, amssymb}
+
+\usepackage{xargs}
+\usepackage{hypcap}
+\usepackage{paralist}
+\usepackage{dsfont}
+\usepackage{mathtools}
+\usepackage{blkarray}
+\usepackage{picins/picins}
+\usepackage{overpic}
 
@@
 
-% formating the table of contents
-\setcounter{tocdepth}{4}
-\makeatletter
-\def\l@part{\@tocline{1}{8pt}{0pc}{}{}}
-\def\l@section{\@tocline{1}{4pt}{0pc}{}{}}
-\makeatother
-\let\oldtocpart=\tocpart
-\renewcommand{\tocpart}[2]{\sc\large\oldtocpart{#1}{#2}}
-\let\oldtocsection=\tocsection
-\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}
-\let\oldtocsubsubsection=\tocsubsubsection
-\renewcommand{\tocsubsubsection}[2]{\quad\oldtocsubsubsection{#1}{#2}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\graphicspath{{figures/}}
+
+%% define your title in the usual way
 \title{Wigglyhedra}
 
-\thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
-  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}
-
-\author{Asilata Bapat}
-\address{The Australian National University}
-\email{asilata.bapat@anu.edu.au}
-\urladdr{\url{https://asilata.github.io}}
-
-\author{Vincent Pilaud}
-\address{Universitat de Barcelona}
-\email{vincent.pilaud@ub.edu}
-\urladdr{\url{https://www.ub.edu/comb/vincentpilaud/}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% define your authors in the usual way
+%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
+%% for more than 3 names, use the Oxford comma: One Author, Two Author, Red Author, \and Blue Author
+\author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}.
+Supported by the Australian DECRA grant DE240100447.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{mailto:vincent.pilaud@ub.edu}.
+Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788) and by the Spanish grant PID2022-137283NB-C21.}\addressmark{2}}
+
+%% then use \addressmark to match authors to institutions here
+\address{\addressmark{1}The Australian National University, Canberra, Australia \\ \addressmark{2}Universitat de Barcelona, Spain}
+
+%% put the date of submission here
+\received{\today}
+
+%% leave this blank until submitting a revised version
+%\revised{}
+
+%% put your English abstract here, or comment this out if you don't have one yet
+%% please don't use custom commands in your abstract / resume, as these will be displayed online
+%% likewise for citations -- please don't use \cite, and instead write out your citation as something like (author year)
+\abstract{Motivated by categorical representation theory, we study the wigglyhedron.
+Its boundary complex encodes wiggly dissections (sets of pairwise pointed and non-crossing arcs wiggling around $n+2$ points on a line).
+Its graph is the Hasse diagram of the sublattice of the weak order induced by wiggly permutations (permutations of $[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$).
+It contains copies of all type~$A_n$ Cambrian lattices and Cambrian fans.}
+
+%% put your French abstract here, or comment this out if you don't have one
+\resume{Motivés par la théorie catégorique des représentations, nous étudions le slalomèdre.
+Son complexe de bord encode les dissections slalomantes (ensembles deux-à-deux pointés et sans croisement d'arcs slalomant autour de $n+2$ points sur une ligne).
+Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations slalomantes (permutations de $[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
+Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.}
+
+%% put your keywords here, or comment this out if you don't have them yet
+%\keywords{math, maths, mathematics}
+
+%% you can include your bibliography however you want, but using an external .bib file is STRONGLY RECOMMENDED and will make the editor's life much easier
+%% regardless of how you do it, please use numerical citations; i.e., [xx, yy] in the text
+
+%% this sample uses biblatex, which (among other things) takes care of URLs in a more flexible way than bibtex
+%% but you can use bibtex if you want
+\usepackage[backend=bibtex]{biblatex}
+\addbibresource{wigglyhedra.bib}
+%% note the \printbibliography command at the end of the file which goes with these biblatex commands
 
@@
 
-\begin{abstract}
-Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on a line, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
-The wiggly complex is a $(2n-1)$-dimensional pseudomanifold, whose facets are wiggly pseudotriangulations.
-We show that wiggly pseudotriangulations are in bijection with wiggly permutations, which are permutations of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
-These permutations define the wiggly lattice, an induced sublattice of the weak order.
-We then prove that the wiggly complex is isomorphic to the boundary complex of the polar of the wigglyhedron, for which we give explicit and simple vertex and facet descriptions.
-Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
-Finally, we recall the correspondence of wiggly arcs with objects in a category, and we develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
-\end{abstract}
+\stepcounter{footnote}
+\stepcounter{footnote}
 
 \maketitle
-
-\centerline{\includegraphics[scale=1.75]{wigglyFlipGraph}}
-
-\tableofcontents
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-In this paper we consider wiggly pseudotriangulations, which are built from arcs wiggling around points on a line.
-We study their combinatorics in detail, construct polyhedral realizations of their flip graph, and interpret them in terms of categorical representation theory.
-
-\bigskip
-\para{Combinatorics}
-Fix $n \ge 1$ and consider the~$n+2$ points on the horizontal axis labelled~${0, \dots, n+1}$.
-A \defn{wiggly arc} is an abscissa monotone curve starting at some point~$i$, ending at some point~$j$ (with~${0 \le i < j \le n+1}$), and passing above or below each point~$i+1, \dots, j-1$.
-Two wiggly arcs are \defn{compatible} if they are pointed (the left endpoint of one is not the right endpoint of the other) and non-crossing (the interiors of the curves are disjoint).
-A \defn{wiggly dissection} is a collection of pairwise compatible wiggly arcs, and a \defn{wiggly pseudotriangulation} is an inclusion maximal wiggly dissection.
-The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of wiggly dissections (minus their external wiggly arcs).
-We first establish the following result.
-
-\begin{proposition*}
-The wiggly complex~$\wigglyComplex_n$ is a $(2n-1)$-dimensional pseudomanifold without boundary.
-\end{proposition*}
-
-In particular, all wiggly pseudotriangulations have $2n-1$ internal wiggly arcs, each of which can be \defn{flipped}.
-We actually describe the flip in terms of wiggly diagonals in wiggly pseudoquadrangles.
-We also orient this flip graph in a canonical way, which we call the \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$.
-The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper (throughout the paper, we implicitly orient the graphs and posets from bottom to top).
-
-We then make a small detour to permutations.
-A \defn{wiggly permutation} is a permutation of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
-Our main result on wiggly permutations is the following.
-
-\begin{proposition*}
-The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, which we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
-Moreover, its Hasse diagram is regular of degree~$2n-1$.
-\end{proposition*}
-
-We then connect wiggly pseudotriangulations to wiggly permutations.
-
-\begin{proposition*}
-The increasing flip graph on wiggly pseudotriangulations~$\wigglyIncreasingFlipGraph_n$ is isomorphic to the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-In particular, the wiggly pseudotriangulations admit a lattice structure.
-\end{proposition*}
-
-\para{Polyhedral geometry}
-We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
-Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing} of support \mbox{$\tau$-tilting} complexes~\cite{AdachiIyamaReiten} on gentle algebras~\cite{ButlerRingel}.
-Namely, we first construct a fan supported by certain $\b{g}$-vectors associated to the wiggly arcs.
-
-\begin{theorem*}
-The cones generated by the $\b{g}$-vectors of wiggly pseudodissections form a complete simplicial fan, called \defn{wiggly fan}~$\wigglyFan_n$, realizing the wiggly complex~$\wigglyComplex_n$.
-\end{theorem*}
-
-The proof of this result is based on a fine understanding of the linear dependences between \mbox{$\b{g}$-vectors}.
-We further use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
-Without entering the details of the definition of~$\kappa$ at the moment, let us just mention that it is obtained by summing some compatibility degrees of wiggly arcs, analogously to the constructions for cluster algebras~\cite{HohlwegPilaudStella} and gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
-Using the $\b{c}$-vectors of each pseudotriangulation, defined to form the dual basis of the $\b{g}$-vectors, we obtain our main result.
-
-\begin{theorem*}
-The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
-\begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
-\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
-\end{itemize}
-\end{theorem*}
-
-Moreover, as for the classical permutahedron and associahedron, we recover our lattice structure by a suitable linear orientation of the graph of the wigglyhedron.
-
-\begin{proposition*}
-The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ (or equivalently, the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$) is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in a suitable direction.
-\end{proposition*}
-
-\para{Further topics}
-The wigglyhedron has interesting connections in lattice theory and discrete geometry.
-We first connect the wigglyhedron to the (type~$A$) Cambrian world.
-
-\begin{theorem*}
-For any~$\delta \in \{-,+\}^n$,
-\begin{itemize}
-\item the $\delta$-Cambrian lattice of~\cite{Reading-CambrianLattices} is an interval in the wiggly lattice~$\wigglyLattice_n$,
-\item the $\delta$-Cambrian fan of~\cite{ReadingSpeyer} is a link in the wiggly fan~$\wigglyFan_n$,
-\item the $\delta$-associahedron of~\cite{HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$.
-\end{itemize}
-\end{theorem*}
-
-We then define the wiggly complex~$\wigglyComplex_P$ of an arbitrary planar point set~$P$ (not necessarily aligned along the horizontal axis, nor necessarily in general position).
-Our definition recovers:
-\begin{itemize}
-\item when $P$ consists of $n+2$ collinear points, the wiggly complex~$\wigglyComplex_n$ considered in this~paper,
-\item when~$P$ is in general position, the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
-\end{itemize}
-These two families of examples motivate the following conjecture.
-
-\begin{conjecture*}
-For any point set~$P$ in the plane, the wiggly complex~$\wigglyComplex_P$ is the boundary complex of a simplicial polytope.
-\end{conjecture*}
-
-We also present a few open questions related to this conjecture, concerning in particular the possible interpretation of the wiggly complex~$\wigglyComplex_P$ in terms of dual pseudoline arrangements, and the extension to multi wiggly complexes and arbitrary finite Coxeter groups.
-
-\pagebreak
-\para{Categorical interpretation}
-Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the wiggly arcs.
-In fact, this correspondence holds for more general curves, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
-
-A general curve can be decomposed into wiggly arcs simply by cutting along its U-turns.
-We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
-
-\begin{proposition*}
-The set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc is a face of the wiggly complex.
-\end{proposition*}
-
-Furthermore, we characterize categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
-
-\begin{proposition*}
-Two wiggly arcs are compatible if and only if there are no extensions between the corresponding objects in the abelian category.
-\end{proposition*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Wiggly pseudotriangulations and wiggly permutations}
-\label{sec:combinatorics}
-
-Fix an integer~$n \ge 1$.
-In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points (\cref{subsec:wigglyPseudotriangulations}) and the wiggly permutations of~$[2n]$ (\cref{subsec:wigglyPermutations}), and we prove that they are in bijection (\cref{subsec:bijection}).
-These two perspectives enable us to endow these combinatorial families with additional structures: the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
-We conclude with a few questions and conjectures on graph properties of the wiggly flip graph (\cref{subsec:graphProperties}).
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly pseudotriangulations and the wiggly complex}
-\label{subsec:wigglyPseudotriangulations}
-
-We start with wiggly pseudodissections of $n+2$ points on a line.
-The following two definitions are illustrated in \cref{fig:incompatible}.
-
-\begin{definition}
-A \defn{wiggly arc} is a quadruple $\alpha \eqdef (i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~${]i,j[} \eqdef \{i+1, \dots, j-1\}$.
+%% note that you DO NOT have to put your abstract here -- it is generated by \maketitle and the \abstract and \resume commands above
+
+Motivated by categorical representation theory, we consider the wiggly complex (\cref{sec:wigglyPseudotriangulations}), whose vertices are arcs wiggling around $n+2$ points on a line, and whose faces are sets of pairwise pointed and non-crossing wiggly arcs.
+It is a $(2n-1)$-dimensional manifold whose maximal faces are wiggly pseudotriangulations of a disc.
+We show (\cref{sec:bijection}) that the flip graph on wiggly pseudotriangulations is isomorphic to the cover graph of the sublattice of the weak order induced by wiggly permutations (\cref{sec:wigglyPermutations}), the permutations of $[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$.
+Inspired by similar constructions for finite type cluster complexes~\cite{HohlwegLangeThomas,HohlwegPilaudStella}, and for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}, we then provide geometric realizations of the wiggly complex.
+We first construct the wiggly fan (\cref{sec:wigglyFan}), a complete simplicial fan realizing the wiggly complex and supported by the $\b{g}$-vectors of the wiggly arcs.
+We then define the wigglyhedron (\cref{sec:wigglyhedron}), a polytope whose normal fan is the wiggly fan and whose support function is given by the incompatibility numbers of wiggly arcs.
+Its graph can be oriented to obtain the Hasse diagram of the wiggly lattice, and it contains copies of all type~$A_n$ Cambrian lattice as faces (\cref{sec:CambrianConsiderations}).
+To conclude, we conjecture that the wiggly complex of any planar point set is polytopal (\cref{sec:planarPointSets}), and we explore representation theoretic aspects of the wiggly complex (\cref{sec:representationTheory}).
+
+\newpage
+\section{Wiggly pseudotriangulations and the wiggly complex}
+\label{sec:wigglyPseudotriangulations}
+
+We start by defining the wiggly complex, the clique complex of a compatibility relation on the following wiggly arcs.
+
+\begin{definition}
+A \defn{wiggly arc} is a quadruple $\alpha \eqdef (i,j,A,B)$ where $0 \!\le\! i \!<\! j \!\le\! n+1$ and the sets~$A$ and~$B$ form a partition of~${]i,j[} \eqdef \{i+1, \dots, j-1\}$.
 We represent $\alpha$ by an $x$-monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
@@
 
-\begin{remark}
-\label{rem:numberWigglyArcs}
-The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell)$.
-\end{remark}
-
 \begin{definition}
@@
 Two wiggly arcs~$(i,j,A,B)$ and~$(i',j',A',B')$ are 
-\begin{itemize}
+\begin{compactitem}
 \item \defn{non pointed} if~$i = j'$ or~$i' = j$,
-\item \defn{crossing} if~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing \ne (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, that is, if the corresponding curves cross,
+\item \defn{crossing} if their curves cross, that is, if $(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing$ and $(A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})\ne \varnothing$,
 \item \defn{incompatible} if they are non pointed or crossing, and \defn{compatible} otherwise.
-\end{itemize}
+\end{compactitem}
 %
-\begin{figure}[b]
-\centerline{\includegraphics[scale=1.3]{incompatible}}
-\caption{Some incompatible wiggly arcs: non pointed (left) and crossing (right).}
-\label{fig:incompatible}
-\end{figure}
-\end{definition}
-
-\begin{remark}
-We want to stress out that our notion of compatibility on wiggly arcs of \cref{def:compatible} might seem similar to, but fundamentally differs from the notion of compatibility used by N.~Reading to define noncrossing arc diagrams~\cite{Reading-arcDiagrams}.
-Namely, our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
-However, we forbid an arc to start where another arc ends but allow two arcs to start or end at the same point,
-%for two wiggly arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints,
-while N.~Reading does precisely the opposite in~\cite{Reading-arcDiagrams}.
-%This results in very different objects.
-\end{remark}
-
-We then consider pairwise compatible sets of wiggly arcs.
-The following two definitions are illustrated~in~\cref{fig:pseudodissections}.
+%\begin{figure}[b]
+%\centerline{\includegraphics[scale=1.3]{incompatible}}
+%\caption{Some incompatible wiggly arcs: non pointed (left) and crossing (right).}
+%\label{fig:incompatible}
+%\end{figure}
+\end{definition}
 
@@
 We denote by~$D^\circ \eqdef D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.5]{wigglyPseudodissections}}
+
+\begin{figure}[b]
+\centerline{\includegraphics[scale=1.4]{wigglyPseudodissections}}
 \caption{Three wiggly pseudodissections for~$n = 7$.
 The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue).
-The other two have $7$ pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and dark blue pseudotriangles.}
+The other two have $7$ pseudotriangles, and are obtained from each other by a flip.}
 \label{fig:pseudodissections}
@@
 
-%\vincent{Here, I am using the fact that a set of pairwise non-crossing wiggly arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
-
-\begin{definition}
-A wiggly pseudodissection~$D$ decomposes the digon bounded by~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ into cells, that we call \defn{wiggly cells}.
-The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of wiggly arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
-Two consecutive wiggly arcs along the boundary of~$c$ define a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$.
-%The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
-\end{definition}
-
-\begin{remark}
-\label{rem:degree}
-Consider a wiggly cell~$c$ in a wiggly pseudodissection~$D$.
-Note that~$\beta_c$ is always even as~$D$ is pointed, so that~$\beta_c/2$ is an integer.
-Moreover, we have~$\beta_c \ge 2$ and~$\kappa_c \ge 1$, where at least one of the two inequalities is strict (as otherwise, the two wiggly arcs bounding~$c$ would coincide).
-%We conclude that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$.
-We thus obtain on the one hand that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$, and on the other hand that~$\beta_c/2+\kappa_c-1 \ge 2$.
-\end{remark}
-
-\begin{definition}
-A \defn{wiggly pseudotriangle} (resp.~\defn{pseudoquadrangle}) is a wiggly cell of degree~$3$ (resp.~$4$).
-\end{definition}
-
-\begin{remark}
-\label{rem:descriptionPseudotrianglesPseudoquadrangles}
-As illustrated in \cref{fig:pseudotriangles}, a wiggly pseudotriangle~$t$ has no point in its interior and $4$ points on its boundary, $3$ corners and $1$ hinge.
-%Hence, it has two corners oriented in the same direction, which we call the \defn{twin corners}.
-As illustrated in \cref{fig:pseudoquadrangles}, a wiggly pseudoquadrangle~$q$ can have
-\begin{enumerate}
-\item either one point in its interior and~$2$ points on its boundary, both corners,
-\item or no point in its interior and $6$ points on its boundary, $4$ corners and $2$ hinges.
-We then distinguish three situations, depending on the position of the two pairs~$p, p'$ of wiggly arcs incident to the two hinges of~$c$, as illustrated in \cref{fig:pseudoquadrangles} (where~$p$ and~$p'$ are colored in red and orange):
-\begin{enumerate}[(a)]
-\item those where $p$ and $p'$ are not consecutive along~$c$, and do not overlap vertically,
-\item those where $p$ and $p'$ are not consecutive along~$c$, but overlap vertically,
-\item those where~$p$ and~$p'$ are consecutive along~$c$.
-\end{enumerate}
-\end{enumerate}
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{pseudotriangles}}
-\caption{Four wiggly pseudotriangles.}
-\label{fig:pseudotriangles}
-\end{figure}
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{pseudoquadrangles}}
-\vspace{-.3cm}
-\caption{Four types of wiggly pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
-\label{fig:pseudoquadrangles}
-\end{figure}
-\end{remark}
-
-\begin{proposition}
-\label{prop:wigglyPseudotriangulations}
-Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
-Moreover, the following are equivalent:
-\begin{enumerate}[(i)]
-\item all wiggly cells of~$D$ are wiggly pseudotriangles,
-\item $D$ contains~$n$ wiggly cells and is connected,
-\item $D$ contains $2n-1$ internal wiggly arcs,
-\item $D$ is an inclusion maximal wiggly pseudodissection.
-\end{enumerate}
-We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
-\end{proposition}
-
-\begin{proof}
-Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
-Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$n - \iota + \gamma = \kappa$.
-Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
-We conclude that~$\gamma \le n$ and~$\iota = n+\gamma-\kappa \le 2n-1$.
-
-%Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
-%Observe that~$\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and that~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-%As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus get~$2 \gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa$.
-%As~$D$ is a planar graph with~$v = n+2$ vertices, $e = \iota+2$ edges, $f = 1+\gamma$ faces, and $\kappa$ connected components, Euler's formula~$1+\kappa = v-e+f$ yields~$2(1+\kappa) = 2(n+2)-2(\iota+2)+2(1+\gamma) \le 2n-2\iota+2+\iota+\kappa$, so that~$\iota \le 2n-\kappa \le 2n-1$ and~$\gamma \le (\iota+\kappa)/2 \le n$.
-
-To prove the second part of the statement, we show that~(i) $\Rightarrow$ (ii) $\Rightarrow$ (iii) $\Rightarrow$ (iv) $\Rightarrow$ (i).
-
-\para{(i) $\Rightarrow$ (ii)}
-For any wiggly cell~$c$, we have~$\delta_c = 3$, so that~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}, hence~$2 = \beta_c/2+\kappa_c-1$.
-Therefore~$\kappa = 1$ ($D$ is connected) and~$2\gamma = \iota+1 = n+\gamma$, so that~$\gamma=n$.
-
-\para{(ii) $\Rightarrow$ (iii)}
-As $\gamma=n$ and~$\kappa=1$, we have~$\iota = n+\gamma-\kappa = 2n-1$.
-
-%\para{(i) $\Rightarrow$ (ii)}
-%We have~$\delta_c = 3$ for any wiggly cell~$c$.
-%Hence~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}.
-%Therefore~$2\gamma = \iota+1$ and~$\kappa = 1$ (so that~$D$ is connected).
-%Applying Euler's formula as before, we get~$2 = (n+2)-(\iota+2)+(1+\gamma) = n-\gamma+2$, so that~$\gamma=n$.
-%
-%\para{(ii) $\Rightarrow$ (iii)}
-%As $\gamma=n$ and~$\kappa=1$, we have~$2n = 2\gamma \le \iota+\kappa = \iota+1$, so that~$\iota = 2n-1$.
-
-\para{(iii) $\Rightarrow$ (iv)}
-If~$D$ already contains~$2n-1$ internal wiggly arcs, it has maximal cardinality among all wiggly pseudodissections, hence it is certainly inclusion maximal.
-
-\para{(iv) $\Rightarrow$ (i)}
-We now consider a wiggly pseudodissection~$D$ containing a wiggly cell~$c$ which is not a wiggly pseudotriangle, and we prove that~$D$ is not inclusion maximal.
-%
-Assume first that the external boundary of~$c$ is a digon bounded by the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i, j, A', B')$.
-Denote by~$m$ the maximum of the points~$(A \symdif A') \cup (B \symdif B')$ located inside this digon (where~$\symdif$ denotes the symmetric difference).
-Then the wiggly arc~$\beta \eqdef \big( i, m, {]i,m[} \cap (A \cup A'), {]i,m[} \cap (B \cap B') \big)$ is compatible with~$D$ (any wiggly arc incompatible with~$\beta$ crosses~$\alpha$ or~$\alpha'$) and is not in~$D$ (it connects the boundary of~$c$ with one of its internal connected components).
-%Indeed, for any wiggly arc~$\gamma \eqdef (k, \ell, X, Y)$ inside~$c$, we have
-%\begin{itemize}
-%\item $i < k < \ell \le m$ so that~$\beta$ and~$\gamma$ are pointed,
-%\item $Y \subseteq {]i,m[} \cap B \cap B'$ so that~$\beta$ and~$\gamma$ are non-crossing.
-%\end{itemize}
-
-Assume now that the external boundary of~$c$ is a not digon.
-Consider a hinge~$j$ of~$c$.
-Assume by symmetry that the boundary of~$c$ contains two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j, A', B')$, such that~$\alpha$ is below~$\alpha'$.
-% (\ie $k \in A'$ or~$k' \in B$).
-Let~$\gamma \eqdef (k, \ell, X, Y)$ denote the uppermost wiggly arc of the boundary of~$c$ such that~$j \in Y$ (it exists since~$j$ is a  hinge of~$c$), and let~$X' \eqdef {]j,\ell[} \cap X$ and~$Y' \eqdef {]j,\ell[} \cap Y$.
-Then the two wiggly arcs~$\beta \eqdef \big( i, \ell, A \cup X', B \cup \{j\} \cup Y')$ and~$\beta' \eqdef \big( i', \ell, A'  \cup \{j\} \cup X', B \cup Y')$ are both compatible with~$D$ (any wiggly arc incompatible with~$\beta$ is incompatible with~$\alpha$ or~$\gamma$, and similarly for~$\beta'$) and cannot both belong to~$D$ (otherwise, $c$ would be a wiggly pseudotriangle bounded by~$\alpha, \alpha', \gamma', \gamma$).
-\end{proof}
-
-\pagebreak
-\begin{remark}
-Note that in the proof of \cref{prop:wigglyPseudotriangulations}, we actually obtained that
-\[
-\sum_{c \in C} (\delta_c-3) = \sum_{c \in D} \beta_c/2 + 2 \sum_{c \in D} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
-\]
-\end{remark}
-
-\begin{example}
-\label{exm:allSmallWigglyPseudotriangulations}
-For~$n = 1$, the $2$ wiggly pseudotriangulations of $3$ points are \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation1}}} and \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation2}}}.
-For~${n = 2}$, the $14$ wiggly pseudotriangulations of $4$ points are \\[.2cm]
-\centerline{\includegraphics[scale=.8]{wigglyPseudotriangulations}}
-\end{example}
-
-\begin{example}
-\label{exm:specialWigglyPseudotriangulations}
-The following wiggly pseudotriangulations are illustrated in \cref{fig:specialWigglyPseudotriangulations}:
-\begin{align*}
-T_\downarrow & \eqdef \set{(i-1, n+1, \varnothing, {[i,n]})}{i \in [n+1]} \cup \set{(0, n+1, [i], {]i,n]})}{i \in [n]}, \\
-T_\uparrow & \eqdef \set{(0, i, \varnothing, {[i-1]})}{i \in [n+1]} \cup \set{(0, n+1, {]i,n]}, [i])}{i \in [n]}, \\
-T_\leftarrow & \eqdef \{(0, 1, \varnothing, \varnothing)\} \cup \set{(0, i+1, \varnothing, [i])}{i \in [n]} \cup \set{(0, i+1, [i], \varnothing)}{i \in [n]}, \\
-T_\rightarrow & \eqdef \{(n, n+1, \varnothing, \varnothing)\} \cup \set{(i-1, n+1, \varnothing, [i,n])}{i \in [n]} \cup \set{(i-1, n+1, [i,n], \varnothing)}{i \in [n]}.
-\end{align*}
-%
-\begin{figure}[h]
-\centerline{\includegraphics[scale=1.3]{specialWigglyPseudotriangulations}}
-\caption{The wiggly pseudotriangulations~$T_\downarrow$ (left), $T_\uparrow$ (middle left), $T_\leftarrow$ (middle right), and $T_\rightarrow$ (right) of \cref{exm:specialWigglyPseudotriangulations} for~$n = 7$.}
-\label{fig:specialWigglyPseudotriangulations}
-\end{figure}
-\end{example}
-
-\begin{remark}
-\label{rem:numberWigglyPseudotriangulations}
-The number~$wp_n$ of wiggly pseudotriangulations of~$n+2$ points is given by
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
-\hline
-wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
-\end{array}
-\]
-To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ \defn{final} internal wiggly arcs (\ie ending at the last point~$n+1$).
-For instance,
-\begin{align*}
-%	wp_0(x) & = 1, \\
-	wp_1(x) & = x + 1, \\
-	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-\end{align*}
-We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPseudotriangulations}.
-We use this additional variable~$x$ to obtain a recursive formula for~$wp_n(x)$.
-%Indeed, any wiggly pseudotriangulation on~$n+1$ points can be obtained from a wiggly pseudotriangulation on~$n+2$ points by collapsing the points~$n$ and~$n+1$.
-Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting a single wiggly pseudotriangle with a hinge at~$n$.
-%There are two kinds of wiggly pseudotriangulations of~$n+2$ points:
-%\begin{itemize}
-%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
-%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
-%\end{itemize}
-Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to:
-\begin{itemize}
-\item $i+2$ wiggly pseudotriangulations of~$n+2$ points with $i+2$ final internal wiggly arcs, containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,
-\item $j+1$ wiggly pseudotriangulations of~$n+2$ points with $j$ final internal wiggly arcs, not containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,  for all~$0 \le j \le i+1$.
-\end{itemize}
-\pagebreak
-This translates to the recursive formula %for all~$n \ge 1$,
-\begin{align*}
-wp_{n}(x) & = \overbracket[.5pt]{x \cdot \frac{\partial}{\partial x} \big( x^2 wp_{n-1}(x) \big)}^{\substack{\text{wiggly pseudotriangulations} \\ \text{containing } (n, n+1, \varnothing, \varnothing)}} + \overbracket[.5pt]{\frac{\partial}{\partial x}\Big( \smash{\frac{wp_{n-1}(1)-x^3wp_{n-1}(x)}{1-x}} \Big)}^{\substack{\qquad\; \text{wiggly pseudotriangulations} \qquad\;  \\ \text{not containing } (n, n+1, \varnothing, \varnothing)}} \\
-& = \frac{1}{(1 - x)^2} \big( wp_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) wp_{n-1}(x) + x^4 (x - 1) wp_{n-1}’(x) \big).
-\end{align*}
-This enables us to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
-%This enables us to quickly compute the generating series of the number of wiggly pseudotriangulations
-%\[
-%\sum_{n \ge 0} wp_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
-%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
-%\dots
-%\]
-\end{remark}
-
-Our next statement prepares for the definition of flips in wiggly pseudotriangulations, and is illustrated in \cref{fig:diagonalsPseudoquadrangles}.
-
-\begin{definition}
-A \defn{wiggly diagonal} of a wiggly cell~$c$ is a wiggly arc inside~$c$ and compatible with~$c$.
-\end{definition}
-
-\begin{proposition}
-\label{prop:diagonalsPseudoquadrangle}
-Any wiggly pseudoquadrangle has exactly two wiggly diagonals.
-Moreover, these two wiggly diagonals either cross precisely once, or are non pointed.
-\end{proposition}
-
-\begin{proof}
-Depending on the four types of pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}:
-\begin{enumerate}
-\item the two diagonals are the two wiggly arcs inside~$q$, incident to the point in the interior~of~$q$,
-\item[(2a)] the two diagonals connect the two pairs of opposite corners of~$q$,
-\item[(2b)] one of two diagonals connects two opposite corners of~$q$ while the other connects the two hinges~of~$q$,
-\item[(2c)] one of the diagonals connects two opposite corners of~$q$ while the other connects an hinge of~$q$ to a corner of~$q$.
-\end{enumerate}
-See \cref{fig:diagonalsPseudoquadrangles} where the two diagonals appear in red and orange.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{diagonalsPseudoquadrangles}}
-\caption{The two diagonals in each of the four types of wiggly pseudoquadrangles.} % described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
-\label{fig:diagonalsPseudoquadrangles}
-\end{figure}
-%Let~$q$ be a wiggly pseudoquadrangle.
-%We distinguish two situations depending on~$\kappa(q)$:
-%\begin{description}
-%\item[$\kappa(q) = 1$] Then the boundary of~$c$ is a single wiggly hexagon, so that it has~$4$ concave points. We distinguish again two situations:
-%	\begin{description}
-%	\item 
-%	\end{description}
-%\item[$\kappa(q) = 2$] Then~$q$ is a digon bounded by two wiggly arcs~$(i, k, A, B \cup \{j\})$ and~$(i, k, A \cup \{j\}, B)$ for some~$1 < i < j < k \le n$ and~$A \sqcup B = {]i,j[} \cup{]j,k[}$.
-Hence, the only two wiggly arcs in the interior of~$q$ are~$(i, j, {]i,j[} \cap A, {]i,j[} \cap B)$ and~$(j, k, {]j,k[} \cap A, {]j,k[} \cap B)$, which are both compatible with~$q$ and are not pointed.
-%\end{description}
-\end{proof}
-
-%\vincent{Asilata has an alternative description of the flip...}
-
-We are now ready to consider the wiggly flip graph and the wiggly complex.
-The following definition is illustrated in \cref{fig:wigglyComplex}\,(right) when~$n = 2$.
-%
+\begin{definition}
+\label{def:wigglyComplex}
+The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
+%In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
+
 \begin{figure}
@@
 \end{figure}
+\end{definition}
+
+\begin{definition}
+A wiggly pseudodissection~$D$ decomposes the digon bounded by~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ into \defn{wiggly cells}.
+The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of wiggly arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
+Two consecutive wiggly arcs along the boundary of~$c$ define a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$.
+%The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
+\end{definition}
+
+\begin{definition}
+A \defn{wiggly pseudotriangle} (resp.~\defn{pseudoquadrangle}) is a cell of degree~$3$ (resp.~$4$).
+\end{definition}
+
+\begin{proposition}
+\label{prop:wigglyPseudotriangulations}
+Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
+Moreover, the following are equivalent:
+\begin{compactenum}[(i)]
+\item all wiggly cells of~$D$ are wiggly pseudotriangles,
+\item $D$ contains~$n$ wiggly cells and is connected,
+\item $D$ contains $2n-1$ internal wiggly arcs,
+\item $D$ is an inclusion maximal wiggly pseudodissection.
+\end{compactenum}
+We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
+\end{proposition}
+
+\begin{example}
+\label{exm:allSmallWigglyPseudotriangulations}
+For~$n = 1$, the $2$ wiggly pseudotriangulations of $3$ points are \smash{\raisebox{-.3cm}{\includegraphics[scale=.85]{wigglyPseudotriangulation1}}} and \smash{\raisebox{-.3cm}{\includegraphics[scale=.85]{wigglyPseudotriangulation2}}}.
+For~${n = 2}$, the $14$ wiggly pseudotriangulations of $4$ points are \\[.2cm]
+\centerline{\includegraphics[scale=.85]{wigglyPseudotriangulations}}
+\end{example}
+
+%\begin{remark}
+%\label{rem:numberWigglyPseudotriangulations}
+%The number~$wp_n$ of wiggly pseudotriangulations of~$n+2$ points is given by
+%\[
+%\begin{array}{c|ccccccccc}
+%n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
+%\hline
+%wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
+%\end{array}
+%\]
+%To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ \defn{final} internal wiggly arcs (\ie ending at the last point~$n+1$).
+%For instance,
+%\begin{align*}
+%%	wp_0(x) & = 1, \\
+%	wp_1(x) & = x + 1, \\
+%	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+%	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
+%	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
+%\end{align*}
+%We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPseudotriangulations}.
+%We use this additional variable~$x$ to obtain a recursive formula for~$wp_n(x)$.
+%%Indeed, any wiggly pseudotriangulation on~$n+1$ points can be obtained from a wiggly pseudotriangulation on~$n+2$ points by collapsing the points~$n$ and~$n+1$.
+%Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting a single wiggly pseudotriangle with a hinge at~$n$.
+%%There are two kinds of wiggly pseudotriangulations of~$n+2$ points:
+%%\begin{itemize}
+%%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
+%%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
+%%\end{itemize}
+%Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to:
+%\begin{compactitem}
+%\item $i+2$ wiggly pseudotriangulations of~$n+2$ points with $i+2$ final internal wiggly arcs, containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,
+%\item $j+1$ wiggly pseudotriangulations of~$n+2$ points with $j$ final internal wiggly arcs, not containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,  for all~$0 \le j \le i+1$.
+%\end{compactitem}
+%\pagebreak
+%This translates to the recursive formula %for all~$n \ge 1$,
+%\begin{align*}
+%wp_{n}(x) & = \overbracket[.5pt]{x \cdot \frac{\partial}{\partial x} \big( x^2 wp_{n-1}(x) \big)}^{\substack{\text{wiggly pseudotriangulations} \\ \text{containing } (n, n+1, \varnothing, \varnothing)}} + \overbracket[.5pt]{\frac{\partial}{\partial x}\Big( \smash{\frac{wp_{n-1}(1)-x^3wp_{n-1}(x)}{1-x}} \Big)}^{\substack{\qquad\; \text{wiggly pseudotriangulations} \qquad\;  \\ \text{not containing } (n, n+1, \varnothing, \varnothing)}} \\
+%& = \frac{1}{(1 - x)^2} \big( wp_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) wp_{n-1}(x) + x^4 (x - 1) wp_{n-1}’(x) \big).
+%\end{align*}
+%This enables us to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
+%\end{remark}
+
+\begin{definition}
+A \defn{wiggly diagonal} of a cell~$c$ is a wiggly arc inside~$c$ and compatible with~$c$.
+\end{definition}
+
+\begin{proposition}
+\label{prop:diagonalsPseudoquadrangle}
+Any wiggly pseudoquadrangle has exactly two wiggly diagonals.
+Moreover, these two wiggly diagonals either cross precisely once, or are non pointed.
+\end{proposition}
 
@@
 
+Consider any wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$.
+By \cref{prop:diagonalsPseudoquadrangle}, the wiggly pseudoquadrangle formed by the union of the two wiggly pseudotriangles of~$T$ containing~$\alpha$ has two wiggly diagonals, $\alpha$ and another one~$\alpha'$.
+Exchanging $\alpha$ by~$\alpha'$ gives a neighbor~$T'$ of~$T$ in the wiggly flip graph.
+This leads to the following statement.
+
 \begin{proposition}
 \label{prop:wigglyFlipGraph}
-The wiggly flip graph~$\wigglyFlipGraph_n$ is regular of degree~$2n-1$ and connected.
-\end{proposition}
-
-\begin{proof}
-Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
-Then~${Q \eqdef T \ssm \{\alpha\}}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
-By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, namely $\alpha$ and another one~$\alpha'$.
-As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
-We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
-This shows that any internal wiggly arc in any wiggly pseudotriangulation can be flipped, hence that the wiggly flip graph is regular of degree~$2n-1$ by \cref{prop:wigglyPseudotriangulations}\,(iii).
-
-There are various possible proofs for the connectedness.
-For instance, it will follow easily from \cref{prop:bijection}.
-To avoid relying on this forward reference, we sketch an alternative direct proof by induction on~$n$.
-We claim that if a wiggly pseudotriangulation has a non-zero number of final internal wiggly arcs (\ie ending at the last point~$n+1$), then at least one of them can be flipped to a non-final wiggly arc.
-This implies that any wiggly pseudotriangulation can be transformed by flips to a wiggly pseudotriangulation with no final internal wiggly arc.
-All wiggly pseudotriangulations with no final internal wiggly arc contain the arcs~$(0,n,\varnothing,[n-1])$ and~$(0,n,[n-1],\varnothing)$, since the latter are compatible with all internal wiggly arcs but the final ones.
-Hence, they induce a subgraph of~$\wigglyFlipGraph_n$ isomorphic to~$\wigglyFlipGraph_{n-1}$, which is connected by induction.
-We conclude that~$\wigglyFlipGraph_n$ is itself connected.
-
-To see the claim, let~$i$ be maximal such that~$T$ contains two distinct wiggly arcs starting at~$i$ and ending at~$n+1$ (it is well-defined as we have the external wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ for~$i = 0$).
-Consider a final internal wiggly arc~$\alpha$ of~$T$ starting weakly after~$i$, and let~$\alpha'$ be the wiggly arc obtained by flipping~$\alpha$ in~$T$.
-If~$\alpha'$ is final, then by~\cref{prop:diagonalsPseudoquadrangle}, at least one pseudotriangle~$t$ of~$T$ incident to~$\alpha$ has two corners at~$n+1$.
-Let~$h$ be the hinge of~$t$ and~$\beta, \beta'$ be the two wiggly arcs of~$t$ joining~$h$ to~$n+1$.
-As~$i < h \le n$ the maximality of~$i$ imposes that~$\beta = \beta'$.
-Flipping $\beta = \beta'$ in~$T$ thus yields a wiggly arc ending at~$h \le n$, hence a non-final arc.
-\end{proof}
-
-We will also consider an oriented version of the wiggly flip graph~$\wigglyFlipGraph_n$.
-The following definition is illustrated in \cref{fig:incompatible2}.
-
-\begin{definition}
-\label{def:wigglyIncreasingFlipGraph}
-Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two wiggly arcs and~$T$ and~$T'$ be two wiggly pseudotriangulations, such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-We say that the flip from~$T$ to~$T'$ is \defn{increasing} if 
-\begin{itemize}
-\item $\alpha$ starts where~$\alpha'$ ends (that is, $i = j'$), or 
-\item $\alpha$ crosses~$\alpha'$ from north-west to south-east (that is, there exists~$k \in [n-1]$ such that $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$).
-\end{itemize}
-The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and an edge for each increasing~flip.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{incompatible2}}
-\caption{The wiggly arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
-\label{fig:incompatible2}
-\end{figure}
-\end{definition}
-
-\pagebreak
-We will need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
+The wiggly flip graph~$\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected.
+\end{proposition}
+
+\cref{prop:wigglyPseudotriangulations,prop:wigglyFlipGraph} imply the main statement of this section.
+
+\begin{theorem}
+The wiggly complex~$\wigglyComplex_n$ is a flag $(2n-1)$-pseudomanifold without boundary.
+\end{theorem}
+
+Finally, we identify an important property of flips in wiggly pseudotriangulations.
 
@@
 Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
-\begin{itemize}
+\begin{compactitem}
 \item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
 (In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ such that~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
+\item $\beta \!\eqdef\!
+\big( i, j', {]i,j'[} \!\ssm\!
+(B \!\cup\!
+B'), {]i,j'[} \!\cap\!
+(B \!\cup\!
+B') \big)$ and~$\beta' \!\eqdef\!
+\big( i', j, {]i',j[} \!\cap\!
+(A \!\cup\!
+A'), {]i',j[} \!\ssm\!
+(A \!\cup\!
+A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ with~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
 (In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
-\end{itemize}
+\end{compactitem}
 %See \cref{fig:incompatible3} for illustrations.
-(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
+%(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
 %
-\begin{figure}
+%\begin{figure}
+
+%\vspace{-.1cm}
 \centerline{\includegraphics[scale=1.3]{incompatible3}}
-\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
-\label{fig:incompatible3}
-\end{figure}
-\end{proposition}
-
-\begin{proof}
-Any wiggly arc non pointed with~$\beta$ would be non pointed with~$\alpha$ or~$\alpha'$ (as the endpoints of~$\beta$ are endpoints of~$\alpha$ or~$\alpha'$).
-Any wiggly arc crossing~$\beta$ would be either non pointed or crossing~$\alpha$ or~$\alpha'$ (as~$\beta$ follows~$\alpha$ or~$\alpha'$, except at the point~$j = i'$ in the first situation).
-\end{proof}
-
-Finally, we are define the wiggly complex~$\wigglyComplex_n$, illustrated in \cref{fig:wigglyComplex}\,(left) when~$n = 2$.
-
-\begin{definition}
-\label{def:wigglyComplex}
-The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
-In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
-\end{definition}
-
-\begin{proposition}
-The wiggly complex~$\wigglyComplex_n$ is a flag $(2n-1)$-dimensional pseudomanifold without boundary.
-\end{proposition}
-
-\begin{proof}
-It is a flag simplicial complex because it is a clique complex.
-It is pure of dimension $2n-1$ by the implication (iv) $\Rightarrow$ (iii) of \cref{prop:wigglyPseudotriangulations}.
-Finally, it is a pseudomanifold without boundary by \cref{prop:wigglyFlipGraph}.
-\end{proof}
-
-\begin{remark}
-$\wigglyComplex_1$ contains two isolated points.
-$\wigglyComplex_2$ is a simplicial $3$-dimensional associahedron (this coincidence fails for~$n > 2$).
-Here are the first few $f$-vectors:
-\begin{align*}
-f(\wigglyComplex_1) & = (1, 2), \\
-f(\wigglyComplex_2) & = (1, 9, 21, 14), \\
-f(\wigglyComplex_3) & = (1, 24, 154, 396, 440, 176), \\
-f(\wigglyComplex_4) & = (1, 55, 729, 4002, 10930, 15684, 11312, 3232), \\
-f(\wigglyComplex_5) & = (1, 118, 2868, 28110, 140782, 400374, 673274, 662668, 352728, 78384),
-\intertext{and the first few $h$-vectors:}
-h(\wigglyComplex_1) & = (1, 1), \\
-h(\wigglyComplex_2) & = (1, 6, 6, 1), \\
-h(\wigglyComplex_3) & = (1, 19, 68, 68, 19, 1), \\
-h(\wigglyComplex_4) & = (1, 48, 420, 1147, 1147, 420, 48, 1), \\
-h(\wigglyComplex_5) & = (1, 109, 1960, 11254, 25868, 25868, 11254, 1960, 109, 1).
-\end{align*}
-Note that the number of vertices and facets of~$\wigglyComplex_n$ were already discussed in \cref{rem:numberWigglyArcs,rem:numberWigglyPseudotriangulations}.
-\end{remark}
-
-%\begin{remark}
-%Note that the number of vertices of~$\wigglyComplex_n$ is the number~$\sum_{j = 0}^n 2^j (n+1-j)$ of wiggly arcs on~$n+2$ points.
-%The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
-%For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal wiggly arcs ending at the last point~$n+1$.
-%For instance,
-%\begin{align*}
-%	f_0(x) & = 1, \\
-%	f_1(x) & = x + 1, \\
-%	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-%	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-%	f_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-%\end{align*}
-%We use this additional variable~$x$ to obtain a recursive formula for~$f_n(x)$, discussing on the wiggly pseudotriangle~$t_n$ with a hinge at~$n$.
-%Namely, there are two types of wiggly pseudotriangulations of~$n+2$ points:
-%\begin{itemize}
-%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
-%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
-%\end{itemize}
-%Hence we obtain for all~$n \ge 1$,
-%\[
-%f_{n}(x) = \frac{1}{(1 - x)^2} \big( f_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) f_{n-1}(x) + x^4 (x - 1) f_{n-1}’(x) \big).
-%\]
-%This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
-%\[
-%\sum_{n \ge 0} f_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
-%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
-%\dots
-%\]
-%\end{remark}
-
-\begin{remark}
-\label{rem:wigglyComplexAutomorphism}
-The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
-Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly permutations and the wiggly lattice}
-\label{subsec:wigglyPermutations}
-
-We now consider wiggly permutations of~$[2n]$, defined as follows.
+%\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
+%\label{fig:incompatible3}
+%\end{figure}
+\vspace{-.4cm}
+\end{proposition}
+
+\section{Wiggly permutations and the wiggly lattice}
+\label{sec:wigglyPermutations}
+
+We now define the wiggly lattice on wiggly permutations of~$[2n]$, illustrated in \cref{fig:wigglyLattice}.
 
@@
 A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
-\begin{itemize}
+\begin{compactitem}
 \item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
 \item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
-\end{itemize}
+\end{compactitem}
 \end{definition}
@@
 For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
+\vspace{-.1cm}
 \[
@@
 
-\begin{example}
-\label{exm:specialWigglyPermutations}
-The permutations
-\[
-\sigma_\downarrow \eqdef 1 2 \cdots (2n),
-\quad
-\sigma_\uparrow \eqdef (2n) \cdots 2 1,
-\quad
-\sigma_\leftarrow \eqdef (2n) \cdots 2 1 \cdots (2n-1),
-\quad
-\sigma_\rightarrow \eqdef 1 \cdots (2n-1) (2n) \cdots 2
-\]
-are wiggly permutations of~$[2n]$.
-\end{example}
-
-\begin{remark}
-\label{rem:numberWigglyPermutations}
-The number~$wp_n$ of wiggly permutations of~$[2n]$ is given by
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
-\hline
-wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
-\end{array}
-\]
-To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ such that the value~$2j$ appears before the gap~$\gamma$ while the value~$2j-1$ appears after the gap~$\gamma$).
-For instance,
-\begin{align*}
-%	wp_0(x) & = 1, \\
-	wp_1(x) & = x + 1, \\
-	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-\end{align*}
-We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPermutations}.
-Any wiggly permutation of~$[2n]$ can be obtained from a wiggly permutation of~$[2n-2]$ by inserting the last values~$2n-1$ and~$2n$.
-Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to:
-\begin{itemize}
-\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps and where~$2n-1$ appears before~$2n$ (they must appear consecutively),
-\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
-\end{itemize}
-We thus obtain the same recursive equation on~$wp_n(x)$ as in \cref{rem:numberWigglyPseudotriangulations}.
-\end{remark}
-
-Recall that the \defn{inversion set} and \defn{non-inversion set} of a permutation~$\sigma$ of~$[2n]$ are the sets
-\begin{align*}
-\inv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) > \sigma(j)}, \\
-\ninv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) < \sigma(j)}.
-\end{align*}
-Note that~$\inv(\sigma)$ and~$\ninv(\sigma)$ are transitive: $\{(c,b), (b,a)\} \subseteq \inv(\sigma)$ implies~$(c,a) \in \inv(\sigma)$ for all~${1 \le a < b < c \le 2n}$, and similarly for~$\ninv$.
-The inversion sets of wiggly permutations are characterized as follows.
-
-\begin{lemma}
-\label{lem:inversionSetsWigglyPermutations}
-A permutation~$\sigma$ of~$[2n]$ is a wiggly permutation if and only if for all~$j \in [n]$,
-\begin{itemize}
-\item $(2j-1, i) \in \inv(\sigma)$ implies $(2j, i) \in \inv(\sigma)$ for all~$i < 2j-1$, and
-\item $(k, 2j-1) \in \inv(\sigma)$ implies $(k, 2j) \in \inv(\sigma)$ for all~$k > 2j$.
-\end{itemize}
-A similar characterization holds for~$\ninv(\sigma)$ by exchanging~$2j-1$ and~$2j$.
-\end{lemma}
-
-\begin{proof}
-Immediate as it corresponds to the pattern avoidance description of \cref{def:wigglyPermutation}.
-\end{proof}
-
-The (left) \defn{weak order} on permutations of~$[2n]$ is defined as the inclusion order of their inversion sets (or equivalently, the reverse inclusion of their non-inversion sets).
-Its cover relations are given by the exchanges of two entries at consecutive positions.
-It is a (congruence uniform) lattice, and the join and meet satisfy
-\[
-\inv(\sigma \join \tau) = \big( \inv(\sigma) \cup \inv(\tau) \big)^\textrm{tc}
-\qquad\text{and}\qquad
-\ninv(\sigma \meet \tau) = \big( \ninv(\sigma) \cup \ninv(\tau) \big)^\textrm{tc}
-\]
-where~$X^\mathrm{tc}$ denotes the transitive closure of~$X$.
-
-The following statements are illustrated on \cref{fig:wigglyLattice}\,(right) when~${n = 2}$.
-%
-\begin{figure}
+\begin{proposition}
+The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, that we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
+\end{proposition}
+
+\begin{proposition}
+Any wiggly permutation covers (resp.~is covered by) one wiggly permutation~for each of its descents (resp.~ascents).
+The cover graph of~$\wigglyLattice_n$ is $(2n-1)$-regular~and~connected.
+\end{proposition}
+
+%\begin{remark}
+%\label{rem:numberWigglyPermutations}
+%The number~$wp_n$ of wiggly permutations of~$[2n]$ is given by
+%\[
+%\begin{array}{c|ccccccccc}
+%n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
+%\hline
+%wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
+%\end{array}
+%\]
+%To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ such that the value~$2j$ appears before the gap~$\gamma$ while the value~$2j-1$ appears after the gap~$\gamma$).
+%For instance,
+%\begin{align*}
+%%	wp_0(x) & = 1, \\
+%	wp_1(x) & = x + 1, \\
+%	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
+%	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14. % \\
+%%	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
+%\end{align*}
+%%We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPermutations}.
+%Any wiggly permutation of~$[2n]$ can be obtained from a wiggly permutation of~$[2n-2]$ by inserting the last values~$2n-1$ and~$2n$.
+%Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to:
+%\begin{compactitem}
+%\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps and where~$2n-1$ appears before~$2n$ (they must appear consecutively),
+%\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
+%\end{compactitem}
+%%We thus obtain the same recursive equation on~$wp_n(x)$ as in \cref{rem:numberWigglyPseudotriangulations}.
+%This translates to the recursive formula %for all~$n \ge 1$,
+%\begin{align*}
+%wp_{n}(x) & = \overbracket[.5pt]{x \cdot \frac{\partial}{\partial x} \big( x^2 wp_{n-1}(x) \big)}^{\substack{\text{wiggly permutations} \\ \text{with~$2n-1$ before~$2n$}}} + \overbracket[.5pt]{\frac{\partial}{\partial x}\Big( \smash{\frac{wp_{n-1}(1)-x^3wp_{n-1}(x)}{1-x}} \Big)}^{\substack{\qquad\; \text{wiggly permutations} \qquad\;  \\ \text{with~$2n$ before~$2n-1$}}} \\
+%& = \frac{1}{(1 - x)^2} \big( wp_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) wp_{n-1}(x) + x^4 (x - 1) wp_{n-1}’(x) \big).
+%\end{align*}
+%This enables us to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
+%\end{remark}
+
+\newpage
+\section{Bijection}
+\label{sec:bijection}
+
+\begin{figure}[t]
 \centerline{\includegraphics[scale=1.1]{wigglyLattice}}
@@
 
-\begin{proposition}
-The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, that we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
-\end{proposition}
-
-\begin{proof}
-Consider two wiggly permutations~$\rho$ and~$\sigma$ of~$[2n]$, and let~$\tau = \rho \join \sigma$.
-Assume that there is~$1 \le i < 2j-1 < 2n$ such that~$(2j-1, i) \in \inv(\tau)$.
-As $\inv(\tau) = \big( \inv(\rho) \cup \inv(\sigma) \big)^\textrm{tc}$, there exist~$i \le i' < 2j-1$ such that~$(i', i) \in \inv(\tau)$ and~$(2j-1, i') \in \inv(\rho) \cup \inv(\sigma)$.
-Since~$\rho$ and~$\sigma$ are wiggly permutations, we obtain by \cref{lem:inversionSetsWigglyPermutations} that~$(2j, i') \in \inv(\rho) \cup \inv(\sigma) \subseteq \inv(\tau)$.
-As~$(i', i) \in \inv(\tau)$ and~$(2j, i') \in \inv(\tau)$ and~$\inv(\tau)$ is transitive, we conclude that~$(2j,i) \in \inv(\tau)$.
-A similar argument shows that~$(k, 2j-1) \in \inv(\tau)$ implies~$(k, 2j) \in \inv(\tau)$ for all~$1 < 2j < k \le 2n$.
-By \cref{lem:inversionSetsWigglyPermutations}, we conclude that~$\tau = \rho \join \sigma$ is a wiggly permutation.
-The proof is similar for~$\rho \meet \sigma$, using $\ninv$ instead of~$\inv$.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyLatticeAntiIsomorphism}
-The map~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_n)$ obviously provides an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$.
-\end{remark}
-
-We now aim at describing the cover relations of the wiggly lattice.
-Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$j$ such that~$\sigma(j) < \sigma(j+1)$ (resp.~$\sigma(j) > \sigma(j+1)$).
-
-\begin{lemma}\label{lem:wigglyCoverRelation}
-Consider an ascent~$j$ of a wiggly permutation~$\sigma$ of~$[2n]$.
-Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
-Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
-Then
-\[
-\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n).
-\]
-is the minimal wiggly permutation such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\sigma^j)$.
-\end{lemma}
-
-\begin{proof}
-We start with a few observations.
-Let~$i < p \le j$ (resp.~$j+1 \le q < k$).
-As~$\sigma$ is a wiggly permutation, we have~$\sigma(p) < \sigma(i)$ (resp.~$\sigma(q) > \sigma(k)$).
-Hence~$\big( \sigma(i), \sigma(p) \big)$ (resp.~$\big( \sigma(q), \sigma(k) \big)$) belongs to~$\inv(\sigma)$.
-Moreover, since~$j$ is an ascent of~$\sigma$, we obtain that~$\sigma(p) < \sigma(q)$ for all~${i \le p \le j < q \le k}$.
-Hence, $\inv(\sigma^j) = \inv(\sigma) \cup \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}$.
-
-We now prove that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$.
-We consider~$v \in [n]$ and~$u < 2v-1$ such that~$(2v-1, u) \in \inv(\sigma^j)$, and we show that~$(2v, u) \in \inv(\sigma^j)$.
-If~$(2v, u) \in \inv(\sigma)$, we are done as~$\inv(\sigma) \subset \inv(\sigma^j)$.
-If~$(2v, u) \not\in \inv(\sigma)$, then~$(2v-1, u) \not\in \inv(\sigma)$ by \cref{lem:inversionSetsWigglyPermutations}, and~$i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v-1) \le k$ since~${\inv(\sigma^j) \ssm \inv(\sigma) = \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}}$.
-We have~$\sigma^{-1}(2v) \le k$ since~$\sigma$ is a wiggly permutation.
-As~$(2v, u) \not\in \inv(\sigma)$ and~$\sigma(p) < \sigma(q)$ for all~$i \le p \le j < q \le k$, we conclude that~$j < \sigma^{-1}(2v) < k$.
-Hence, we obtain that ${i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v) \le k}$, so that~$(2v,u) \in \inv(\sigma^j)$.
-Similarly~${(w, 2v-1) \in \inv(\sigma^j)}$ implies~$(w, 2v) \in \inv(\sigma^j)$ for all~$v \in [n]$ and~$w > 2v$.
-We conclude that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$ by \cref{lem:inversionSetsWigglyPermutations}.
-
-Consider now any wiggly transposition~$\tau$ such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\tau)$.
-By \cref{lem:inversionSetsWigglyPermutations}, we obtain that~$\inv(\tau)$ also contains % both~$\big( \sigma(j+1), \sigma(i) \big)$ and~$\big( \sigma(k), \sigma(j) \big)$, hence also~
-$\big( \sigma(k), \sigma(i) \big)$.
-Since~$\inv(\sigma) \subset \inv(\tau)$ and~$\inv(\sigma)$ contains~$\big( \sigma(i), \sigma(p) \big)$ and~$\big( \sigma(q), \sigma(k) \big)$ for all~$i < p \le j$ and~$j+1 \le q < k$, we conclude by transitivity that~$\inv(\tau)$ contains~$\big( \sigma(q), \sigma(p) \big)$ for all~$i \le p \le j < q \le k$.
-\end{proof}
-
-\begin{proposition}
-Each wiggly permutation~$\sigma$ covers (resp.~is covered by) as many wiggly permutations as its number of descents (resp.~ascents).
-Hence, the cover graph of~$\wigglyLattice_n$ is regular of degree~$2n-1$ and connected.
-\end{proposition}
-
-\begin{proof}
-%Consider an ascent~$j$ of~$\sigma$.
-%Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
-%Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
-%Let~$\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n)$.
-%Then~$\sigma^j$ is the minimal wiggly permutation such that~$\inv(\sigma^j) \supseteq \inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\}$.
-Observe that~$\sigma^j \ne \sigma^{j'}$ for distinct ascents~$j \ne j'$.
-As any permutation~$\sigma'$ larger than~$\sigma$ satisfies~${\inv(\sigma') \supseteq \inv(\sigma) \cup \{\sigma(j+1), \sigma(j)\}}$ for some ascent~$j$ of~$\sigma$, we thus obtain that~$j \to \sigma^j$ is a bijection from the ascents of~$\sigma$ to the wiggly permutations covering~$\sigma$.
-The proof is symmetrical for the bijection from descents of~$\sigma$ to wiggly permutations covered by~$\sigma$.
-\end{proof}
-
-%%%%%%%%%%%%
-
-\subsection{Bijection}
-\label{subsec:bijection}
-
-\enlargethispage{.3cm}
-We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
-The following two definitions are illustrated in \cref{fig:wigglyLattice,fig:bijection}.
-
-\begin{figure}
-\centerline{\includegraphics[scale=1.7]{bijection}}
-\caption{The bijection between wiggly pseudotriangulations and wiggly permutations.}
-\label{fig:bijection}
-\end{figure}
-
+We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection.
+%, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
+The following two definitions are illustrated in \cref{fig:wigglyLattice}.
+
+%\begin{figure}
+%\centerline{\includegraphics[scale=1.7]{bijection}}
+%\caption{The bijection between wiggly pseudotriangulations and wiggly permutations.}
+%\label{fig:bijection}
+%\end{figure}
+
+\parpic(3.6cm,5cm)(-10pt, 133pt)[r][b]{\includegraphics[scale=2]{bijection}}{
 \begin{definition}
@@
 Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
-We define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
-\end{definition}
-
-\begin{example}
-The map~$\Phi$ sends the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} to the wiggly permutations of \cref{exm:specialWigglyPermutations}.
-Namely, $\Phi(T_\downarrow) = \sigma_\downarrow$, $\Phi(T_\uparrow) = \sigma_\uparrow$, $\Phi(T_\leftarrow) = \sigma_\leftarrow$, and~$\Phi(T_\rightarrow) = \sigma_\rightarrow$.
-\end{example}
+Define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
+See example on the right.
+\end{definition}
 
@@
 \label{def:bijection2}
-For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
-\begin{align*}
-i & \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i}, \\
-j & \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1}, \\
-A & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \subseteq \sigma([k])}, \\
-B & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) = \varnothing}.
-\end{align*}
-\end{definition}
-
-\begin{example}
-The map~$\Psi$ sends the wiggly permutations of \cref{exm:specialWigglyPermutations} to the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-Namely, $\Psi(\sigma_\downarrow) = T_\downarrow$, $\Psi(\sigma_\uparrow) = T_\uparrow$, $\Psi(\sigma_\leftarrow) = T_\leftarrow$, and~$\Psi(\sigma_\rightarrow) = T_\rightarrow$.
-\end{example}
+For a wiggly permutation~$\sigma$ of~$[2n]$, define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
+\begin{alignat*}{3}
+i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i} \quad &
+A & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])} \\
+j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1} \;\;\; &
+B & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing}
+\end{alignat*}
+\end{definition}
+}
 
@@
 \label{prop:bijection}
-The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a directed graph isomorphism between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-\end{proposition}
-
-\begin{proof}
-First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
-Observe first that~\(\Phi(T)\) is by construction a permutation~$\sigma$ of~$[2n]$.
-For any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
-Suppose that \(2j-1\) appears before \(2j\) in \(\sigma\) for some fixed \(j \in [n]\).
-This means that the pseudotriangle~\(t_j\) has its unlabelled corner to the left of its labelled corners.
-In other words, its hinge opens to the right (see \eg $t_2$ in~\cref{fig:bijection}).
-Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
-This label belongs to some pseudotriangle \(t_h\) with~$h > j$.
-In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i < 2j-1\).
-The other case (in which \(2j\) appears before \(2j-1\) in \(\sigma\)) is symmetric.
-
-Next, we show that \(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).
-Observe first that for any~$1 \le u < v \le n$, we cannot see~$\{2u, 2v-1\}$ before~$\{2u-1, 2v\}$ in~$\sigma$ as it contains no forbidden pattern of \cref{def:wigglyPermutation}.
-Using the notations of \cref{def:bijection2}, this implies that~$i < j$ and that~${]i,j[} = A \sqcup B$, so that~$\alpha(\sigma,k) \eqdef (i, j, A, B)$ is indeed a wiggly arc for each~$k \in [2n-1]$.
-By~\cref{prop:wigglyPseudotriangulations}, it thus suffices to check that for each \(k \neq k'\) in \([2n-1]\), the wiggly arcs 
-\(\alpha(\sigma,k)\) and~\(\alpha(\sigma,k')\) are distinct and compatible.
-\begin{enumerate}
-\item \textbf{Distinctness.}
-Suppose by contradiction that \(\alpha(\sigma,k) = (i,j,A,B) = \alpha(\sigma,k')\) for some~\({k < k'}\).
-Let~${\ell \in \sigma([k'] \ssm [k])}$ and~$\bar\ell \eqdef \lceil \ell/2 \rceil$.
-As~$\ell \notin \sigma([k])$, we have~$\bar\ell \notin A$.
-As~$\ell \in \sigma([k'])$, we have~$\bar\ell \notin B$.
-As~$\{2i-1, 2j\} \subseteq \sigma([k])$ and~$\{2i, 2j-1\} \cap \sigma([k']) = \varnothing$ and~$\sigma$ avoids the forbidden pattern of \cref{def:wigglyPermutation}, we have~$2i < \ell < 2j-1$, so that~$i < \bar\ell < j$.
-This contradicts the fact that~${]i,j[} = A \sqcup B$.
-
-\item \textbf{Compatibility.}
-Let $\alpha(\sigma, k) = (i,j,A,B)$ and $\alpha(\sigma, k') = (i',j',A',B')$ for some \(k < k'\).
-It is clear from the definition that \(i \neq j'\), as the sets over which we take the $\max$ and $\min$ to define \(i\) and \(j'\) respectively are disjoint.
-Similarly, \(j \neq i'\).
-Hence, the two wiggly arcs are pointed.
-To check that the wiggly arcs are non-crossing, we show that~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) = \varnothing$.
-Indeed~$A \cap B' = \varnothing$ since~$A \subseteq A'$ because~$\sigma([k]) \subseteq \sigma([k'])$.
-Moreover, \(\{i,j\} \cap B' = \emptyset\) since~\(\{2i - 1, 2j\} \subseteq \sigma([k]) \subseteq \sigma([k'])\).
-Finally, \(A \cap \{i',j'\} = \emptyset\) since~\(\{2i', 2j'-1\} \cap \sigma([k]) \subseteq \{2i', 2j'-1\} \cap \sigma([k']) = \varnothing\).
-\end{enumerate}
-
-Next, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
-Let \(\sigma\) be a wiggly permutation, so that \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
-Let~$k \in [2n-1]$ and~$m \eqdef \lceil \sigma(k)/2 \rceil$.
-Then observe~that
-\begin{itemize}
-\item if $\{2m, 2m-1\} \subseteq \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ passes above the point~$m$,
-\item if~$\sigma(k) = 2m$ and~$2m-1 \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has right endpoint~$m$,
-\item if~$\sigma(k) = 2m-1$ and~$2m \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has left endpoint~$m$.
-\end{itemize}
-It follows that in the wiggly pseudotriangulation~\(\Psi(\sigma)\), the wiggly arc \(\alpha(\sigma, k)\) is precisely the wiggly arc lying immediately above the angle labelled by~\(\sigma(k)\).
-Therefore, we have~\(\Phi(\Psi(\sigma)) = \sigma\).
-
-Conversely, let \(T\) be a wiggly pseudotriangulation, so that \(\sigma = \Phi(T)\) is a wiggly permutation.
-Then for any \(k \in [2n-1]\), the wiggly arc immediately above the angle of~$T$ labelled by~$\sigma(k)$ is precisely the one constructed as~\(\alpha(\sigma, k)\).
-This shows that \(\Psi(\Phi(T)) = T\).
-
-Finally, consider a cover relation~$\sigma \lessdot \sigma^j$ in the wiggly lattice~$\wigglyLattice_n$ as described in~\cref{lem:wigglyCoverRelation}.
-Using the notations of~\cref{lem:wigglyCoverRelation}, observe that
-\begin{itemize}
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell)$ for all~$\ell < i$ or~$\ell > k$,
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell+k-j)$ for all~$i \le \ell < j$, and
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell-j+i-1)$ for all~$j < \ell \le k$.
-\end{itemize}
-Hence, $\Psi(\sigma) \ssm \{\alpha(\sigma, j)\} = \Psi(\sigma^j) \ssm \{\alpha(\sigma^j, j)\}$.
-This implies that~$\Psi$ is a directed graph morphism from the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ to the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$.
-As the underlying undirected graphs are both regular of degree~$2n-1$, we conclude that~$\Phi$ and~$\Psi$ induce directed graph isomorphisms between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-\end{proof}
-
-\begin{remark}
-Transporting the wiggly lattice~$\wigglyLattice_n$ via the map~$\Psi$ to the wiggly pseudotriangulation, note that the minimal wiggly pseudotriangulation is~$\Psi(\sigma_\downarrow) = T_\downarrow$ while the maximal wiggly pseudotriangulation is~$\Psi(\sigma_\uparrow) = T_\uparrow$.
-See \cref{exm:specialWigglyPseudotriangulations,fig:specialWigglyPseudotriangulations} for illustrations.
-\end{remark}
-
-\begin{remark}
-The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
-\end{remark}
-
-\begin{remark}
-The map~$\Phi$ sends wiggly pseudotriangulations with $i$ final internal wiggly arcs to wiggly permutations with $i$ admissible gaps, explaining the similarities of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Graph properties}
-\label{subsec:graphProperties}
-
-We conclude this combinatorial section with two open questions and a conjecture on graphical properties of the wiggly flip graph~$\wigglyFlipGraph_n$ (or equivalently of the cover graph of the wiggly lattice~$\wigglyLattice_n$), motivated by the relevance of similar questions for the associahedron.
-
-First, we are interested in the graph diameter~$\delta_n$ of~$\wigglyFlipGraph_n$.
-It is clearly bounded below by~$2n-1$ (as~$T_\leftarrow \cap T_\rightarrow = \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$, all $2n-1$ internal wiggly arcs must sometimes be flipped at least once) and above by~$\binom{2n}{2}$ (as we have a sublattice of the weak order on permutations of~$[2n]$).
-The first few values of~$\delta_n$ are
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & \dots \\
-\hline
-\delta_n & 1 & 4 & 8 & 14 & 20 & \dots
-\end{array}
-\]
-but they might be misleading as for the associahedron~\cite{Pournin}.
-This raises the following question.
-
-\begin{question}
-Compute (or estimate) the diameter~$\delta_n$ of the wiggly flip graph~$\wigglyFlipGraph_n$.
-\end{question}
-
-Related to the estimation of the diameter~$\delta_n$ is the study of the properties of the geodesic paths in~$\wigglyFlipGraph_n$.
-We refer to~\cite{CeballosPilaud-diameterDAssociahedron} for a discussion on geodesic properties in a polytope, in connection to the revisiting path property and the complexity of the simplex algorithm~\cite{Santos-surveyHirsch,Santos-Hirsch}.
-
-\begin{question}
-Does the wiggly complex has the non-leaving face property of~\cite{CeballosPilaud-diameterDAssociahedron}?
-\end{question}
-
-Finally, we checked the following conjecture computationally up to~$n = 3$.
-
-\begin{conjecture}
-\label{conj:Hamiltonian}
-The wiggly flip graph~$\wigglyFlipGraph_n$ admits an Hamiltonian path (or even cycle).
-\end{conjecture}
-
-Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Wiggly fan and wigglyhedron}
-\label{sec:geometry}
-
-In this section, we use $\b{g}$- and $\b{c}$-vectors (\cref{subsec:gcvectors}) to define the wiggly fan (\cref{subsec:wigglyFan}) and the wigglyhedron (\cref{subsec:wigglyhedron}), which provide geometric realizations of the wiggly complex and of the wiggly lattice.
-
-%%%%%%%%%%%%
-
-\subsection{Polyhedral geometry}
-\label{subsec:polyhedralGeometry}
-
-We refer to \cite{Ziegler-polytopes} for a reference on polyhedral geometry, and only remind the basic notions needed later in the paper.
-
-A (polyhedral) \defn{cone} is the positive span~$\R_{\ge 0}\b{R}$ of a finite set~$\b{R}$ of vectors of~$\R^d$ or equivalently, the intersection of finitely many closed linear half-spaces of~$\R^d.$ 
-The \defn{faces} of a cone are its intersections with its supporting hyperplanes. 
-The \defn{rays} (resp.~\defn{facets}) are the faces of dimension~$1$ (resp.~ codimension~$1$).
-A cone is \defn{simplicial} if its rays are linearly independent.
-A (polyhedral) \defn{fan}~$\Fan$ is a set of cones such that any face of a cone of~$\Fan$ belongs to~$\Fan$, and any two cones of~$\Fan$ intersect along a face of both. 
-A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^d$, and \defn{simplicial} if all its cones are simplicial.
-
-Note that a simplicial fan defines a simplicial complex on its rays (the simplices of the simplicial complex are the subsets of rays which span a cone of the fan).
-Conversely, given a simplicial complex~$\Delta$ with ground set~$V$, one can try to realize it geometrically by associating a ray~$\b{r}_v$ of~$\R^d$ to each~$v \in V$, and the cone~$\R_{\ge 0}\b{R}_\triangle$ generated by the set~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ to each~$\triangle \in \Delta$.
-To show that the resulting cones indeed form a fan, we will need the following statement, which can be seen as a reformulation of~\cite[Coro.~4.5.20]{DeLoeraRambauSantos}.
-
-\begin{proposition}
-\label{prop:characterizationFan}
-Consider a simplicial $(d-1)$-dimensional pseudomanifold~$\Delta$ without boundary on a ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
-Then the collection of cones~$\set{\R_{\ge 0}\b{R}_\triangle}{\triangle \in \Delta}$ forms a complete simplicial fan of~$\R^d$ if and~only~if
-\begin{itemize}
-\item there exists a vector~$\b{v}$ of~$\R^d$ contained in only one of the cones~$\R_{\ge 0}\b{R}_\triangle$ for~$\triangle \in \Delta$,
-\item for any two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have~$\lambda_v \lambda_{v'} > 0$~where
-\[
-\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
-\]
-denotes the unique (up to rescaling) linear dependence on~$\b{R}_{\triangle \cup \triangle'}$.
-\end{itemize}
-\end{proposition}
-
-A \defn{polytope} is the convex hull of finitely many points of~$\R^d$ or equivalently, a bounded intersection of finitely many closed affine half-spaces of~$\R^d$.
-The \defn{faces} of a polytope are its intersections with its supporting hyperplanes.
-The \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) are the faces of dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$).
-
-The \defn{normal cone} of a face~$\polytope{F}$ of a polytope~$\polytope{P}$ is the cone generated by the normal vectors to the supporting hyperplanes of~$\polytope{P}$ containing~$\polytope{F}$.
-Said differently, it is the cone of vectors~$\b{c}$ of~$\R^d$ such that the linear form~$\b{x} \mapsto \dotprod{\b{c}}{\b{x}}$ on~$\polytope{P}$ is maximized by all points of the face~$\polytope{F}$.
-The \defn{normal fan} of~$\polytope{P}$ is the set of normal cones of all its faces.
-
-\enlargethispage{.5cm}
-Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
-To realize the fan~$\Fan$, one can try to pick a height vector~$\b{h} \eqdef (h_v)_{v \in V} \in \R^V$ and consider the polytope
-\(
-\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}.
-\)
-The following classical statement characterizes the height vectors~$\b{h}$ for which the fan~$\Fan$ is the normal fan of this polytope~$\polytope{P}_{\b{h}}$.
-We borrow the formulation from~\cite[Lem.~2.1]{ChapotonFominZelevinsky}.
-
-\begin{proposition}
-\label{prop:characterizationPolytopalFan}
-Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~$\triangle \in \Delta$.
-Then the following are equivalent for any height vector~$\b{h} \in \R^V$:
-\begin{itemize}
-\item The fan~$\Fan$ is the normal fan of the polytope~$\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}$.
-\item For two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, the height vector~$\b{h}$ satisfies the \defn{wall crossing inequality}
-\[
-\lambda_v \, h_v + \lambda_{v'} \, h_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, h_w > 0,
-\]
-where
-\[
-\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
-\]
-denotes the unique linear dependence on~$\b{R}_{\triangle \cup \triangle'}$ such that~$\lambda_v + \lambda_{v'} = 2$.
-\end{itemize}
-\end{proposition}
-
-We denote by~$(\b{e}_i)_{i \in [d]}$ the standard basis of~$\R^d$.
-For~$I \subseteq [d]$, we define~$\one_I \eqdef \sum_{i \in I} \b{e}_i$, and we often shorten~$\one_{[d]}$ by~$\one_d$.
+The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, inducing a graph isomorphism between the wiggly flip graph~$\wigglyIncreasingFlipGraph_n$ and the cover diagram of the wiggly lattice~$\wigglyLattice_n$.
+\end{proposition}
+
+\newpage
+\section{Wiggly fan}
+\label{sec:wigglyFan}
+
+We denote by~$\smash{(\b{e}_i)_{i \in [d]}}$ the standard basis of~$\R^d$.
+For~$I \subseteq [d]$, we define~$\one_I \eqdef \sum_{i \in I} \b{e}_i$, and we often shorten~$\smash{\one_{[d]}}$ by~$\one_d$.
 We denote by~$\HH_d$ the hyperplane of~$\R^d$ defined by the equation~$\dotprod{\b{x}}{\one_d} = 0$, and we denote by~$\pi : \R^d \to \HH$ the orthogonal projection on~$\HH_d$, that is~$\pi(\b{x}) \eqdef \b{x} - (\dotprod{\b{x}}{\one_d} / d) \one_d$.
-
-%%%%%%%%%%%%
-
-\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
-\label{subsec:gcvectors}
-
-We now define two families of vectors, illustrated in \cref{fig:pseudotriangulationMatrices}.
 %
-\begin{figure}
+We now define a first family of vectors, see \cref{fig:pseudotriangulationMatrices}.
+%
+\begin{figure}[b]
 \centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $4$ times the $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.} % The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
 The colors of the columns match the colors of the wiggly arcs.}
@@
 The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
+\vspace{-.25cm}
 \begin{align*}
@@
 \alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
+\\[-.9cm]
 \end{align*}
-If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
-Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
+%If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
+%Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
+\noindent
 We define~$\b{g}(D) \eqdef \set{\b{g}(\alpha)}{\alpha \in D^\circ}$ for a set~$D$ of wiggly arcs.
@@
 
-\begin{example}
-\label{exm:specialGMatrices}
-\cref{table:specialGMatrices} gathers the $\b{g}$-matrices (\ie matrices whose columns are the $\b{g}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
-
-\begin{table}[p]
-	\begingroup
-	\fontsize{10}{10}\selectfont
-	\setlength\arraycolsep{2pt}
-	\begin{alignat*}{3}
-%	\b{g}(T_\downarrow) & = \begin{pmatrix}
-%		1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & 1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 1 & 0 & -1 & -1 & \dots & -1 & 1 \\
-%		-1 & -1 & \dots & -1 & 0 & -1 & -1 & \dots & -1 & 1 \\
-%		-1 & -1 & \dots & -1 & 1 & -1 & -1 & \dots & -1 & -1 \\
-%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\b{g}(T_\downarrow) & = \begin{pmatrix}
-		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
-	\end{pmatrix}
-	\qquad &
-%	\b{g}(T_\leftarrow) & = \begin{pmatrix}
-%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & -1 & \dots & -1 & -1 & -1 & 1 & \dots & 1 & 1 \\
-%		0 & 1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & -1 & -1 & 0 & -1 & \dots & 1 & 1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & -1 & 1 \\
-%		0 & 0 & \dots & 1 & -1 & 0 & 0 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & 1 & 0 & 0 & \dots & 0 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\b{g}(T_\leftarrow) & = \begin{pmatrix}
-		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
-		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
-		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-	\end{pmatrix}
-	\\[.3cm]
-%	\b{g}(T_\uparrow) & = \begin{pmatrix}
-%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%		1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%		0 & -1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
-%		0 & 1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & -1 \\
-%		0 & 0 & \dots & 1 & -1 & 1 & 1 & \dots & 1 & -1 \\
-%		0 & 0 & \dots & 0 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & 0 & 1 & 1 & 1 & \dots & 1 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\b{g}(T_\uparrow) & = \begin{pmatrix}
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-	\end{pmatrix}
-	\qquad &
-%	\b{g}(T_\rightarrow) & = \begin{pmatrix}
-%		1 & 0 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		-1 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
-%		-1 & 1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & -1 & \dots & 0 & 0 \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & -1 & 0 \\
-%		-1 & -1 & \dots & 1 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & -1 & 0 & 1 & 1 & \dots & 1 & -1 \\
-%		-1 & -1 & \dots & -1 & 1 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\b{g}(T_\rightarrow) & = \begin{pmatrix}
-		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
-		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots  & \ddots & \vdots & \vdots \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
-	\end{pmatrix}
-	\end{alignat*}
-	\endgroup
-	\caption{The $\b{g}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\b{g}(T)$ is the $\b{g}$-vector~$\b{g}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
-}
-	\label{table:specialGMatrices}
-\end{table}
-\end{example}
-
-Observe that the $\b{g}$-matrices of \cref{exm:specialGMatrices} have full rank.
-More generally, we will see in \cref{coro:basis} that~$\b{G}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis.
+The main feature of these $\b{g}$-vectors is that we control their behavior under flip.
+
+\begin{proposition}
+\label{prop:linearDependences}
+Let~$T$ and~$T'$ be two wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
+Then~$\{\beta, \beta'\} \in T \cap T'$ and
+\begin{compactitem}
+\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$,
+\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
+\end{compactitem}
+\end{proposition}
+
+This property implies in particular that the $\b{g}$-vectors of each wiggly pseudotriangulation form a basis of~$\HH_{2n}$, which enables us to define the dual basis, called $\b{c}$-vectors.
+
+\begin{proposition}
+\label{prop:basis}
+For any wiggly pseudotriangulation~$T$, the set~$\b{g}(T)$ is a basis of~$\HH_{2n}$.
+\end{proposition}
 
@@
 \label{def:cvectors}
-The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$ is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha)} = 1$ and~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha')} = 0$ for all interior wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
-In other words, $\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ is the dual basis of~$\b{g}(T)$~in~$\HH_{2n}$.
-\end{definition}
-
-\begin{remark}
-The $\b{c}$-vector~$\b{c}(\alpha, T)$ can also be described combinatorially.
-Namely, label the the corners of~$T$ as in \cref{def:bijection1}, and denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-Then the $\b{c}$-vector~$\b{c}(\alpha, T)$ has coordinates
-\begin{itemize}
-\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
-\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
-\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
-\end{itemize}
-The tedious proof of this description is not needed here as we only use the dual basis property.
-\end{remark}
-
-\begin{example}
-\label{exm:specialCMatrices}
-\cref{table:specialCMatrices} gathers the $\b{c}$-matrices (\ie matrices whose columns are the $\b{c}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
-
-\begin{table}
-	\begingroup
-	\fontsize{10}{10}\selectfont
-	\setlength\arraycolsep{2pt}
-	\begin{alignat*}{3}
-%	4\b{c}(T_\downarrow) & = \begin{pmatrix}
-%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
-%		-2 & 0 & \dots & 0 & 0 & 2 & 0 & \dots & 0 & 0 \\
-%		0 & 2 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
-%		0 & -2 & \dots & 0 & 0 & -1 & 2 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & -1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 2 & 0 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & -1 & 2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & -1 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\downarrow) & = \begin{pmatrix}
-		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
-		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
-		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		0 & 0 & 0& 0 & \dots & 2 & 0 & 0 \\
-		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
-	\end{pmatrix}
-	\quad &
-%	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
-%		-2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & -2 & 1 & \dots & 0 & 0 \\
-%		0 & 2 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & -2 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & 0 & 0 & 0 & \dots & 1 & 0 \\
-%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & -2 & 1 \\
-%		0 & 0 & \dots & 2 & -1 & 0 & 0 & \dots & 0 & 1 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & -2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
-		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
-		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
-		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-	\end{pmatrix}
-	\quad
-	\\[.3cm]
-%	4\b{c}(T_\uparrow) & = \begin{pmatrix}
-%		-2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
-%		2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
-%		0 & -2 & \dots & 0 & 0 & 2 & -1 & \dots & -1 & 2 \\
-%		0 & 2 & \dots & 0 & 0 & 0 & -1 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 2 & \dots & 2 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & 2 & -1 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & 2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\uparrow) & = \begin{pmatrix}
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
-		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 2 & 0 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
-		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
-		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
-		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-	\end{pmatrix}
-	\quad &
-%	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
-%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & -2 & 0 & \dots & 0 & 0 \\
-%		-1 & 2 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		-1 & 0 & \dots & 0 & 0 & 1 & -2 & \dots & 0 & 0 \\
-%		0 & -1 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -2 & 0 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 1 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 1 & -2 \\
-%		0 & 0 & \dots & -1 & 2 & 0 & 0 & \dots & 0 & 1 \\
-%		0 & 0 & \dots & -1 & -2 & 0 & 0 & \dots & 0 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
-		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
-		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
-		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
-	\end{pmatrix}
-	\end{alignat*}
-	\endgroup
-	\caption{$4$ times the $\b{c}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\b{c}(T)$ is $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).}
-	\label{table:specialCMatrices}
-\end{table}
-\end{example}
-
-%\begin{definition}
-%\label{def:cvectors}
-%Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
-%Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-%The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
-%\begin{itemize}
-%\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-%\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
-%\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
-%\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
-%\end{itemize}
-%Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
-%\end{definition}
-%
-%\begin{proposition}
-%\label{prop:dualBases}
-%For any wiggly pseudotriangulation~$T$, the sets~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases~of~$\HH_{2n}$.
-%\end{proposition}
-%
-%\begin{proof}
-%We claim that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
-%Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
-%Hence, we obtain that~$\dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \dotprod{\pi(\hat{\b{g}}(\alpha))}{\b{c}(\alpha', T)} = \dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$.
-%We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
-%
-%The proof of the claim is a boring case analysis.
-%Let~$i < j$ be the endpoints of~$\alpha$, and let~$u$ and~$v$ the labels (in the corner labeling of~$T$) incident to~$\alpha'$ and respectively below and above~$\alpha'$, and~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-%By symmetry, we can assume that~$u < v$ so that~$\bar u \le \bar v$.
-%Let us write~$\hat{\b{g}}(\alpha) \eqdef (g_1, \dots, g_{2n})$ and~$\b{c}(\alpha', T) \eqdef (c_1, \dots, c_{2n})$, and define~$gc_k \eqdef g_{2k-1}c_{2k-1} + g_{2k}c_{2k}$.
-%Hence, we have~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \sum_{k \in [n]} gc_k = \sum_{k \in \{i, j, \bar u, \bar v\}} gc_k$.
-%Indeed, the last equality holds since~$g_{2k-1} = g_{2k}$ for all~$k \in [n] \ssm \{i,j\}$ and~$c_{2k-1} = -c_{2k}$ for all~$k \in [n] \ssm \{\bar u, \bar v\}$.
-%
-%Assume first that~$\alpha = \alpha'$.
-%Hence, we have~$i \le \bar u \le \bar v \le j$.
-%We distinguish two cases:
-%\begin{enumerate}
-%\item If~$i = \bar u = \bar v < j$, then~$u = 2i-1$ and~$v = 2i$, so that~$gc_i = 1 \cdot 1/2 + (-1) \cdot (-1/2) = 1$ and~$gc_j = 0$, thus~$\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = gc_i + gc_j = 1$.
-%\item Otherwise, $i \le \bar u < \bar v \le j$.
-%If~$i = \bar u$, we have~$u = 2i-1$ so that~$gc_{\bar u} = 1 \cdot 1/2 + (-1) \cdot 0 = 1/2$.
-%If~$i < \bar u$, we have~$gc_i = 0$ (since~$c_{2i-1} = c_{2i} = 0$) and~$gc_{\bar u} = 1/2$ (since~$g_{2\bar u-1} = g_{2\bar u} = 1$ and~${c_{2\bar u-1} + c_{2\bar u} = 1/2}$).
-%In both cases, we get that~$\sum_{k \in \{i, \bar u\}} gc_k = 1/2$.
-%By symmetric arguments, we conclude~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = \sum_{k \in \{i, \bar u\}} gc_k + \sum_{k \in \{j, \bar v\}} gc_k = 1/2 + 1/2 = 1}$.
-%\end{enumerate}
-%
-%Assume now that~$\alpha \ne \alpha'$.
-%\vincent{I am really unhappy with this proof. I can do the case analysis, but it is really unsatisfactory. I am waiting to see if I find another idea...}
-%We distinguish ten cases:
-%\begin{enumerate}
-%\item If~$j < \bar u$, then~$c_{2i-1} = c_{2i} = c_{2j-1} = c_{2j} = 0$ and~$g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-%\item If~$j = \bar u < \bar v$, then~$c_{2i-1} \! = \! c_{2i} \! = \! 0$, $g_{2j-1} \! = \! -g_{2j}$ and~$c_{2j-1} \! = \! c_{2j}$,  and~${g_{2 \bar v-1} \! = \! g_{2 \bar v} = 0}$.
-%\item If~$i < \bar u < j < \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2 \bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$, and~$g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-%\item If~$i < \bar u < j = \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2\bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$.
-%\item If~$i < \bar u \le \bar v < j$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v}$ and~$c_{2 \bar u-1} + c_{2\bar u} + c_{2j-1} + c_{2j} = 0$, and~$c_{2j-1} = c_{2j} = 0$.
-%\item If~$i = \bar u < j < \bar v$, then \dots
-%\item If~$i = \bar u < j = \bar v$, then \dots
-%\item If~$i = \bar u < \bar v < j$, then \dots
-%\item If~$\bar u < i < j < \bar v$, then \dots
-%\item If~$\bar u < i < j = \bar v$, then \dots
-%\item If~$\bar u < i < \bar v < j$, then \dots
-%\item If~$\bar u < i = \bar v < j$, then \dots
-%\item If~$\bar u < \bar v < i < j$, then \dots
-%\end{enumerate}
-%(Note that~$\bar u = \bar v$ implies that~$\{i,j\} \notin \bar u$.)
-%In all cases, we check that~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = 0}$.
-%\end{proof}
-
-\begin{remark}
-\label{rem:gcvectorsSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism}, note that the vertical and horizontal symmetries on wiggly arcs translate on $\b{g}$- and $\b{c}$-vectors to the isometries sending~$(x_1, x_2, \dots, x_{2n-1}, x_{2n}) \in \HH_{2n}$ to~$(x_{2n}, x_{2n-1}, \dots, x_2, x_1)$ and to~$(-x_2, -x_1, \dots, -x_{2n}, -x_{2n-1})$ respectively.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly fan}
-\label{subsec:wigglyFan}
-
-We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$.
+The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a \mbox{wiggly pseudotriangulation~$T$} is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha)} \!=\!
+1$ and~$\dotprod{\b{c}(\alpha, T)\!}{\!\b{g}(\alpha')} \!=\!
+0$~for~all wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
+That is, $\b{c}(T) \eqdef \! \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ and~$\b{g}(T)$ are dual bases~in~$\HH_{2n}$.
+\end{definition}
+
+We finally exploit $\b{g}$-vectors to support the wiggly fan realizing the wiggly complex.
 
@@
 
-To prove \cref{thm:wigglyFan}, we just need to check the conditions of \cref{prop:characterizationFan}.
-We first find a vector contained in the cone~$\R_{\ge 0} \b{g}(T)$ for a single wiggly pseudotriangulation~$T$.
-
-\begin{lemma}
-\label{lem:-+...-+}
-Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and for~${i \in [n]}$, let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$.
-Then~$T_\leftarrow \eqdef \{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
-\end{lemma}
-
-\begin{proof}
-Observe first that, for any wiggly arc~$\alpha \eqdef (i, j, A, B)$ and any~$k \in [n]$, we have
-%\begin{itemize}
-%\item $\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = 1$ if~$k = i$, $-1$ if~$k = j$, and~$0$ otherwise,
-%\item $\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = 2$ if~$k \in A$, $-2$ if~$k \in B$, and~$0$ otherwise.
-%\end{itemize}
-\[
-\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 1 & \text{if~$k = i$,} \\ -1 & \text{if~$k = j$,} \\ 0 & \text{otherwise}, \end{cases}
-\qquad\text{and}\qquad
-\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 2 & \text{if~$k \in A$,} \\ -2 & \text{if~$k \in B$,} \\ 0 & \text{otherwise}. \end{cases}
-\]
-
-Assume now that~$\b{v} = \sum_\alpha \lambda_\alpha \, \hat{\b{g}}(\alpha)$ where the sum ranges over all wiggly arcs~$\alpha$ for some positive scalars~$\lambda_\alpha \ge 0$ such that~$\lambda_\alpha \cdot \lambda_{\alpha'} = 0$ for all incompatible wiggly arcs~$\alpha$ and~$\alpha'$.
-For~$k \in [n]$, let~$\underline{\Lambda}_k$ (resp.~$\overline{\Lambda}_k$) denote the sum of~$\lambda_\alpha$ over the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$k \in A$ (resp.~$k \in B$).
-Note that~$\underline{\Lambda}_k = \overline{\Lambda}_k$ since~$0 = \b{v}_{2k-1} + \b{v}_{2k} = \sum_\alpha \lambda_\alpha \big( \hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} \big) = 2\underline{\Lambda}_k - 2\overline{\Lambda}_k$.
-
-As~$\b{v}_1 - \b{v}_2 = -2$ and~$\hat{\b{g}}(\alpha)_1 - \hat{\b{g}}(\alpha)_2 \ge 0$ except if~$\alpha = \alpha_0$, we have~$\lambda_{\alpha_0} > 0$, and thus~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$1$.
-%As~$\b{g}(\alpha)_1 - \b{g}(\alpha)_2 = 0$ for all wiggly arcs~$\alpha$ with no endpoint at~$1$, we thus obtain that~$\lambda_{\alpha_0} = 1$.
-We then prove by induction on~$i \in [n-1]$ that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$ and that~$\lambda_\alpha = 0$ for all wiggly arcs starting at~$i+1$.
-Consider~$i \in [n-1]$ and assume that we proved it for~$i-1$.
-As~$\smash{\lambda_{\underline{\alpha}_{i-1}} \cdot \lambda_{\overline{\alpha}_{i-1}} > 0}$, we already have~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ ending at~$i+1$, except if~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
-As~$\b{v}_{2i+1} - \b{v}_{2i+2} = -2$, this implies that~$\smash{\lambda_{\underline{\alpha}_i} + \lambda_{\overline{\alpha}_i} = 1}$.
-This already implies that~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$i+1$.
-Moreover, assume for instance that~$\lambda_{\overline{\alpha}_i} > 0$.
-Hence, $\lambda_\alpha = 0$ for all wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$i \in A$ and~$i+1 \in B$.
-We thus obtain that~$\underline{\Lambda}_i - \lambda_{\underline{\alpha}_i} \le \underline{\Lambda}_{i+1}$ and~$\overline{\Lambda}_i - \lambda_{\overline{\alpha}_i} \ge \overline{\Lambda}_{i+1}$.
-As~$\underline{\Lambda}_i = \overline{\Lambda}_i$ and~$\underline{\Lambda}_{i+1} = \overline{\Lambda}_{i+1}$, we thus obtain that~$\lambda_{\underline{\alpha}_i} \ge \lambda_{\overline{\alpha}_i} > 0$, hence that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$.
-We conclude that~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ except if~$\alpha = \alpha_0$ or~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$ for some~$i \in [n]$.
-
-Consider now a wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
-Write~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \b{g}(\alpha)$ with~$\lambda_\alpha \ge 0$ for all~$\alpha \in T^\circ$.
-Let~$\mu \eqdef \sum_{\alpha \in T^\circ} \lambda_\alpha \dotprod{\hat{\b{g}}(\alpha)}{\one_{2n}}$.
-As~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \hat{\b{g}}(\alpha) - \mu \, \one_{2n}$ and~$\one_{2n} = \hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)$, we thus conclude from the previous paragraph that~$T = T_\leftarrow$.
-%\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
-\end{proof}
-
-We now describe the unique linear dependence between the $\b{g}$-vectors of two adjacent facets of the wiggly complex~$\wigglyComplex_n$.
-The following statement is illustrated in \cref{fig:incompatible3}.
-
-\begin{lemma}
-\label{lem:linearDependences}
-Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
-Then~$\{\beta, \beta'\} \in T \cap T'$ and
-\begin{itemize}
-\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$,
-\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-In both situations, we will just prove that the same linear dependence holds on the vectors~$\hat{\b{g}}(\alpha), \hat{\b{g}}(\alpha'), \hat{\b{g}}(\beta), \hat{\b{g}}(\beta')$, which will imply the statement as~$\pi$ is a linear map.
-
-If~$\alpha$ and~$\alpha'$ are non pointed, then we have
-\[
-\alpha^+ \sqcup \alpha'^+ = \beta^+ \sqcup \{2j-1, 2j\} = \beta'^+
-\qquad\text{and}\qquad 
-\alpha^- \sqcup \alpha'^- = \beta^- = \beta'^- \sqcup \{2j-1, 2j\}.
-\]
-We thus obtain that
-\[
-\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\beta^+} + \b{e}_{2j-1} + \b{e}_{2j} = \one_{\beta'^+}
-\qquad\text{and}\qquad 
-\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} = \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}.
-\]
-hence
-\begin{align*}
-2 \big( \hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') \big)
-& = 2(\one_{\alpha^+} - \one_{\alpha^-}) + 2(\one_{\alpha'^+} - \one_{\alpha'^-})
-= 2(\one_{\alpha^+} + \one_{\alpha'^+}) - 2(\one_{\alpha^-} + \one_{\alpha'^-}) \\
-& = (\one_{\beta^+} + \one_{\beta'^+} + \b{e}_{2j-1} + \b{e}_{2j}) - (\one_{\beta^-} + \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}) \\
-& = (\one_{\beta^+} + \one_{\beta'^+}) - (\one_{\beta^-} + \one_{\beta'^-})
-= (\one_{\beta^+} - \one_{\beta^-}) + (\one_{\beta^-} + \one_{\beta'^-})
-= \hat{\b{g}}(\beta) + \hat{\b{g}}(\beta').
-\end{align*}
-
-If~$\alpha$ and~$\alpha'$ cross, then we have
-\begin{gather*}
-\alpha^+ \cup \alpha'^+ = \beta^+ \cup \beta'^+ \qquad\text{and}\qquad \alpha^+ \cap \alpha'^+ = \beta^+ \cap \beta'^+, \\
-\alpha^- \cup \alpha'^- = \beta^- \cup \beta'^- \qquad\text{and}\qquad \alpha^- \cap \alpha'^- = \beta^- \cap \beta'^-.
-\end{gather*}
-We thus obtain that
-\[
-\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\alpha^+ \cup \alpha'^+} + \one_{\alpha^+ \cap \alpha'^+} = \one_{\beta^+ \cup \beta'^+} + \one_{\beta^+ \cap \beta'^+} = \one_{\beta^+} + \one_{\beta'^+}
-\]
-and similarly~$\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} + \one_{\beta'^-}$, so that~$\hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') =\hat{\b{g}}(\beta) + \hat{\b{g}}(\beta')$.
-\end{proof}
-
-\begin{corollary}
-\label{coro:basis}
-For any wiggly pseudotriangulation~$T$, the set~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ is a basis of~$\HH_{2n}$.
-\end{corollary}
-
-\begin{proof}
-Observe that the $\b{g}$-matrix~$\b{g}(T_\leftarrow)$ presented in \cref{exm:specialGMatrices} has full rank (it is very easy to check for~$\b{g}(T_\leftarrow)$, but any other would do).
-The statement thus follows from \cref{lem:linearDependences} and the connectedness of the flip graph on wiggly pseudotriangulations.
-\end{proof}
-
-Finally, we wrap up \cref{thm:wigglyFan}.
-
-\begin{proof}[Proof of \cref{thm:wigglyFan}]
-Directly follows from \cref{prop:characterizationFan,lem:-+...-+,lem:linearDependences}.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyFanSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define linear automorphisms of the wiggly fan~$\wigglyFan_n$.
-\end{remark}
-
-\begin{remark}
-By definition, each wall of the wiggly fan is normal to a $\b{c}$-vector.
-Hence, the wiggly fan coarsens the \defn{$\b{c}$-vector fan}, defined by the arrangement of hyperplanes~$\set{\b{x} \in \HH_{2n}}{\dotprod{\b{x}}{\b{c}(\alpha, T}}$ for all wiggly arcs~$\alpha$ and wiggly pseudotriangulations~$T$ with~$\alpha \in T$.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wigglyhedron}
-\label{subsec:wigglyhedron}
+\newpage
+\section{Wigglyhedron}
+\label{sec:wigglyhedron}
 
 We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
+For this, we just choose a support function on the rays of the wiggly fan~$\wigglyFan_n$, inspired from~\cite{HohlwegPilaudStella,PaluPilaudPlamondon-nonkissing}.
 %
-\afterpage{
-\begin{figure}
-\centerline{\input{wigglyhedron}}
+\begin{figure}[b]
+\centerline{\input{figures/wigglyhedron}}
 \caption{The wigglyhedron~$\wigglyhedron_2$.}
@@
 \end{figure}
-}
 
@@
 \label{def:incompatibilityDegree}
-The \defn{incompatibility degree}~$\delta(\alpha, \alpha')$ of two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ is given by
-\begin{itemize}
+The \defn{incompatibility degree}~$\delta(\alpha, \alpha')$ of~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ is %given by
+\begin{compactitem}
 \item $0$ if~$\alpha$ and~$\alpha'$ are pointed and non-crossing,
-\item $1$ is~$\alpha$ and~$\alpha'$ are not pointed (\ie $i = j'$ or~$i' = j$),
-\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing (\ie the number of~$p \in \{0, \dots, n\}$ with $p \in (A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\})$ and~$p+1 \in (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, or the opposite).
-\end{itemize}
+\item $1$ is~$\alpha$ and~$\alpha'$ are not pointed, % (\ie $i = j'$ or~$i' = j$),
+\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing.
+% (\ie the number of~$p \in \{0, \dots, n\}$ with $p \in (A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\})$ and~$p+1 \in (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, or the opposite).
+\end{compactitem}
 The \defn{incompatibility number} of a wiggly arc~$\alpha$ is~$\kappa(\alpha) \eqdef \sum_{\alpha'} \delta(\alpha, \alpha')$.
@@
 
-\begin{remark}\label{rem:incompatibility-deg}
-Note that~$\delta$ is indeed an incompatibility degree in the sense that
-\begin{itemize}
-\item $\alpha$ and~$\alpha'$ are compatible if and only if~$\delta(\alpha, \alpha') = 0$,
-\item $\alpha$ and~$\alpha'$ are exchangeable if and only if~$\delta(\alpha, \alpha') = 1$.
-\end{itemize}
-Observe also that~$\delta$ (and thus~$\kappa$) is preserved by the automorphisms of \cref{rem:wigglyComplexAutomorphism}.
-\end{remark}
-
-%\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}
-
-\begin{example}
-Observe that
-$\kappa \big( (0, j, {[1,j[}, \varnothing) \big) 
-= \kappa \big( (0, j, \varnothing, {[1,j[}) \big) 
-%= \kappa \big( (n+1-j, n+1, {]n+1-j, n]}, \varnothing) \big) 
-%= \kappa \big( (n+1-j, n+1, \varnothing, {]n+1-j, n]}) \big) 
-= (2^j-1)(2^{n+1-j}-1)$.
-\end{example}
-
-\begin{lemma}
-\label{lem:wallCrossingInequalities}
-Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
+Note that~$\delta(\alpha, \alpha')$ is indeed an incompatibility degree, in the sense that~$\alpha$ and~$\alpha'$ are compatible if and only if~$\delta(\alpha, \alpha') = 0$ and exchangeable if and only if~$\delta(\alpha, \alpha') = 1$.
+The following statement is the main feature of the incompatibility number.
+
+\begin{proposition}
+\label{prop:wallCrossingInequalities}
+Let~$T$ and~$T'$ be two wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
 Then
-\begin{itemize}
+\begin{compactitem}
 \item if $\alpha$ and~$\alpha'$ are not pointed, then~$\kappa(\alpha) + \kappa(\alpha') > \big( \kappa(\beta) + \kappa(\beta') \big) / 2$,
 \item if~$\alpha$ and~$\alpha'$ are crossing, then~${\kappa(\alpha) + \kappa(\alpha') > \kappa(\beta) + \kappa(\beta')}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-Any crossing between a wiggly arc~$\gamma$ and~$\beta$ or~$\beta'$ translates to a crossing with~$\alpha$ or~$\alpha'$.
-When~$\alpha$ and~$\alpha'$ are not pointed, a crossing with~$\alpha$ or~$\alpha'$ can correspond to a crossing with~$\beta$ and a crossing with~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \big( \delta(\beta, \gamma) + \delta(\beta', \gamma) \big) / 2$.
-When~$\alpha$ and~$\alpha'$ are crossing, then there is a correspondence between the crossings with~$\alpha$ or~$\alpha'$ and the crossings with~$\beta$ or~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \delta(\beta, \gamma) + \delta(\beta', \gamma)$.
-Moreover, both inequalities are strict for~$\gamma = \alpha'$ since~$\delta(\alpha,\alpha') = 1$ while~$\delta(\beta, \alpha') = \delta(\beta, \alpha') = 0$.
-The result thus follows by summation.
-\end{proof}
+\end{compactitem}
+\end{proposition}
+
+Combining \cref{prop:linearDependences,prop:wallCrossingInequalities}, the incompatibility number satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$, from which we derive our main statement.
+%that it behaves properly with respect to the linear dependences of
 
@@
 The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
-\begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \! \le \! \kappa(\alpha)}$ for all internal wiggly~arcs~$\alpha$,
-\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
-\end{itemize}
+\begin{compactitem}
+\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!\!}{\!\!\dotprod{\b{g}(\alpha)\!}{\!\b{x}} \! \le \! \kappa(\alpha)}$ for all internal wiggly~arcs~$\alpha$,
+\item the convex hull of the points~$\smash{\b{p}(T) \eqdef \!\! \displaystyle\sum\limits_{\alpha \in T} \!\kappa(\alpha) \, \b{c}(\alpha, T)}$ for all wiggly pseudotriangulations~$T$.
+\end{compactitem}
 \end{theorem}
-
-\begin{proof}
-By \cref{prop:characterizationPolytopalFan,lem:linearDependences,lem:wallCrossingInequalities}, the wiggly fan is indeed the normal fan of the polytope~$\wigglyhedron_n$ defined by the inequalities~$\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$.
-For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\alpha' \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{def:cvectors}.
-Hence, $\b{p}(T)$ is indeed the point of~$\wigglyhedron_n$ corresponding to~$T$, which is located at the intersection of the hyperplanes~$\dotprod{\b{g}(\alpha)}{\b{x}} = \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$ in~$T$.
-\end{proof}
-
-In fact, the wigglyhedron even recovers the wiggly lattice of \cref{subsec:wigglyPermutations}.
 
@@
 
-\begin{proof}
-Consider an increasing flip~$T \to T'$ between two wiggly pseudotriangulations~$T$ and~$T'$ with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-Denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$ in the corner labeling of~$T$ described in \cref{def:bijection1}, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-We have~$u < v$ because the flip~$T \to T'$ is increasing, so that~$\bar u \le \bar v$.
-
-Observe now that~${\b{p}(T') - \b{p}(T)}$ is orthogonal to the $(2n-2)$-dimensional cone of the wiggly fan generated by the $\b{g}$-vectors of the wiggly arcs in~$T \cap T'$, and points from the side containing~$\b{g}(\alpha)$ to the side containing~$\b{g}(\alpha')$.
-Hence, $\b{p}(T') - \b{p}(T)$ is a positive multiple of~$-\b{c}(\alpha, T)$.
-From \cref{def:cvectors}, we observe that
-\begin{itemize}
-\item $\dotprod{\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} = 1/2$ if~$i = \bar u \ne \bar v$, $-1/2$ if~$i = \bar v \ne \bar u$, and $0$ otherwise,
-\item $|\dotprod{\b{c}(\alpha, T)}{\b{e}_j}| \le 1/2$ for all~$j \in [2n]$.
-\end{itemize}
-We now distinguish two situations.
-If~$\bar u \ne \bar v$, then
-\[
-\dotprod{-\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} \ge 2n(\bar v - \bar u) - n > 0.
-\]
-If~$\bar u = \bar v$, then~$u = 2k-1$ and~$v = 2k$ for some~$k \in [n]$, and we have
-\[
-\dotprod{\b{c}(\alpha, T)}{\b{\omega}} = \!\!
-\sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \!\!
-\sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} = \frac{2k}{2}-\frac{2k-1}{2} = 1/2 > 0.
-\]
-We conclude in both cases that~$\dotprod{\b{c}(\alpha, T)}{\b{\omega}} > 0$, so that we recover the increasing flip graph by orienting the graph of the wigglyhedron~$\wigglyhedron_n$ in direction~$\b{\omega}$.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyhedronSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define isometries of the wigglyhedron~$\wigglyhedron_n$.
-\end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Further topics}
-\label{sec:furtherTopics}
-
-In this section, we explore two further topics on the wigglyhedron.
-We first observe that any (type~$A$) Cambrian associahedron~\cite{Reading-CambrianLattices,HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$ (\cref{subsec:CambrianConsiderations}).
-We then raise the question to extend our construction to wiggly complexes of arbitrary planar point sets (\cref{subsec:planarPointSets}).
-
-%%%%%%%%%%%%
-
-\subsection{Cambrian considerations}
-\label{subsec:CambrianConsiderations}
-
-In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
-We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice of \cref{sec:combinatorics} and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron of \cref{sec:geometry}.
+\newpage
+\section{Cambrian considerations}
+\label{sec:CambrianConsiderations}
+
+In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 = \delta_{n+1} = 0$.
+We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
+and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
 \cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.
 
-\begin{figure}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian1}}
-\vspace{-.3cm}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian2}}
-\vspace{-.5cm}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian3}}
-\caption{Cambrian lattices as intervals of wiggly lattices.}
+\begin{figure}[b]
+%\centerline{\includegraphics[scale=1]{wigglyCambrian1}}
+%\vspace{-.3cm}
+%\centerline{\includegraphics[scale=1.1]{wigglyCambrian2}}
+%\vspace{-.5cm}
+\centerline{\begin{overpic}[scale=.87]{wigglyCambrian3} \put(44,2){$\delta = {+}{+}{-}{-}$}\end{overpic}}
+\caption{The $\delta$-Cambrian lattice (left) is an interval of the wiggly lattice~$\wigglyLattice_4$~(right).}
 \label{fig:wigglyCambrian}
@@
 \label{def:CambrianTriangulations}
-The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point with abscissa~$i$ and with ordinate of the same sign as~$\delta_i$  for all~$0 \le i \le n+1$.
+The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point at abscissa~$i$ and ordinate of the same sign as~$\delta_i$  for~$0 \!\le\! i \!\le\! n+1$.
 A \defn{$\delta$-triangulation} is a triangulation of the $\delta$-gon.
-The \defn{$\delta$-triangulation lattice} is the transitive closure of the slope increasing flip graph on $\delta$-triangulations.
+The \defn{$\delta$-triangulation lattice} is the transitive closure of slope increasing flips on $\delta$-triangulations.
 %If~$T$ and~$T'$ are two $\delta$-triangulations with~$T \ssm \{d\} = T' \ssm \{d'\}$, then the flip from~$T$ to~$T'$ is \defn{increasing} if the slope of~$d$ is smaller than the slope of~$d'$.
@@
 \label{def:CambrianPermutations}
-A \defn{$\delta$-permutation} is a permutation of~$[n]$ which avoids~$\cdots ik \cdots j \cdots$ with~$i < j < k$ and~$\delta_j = -$, and~$\cdots j \cdots ki \cdots$ with~$i < j < k$ and~$\delta_j = +$.
+A \defn{$\delta$-permutation} is a permutation of~$[n]$ avoiding $\cdots ik \cdots j \cdots$ if~$\delta_j = -$, and~$\cdots j \cdots ki \cdots$ if~$\delta_j = +$ for~$i < j < k$.
 The \defn{$\delta$-permutation lattice} is the sublattice of the weak order induced by $\delta$-permutations.
@@
 \label{def:CambrianWigglyPseudotriangulations}
-The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j = {+}$ and~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j = {-}$.
+The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j = {-}$ and~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j = {+}$.
 A \defn{$\delta$-wiggly pseudotriangulation} is a wiggly pseudotriangulation containing all $\delta$-wiggly arcs.
@@
 \label{def:CambrianWigglyPermutations}
-A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ such that
+A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ with
 % for all~$j \in [n]$, we have~ and~$\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$i \in [2j-2]$.
@@
 %\end{itemize}
-\[
-\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
-\qquad\text{and}\qquad
-\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)
-\]
+$\smash{\sigma^{-1}_{2j} \!\le\! \sigma^{-1}_{i}}$ if $\delta_j = {-}$, and $\smash{\sigma^{-1}_{i} \le \sigma^{-1}_{2j-1}}$ if $\delta_j = {+}$
 %$\delta_j > 0 \implies \sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ and~$\delta_j < 0 \implies \sigma^{-1}(i) \ge \sigma^{-1}(2j)$
 for all~$1 \le i \le 2j \le 2n$.
-The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly permutation lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
-\end{definition}
-
-\begin{remark}
-We had to make a choice in \cref{def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations}.
-For~$\delta_j = {+}$, we could replace ``$(0, j, {[1,j[}, \varnothing)$'' by~``$(j, n+1, {]j,n]}, \varnothing)$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
-Independently, for~$\delta_j = {-}$, we could replace ``$(0, j, \varnothing, {[1,j[})$'' by~``$(j, n+1, \varnothing, {]j,n]})$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(2j) \le \sigma^{-1}(i)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(2j-1) \le \sigma^{-1}(i)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
-\cref{prop:CambrianLattice,prop:CambrianFan} would still hold.
-\end{remark}
-
-\begin{remark}
-\label{rem:CambrianSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries,rem:wigglyhedronSymmetries}, note that the vertical and horizontal symmetries send $\delta \eqdef \delta_1 \dots \delta_n$ to~$\delta_n \cdots \delta_1$ and $(-\delta_1) \cdots (-\delta_n)$ respectively.
-\end{remark}
+The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
+\end{definition}
 
@@
 \label{prop:CambrianLattice}
-For any signature~$\delta \in \{+,-\}^n$, the $\delta$-triangulation lattice, $\delta$-permutation lattice, \mbox{$\delta$-wiggly} pseudotriangulation lattice, and $\delta$-wiggly permutation lattice are all isomorphic, and are known as the \defn{$\delta$-Cambrian lattice}~\cite{Reading-CambrianLattices}.
-\end{proposition}
-
-\begin{proof}
-We only describe the following bijections
-\begin{center}
-\begin{tikzcd}[column sep=3cm]
-\text{$\delta$-triangulations} \arrow[d] & \text{$\delta$-permutations} \arrow[l] \\
-\text{$\delta$-wiggly pseudotriangulations} \arrow[r] & \text{$\delta$-wiggly permutations} \arrow[u]
-%\text{$\delta$-triangulations} \arrow[d, "\lambda"'] & \text{$\delta$-permutations} \arrow[l, "\zeta"'] \\
-%\text{$\delta$-wiggly pseudotriangulations} \arrow[r, "\mu"'] & \text{$\delta$-wiggly permutations} \arrow[u, "\nu"']
-\end{tikzcd}
-\end{center}
-illustrated in \cref{fig:wigglyCambrian}.
-We let the readers convince themselves that they are well-defined, that they compose to the identity, and that they preserve the flip structure.
-We also invite the reader to work out the explicit description of the 8 missing arrows.
-For~$I \subseteq [n]$, we set~$I^+ \eqdef \set{i \in I}{\delta_i = {+}}$ and~$I^- \eqdef \set{i \in I}{\delta_i = {-}}$.
-
-\para{From $\delta$-triangulations to $\delta$-wiggly pseudotriangulations}
-Replace each diagonal~$(i,j)$ of the $\delta$-gon by the wiggly arc~$(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
-
-\para{From $\delta$-wiggly pseudotriangulations to $\delta$-wiggly permutations}
-Specialization of \cref{def:bijection1}.
-
-\para{From $\delta$-wiggly permutations to $\delta$-permutations}
-For all~$j \in [n]$, erase~$2j-1$ and replace~$2j$ by~$j$ if~$\delta_j = {+}$, and erase~$2j$ and replace~$2j-1$ by~$j$ if~$\delta_j = {-}$.
-
-\para{From $\delta$-permutations to $\delta$-triangulations}
-Already described in~\cite{Reading-CambrianLattices}.
-Given a permutation~$\pi$, construct the union of the upper hulls of the point sets~$[n]^- \symdif \pi([j])$ for all~$j \in \{0, \dots, n\}$.
-\end{proof}
-
-Recall that the $\delta$-Cambrian lattice can be realized by the $\delta$-Cambrian fan~\cite{ReadingSpeyer} and the $\delta$-associahedron of~\cite{HohlwegLange}.
-Namely, to each diagonal~$(i,j)$ of the $\delta$-gon, we associate the subset~$X(\delta)$ of points of the $\delta$-gon distinct from~$0$ and~$n+1$, and located below the line~$(i,j)$, including~$i$ if and only if~$\delta_i = {+}$ and~$j$ if and only if~$\delta_j = {+}$.
-The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
-The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \ge \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
+The $\delta$-triangulation, $\delta$-permutation, \mbox{$\delta$-wiggly} pseudotriangulation, and $\delta$-wiggly permutation lattices are all isomorphic, and are known as the \defn{$\delta$-Cambrian~lattice}~\cite{Reading-CambrianLattices}.
+\end{proposition}
 
@@
 \label{prop:CambrianFan}
-The $\delta$-associahedron~$\Asso_\delta$ is normally equivalent to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly arcs.
-\end{proposition}
-
-\begin{proof}
-Following the proof of \cref{prop:CambrianLattice}, consider the map~$\zeta$ sending a diagonal~$(i,j)$ of the $\delta$-gon to the wiggly arc $(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
-Let~$a \eqdef (i,j)$ and~$a' \eqdef (i',j')$ be two crossing diagonals of the~$\delta$-gon.
-Then any $\delta$-triangulations~$T$ and~$T'$ with~$T \ssm \{a\} = T' \ssm \{a'\}$ contain the diagonals~$b \eqdef (i',j)$ and~$b' \eqdef (i,j')$ of the $\delta$-gon, and~$\b{g}(a) + \b{g}(a') = \b{g}(b) + \b{g}(b')$.
-Moreover, if~$\alpha \eqdef \zeta(a)$, $\alpha' \eqdef \zeta(a')$, $\beta \eqdef \zeta(b)$ and~$\beta' \eqdef \zeta(b')$, then~$\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')$.
-We thus conclude that $\zeta$ preserves the linear dependences among $\b{g}$-vectors.
-Hence, there is a linear map~$Z : \HH_n \to \HH_{2n}$ such that~$Z \big( \b{g}(d) \big) = \b{g} \big( \zeta(d) \big)$ for all diagonals~$d$ of the $\delta$-gon.
-This map is a normal equivalence from the $\delta$-associahedron~$\Asso_\delta$ to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly~arcs.
-\end{proof}
-
-%\vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
-
-\begin{remark}
-In their work on polytopal realizations of $\b{g}$-vector fans of finite type cluster algebras~\cite{HohlwegPilaudStella}, C.~Hohlweg, V.~Pilaud and S.~Stella already constructed a \defn{universal associahedron}~$\polytope{U}_n$ which somehow contains all Cambrian fans (actually all $\b{g}$-vector fans from any initial cluster seed).
-More precisely, the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$  appears as a section of the normal fan of the universal associahedron~$\polytope{U}_n$, which is a $(n^2+n-4)/2$-dimensional polytope.
-In contrast, \cref{prop:CambrianFan} states that the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$ appears as a link of the normal fan of the wigglyhedron~$\wigglyhedron_n$, which is a $(2n-1)$-dimensional polytope.
-There seem to be no connection between these two universal polytopes.
-However, this certainly raises the question to construct analogues of the wigglyhedron for all finite Coxeter groups.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly pseudotriangulations of planar point sets}
-\label{subsec:planarPointSets}
-
-We now consider \cref{thm:wigglyhedron,conj:Hamiltonian} for wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).
+The $\delta$-associahedron~$\Asso_\delta$ of~\cite{HohlwegLange} is normally equivalent to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly arcs.
+\end{proposition}
+
+\newpage
+\section{Wiggly pseudotriangulations of planar point sets}
+\label{sec:planarPointSets}
+
+We now present a conjecture on wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).
 
@@
 Two wiggly arcs~$(p,q,R,S)$ and~$(p',q',R',S')$ are \defn{crossing} if 
-\begin{itemize}
+\begin{compactitem}
 \item either the segments~$[p,q]$ and~$[p',q']$ cross, 
-\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$,
-\end{itemize}
+\item or~$(R \!\cap\! S') \cup (\{p,q\} \!\cap\! S') \cup (R \!\cap\! \{p',q'\}) \ne \varnothing \ne (R' \!\cap\! S) \cup (\{p',q'\} \!\cap\! S) \cup (R' \!\cap\! \{p,q\})$.
+\end{compactitem}
 A set~$X$ of wiggly arcs is \defn{pointed} if for any~$p \in P$, the wiggly arcs of~$X$ with an endpoint at~$p$ generate a pointed cone.
@@
 A \defn{wiggly pseudotriangulation} of~$P$ is a facet of~$\wigglyComplex_P$.
-The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
+%The \defn{wiggly flip graph}~$\wigglyFlipGraph_P$ is the adjacency graph of the facets of~$\wigglyComplex_P$.
 %Note that, by construction, $\wigglyFlipGraph_P$ is regular.
-See \cref{fig:wigglyComplexSquarre} for an illustration.
+See \cref{fig:wigglyComplexSquarre}.
 %
 \begin{figure}[!h]
-\centerline{\includegraphics[scale=1]{wigglyComplexSquare}}
-\caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}
+\centerline{\includegraphics[scale=.95]{wigglyComplexSquare}}
+\caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of~$P$.}
 \label{fig:wigglyComplexSquarre}
@@
 
-Note that \cref{def:wigglyComplexPointSet} recovers two specific situations, namely
-\begin{itemize}
-\item \cref{def:wigglyComplex,def:wigglyFlipGraph} in the case of aligned points, and
-\item the pseudodissection complex of~$P$ and pseudotriangulation flip graph of~$P$ in the case of points~$P$ in general position.
-We refer to the original article of M.~Pocchiola and G.~Vegter~\cite{PocchiolaVegter} and to the nice survey of G.~Rote, F.~Santos and I.~Streinu~\cite{RoteSantosStreinu-pseudotriangulations}.
-\end{itemize}
-
-Observe that it is not even clear from \cref{def:wigglyComplexPointSet} that the wiggly complex~$\wigglyComplex_P$ is a pure pseudomanifold (hence that the wiggly flip graph~$\wigglyFlipGraph_P$ is well-defined).
-However, we make the following ambitious conjecture.
+%Observe that it is not even clear from \cref{def:wigglyComplexPointSet} that the wiggly complex~$\wigglyComplex_P$ is a pure pseudomanifold (hence that the wiggly flip graph~$\wigglyFlipGraph_P$ is well-defined).
+%However, we make the following ambitious conjecture.
 
@@
 
-In \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
-This raises in particular the following question.
-
-\begin{question}
-Can the construction of \cref{thm:wigglyhedron} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (\aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
-\end{question}
-
-Using the duality between lines in the plane and points in the M\"obius strip, the pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations} were interpreted in~\cite{PilaudPocchiola} as pseudoline arrangements on sorting networks.
-It is natural to look for the analogue of this interpretation in the wiggly setting.
-
-\begin{question}
-Is there a dual interpretation of wiggly pseudotriangulations as some sort of pseudoline arrangements? 
-\end{question}
-
-This dual interpretation enables \cite{PilaudPocchiola} to consider the pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations} and the multitriangulations of~\cite{PilaudSantos-multitriangulations} under the same roof, and to define multi-pseudo-triangulations.
-The extension to the wiggly case is a natural question.
-
-\begin{question}
-Is there a multi wiggly complex?
-\end{question}
-
-Moreover, pseudoline arrangements on sorting networks can also be interpreted as (type~$A$) subword complexes of~\cite{KnutsonMiller-subwordComplex}, which in turn extend to arbitrary finite Coxeter group.
-See \cite{Stump, CeballosLabbeStump} for the study of subword complexes corresponding to cluster complexes and multi-cluster complexes.
-
-\begin{question}
-Can the wiggly complex be extended to arbitrary finite Coxeter groups?
-\end{question}
-
-%\begin{question}
-%\begin{itemize}
-%\item Is there a dual interpretation of wiggly pseudotriangulations as some sort of pseudoline arrangements? 
-%\item Is there a multi wiggly complex?
-%\item Can this interpretation be extended to other finite Coxeter groups?
-%\end{itemize}
-%\end{question}
-
-Finally, it is natural to consider the extension of \cref{conj:Hamiltonian}.
-
-\begin{question}
-\label{qu:Hamiltonian}
-Is the wiggly flip graph~$\wigglyFlipGraph_P$ Hamiltonian for any point set~$P$ in the plane?
-\end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Categorical interpretation of wiggly pseudotriangulations}
-\label{sec:categoricalInterpretation}
-
-The aim of this section is to explain a categorical interpretation of wiggly arcs.
-We first present a particular triangulated category (\cref{subsec:category}), and recall results of Khovanov--Seidel~\cite{kho.sei:02} (\cref{subsec:KSCurveModel}) that interpret the objects of this category as wiggly arcs, such that intersections between wiggly arcs correspond to morphisms in this category.
-We then explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of objects (\cref{subsec:cohomologyFiltrations}).
-We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible} (\cref{subsec:categoricalCompatibility}).
-
-%%%%%%%%%%%%
-
-\subsection{A triangulated category associated to a quiver}
-\label{subsec:category}
-
-We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-That is, a subcategory of the bounded derived category of finitely generated \(A_m\)-modules.
-The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
-Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
-Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
-A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).
-
-\begin{figure}
-	\centering
-	\begin{tikzcd}
-		1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
-	\end{tikzcd}
-	\caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
-	\label{fig:am-quiver}
-\end{figure}
-
-\begin{definition}
-The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
-\end{definition}
-
-\begin{remark}
-The definition of the zigzag algebra as used here originally appeared in~\cite[Sect.~3]{hue.kho:01}.
-This is the ``un-signed'' zigzag algebra.
-It is technically better to use a ``signed'' zigzag algebra, and the comparison between the two is discussed in~\cite[Rem.~6.6]{bap.deo.lic:20}.
-As the two versions are isomorphic in our example, we ignore this technicality and use the easier definition.
-\end{remark}
-
-Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
-For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
-In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).
-
-\begin{definition}
-The category \(\mathcal{C}_m\) is defined to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
-\end{definition}
-
-For further discussion on the construction, see \eg~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
-The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
-For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{g,h}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of internal degree \(g\) and homological degree \(h\).
-In other words, we have
-\[
-\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).
-\]
-Furthermore, for any integers \(a\) and \(b\), we have
-\[
-\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).
-\]
-
-\begin{remark}
-\label{rem:generating-morphisms}
-The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
-\end{remark}
-
-We now describe the \(t\)-structure induced by the full subcategory of \defn{linear complexes} of \(\mathcal{C}_m\).
-A variant of this construction is also described in~\cite[Sect.~2.5]{lic.que:21}.
-It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\) as a bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
-More precisely, we can write
-\[
-P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],
-\]
-where \(g\) is the internal grading shift, \(h\) is the homological grading shift, and 
-each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
-Set \(P^h\) to be the direct sum of all summands that have homological grading shift \(h\).
-That is, in the notation above, we have
-\[
-P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].
-\]
-
-\begin{warning}
-  By convention, if \(M_i\) is an \(A_m\)-module, then the object \(M_i[h]\) is placed in homological degree \(-h\).
-  Since the differential \(d\) raises the homological degree by one, it lowers the homological shift by one.
-  That is, we have
-  \[d \colon M_i\langle g \rangle[h] \to \bigoplus_{g',i'} M_{i'}\langle g' \rangle[h-1].\]
-  In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
-\end{warning}
-
-\begin{definition}
-\label{def:linear-complex}
-Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
-\[
-P^{\bullet} = \bigoplus M_i\langle g \rangle[h]
-\]
-together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
-We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some~\(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
-We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
-\end{definition}
-
-For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq -N\).
-For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq -N\).
-
-We refer the reader to \eg~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
-The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
-
-\begin{proposition}
-The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
-\end{proposition}
-
-We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
-Set \(\mathcal{A}_m \eqdef \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
-It follows that \(\mathcal{A}_m\) is abelian.
-
-Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}
-
-\begin{defprop}
-\label{defprop:cohomology}
-Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart~\(\mathcal{A} \eqdef \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
-For each integer \(i\), we have the \(i\)th truncation functors
-\[
-\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i} \quad\text{and}\quad \tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},
-\]
-which are right and left adjoint respectively to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
-The \(i\)th \defn{cohomology functor} is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
-It is canonically isomorphic to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
-\end{defprop}
-
-The next statement, easy to check from the definitions, is mentioned \eg in~\cite[Sect.~3.3]{bayer2011tour}.
-
-\begin{defprop}
-\label{defprop:cohomology-filtration}
-Let \(\mathcal{C}\) be any triangulated category, and \(\mathcal{A} \subset \mathcal{C}\) the heart of a bounded \(t\)-structure on \(\mathcal{C}\).
-Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(\ell\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^\ell(X)\) are non-zero.
-Then \(X\) has a unique \defn{cohomology filtration}, which is the unique filtration of the form
-\[
-\begin{tikzcd}[column sep=0.1cm]
-	0  \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k+1} \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-	& H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X)[-k] \arrow[dashed]{ul}{+1}
-\end{tikzcd}
-\]  
-\end{defprop}
-
-%%%%%%%%%%%%
-
-\subsection{The Khovanov--Seidel curve model}
-\label{subsec:KSCurveModel}
-
-\afterpage{
-\begin{figure}
-\centerline{
-	\begin{tabular}{c@{\qquad}c@{\qquad}c}
-		Spherical objects in bounded 
-		&
-		&
-		\\
-		homotopy category of graded projective 
-		&
-		$\smash{\xrightarrow[\quad\text{combinatorial model}\quad]{}}$
-		&
-		Curves
-		\\
-		modules over the zigzag algebra
-		&
-		&
-                \\
-		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
-			\&           \& P_3 \langle -1 \rangle\arrow{dr} \& \\
-			\&           \&                      \& P_2\\
-			P_1\langle -5 \rangle\arrow{r}    \& P_1\langle -3 \rangle\arrow{r}   \& P_1 \langle -1 \rangle\arrow{ur} \& 
-		\end{tikzcd}
-		&
-		&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve1}}
-		\\[.5cm]
-		{\scriptsize cohomology} $\Bigg\downarrow$ {\scriptsize filtration}
-		&
-		&
-		$\Bigg\downarrow$ {\scriptsize cut}
-		\\[.5cm]
-		Heart of the standard $t$-structure
-		&
-		$\xrightarrow[\quad\text{combinatorial model}\quad]{}$
-		&
-		Wiggly arcs
-		\\
-		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
-			P_1\langle -1 \rangle \arrow{dr}\& \\
-			\& P_2 \\
-			P_3 \langle -1 \rangle \arrow{ur}
-		\end{tikzcd}
-		&
-          	&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve2}}
-		\\
-		\(P_1\)
-		&
-		&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve3}	}
-	\end{tabular}
-}
-\caption{An illustration of the Khovanov--Seidel curve model and \cref{prop:cohomology-pieces}.}
-\label{fig:curveModel}
-\end{figure}
-}
-
-In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
-In fact, the procedure works on more general curves as well (namely, those that are not necessarily \(x\)-monotone).
-
-Consider \(n+2\) points arranged in a straight horizontal line, and labelled \(0,1, \ldots, n+1\) as in~\cref{sec:combinatorics}.
-In addition to the wiggly arcs, consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-For convenience, we refer to such an isotopy class as a \defn{curve}.
-
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to an overall grading and homological shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
-We illustrate this correspondence and~\cref{prop:cohomology-pieces} in~\cref{fig:curveModel}.
-In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
-Moreover, the minimal intersection number between any pair of curves is the number of morphisms between the associated objects~\cite[Prop.~4.9]{kho.sei:02}.
-In fact, the proposition in~\cite{kho.sei:02} is a stronger result: by considering \emph{bigraded curves}, we obtain \emph{bigraded intersection numbers} between the two associated objects.
-
-Any object \(X\) obtained via the Khovanov--Seidel correspondence is~\defn{spherical}; that is, \(\Hom^{g,0}(X,X)\) is \(k\) when \(g = 0,2\), and \(\Hom^{g,h}(X,X) = 0\) in all other cases.
-A spherical object \(X\) is necessarily indecomposable as \(\Hom^{0,0}(X,X) = k\).
-
-\begin{proposition}
-\label{prop:cohomology-pieces}
-Let \(\alpha\) be any curve, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
-Recall that for any integer \(j\), the cohomology object \(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
-\begin{enumerate}
-\item The object \(X\) is a (spherical) object of \(\mathcal{A}_m\) up to shift if and only if \(\alpha\) is a wiggly arc.
-In this case, \(H^j(X) \neq 0\) for exactly one \(j\), such that \(X \cong H^j(X)[-j]\).
-\item If \(\alpha\) is a general curve, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) curve \(\alpha\).
-  Recall from~\cite{kho.sei:02} that \(X\) is spherical, and hence indecomposable.
-  Let us now analyse the indecomposable summands of its cohomology objects.
-
-  We recall that the procedure to build up \(X\) from \(\alpha\) explicitly describes the differential.
-  We analyse the possible non-zero components of the differential, checking how each interacts with the level.
-  The only two possibilities are as follows:
-  \begin{enumerate}
-  \item a map \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\), namely multiplication on the right by the path \((i,i\pm1)\), which does not change the level; or
-  \item a map \(P_i\langle g \rangle[h] \to P_{i}\langle g+2 \rangle[h-1]\), namely multiplication on the right by the ``loop'' path \((i,i\pm1, i)\), which raises the level by one.
-  \end{enumerate}
-  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the \((i-1)\)th point.
-  The second possibility appears each time the curve makes a U-turn around the right of \(i\)th or the left of the \((i-1)\)th point.
-
-  Computing the \(j\)th cohomology \(H^j(X)\) simply amounts to truncating the complex to level \(j\).
-  Explicitly, the truncation is a new chain complex in which we only keep the terms of \(X\) that have level \(j\), together with all maps between them, and forget all the other terms.
-  From the calculation above, we see that the resulting complex only has components in its differential of the first type, namely \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\) where \(g + h = j\).
-  We kill all components of the second type (the ``loop'' components).
-  The resulting chain complex breaks up into indecomposable summands, each of which is an object of~\(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
-
-  The object \(X\) is in the heart up to shift if and only if it is concentrated in a single level \(j\).
-  Truncating to level \(j\) as described above, we do not delete any of the terms of \(X\).
-  This can happen if and only if the differential of \(X\) contains no ``loop'' components,
-  which appear in the complex if and only if \(\alpha\) makes a U-turn around one of the \(n+2\) points.
-  Thus \(X\) is in the heart up to shift if and only if \(\alpha\) is  \(x\)-monotone.
-  This proves the first part of the proposition.
-
-  More generally, consider the indecomposable pieces of the level-\(j\) truncations of \(X\) for various~\(j\), up to shift.
-  As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve~\(\alpha\) into \(x\)-monotone portions.
-  More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by making a U-turn around a point \(p_1\).
-  In this case, we take the portion of \(\alpha\) between \(p_0\) and \(p_1\), calling it \(\alpha_1\), and setting its endpoints to be \(p_0\) and \(p_1\) respectively.
-  Note that \(p_0 \neq p_1\) because \(\alpha\) is \(x\)-monotone between \(p_0\) and \(p_1\).
-  We continue with the remainder of \(\alpha\) starting at \(p_1\), greedily taking the maximal \(x\)-monotone portion each time, to obtain pieces \(\alpha_1,\alpha_2, \ldots, \alpha_k\), which are all wiggly arcs.
-  These wiggly arcs correspond to complexes \(X_1, \ldots, X_k\), which are spherical objects of \(\mathcal{A}_m\), up to shift.
-  It is clear from the construction of the associated complex that these objects, up to shift, are exactly the indecomposable pieces of the cohomology truncations \(H^j(X)\) for various \(j\).
-  This argument proves the second part of the proposition.
-\end{proof}
-
-%%%%%%%%%%%%
-
-\subsection{Cohomology filtrations of spherical objects}
-\label{subsec:cohomologyFiltrations}
-
-In this section we explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of spherical objects of \(\mathcal{C}_m\).
-
-For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
-However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
-
-\begin{proposition}
-\label{prop:hn-filtration}
-  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
-  Consider its cohomology filtration
-  \[
-    \begin{tikzcd}[column sep=0.3cm]
-      0 \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-      & H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} & \cdots & H^k(X)[-k] \arrow[dashed]{ul}{+1}
-    \end{tikzcd}
-  \]
-  Consider the set of all possible indecomposable summands of the cohomology objects \(\{H^j(X)\}\) taken without multiplicity.
-  Let \(T\) be corresponding set of wiggly arcs, as explained in~\cref{prop:cohomology-pieces}.~Then
-  \begin{enumerate}
-  \item 
-    \(T\) is a subset of a wiggly pseudotriangulation,
-  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
-  \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of curves on the disk with marked points.
-  Let \(X_1, \ldots, X_k\) be the objects in \(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
-  Let \(\beta = (i,j,A,B)\) and \(\beta' = (i',j', A',B')\) be two distinct wiggly arcs among \(\{\alpha_1, \ldots,\alpha_k\}\).
-  We check that \(\beta\) and \(\beta'\) are compatible in the sense of~\cref{def:compatible}.
-
-  Recall that \(\beta\) and \(\beta'\) are two pieces of the curve \(\alpha\).
-  Therefore \(\beta\) and \(\beta'\) cannot cross, because~\(\alpha\) does not cross itself.
-  Suppose that \(\beta\) and \(\beta'\) are non pointed, and without loss of generality, suppose that \(i' = j\).
-  This means that the piece \(\beta\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the right of the point \(i'\).
-  Moreover, if \(i'\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(i'\) lies to the left of \(i'\).
-
-  Similarly, the piece \(\beta'\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because~\(\alpha\) loops around the left of the point \(j\).
-  Moreover, if \(j\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(j\) lies to the right of \(j\).
-
-  We have four possible combinations:
-  \begin{enumerate}
-  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\);
-  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
-  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\); 
-  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
-  \end{enumerate}
-  It is clear that none of these possibilities can occur within the curve \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
-  Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.
-
-  Now suppose for contradiction that \(T\) contains both external edges.
-  Then some portion of \(\alpha\) curves around each of the extreme endpoints \(0\) and \(n+1\).
-  Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
-  These must then connect to each other, resulting in \(\alpha\) having a separate closed component that winds around the outside of the \(n+2\) points.
-  This is not possible because \(\alpha\) is a connected curve with two endpoints.
-  Therefore \(T\) cannot contain both external edges.
-\end{proof}
-
-\begin{remark}
-Note that in \cref{def:wigglyComplex}, we adopted the convention that the faces of the wiggly complex contain none of the two external wiggly arcs.
-In contrast, the wiggly dissections of \cref{prop:hn-filtration} contain at most one of the two external wiggly arcs.
-Combinatorially, this is just the Cartesian product of the wiggly complex with an edge.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Categorical constraints on compatibility of curves}
-\label{subsec:categoricalCompatibility}
-
-In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
-As such, this section is somewhat dual to the previous section: the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
-
-Recall that two wiggly arcs \(\alpha\) and \(\alpha'\) are said to be compatible (as in~\cref{def:compatible}) if they are non-crossing and pointed.
-The incompatibility degree of \(\alpha\) and \(\alpha'\) (as in~\cref{def:incompatibilityDegree}) is \(1\) if \(\alpha\) and \(\alpha'\) are non pointed, and the number of crossings of \(\alpha\) and \(\alpha'\) otherwise.
-\begin{proposition}
-\label{prop:ext1}
-Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible if and only if \(\Ext^1(X, X') = 0\).
-  More generally, the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext^1(X,X')\).
-\end{proposition}
-
-\begin{proof}
-  The proof follows from a specialisation of the bigraded intersection number calculations that appear in Sections 3 and 4 of~\cite{kho.sei:02}.
-  The bigraded intersection number as defined in~\cite[Sect.~3d]{kho.sei:02} between the curves \(\alpha\) and \(\alpha'\) is a polynomial in the variables \(q_1^{\pm}\), \(q_2^{\pm}\).
-  It follows from~\cite[Prop.~4.9]{kho.sei:02} that this bigraded intersection number equals the Poincar{\'e} polynomial of the morphisms between \(X\) and \(X'\), namely the expression
-  \begin{equation}
-    \label{eq:bigraded-homs}
-  \sum_{s_1,s_2}\dim(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1]))q_1^{s_1}q_2^{s_2}.    
-\end{equation}
-However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
-So we have to modify the gradings when we construct the complexes.
-In particular, the table in~\cite[Lem.~3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lem.~4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
-
-With our path-length grading, note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes an object \(X\) of level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) of level \(s_1 - s_2\).
-  We can thus obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
-    The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
-
-It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
-Morphisms arising from other intersections do not contribute to \(\Ext^1\).
-This calculation proves the proposition.
-\end{proof}
-
-\begin{remark}
-  \cref{prop:ext1} is very similar to the condition of being compatible in a cluster-tilting object of a cluster category (see, \eg~\cite[Cor.~4.3]{bua.mar.rei.ea:06}) or in a $\tau$-tilting object (see, \eg~\cite{AdachiIyamaReiten}).
-  The condition in terms of crossings of curves already appears for some specializations (see, \eg~\cite{FominShapiroThurston, PaluPilaudPlamondon-surfaces}).
-  However, in \cref{prop:ext1}, it depends on shifting the objects~\(X\) and~\(X'\) so that they both lie in the standard heart, which is an auxiliary step that is not required in cluster-tilting and $\tau$-tilting theory.
-\end{remark}
-
-\begin{remark}
-  As stated,~\cref{prop:ext1} in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
-  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
-  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
-\end{remark}
-
-\pagebreak
-Recall from~\cref{rem:incompatibility-deg} that two wiggly arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
-Recall from~\cref{prop:uerp} the wiggly arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
-Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the wiggly arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
-Let us interpret this dependence categorically.
-
-Let \(X\), \(X'\), \(Y\) and~\(Y'\) be spherical objects in the standard heart that correspond to \(\alpha\), \(\alpha'\), \(\beta\) and~\(\beta'\) respectively.
-First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
-Next, let us understand~\(Y\) and \(Y'\) categorically.
-
-\begin{proposition}\label{prop:extensions}
-For \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\), \(Y\), \(Y'\) as just discussed,
-\begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
-  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0,\]
-\item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
-  \[0 \to X' \to (Y \oplus Y') \to X \to 0.\]
-\end{itemize}
-\end{proposition}
-
-\begin{proof}
-  The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
-  We do not reproduce the proof here, as the argument is contained in the proof of~\cite[Thm.~5.5]{tho:06}.
-  (See also~\cite[Fig.~4]{tho:06}.)
-\end{proof}
-Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(\b{g}\)-vectors in~\cref{lem:linearDependences}.
-More precisely, we have that
-\begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then
-  \([Y] = [X] + [X'] = [Y']\),
-  from which we see \([X] + [X'] = ([Y] + [Y'])/2\);
-\item if \(\alpha\) and \(\alpha'\) are crossing, then
-  \([X] + [X'] = [Y] + [Y'].\)
-\end{itemize}
-This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
-The \(\b{g}\)-vector of an object \(X\) corresponding to a wiggly arc \(\alpha\) can, of course, be reconstructed from \(\alpha\).
-However, at the moment we do not have a purely categorical construction of the \(\b{g}\)-vector of \(X\) that does not refer to \(\alpha\), and it would be interesting to find this.
-
-\begin{question}
-  Suppose we have a collection of spherical objects in the standard heart \(\mathcal{A}_m\) that satisfy the compatibility condition of~\cref{prop:ext1}.
-  That is, the \(\Ext^1\) between any pair of objects in this collection is zero.
-  \begin{enumerate}
-  \item Can we prove properties about a maximal such collection without reference to curves?
-  \item In particular, can we understand the combinatorics of maximal such collections without reference to curves?
-  \item Given a maximal compatible collection of objects, can we always find a larger spherical object such that the factors of the cohomology filtration of that object are precisely shifts of the objects in the given collection?
-  \end{enumerate}
-\end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-This work started during the \emph{Winterbraids XIII: School on low dimensional topology, braid groups and interactions}.
-We are grateful to the organizers Bérénice Delcroix-Oger, Peter Feller, Vincent Florens, Hoel Queffelec for this fruitful event.
-We thank Anand Deopurkar and Anthony M. Licata for many useful conversations and ideas.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-\addtocontents{toc}{ \vspace{.1cm} }
-\bibliographystyle{alpha}
-\bibliography{wigglyhedra}
-\label{sec:biblio}
+\cref{conj:polytopality} holds in two extreme situations: the wiggly complex~$\wigglyComplex_P$ is realized
+\begin{compactitem}
+\item by the wigglyhedron of~\cref{thm:wigglyhedron} when the point set~$P$ is alogned, and
+\item by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}, realizing the flip graph on the original pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, when the point set~$P$ is in general position.
+\end{compactitem}
+
+\newpage
+\section{Categorical representation theory}
+\label{sec:representationTheory}
+
+\newpage
+%% if you use biblatex then this generates the bibliography
+%% if you use some other method then remove this and do it your own way
+\printbibliography
 
 \end{document}
-
-% Local Variables:
-% TeX-command-extra-options: "-pvc"
-% End:

### 2024-10-11 draft/wigglyhedra.tex
start FPSAC

@@
 \label{rem:numberWigglyArcs}
-The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell)$.
+The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell) = 2^{n+2}-n-3$.
 \end{remark}
@@
 for all~$1 \le i \le 2j \le 2n$.
-The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly permutation lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
+The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
 \end{definition}
@@
 \item either the segments~$[p,q]$ and~$[p',q']$ cross, 
-\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$,
+\item or~$(R \cap S') \cup (\{p,q\} \cap S') \cup (R \cap \{p',q'\}) \ne \varnothing \ne (R' \cap S) \cup (\{p',q'\} \cap S) \cup (R' \cap \{p,q\})$.
 \end{itemize}

### 2024-10-11 exposeBerlin2410/exposeBerlin2410.tex
start FPSAC

@@
 \hspace{3.4cm} 
-\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
+\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter ('96)} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\  \end{tabular}
 \hspace{2cm} 
@@
 \hspace{3.4cm} 
-\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
+\begin{tabular}[t]{c} crossing-free pointed \\ \papier{Pocchiola--Vegter ('96)} \\[-.3cm] \papier{Rote--Santos--Streinu ('08)} \\ \\ pseudotriangles \end{tabular}
 \hspace{2cm} 
@@
 \begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
-\hspace{1.5cm} associahedron \hspace{2.6cm} pseudotriangulation polytope \hspace{1.2cm} multiassociahedron
+\hspace{1.5cm} associahedron \hspace{2.4cm} \begin{tabular}[t]{c}pseudotriangulation polytope \\  \papier{Rote--Santos--Streinu ('03)} \end{tabular} \hspace{1cm} multiassociahedron
 
@@
 
-\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}
-
-\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}
-
-\end{slide}
-
-%%%%%%%
-
-\multido{\n=0+1}{10}{%
-\begin{slide}{Duality}
-\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
-\vspace{-.5cm}\\
-\vspace*{-2cm}
-\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
-\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
-\end{slide}
-}
-
-%%%
+%\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}
+%
+%\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}
+%
+%\end{slide}
+%
+%%%%%%%%
+%
+%\multido{\n=0+1}{10}{%
+%\begin{slide}{Duality}
+%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
+%\vspace{-.5cm}\\
+%\vspace*{-2cm}
+%\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
+%\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+%\end{slide}
+%}
+%
+%%%%
 
@@
 \vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+
+\vspace{7.6cm}
+\papier{P.--Pocchiola ('12)}
+
+\vspace*{-3cm}
 \end{slide}
@@
 \vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
-\end{slide}
-
-%%%
-
-\multido{\n=0+1}{10}{%
-\begin{slide}{Duality}
-\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
-\vspace{-.5cm}\\
-\vspace*{-2cm}
-\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
-\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
-\end{slide}
-}
-
-%%%
+
+\vspace{7.6cm}
+\papier{P.--Pocchiola ('12)}
+
+\vspace*{-3cm}
+\end{slide}
+
+%%%%
+%
+%\multido{\n=0+1}{10}{%
+%\begin{slide}{Duality}
+%\hspace{1.6cm} triangulations \hspace{3.4cm} pseudotriangulations \hspace{2.5cm} multitriangulations\\
+%\vspace{-.5cm}\\
+%\vspace*{-2cm}
+%\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
+%\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
+%\end{slide}
+%}
+%
+%%%%
 
@@
 \vspace{.1cm}
-\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}}
+\theo{PROP}{The inclusion maximal wiggly pseudodissections are the pseudotriangulations, and contain $2n-1$ internal arcs and $n$ cells. \hfill \papier{Bapat--P. (24$^+$)}
+
+}
 
@@
 
-\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}}
+\theo{PROP}{Any wiggly pseudoquadrangle has exactly two wiggly diagonals, and they either cross or are non pointed. \hfill \papier{Bapat--P. (24$^+$)}
+
+}
 
@@
 \vspace{.5cm}
-\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}}
+\theo{PROP}{The wiggly flip graph $\wigglyFlipGraph_n$ is $(2n-1)$-regular and connected. \hfill \papier{Bapat--P. (24$^+$)}
+
+}
 
@@
 \hfill \papier{Bapat--P. (24$^+$)}
+
 }
@@
 \hfill \papier{Bapat--P.
-(24$^+$)}}
+(24$^+$)}
+
+}
 
@@
 (24$^+$)}
+
 }
@@
 
-\hfill \color{gray}{[NB: wiggly permutations do not form a zigzag language, right?]}
+\hfill \color{gray}{[NB: wiggly permutations do not form a zigzag language]}
 }

### 2024-10-11 programmation/wigglyPseudotriangulations.py

@@ -7,12 +7,13 @@ from functools import cmp_to_key
 def number_arcs(n):
     r"""
     Return the number of arcs on n+2 points.
+    This is add(2**j * (n+1-j) for j in range(n+1)) = 2**(n+2)-n-3
 
     EXAMPLES::
         sage: [number_arcs(n) for n in range(10)]
         [1, 4, 11, 26, 57, 120, 247, 502, 1013, 2036]
     """
-    return add(2**j * (n+1-j) for j in range(n+1))
+    return 2**(n+2)-n-3
 
 def number_relevant_arcs(n):
     r"""
@@ -653,6 +654,53 @@ def cambrian_wiggly_permutations_sublattice(signature):
     f = cambrian_face(signature)
     return wiggly_permutations_lattice(n).sublattice([wpt2wp(list(f) + list(g)) for g in cambrian_complex(signature).facets()])
 
+### OTHER ASSOCIAHEDRA
+
+def multigraph(d,n):
+    r"""
+    Return the multigraph corresponding to a wiggly dissection d.
+    """
+    G = Graph(n+2, multiedges=True)
+    G.add_edges([[a[0], a[1]] for a in d] + [[0,n+1],[0,n+1]])
+    return G
+
+@cached_function
+def wiggly_trees(n):
+    r"""
+    Return the wiggly dissections whose multigraph is a tree.
+
+    EXAMPLES::
+        sage: wiggly_trees(2)
+        [((1, 2, (), ()), (1, 3, (2,), ())),
+         ((0, 2, (1,), ()), (0, 1, (), ())),
+         ((1, 2, (), ()), (0, 2, (1,), ())),
+         ((2, 3, (), ()), (1, 3, (), (2,))),
+         ((0, 2, (1,), ()), (1, 3, (), (2,))),
+         ((1, 2, (), ()), (1, 3, (), (2,))),
+         ((2, 3, (), ()), (1, 3, (2,), ())),
+         ((2, 3, (), ()), (0, 1, (), ())),
+         ((0, 2, (), (1,)), (1, 3, (2,), ())),
+         ((0, 2, (), (1,)), (0, 1, (), ())),
+         ((0, 2, (), (1,)), (1, 2, (), ()))]
+    """
+    return [d for d in wiggly_complex(n).faces()[n-1] if multigraph(d,n).is_connected()]
+
+@cached_function
+def wiggly_associahedron(wt, n):
+    r"""
[…]

### 2024-10-12 FPSAC25/wigglyhedraFPSAC.tex
minor changes

@@
 %% put your French abstract here, or comment this out if you don't have one
-\resume{Motivés par la théorie catégorique des représentations, nous étudions le slalomèdre.
-Son complexe de bord encode les dissections slalomantes (ensembles deux-à-deux pointés et sans croisement d'arcs slalomant autour de $n+2$ points sur une ligne).
-Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations slalomantes (permutations de $[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
+\resume{Motivés par la théorie catégorique des représentations, nous étudions \linebreak l'onduloèdre.
+Son complexe de bord encode les dissections ondulantes (ensembles d'arcs ondulant autour de $n+2$ points sur une ligne, deux-à-deux pointés et sans croisement).
+Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations ondulantes (permutations de $[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
 Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.}
@@
 We then define the wigglyhedron (\cref{sec:wigglyhedron}), a polytope whose normal fan is the wiggly fan and whose support function is given by the incompatibility numbers of wiggly arcs.
-Its graph can be oriented to obtain the Hasse diagram of the wiggly lattice, and it contains copies of all type~$A_n$ Cambrian lattice as faces (\cref{sec:CambrianConsiderations}).
+Its graph can be oriented to obtain the Hasse diagram of the wiggly lattice, and it contains copies of all type~$A_n$ Cambrian lattices~\cite{Reading-CambrianLattices} as faces (\cref{sec:CambrianConsiderations}).
 To conclude, we conjecture that the wiggly complex of any planar point set is polytopal (\cref{sec:planarPointSets}), and we explore representation theoretic aspects of the wiggly complex (\cref{sec:representationTheory}).
@@
 \label{def:wigglyComplex}
-The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
+The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of subsets of pairwise compatible internal wiggly arcs.
 %In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.

### 2024-10-14 FPSAC25/wigglyhedraFPSAC.tex
minor changes
minor change

@@
 Its boundary complex encodes wiggly dissections (sets of pairwise pointed and non-crossing arcs wiggling around $n+2$ points on a line).
-Its graph is the Hasse diagram of the sublattice of the weak order induced by wiggly permutations (permutations of $[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$).
+Its graph is the Hasse diagram of the sublattice of the weak order induced by wiggly permutations (permutations of~$[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$).
 It contains copies of all type~$A_n$ Cambrian lattices and Cambrian fans.}
@@
 Son complexe de bord encode les dissections ondulantes (ensembles d'arcs ondulant autour de $n+2$ points sur une ligne, deux-à-deux pointés et sans croisement).
-Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations ondulantes (permutations de $[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
+Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations ondulantes (permutations de~$[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
 Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.}
@@
 It is a $(2n-1)$-dimensional manifold whose maximal faces are wiggly pseudotriangulations of a disc.
-We show (\cref{sec:bijection}) that the flip graph on wiggly pseudotriangulations is isomorphic to the cover graph of the sublattice of the weak order induced by wiggly permutations (\cref{sec:wigglyPermutations}), the permutations of $[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$.
+We show (\cref{sec:bijection}) that the flip graph on wiggly pseudotriangulations is isomorphic to the cover graph of the sublattice of the weak order induced by wiggly permutations (\cref{sec:wigglyPermutations}), the permutations of~$[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$.
 Inspired by similar constructions for finite type cluster complexes~\cite{HohlwegLangeThomas,HohlwegPilaudStella}, and for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}, we then provide geometric realizations of the wiggly complex.
@@
 \begin{alignat*}{3}
-i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i} \quad &
-A & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])} \\
-j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1} \;\;\; &
-B & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing}
+i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i}\!, \quad &
+A & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])}\!, \\
+j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1}\!, \;\, &
+B & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing} \!.
 \end{alignat*}

### 2024-10-17 FPSAC25/wigglyhedraFPSAC.tex
improve FPSAC

@@
 We start by defining the wiggly complex, the clique complex of a compatibility relation on the following wiggly arcs.
+See \cref{fig:pseudodissections}.
 
@@
 A \defn{wiggly pseudodissection}~$D$ is a set of pairwise compatible wiggly arcs which contains the exterior wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$.
-We denote by~$D^\circ \eqdef D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.
+We denote by~$D^\circ \!\eqdef\!
+D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.
 
@@
 The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue).
-The other two have $7$ pseudotriangles, and are obtained from each other by a flip.}
+The other two have $7$ wiggly pseudotriangles, and are obtained from each other by a flip.}
 \label{fig:pseudodissections}
@@
 %In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
+See \cref{fig:wigglyComplex}\,(left).
 
@@
 Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
-Moreover, the following are equivalent:
+Moreover, the following assertions are equivalent:
 \begin{compactenum}[(i)]
@@
 \item $\beta \!\eqdef\!
-\big( i, j', {]i,j'[} \!\ssm\!
+\big( i', j, {]i,j'[} \!\ssm\!
 (B \!\cup\!
@@
 B') \big)$ and~$\beta' \!\eqdef\!
-\big( i', j, {]i',j[} \!\cap\!
+\big( i, j', {]i',j[} \!\cap\!
 (A \!\cup\!
@@
 (A \!\cup\!
-A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ with~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
-(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
+A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and $\alpha$ crosses~$\alpha'$ from north-west to south-east.
+(In other words, $\beta$ is the wiggly arc starting at~$i'$ and ending at~$j$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i$ and ending~at~$j'$ which follows the upper hull of~$\alpha$~and~$\alpha'$.)
 \end{compactitem}
@@
 
-%\vspace{-.1cm}
-\centerline{\includegraphics[scale=1.3]{incompatible3}}
+\vspace{.1cm}
+\centerline{\includegraphics[scale=1.55]{incompatible3}}
 %\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
@@
 %\end{figure}
-\vspace{-.4cm}
 \end{proposition}
@@
 \label{def:wigglyPermutation}
-A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
+A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns
 \begin{compactitem}
@@
 For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
-\vspace{-.1cm}
 \[
-1234, 1243, 1342, 1423, 1432, 2134, 2143, 3412, 3421, 4123, 4132, 4213, 4312, 4321.
+1234, \; 1243, \; 1342, \; 1423, \; 1432, \; 2134, \; 2143, \; 3412, \; 3421, \; 4123, \; 4132, \; 4213, \; 4312, \; 4321.
 \]
@@
 
-\parpic(3.6cm,5cm)(-10pt, 133pt)[r][b]{\includegraphics[scale=2]{bijection}}{
+\parpic(3.6cm,3.5cm)(-10pt, 133pt)[r][b]{\includegraphics[scale=2]{bijection}}{
 \begin{definition}
@@
 \label{def:bijection2}
-For a wiggly permutation~$\sigma$ of~$[2n]$, define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
+For a wiggly permutation~$\sigma$ of~$[2n]$, define~$\Psi(\sigma) \eqdef\! \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
 \begin{alignat*}{3}
 i & \eqdef \max \{0\} \cup \set{i \!\in\! [n]}{2i-1 \!\in\! \sigma([k]) \!\!\not\ni\! 2i}\!, \quad &
-A & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])}\!, \\
+A & \eqdef \set{\ell \!\in\! {]i,j[}}{\!\{2\ell-1, 2\ell\} \!\subseteq\! \sigma([k])}\!, \\
 j & \eqdef \min \{n+1\} \cup \set{j \!\in\! [n]}{2j \!\in\! \sigma([k]) \!\!\not\ni\! 2j-1}\!, \;\, &
-B & \eqdef \set{\ell \!\in\! {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing} \!.
+B & \eqdef \set{\ell \!\in\! {]i,j[}}{\!\{2\ell-1, 2\ell\} \cap \sigma([k]) \!=\! \varnothing} \!.
 \end{alignat*}
@@
 The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
-\vspace{-.25cm}
 \begin{align*}
@@
 \alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
-\\[-.9cm]
 \end{align*}
@@
 0$~for~all wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
-That is, $\b{c}(T) \eqdef \! \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ and~$\b{g}(T)$ are dual bases~in~$\HH_{2n}$.
+That is, $\b{c}(T) \eqdef \! \set{\b{c}(\alpha, T)}{\alpha \!\in\! T^\circ}$ and~$\b{g}(T)$ are dual bases~in~$\HH_{2n}$.
 \end{definition}
@@
 
-Combining \cref{prop:linearDependences,prop:wallCrossingInequalities}, the incompatibility number satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$, from which we derive our main statement.
+Combining \cref{prop:linearDependences,prop:wallCrossingInequalities}, the incompatibility numbers satisfy all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$, from which we derive our main statement.
 %that it behaves properly with respect to the linear dependences of
@@
 
-In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 = \delta_{n+1} = 0$.
+In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
 We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
@@
 \label{prop:CambrianLattice}
-The $\delta$-triangulation, $\delta$-permutation, \mbox{$\delta$-wiggly} pseudotriangulation, and $\delta$-wiggly permutation lattices are all isomorphic, and are known as the \defn{$\delta$-Cambrian~lattice}~\cite{Reading-CambrianLattices}.
+The $\delta$-triangulation, $\delta$-permutation, \mbox{$\delta$-wiggly} pseudotriangulation, and $\delta$-wig\-gly permutation lattices are all isomorphic, and are known as the \defn{$\delta$-Cambrian~lattice}~\cite{Reading-CambrianLattices}.
 \end{proposition}
@@
 \begin{compactitem}
-\item by the wigglyhedron of~\cref{thm:wigglyhedron} when the point set~$P$ is alogned, and
+\item by the wigglyhedron of~\cref{thm:wigglyhedron} when the point set~$P$ is aligned, and
 \item by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}, realizing the flip graph on the original pseudotriangulations of~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, when the point set~$P$ is in general position.

### 2024-10-17 draft/wigglyhedra.tex
improve FPSAC

@@
 The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue).
-The other two have $7$ pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and dark blue pseudotriangles.}
+The other two have $7$ wiggly pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and dark blue wiggly pseudotriangles.}
 \label{fig:pseudodissections}
@@
 Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
-Moreover, the following are equivalent:
+Moreover, the following assertions are equivalent:
 \begin{enumerate}[(i)]
@@
 \item $\alpha$ starts where~$\alpha'$ ends (that is, $i = j'$), or 
-\item $\alpha$ crosses~$\alpha'$ from north-west to south-east (that is, there exists~$k \in [n-1]$ such that $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$).
+\item $\alpha$ crosses~$\alpha'$ from north-west to south-east (that is, there exists~$1 \le k < \ell \le n$ such that $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$\ell \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$).
 \end{itemize}
@@
 (In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i, j', {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i', j, {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and there is~$k \in [n-1]$ such that~$k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$k+1 \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$.
-(In other words, $\beta$ is the wiggly arc starting at~$i$ and ending at~$j'$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i'$ and ending~at~$j$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
+\item $\beta \eqdef \big( i', j, {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i, j', {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and $\alpha$ crosses~$\alpha'$ from north-west to south-east.
+(In other words, $\beta$ is the wiggly arc starting at~$i'$ and ending at~$j$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i$ and ending~at~$j'$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
 \end{itemize}
 %See \cref{fig:incompatible3} for illustrations.
-(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ and~$\alpha'$ are crossing with~$i \in B'$ or~$i' \in A$.)
+(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ crosses~$\alpha'$ from south-east to north-west.)
 %
@@
 \label{def:wigglyPermutation}
-A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns:
+A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns
 \begin{itemize}
@@
 
-In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, we set~$\delta_0 = \delta_{n+1} = 0$.
+In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, we set~$\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
 We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice of \cref{sec:combinatorics} and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron of \cref{sec:geometry}.

### 2024-11-07 FPSAC25/wigglyhedraFPSAC.tex
Wrote up a draft categorical section.

@@
 \usepackage{overpic}
+\usepackage{tikz-cd}
 
@@
 \author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}.
-Supported by the Australian DECRA grant DE240100447.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{mailto:vincent.pilaud@ub.edu}.
+Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{mailto:vincent.pilaud@ub.edu}.
 Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788) and by the Spanish grant PID2022-137283NB-C21.}\addressmark{2}}
@@
 \label{sec:representationTheory}
+The aim of this section is to interpret the combinatorial results of the previous sections in terms of operations in a triangulated category.
+We briefly recall this category, which arises from an algebra associated to the quiver depicted in the following figure.
+\begin{figure}[h]
+  \centering
+  \begin{tikzcd}
+    1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
+  \end{tikzcd}
+  \caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
+  \label{fig:am-quiver}
+\end{figure}
 
-\newpage
+We work over the field \(k = \mathbb{C}\).
+Given a quiver \(Q\), we denote by \defn{kQ} its path algebra, which is generated by the idempotent paths \(e_i\) and the arrows \((i,i\pm1)\).
+A longer path is denoted \((i_1,\ldots,i_n)\), by the vertices it passes through in order.
+\begin{definition}
+The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
+\end{definition}
+The basis elements of \(A_m\) are graded by path-length.
+We will consider graded modules over \(A_m\).
+Let \(P_i = A_m\cdot e_i\) be the \(i\)th indecomposable projective \(A_m\)-module.
+For \(j \in \mathbb{Z}\) and any \(A_m\)-module \(M\), let \(M\langle j \rangle\) denote its graded shift by \(j\).
+The triangulated category \(\mathcal{C}_m\) defined below is discussed further in e.g.~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
+\begin{definition}
+The category \(\mathcal{C}_m\) is the smallest triangulated subcategory of \(D^b(A_m\text{-gr-mod})\) containing all the objects \(P_i\langle j \rangle\).
+\end{definition}
+Objects in \(\mathcal{C}_m\) are of the form \((M^{\bullet}, d)\), where \(M^{\bullet}\) is a direct sum of graded and homological shifts of objects in \(\{P_1,\ldots, P_m\}\), and \(d \colon M^{\bullet} \to M^{\bullet}\) is a differential that raises homological degree by \(1\).
+The \defn{level} of a summand with grading shift \(g\) and homological shift \(h\) is defined to be \(g+h\).
+We say that \((M^{\bullet},d)\) is \defn{linear} if each constituent summand has level zero.
+We say that an object \((M^{\bullet},d)\) is \defn{spherical} if it has a unique nontrivial endomorphism of graded degree zero, and a unique nontrivial endomorphism of graded degree \(2\), up to scaling.
+We refer the reader to~\cite{bel.ber.del:82} for standard results about \(t\)-structures.
+\begin{proposition}
+  The collection of all linear objects \((M^{\bullet}, d)\) in \(\mathcal{C}_m\) is an abelian subcategory of \(\mathcal{C}_m\), which is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\).
+  Let \(\mathcal{A}_m\) be this abelian subcategory.
+\end{proposition}
+
+Let \(\mathcal{C}\) be a triangulated category, and let \(\mathcal{A} \subset \mathcal{C}\) be the heart of a \(t\)-structure on \(\mathcal{C}\).
+Then for any integer \(i\), we have the \(i\)th homology functor
+\(H^i \colon \mathcal {C} \to \mathcal{A}\),
+which truncates an arbitrary object in \(\mathcal{C}\) to its portion in the \(i\)th homological degree.
+Furthermore, it is standard that if \(\mathcal{A}\) is the heart of a \emph{bounded} \(t\)-structure, then any object \(X\) has a canonical filtration whose factors are \(H^i(X)[-i]\).
+This filtration is called the \defn{cohomology filtration}.
+
+Now consider \(n+2\) points arranged in a horizontal line.
+In addition to the wiggly arcs, we also consider \defn{curves}: these are isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
+The \emph{Khovanov--Seidel curve model}~\cite[Sect.~4]{kho.sei:02} is a mapping from curves to objects of \(\mathcal{A}_{n+1}\) up to an overall grading and homological shift, as illustrated in~\cref{fig:curveModel}.
+An object in \(\mathcal{A}_{n+1}\) lies in the image of this mapping if and only if it is spherical.
+Moreover, the minimal intersection number between any pair of curves is the number of morphisms between the associated objects.
+
+\begin{figure}
+\centerline{
+	\begin{tabular}{c@{\qquad}c@{\qquad}c}
+		Spherical objects in bounded 
+		&
+		&
+		\\
+		homotopy category of graded projective 
+		&
+		$\smash{\xrightarrow[\quad\text{combinatorial model}\quad]{}}$
+		&
+		Curves
+		\\
+		modules over the zigzag algebra
+		&
+		&
+                \\
+		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
+			\&           \& P_3 \langle -1 \rangle\arrow{dr} \& \\
+			\&           \&                      \& P_2\\
+			P_1\langle -5 \rangle\arrow{r}    \& P_1\langle -3 \rangle\arrow{r}   \& P_1 \langle -1 \rangle\arrow{ur} \& 
+		\end{tikzcd}
+		&
+		&
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve1}}
+		\\[.5cm]
+		{\scriptsize cohomology} $\Bigg\downarrow$ {\scriptsize filtration}
+		&
+		&
+		$\Bigg\downarrow$ {\scriptsize cut}
+		\\[.5cm]
+		Heart of the standard $t$-structure
+		&
+		$\xrightarrow[\quad\text{combinatorial model}\quad]{}$
+		&
+		Wiggly arcs
+		\\
+		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
+			P_1\langle -1 \rangle \arrow{dr}\& \\
+			\& P_2 \\
+			P_3 \langle -1 \rangle \arrow{ur}
+		\end{tikzcd}
+		&
+          	&
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve2}}
+		\\
+		\(P_1\)
+		&
+		&
+		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve3}	}
+	\end{tabular}
+}
+\caption{An illustration of the Khovanov--Seidel curve model and \cref{prop:cohomology-pieces}.}
+\label{fig:curveModel}
+\end{figure}
+\begin{proposition}
+\label{prop:cohomology-pieces}
+Let \(\alpha\) be any curve on \(n+2\) points, and let \(X\) be the associated object in \(\mathcal{C}_{n+1}\).
+\begin{enumerate}
+\item The object \(X[j]\) lies in \(\mathcal{A}_m\) for some \(j \in \mathbb{Z}\) if and only if \(\alpha\) is a wiggly arc.
+  In this case, \(X \cong H^j(X)[-j]\), and \(H^i(X) = 0\) for \(i \neq j\).
+\item If \(\alpha\) is a general curve and \(j \in \mathbb{Z}\), each indecomposable summand of \(H^j(X)\) is a spherical object of \(\mathcal{A}_m\).
+\end{enumerate}
+\end{proposition}
+
+\begin{proposition}
+\label{prop:hn-filtration}
+  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
+  Consider the set of all indecomposable summands of the nonzero objects \(H^j(X)\).
+  Let \(T\) be the corresponding set of wiggly arcs.
+  Then
+  \begin{enumerate}
+  \item 
+    \(T\) is a subset of a wiggly pseudotriangulation,
+  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
+  \end{enumerate}
+\end{proposition}
+\begin{proposition}
+\label{prop:ext1}
+Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
+Then the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext_{\mathcal{A}_m}^1(X,X')\).
+Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:incompatibilityDegree}) if and only if \(\Ext_{\mathcal{A}_m}^1(X, X') = 0\).
+\end{proposition}
+
+%\newpage
 %% if you use biblatex then this generates the bibliography

### 2024-11-07 FPSAC25/wigglyhedraFPSAC.tex
minor corrections

@@
 \begin{definition}
-The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
+The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of the path algebra \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
 \end{definition}
 The basis elements of \(A_m\) are graded by path-length.
-We will consider graded modules over \(A_m\).
+We consider graded modules over \(A_m\).
 Let \(P_i = A_m\cdot e_i\) be the \(i\)th indecomposable projective \(A_m\)-module.
 For \(j \in \mathbb{Z}\) and any \(A_m\)-module \(M\), let \(M\langle j \rangle\) denote its graded shift by \(j\).
-The triangulated category \(\mathcal{C}_m\) defined below is discussed further in e.g.~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
+The triangulated category~\(\mathcal{C}_m\) defined below is discussed further in e.g.~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
 \begin{definition}
@@
 \begin{proposition}
-  The collection of all linear objects \((M^{\bullet}, d)\) in \(\mathcal{C}_m\) is an abelian subcategory of \(\mathcal{C}_m\), which is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\).
+  The collection of all linear objects \((M^{\bullet}, d)\) in \(\mathcal{C}_m\) is an abelian subcategory of~\(\mathcal{C}_m\), which is the heart of a bounded \(t\)-structure on \(\mathcal{C}_m\).
   Let \(\mathcal{A}_m\) be this abelian subcategory.
@@
 In addition to the wiggly arcs, we also consider \defn{curves}: these are isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-The \emph{Khovanov--Seidel curve model}~\cite[Sect.~4]{kho.sei:02} is a mapping from curves to objects of \(\mathcal{A}_{n+1}\) up to an overall grading and homological shift, as illustrated in~\cref{fig:curveModel}.
+The \defn{Khovanov--Seidel curve model}~\cite[Sect.~4]{kho.sei:02} is a mapping from curves to objects of \(\mathcal{A}_{n+1}\) up to an overall grading and homological shift, as illustrated in~\cref{fig:curveModel}.
 An object in \(\mathcal{A}_{n+1}\) lies in the image of this mapping if and only if it is spherical.
@@
 		&
-                \\
+                \\[.2cm]
 		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
@@
 		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve1}}
-		\\[.5cm]
+		\\[.6cm]
 		{\scriptsize cohomology} $\Bigg\downarrow$ {\scriptsize filtration}
@@
 		$\Bigg\downarrow$ {\scriptsize cut}
-		\\[.5cm]
+		\\[.6cm]
 		Heart of the standard $t$-structure
@@
 Let \(\alpha\) be any curve on \(n+2\) points, and let \(X\) be the associated object in \(\mathcal{C}_{n+1}\).
-\begin{enumerate}
+\begin{compactenum}
 \item The object \(X[j]\) lies in \(\mathcal{A}_m\) for some \(j \in \mathbb{Z}\) if and only if \(\alpha\) is a wiggly arc.
@@
 \item If \(\alpha\) is a general curve and \(j \in \mathbb{Z}\), each indecomposable summand of \(H^j(X)\) is a spherical object of \(\mathcal{A}_m\).
-\end{enumerate}
+\end{compactenum}
 \end{proposition}
@@
   Then
-  \begin{enumerate}
+  \begin{compactenum}
   \item 
-    \(T\) is a subset of a wiggly pseudotriangulation,
+    \(T\) is a subset of a wiggly pseudotriangulation.
   \item \(T\) contains at most one of the two irrelevant wiggly arcs.
-  \end{enumerate}
+  \end{compactenum}
 \end{proposition}
@@
 \label{prop:ext1}
-Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
+Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\).
 Then the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext_{\mathcal{A}_m}^1(X,X')\).
-Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:incompatibilityDegree}) if and only if \(\Ext_{\mathcal{A}_m}^1(X, X') = 0\).
+Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:incompatibilityDegree}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
 \end{proposition}

### 2024-11-07 FPSAC25/wigglyhedraFPSAC.tex
minor corrections
change intro to cite preprint

@@
 %% likewise for citations -- please don't use \cite, and instead write out your citation as something like (author year)
-\abstract{Motivated by categorical representation theory, we study the wigglyhedron.
+\abstract{
+%Motivated by categorical representation theory, we study the wigglyhedron.
 Its boundary complex encodes wiggly dissections (sets of pairwise pointed and non-crossing arcs wiggling around $n+2$ points on a line).
 Its graph is the Hasse diagram of the sublattice of the weak order induced by wiggly permutations (permutations of~$[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$).
-It contains copies of all type~$A_n$ Cambrian lattices and Cambrian fans.}
+It contains copies of all type~$A_n$ Cambrian lattices and Cambrian fans.
+Motivated by categorical representation theory, we study the wigglyhedron.
+Its boundary complex encodes wiggly dissections of $n+2$ points on a line.
+Its skeleton is the Hasse diagram of the sublattice of the weak order induced by wiggly permutations of~$[2n]$.
+It contains copies of all type~$A_n$ Cambrian lattices and Cambrian~fans.
+}
 
 %% put your French abstract here, or comment this out if you don't have one
-\resume{Motivés par la théorie catégorique des représentations, nous étudions \linebreak l'onduloèdre.
+\resume{
+%Motivés par la théorie catégorique des représentations, nous étudions \linebreak l'onduloèdre.
 Son complexe de bord encode les dissections ondulantes (ensembles d'arcs ondulant autour de $n+2$ points sur une ligne, deux-à-deux pointés et sans croisement).
 Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations ondulantes (permutations de~$[2n]$ évitant~$2j-1 \cdots i \cdots 2j$ pour~$i < 2j-1$ et~$2j \cdots k \cdots 2j-1$ pour~$k > 2j$).
-Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.}
+Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.
+Motivés par la théorie catégorique des représentations, nous étudions \linebreak l'onduloèdre.
+Son complexe de bord encode les dissections ondulantes de $n+2$ points sur une ligne.
+Son graphe est le diagramme de Hasse du sous-treillis de l'ordre faible induit par les permutations ondulantes de~$[2n]$.
+Il contient des copies de tous les treillis Cambriens et associaèdres Cambriens de type~$A_n$.
+}
 
@@
 Motivated by categorical representation theory, we consider the wiggly complex (\cref{sec:wigglyPseudotriangulations}), whose vertices are arcs wiggling around $n+2$ points on a line, and whose faces are sets of pairwise pointed and non-crossing wiggly arcs.
-It is a $(2n-1)$-dimensional manifold whose maximal faces are wiggly pseudotriangulations of a disc.
+It is a $(2n-1)$-dimensional manifold whose maximal faces are wiggly pseudotriangulations.
 We show (\cref{sec:bijection}) that the flip graph on wiggly pseudotriangulations is isomorphic to the cover graph of the sublattice of the weak order induced by wiggly permutations (\cref{sec:wigglyPermutations}), the permutations of~$[2n]$ avoiding~$2j-1 \cdots i \cdots 2j$ for~$i < 2j-1$ and~$2j \cdots k \cdots 2j-1$ for~$k > 2j$.
+
 Inspired by similar constructions for finite type cluster complexes~\cite{HohlwegLangeThomas,HohlwegPilaudStella}, and for support $\tau$-tilting complexes on gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}, we then provide geometric realizations of the wiggly complex.
@@
 Its graph can be oriented to obtain the Hasse diagram of the wiggly lattice, and it contains copies of all type~$A_n$ Cambrian lattices~\cite{Reading-CambrianLattices} as faces (\cref{sec:CambrianConsiderations}).
-To conclude, we conjecture that the wiggly complex of any planar point set is polytopal (\cref{sec:planarPointSets}), and we explore representation theoretic aspects of the wiggly complex (\cref{sec:representationTheory}).
+
+We conclude with two further topics.
+First, we conjecture that the wiggly complex of any planar point set is polytopal (\cref{sec:planarPointSets}), extending the wigglyhedron for aligned points and the pointed pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope} for points in general position.
+We then explore representation theoretic aspects of the wiggly complex (\cref{sec:representationTheory}), interpreting our combinatorial results in terms of operations in a triangulated category.
+
+Due to space limitations, this extended abstract omits many details and proofs of~\cite{BapatPilaud}.
 
@@
 Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:incompatibilityDegree}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
+\vincent{Do you mean \cref{def:compatible} here?}
 \end{proposition}

### 2024-11-07 FPSAC25/wigglyhedraFPSAC.tex
minor corrections

@@
 and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
-\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.
+\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in~\cref{fig:wigglyCambrian}.
 

### 2024-11-13 FPSAC25/wigglyhedraFPSAC.tex
update affiliation and grants

@@
 \author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}.
-Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{mailto:vincent.pilaud@ub.edu}.
-Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788) and by the Spanish grant PID2022-137283NB-C21.}\addressmark{2}}
+Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{vincent.pilaud@ub.edu}.
+Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788), and by the Spanish grants PID2022-137283NB-C21, 2021 SGR 00697 and CEX2020-001084-M.}\addressmark{2}}
 
 %% then use \addressmark to match authors to institutions here
-\address{\addressmark{1}The Australian National University, Canberra, Australia \\ \addressmark{2}Universitat de Barcelona, Spain}
+\address{
+	\addressmark{1}The Australian National University, Canberra, Australia \\ 
+	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Spain
+}
 

### 2024-11-13 FPSAC25/wigglyhedraFPSAC.tex
cleaning bib file

@@
 %% for more than 3 names, use the Oxford comma: One Author, Two Author, Red Author, \and Blue Author
-\author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}.
+\author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{asilata.bapat@anu.edu.au}.
 Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{vincent.pilaud@ub.edu}.
@@
 Then the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext_{\mathcal{A}_m}^1(X,X')\).
-Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:incompatibilityDegree}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
-\vincent{Do you mean \cref{def:compatible} here?}
+Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:compatible}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
+%\vincent{Do you mean \cref{def:compatible} here?}
 \end{proposition}

### 2024-11-15 FPSAC25/wigglyhedraFPSAC.tex
update affiliation and grants
improve last section

@@
 	\addressmark{1}The Australian National University, Canberra, Australia \\ 
-	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Spain
+	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Barcelona, Spain
 }
@@
 
+For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
+However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
+This categorical interpretation of the pseudotriangulations was our initial motivation to study the wiggly complex.
+
 \begin{proposition}
@@
 \end{proposition}
+
+We finally give a categorical interpretation of the compatibility (see~\cref{def:compatible}) and incompatibility degree (see~\cref{def:incompatibilityDegree}) of two arcs.
+
 \begin{proposition}
@@
 Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\).
-Then the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext_{\mathcal{A}_m}^1(X,X')\).
-Thus \(\alpha\) and \(\alpha'\) are compatible (as in~\cref{def:compatible}) if and only if \({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
+Then the incompatibility degree of \(\alpha\) and \(\alpha'\)  is the dimension of~\(\Ext_{\mathcal{A}_m}^1(X,X')\).
+Thus \(\alpha\) and \(\alpha'\) are compatible if and only if~\({\Ext_{\mathcal{A}_m}^1(X, X') = 0}\).
 %\vincent{Do you mean \cref{def:compatible} here?}

### 2024-11-15 FPSAC25/wigglyhedraFPSAC.tex
improve last section

@@
 For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
-However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
+However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations (see \cref{prop:wigglyPseudotriangulations}).
 This categorical interpretation of the pseudotriangulations was our initial motivation to study the wiggly complex.
@@
   \begin{compactenum}
-  \item 
-    \(T\) is a subset of a wiggly pseudotriangulation.
+  \item \(T\) is a subset of a wiggly pseudotriangulation.
   \item \(T\) contains at most one of the two irrelevant wiggly arcs.

### 2025-01-02 MZ/answerReferee.tex
start corrections

\documentclass{letter}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{shuffle}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[a4paper, top=1in, bottom=.8in, left=1in, right=1in]{geometry}
\signature{%
Asilata Bapat and Vincent Pilaud \Letter
}

\address{\bf Asilata Bapat \\
\small The Australian National University \\
\small \url{asilata.bapat@anu.edu.au} \\[.3cm]
\bf Vincent Pilaud \Letter \\
\small Universitat de Barcelona \\
\small \url{vincent.pilaud@ub.edu}
}

\begin{document}

\begin{letter}{{\bf Editors and Referees} \\ Mathematische Zeitschrift}
\opening{Dear Editors, dear Referee,}

We are grateful to the referee for their thorough reading and their constructive suggestions on our manuscript \emph{Wigglyhedra}. We would like to submit a revised version of this manuscript to the \emph{Mathematische Zeitschrift}.

We agreed with all comments and suggestions of the referee and we have revised our submission accordingly. To simplify the second reading, we now answer the comments of the referee and summarize the changes from the last version:

{\bf Required Corrections}

\begin{itemize}
\item \textsl{\color{gray} Remark 9: I believe there are (edge) cases of pseudotriangles with only 3 points on its boundary; e.g.~take pseudotriangles in the $n = 1$ case (unless I’m supposed to count one of the boundary point twice, which isn’t clear to me).} \\
We indeed count points with multiplicity. We defined corners and hinges by the sentence ``Two consecutive wiggly arcs along the boundary of~$c$ define a \emph{corner} (resp.~a \emph{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$'' in Definition 6. So two corners can coincide at the same point. To insist on this fact, we have added ``Note that two corners of~$c$ can coincide at the same point~$i \in [n]$'' in Definition 6 and ``(two corners can coincide at the same point~$i \in [n]$)'' twice in Remark 9.

\item \textsl{\color{gray} Definition 34: I believe the other label should be $2h$ instead of $2h+1$.} \\
You are absolutely right, this is a typo. Thank you so much for noticing it.

\item \textsl{\color{gray} $g$-vectors, §3.2: This is probably the most important one. I was very confused after reading your definition of a $g$-vector; in particular, whether a $g$-vector is actually a vector in $\mathbb{H}_{2n}$. In Definition 47, you define the $g$-vector as the orthogonal projection of $\hat{g}$ onto $\mathbb{H}_{2n}$. However, the sentence right after the defining equations for $\alpha^\pm$ seems to agree with the definition that one gets before taking the projection (i.e. supposedly $\hat{g}$). I accepted this as a typo (that the $g$ should’ve been a $\hat{g}$ here), but then looking through the $g$-matrices examples that you’ve provided in the figures, I found that most of their $g$-vectors (columns) do not live in $\mathbb{H}_{2n}$ and behave more like $\hat{g}$ instead – in fact, the entries of the $g$-vectors generally did not sum to $0$, which I believe is the definition of being a vector in $\mathbb{H}_{2n}$. In reading the rest of the paper I deduced that you do want $g$-vectors to be in $\mathbb{H}_{2n}$, but please make sure that it is consistent with the examples you’ve provided.} \\
TODO

\item \textsl{\color{gray} Complexes associated to curves and extensions in the linear heart: This is perhaps more pedantic, but I think it is nonetheless important. I believe that under your definition, every curve, and in particular every wiggly arc, is only associated with a complex up to overall shifts in internal (path length) and homological gradings. While I understood that many of the claims involving these objects should be implicitly considered “up to both gradings shifts”, I think the claims would benefit from a more precise wording. For example, Proposition 94 as it currently is can be confusing and is falsifiable. For concreteness take $n = 1$ and the arcs $\alpha := (0, 1, \emptyset, \emptyset)$ and $\alpha' := (1, 2, \emptyset, \emptyset)$, which are not compatible (non-pointed). If I were to pick $X := P_1$ and $X' := P_2$, then $\mathrm{Ext}^1(X, X') = 0$ in $A_2$, which contradicts Proposition 94. Of course there are ``better'' choices of $X$ and $X'$, which would make the statement true. One way to correctly state it would be, e.g. ``$\mathrm{Ext}^1(X,X') = 0$ for all representatives $X$ and $X'$ of $\alpha$ and $\alpha'$ respectively''. Similar issue appears in Proposition 97, where as is currently stated, there may or may not be an extension depending on the choice of $X, X', Y, Y'$.} \\
TODO

\end{itemize}

{\bf Minor remarks}

\begin{itemize}
\item \textsl{\color{gray} pg.\,4 (C1): I would add ``($x$-coordinate monotone)'' or ``(abcissa monotone)''.} \\
We have replaced ``$x$-monotone'' by ``abscissa monotone''.

\item \textsl{\color{gray} pg.\,4 (C2): Maybe it should be mentioned that they cross even up to isotopy, or define what it means to be intersecting minimally.} \\
We have added ``(i.e.~any isotopy representatives must cross)''.

\item \textsl{\color{gray} pg.\,5 (C1): Perhaps more precisely, ``as arcs in D are pairwise pointed''.} \\
Indeed, this was unprecise. We modified it as suggested.

\item \textsl{\color{gray} pg.\,5 (C2)*: Possibly 3 points in the boundary, as mentioned in previous section.} \\
We have added ``(two corners can coincide at the same point~$i \in [n]$)'', see above.

\item \textsl{\color{gray} pg.\,6 (C1): As $D$ is a priori a pseudodissection, I wasn't sure what should be included in the counting of connected components. Maybe something along the lines of ``where $D$ is viewed as the set of edges of the graph with vertices given by the marked points $0$ to $n+1$'' might help.} \\
Indeed, this was too implicit. We have added ``(where $D$ is viewed as the edge set of the graph with vertex set given by the marked points $0$ to $n+1$)''.

\item \textsl{\color{gray} pg.\,6 (C2): Since $D$ is by definition a set of wiggly arcs, $c \in D$ can be confused with arcs in $D$ rather than connected components.} \\
Again, this was too implicit. The $c$ in all sums of this paragraph actually ranges over the wiggly cells of~$D$. We have added ``(both sums range over the wiggly cells~$c$ of~$D$)'' at the end of the sentence.

\item \textsl{\color{gray} pg.\,6 (C3): Aren’t there examples of internal arcs which only bounds one wiggly cell? Take again $n = 1$ and the unique internal wiggly arc of any pseudotriangulation.} \\
TODO

\item \textsl{\color{gray} pg.\,7 (C1): This is a personal tangential comment: is this a new sequence that is not currently in OEIS? If so it might be worth submitting it.} \\
Indeed, we should include it. It is not in OEIS.

\item \textsl{\color{gray} pg.\,7 (C2): I was a bit slow in understanding this; I actually had to go to the corresponding description for wiggly permutations and work my way backwards to understand this. I believe an example would help a lot.} \\
TODO

\item \textsl{\color{gray} pg.\,8 (C1): Perhaps more precisely, “compatible with wiggly arcs in c”.} \\
Indeed, we have added ``compatible with all wiggly arcs of~$c$''.

\item \textsl{\color{gray} pg.\,9 (C1): Maybe this is standard abuse of notation, but technically you’ve provided the clique graph and not the complex itself.} \\
TODO

\item \textsl{\color{gray} pg.\,10 (C1): Typo ``we are define''.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,12 (C1): This should be ``admissible gaps''?} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,13 (C1): I find this description confusing. Maybe ``Following in a counterclockwise direction...'' would be better.} \\
We have replaced by ``Following each wiggly pseudotriangle of~$T$ in counterclockwise direction''.
\item \textsl{\color{gray} pg.\,13 (C2) Definition 34*: $2h + 1$ should be $2h$.} \\
You are absolutely right, we have corrected this typo.

\item \textsl{\color{gray} pg.\,14 (C1): I think it is important to first point out that every $j \in [n]$ is the hinge of exactly one pseudotriangle, which implies the highlighted sentence.} \\
Indeed, we have added ``As every~$j \in [n]$ is the hinge of precisely one pseudotriangle of~$T$''.

\item \textsl{\color{gray} Figures in §3.2 and §3.3*: As mentioned in the previous section, all $g(T)$ in figures should be replaced by the correct $g$-matrices (whose column vectors are in~$\mathbb{H}_{2n}$).} \\
TODO

\item \textsl{\color{gray} pg.\,17 (C1): Subscript missing: $\mathbb{H}_d$} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,17 (C2): I assume this is a typo: $g(\alpha)$ should be $\hat{g}(\alpha)$.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,17 (C3): Unintended capitalisation: should be $g(T)$.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,18 (C1): I think $1$ and $-1$ should be $2$ and $-2$ respectively.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,26 (C1): The definition of zigzag algebra as it is would not be correct for $m = 2$; adding in the relation (superfluous for $m > 2$) ``all paths of length $3$ and above are killed'' should suffice.} \\
TODO

\item \textsl{\color{gray} pg.\,27 (C1): I'd add the adjective ``full''.} \\
TODO

\item \textsl{\color{gray} pg.\,29 (C1): Given your setting, I assume you meant ``derived category'' instead?} \\
TODO

\item \textsl{\color{gray} pg.\,30 (C1): Is ``irrelevant'' meant to be ``external''? I’m not sure where ``irrelevant wiggly arc'' was defined.} \\
TODO

\item \textsl{\color{gray} pg.\,31 (C1)*: As mentioned in the previous section.} \\
TODO

\item \textsl{\color{gray} pg.\,31 (C2): ``up to equivalence'' should probably also include ``up to scalar multiplication''; same for ``unique element''.} \\
TODO

\item \textsl{\color{gray} pg.\,32 (C1)*: As mentioned in the previous section, some sort of ``up to appropriate shift in gradings'' should be included.} \\
TODO

\end{itemize}

We are really grateful for all these improvements and would like to thank the referee again for the efforts they offered to our work. We hope that we have addressed their comments carefully, but we will be happy to have any further comments on this submission.

%Sincerely,
%
%\vspace{.5cm}
%\hspace{8cm} Asilata Bapat and Vincent Pilaud

\closing{Sincerely yours,}

\end{letter}

\end{document}

### 2025-01-02 draft/wigglyhedra.tex
start corrections

@@
 A \defn{wiggly arc} is a quadruple $\alpha \eqdef (i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~${]i,j[} \eqdef \{i+1, \dots, j-1\}$.
-We represent $\alpha$ by an $x$-monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
-The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~$\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])$ are called \defn{external}, all other wiggly arcs are called \defn{internal}.
+We represent $\alpha$ by an abscissa monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
+The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~${\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])}$ are called \defn{external}, all other wiggly arcs are called \defn{internal}.
 \end{definition}
@@
 \item \defn{non pointed} if~$i = j'$ or~$i' = j$,
-\item \defn{crossing} if~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing \ne (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, that is, if the corresponding curves cross,
+\item \defn{crossing} if~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing \ne (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, that is, if the corresponding curves cross (\ie any isotopy representatives must cross),
 \item \defn{incompatible} if they are non pointed or crossing, and \defn{compatible} otherwise.
@@
 Two consecutive wiggly arcs along the boundary of~$c$ define a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$.
+Note that two corners of~$c$ can coincide at the same point~$i \in [n]$.
 %The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
@@
 Consider a wiggly cell~$c$ in a wiggly pseudodissection~$D$.
-Note that~$\beta_c$ is always even as~$D$ is pointed, so that~$\beta_c/2$ is an integer.
+Note that~$\beta_c$ is always even as the arcs of~$D$ are pairwise pointed, so that~$\beta_c/2$ is an integer.
 Moreover, we have~$\beta_c \ge 2$ and~$\kappa_c \ge 1$, where at least one of the two inequalities is strict (as otherwise, the two wiggly arcs bounding~$c$ would coincide).
@@
 \label{rem:descriptionPseudotrianglesPseudoquadrangles}
-As illustrated in \cref{fig:pseudotriangles}, a wiggly pseudotriangle~$t$ has no point in its interior and $4$ points on its boundary, $3$ corners and $1$ hinge.
+As illustrated in \cref{fig:pseudotriangles}, a wiggly pseudotriangle~$t$ has no point in its interior and $4$ points on its boundary, $3$ corners and $1$ hinge (two corners can coincide at the same point~$i \in [n]$).
 %Hence, it has two corners oriented in the same direction, which we call the \defn{twin corners}.
@@
 \item either one point in its interior and~$2$ points on its boundary, both corners,
-\item or no point in its interior and $6$ points on its boundary, $4$ corners and $2$ hinges.
+\item or no point in its interior and $6$ points on its boundary, $4$ corners and $2$ hinges (two corners can coincide at the same point~$i \in [n]$).
 We then distinguish three situations, depending on the position of the two pairs~$p, p'$ of wiggly arcs incident to the two hinges of~$c$, as illustrated in \cref{fig:pseudoquadrangles} (where~$p$ and~$p'$ are colored in red and orange):
@@
 \begin{proof}
-Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
+Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components (where $D$ is viewed as the edge set of the graph with vertex set given by the marked points $0$ to $n+1$).
 Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$n - \iota + \gamma = \kappa$.
-Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
+Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$ (both sums range over the wiggly cells~$c$ of~$D$).
 As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
@@
 \[
-\sum_{c \in C} (\delta_c-3) = \sum_{c \in D} \beta_c/2 + 2 \sum_{c \in D} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
+\sum_{c \in D} (\delta_c-3) = \sum_{c \in D} \beta_c/2 + 2 \sum_{c \in D} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
 \]
@@
 \begin{definition}
-A \defn{wiggly diagonal} of a wiggly cell~$c$ is a wiggly arc inside~$c$ and compatible with~$c$.
+A \defn{wiggly diagonal} of a wiggly cell~$c$ is a wiggly arc inside~$c$ and compatible with all wiggly arcs of~$c$.
 \end{definition}
@@
 
-Finally, we are define the wiggly complex~$\wigglyComplex_n$, illustrated in \cref{fig:wigglyComplex}\,(left) when~$n = 2$.
+Finally, we define the wiggly complex~$\wigglyComplex_n$, illustrated in \cref{fig:wigglyComplex}\,(left) when~$n = 2$.
 
@@
 \item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps and where~$2n-1$ appears before~$2n$ (they must appear consecutively),
-\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible arcs and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
+\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible gaps and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
 \end{itemize}
@@
 Consider a wiggly pseudotriangulation~$T$.
-Rotating counterclockwise inside each wiggly pseudotriangle of~$T$, we label by~$2h-1$ (resp.~$2h+1$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
+Following each wiggly pseudotriangle of~$T$ in counterclockwise direction, we label by~$2h-1$ (resp.~$2h$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
 We define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
@@
 First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
-Observe first that~\(\Phi(T)\) is by construction a permutation~$\sigma$ of~$[2n]$.
+As every~$j \in [n]$ is the hinge of precisely one pseudotriangle of~$T$, we obtain that~\(\Phi(T)\) is by construction a permutation~$\sigma$ of~$[2n]$.
 For any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
@@
 For~$I \subseteq [d]$, we define~$\one_I \eqdef \sum_{i \in I} \b{e}_i$, and we often shorten~$\one_{[d]}$ by~$\one_d$.
-We denote by~$\HH_d$ the hyperplane of~$\R^d$ defined by the equation~$\dotprod{\b{x}}{\one_d} = 0$, and we denote by~$\pi : \R^d \to \HH$ the orthogonal projection on~$\HH_d$, that is~$\pi(\b{x}) \eqdef \b{x} - (\dotprod{\b{x}}{\one_d} / d) \one_d$.
+We denote by~$\HH_d$ the hyperplane of~$\R^d$ defined by the equation~$\dotprod{\b{x}}{\one_d} = 0$, and we denote by~$\pi : \R^d \to \HH_d$ the orthogonal projection on~$\HH_d$, that is~$\pi(\b{x}) \eqdef \b{x} - (\dotprod{\b{x}}{\one_d} / d) \one_d$.
 
@@
 \centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $4$ times the $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+\caption{The $\hat{\b{g}}$-matrix~$\hat{\b{g}}(T)$ and $4$ times the $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
+The $i$th column of these matrices are the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
 The colors of the columns match the colors of the wiggly arcs.}
@@
 \label{def:gvectors}
-The \defn{$\b{g}$-vector}~$\b{g}(\alpha)$ of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
+The \defn{$\b{g}$-vector} of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is the vector~$\b{g}(\alpha)$ of~$\HH_{2n}$ defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
 \begin{align*}
@@
 \end{align*}
-If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\b{g}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
+If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\hat{\b{g}}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
 Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
@@
 \label{exm:specialGMatrices}
-\cref{table:specialGMatrices} gathers the $\b{g}$-matrices (\ie matrices whose columns are the $\b{g}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
+\cref{table:specialGMatrices} gathers the $\hat{\b{g}}$-matrices (\ie matrices whose columns are the $\hat{\b{g}}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
 
@@
 %	\qquad &
-	\b{g}(T_\downarrow) & = \begin{pmatrix}
+	\hat{\b{g}}(T_\downarrow) & = \begin{pmatrix}
 		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
@@
 %	\qquad &
-	\b{g}(T_\leftarrow) & = \begin{pmatrix}
+	\hat{\b{g}}(T_\leftarrow) & = \begin{pmatrix}
 		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
@@
 %	\qquad &
-	\b{g}(T_\uparrow) & = \begin{pmatrix}
+	\hat{\b{g}}(T_\uparrow) & = \begin{pmatrix}
 		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
@@
 %	\qquad &
-	\b{g}(T_\rightarrow) & = \begin{pmatrix}
+	\hat{\b{g}}(T_\rightarrow) & = \begin{pmatrix}
 		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
@@
 	\endgroup
-	\caption{The $\b{g}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\b{g}(T)$ is the $\b{g}$-vector~$\b{g}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+	\caption{The $\hat{\b{g}}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
+The $i$th column of~$\hat{\b{g}}(T)$ is the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
 }
@@
 
-Observe that the $\b{g}$-matrices of \cref{exm:specialGMatrices} have full rank.
-More generally, we will see in \cref{coro:basis} that~$\b{G}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis.
+Observe that the $\hat{\b{g}}$-matrices of \cref{exm:specialGMatrices} have rank~$2n-1$.
+More generally, we will see in \cref{coro:basis} that~$\b{g}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis.
 
@@
 \[
-\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 1 & \text{if~$k = i$,} \\ -1 & \text{if~$k = j$,} \\ 0 & \text{otherwise}, \end{cases}
+\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 2 & \text{if~$k = i$,} \\ -2 & \text{if~$k = j$,} \\ 0 & \text{otherwise}, \end{cases}
 \qquad\text{and}\qquad

### 2025-01-02 MZ/answerReferee.tex
more corrections

@@
 We defined corners and hinges by the sentence ``Two consecutive wiggly arcs along the boundary of~$c$ define a \emph{corner} (resp.~a \emph{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$'' in Definition 6.
-So two corners can coincide at the same point.
+So two corners can indeed coincide at the same point.
 To insist on this fact, we have added ``Note that two corners of~$c$ can coincide at the same point~$i \in [n]$'' in Definition 6 and ``(two corners can coincide at the same point~$i \in [n]$)'' twice in Remark 9.
+Thank you for pointing out that this was unclear.
 
 \item \textsl{\color{gray} Definition 34: I believe the other label should be $2h$ instead of $2h+1$.} \\
-You are absolutely right, this is a typo. Thank you so much for noticing it.
+You are absolutely right, this is a typo. Thank you for noticing it.
 
@@
 In reading the rest of the paper I deduced that you do want $g$-vectors to be in $\mathbb{H}_{2n}$, but please make sure that it is consistent with the examples you’ve provided.} \\
-TODO
+We agree with the referee that the implicit identification of the $\hat{g}$-vectors and $g$-vectors in our illustrations was really confusing. We have proceed to the following changes:
+\begin{itemize}
+\item We have split Figure 12 into two figures.
+Figure 12 now presents the $\hat{g}$-vectors and the \mbox{$g$-vectors} of a wiggly pseudotriangulation side to side, so that the projection is clearer.
+Figure~13 presents the $g$-vectors and the $c$-vectors of a wiggly pseudotriangulation side to side, so that the duality is visible.
+\item We made clear in Example 48 and the caption of Table 1 that we represent here the $\hat{g}$-matrices.
+We decided to keep the $\hat{g}$-matrices rather than the $g$-matrices as the former are easier to read from Figure 5, while the latter have unnecessarily involved coefficients due to the projection.
+We believe that representing the $g$-matrices here would not help the reader.
+\end{itemize}
 
@@
 The $c$ in all sums of this paragraph actually ranges over the wiggly cells of~$D$.
-We have added ``(both sums range over the wiggly cells~$c$ of~$D$)'' at the end of the sentence.
+We have added ``denoting by~$C$ the set of wiggly cells of~$D$'' and replaced~``$c \in D$'' by~``$c \in C$'' as indices of the sums.
 
 \item \textsl{\color{gray} pg.\,6 (C3): Aren’t there examples of internal arcs which only bounds one wiggly cell? Take again $n = 1$ and the unique internal wiggly arc of any pseudotriangulation.} \\
-TODO
+We count with multiplicities. We have added ``(we count a wiggly arc~$\alpha$ with multiplicity~$2$ if it appears twice along the boundary of~$c$)'' to make it clear.
 
 \item \textsl{\color{gray} pg.\,7 (C1): This is a personal tangential comment: is this a new sequence that is not currently in OEIS? If so it might be worth submitting it.} \\
-Indeed, we should include it. It is not in OEIS.
+Indeed, we should include it. It is not in OEIS at the moment.
 
@@
 I believe an example would help a lot.} \\
+This is actually the way this decomposition was found: we first worked it out on wiggly permutations and transported it back to wiggly pseudotriangulations through the bijection.
 TODO
@@
 \item \textsl{\color{gray} Figures in §3.2 and §3.3*: As mentioned in the previous section, all $g(T)$ in figures should be replaced by the correct $g$-matrices (whose column vectors are in~$\mathbb{H}_{2n}$).} \\
-TODO
+We now have the $\hat{g}$-matrix and $g$-matrix side by side in Figure 12.
+For Table~1, we have chosen to keep the $\hat{g}$-matrices (but we made it clear in the caption).
+See answer above for more explanations.
 

### 2025-01-02 draft/wigglyhedra.tex
more corrections

@@
 Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$n - \iota + \gamma = \kappa$.
-Moreover, $\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$ (both sums range over the wiggly cells~$c$ of~$D$).
-As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
+Moreover, denoting by~$C$ the set of wiggly cells of~$D$, we have~$\sum_{c \in C} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$ (we count a wiggly arc~$\alpha$ with multiplicity~$2$ if it appears twice along the boundary of~$c$), and~${\sum_{c \in C} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
+As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in C} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
 We conclude that~$\gamma \le n$ and~$\iota = n+\gamma-\kappa \le 2n-1$.
@@
 %Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
-%Observe that~$\sum_{c \in D} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and that~${\sum_{c \in D} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-%As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus get~$2 \gamma \le \sum_{c \in D} (\beta_c/2+\kappa_c-1) = \iota+\kappa$.
+%Observe that~$\sum_{c \in C} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and that~${\sum_{c \in C} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
+%As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus get~$2 \gamma \le \sum_{c \in C} (\beta_c/2+\kappa_c-1) = \iota+\kappa$.
 %As~$D$ is a planar graph with~$v = n+2$ vertices, $e = \iota+2$ edges, $f = 1+\gamma$ faces, and $\kappa$ connected components, Euler's formula~$1+\kappa = v-e+f$ yields~$2(1+\kappa) = 2(n+2)-2(\iota+2)+2(1+\gamma) \le 2n-2\iota+2+\iota+\kappa$, so that~$\iota \le 2n-\kappa \le 2n-1$ and~$\gamma \le (\iota+\kappa)/2 \le n$.
@@
 \[
-\sum_{c \in D} (\delta_c-3) = \sum_{c \in D} \beta_c/2 + 2 \sum_{c \in D} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
+\sum_{c \in C} (\delta_c-3) = \sum_{c \in C} \beta_c/2 + 2 \sum_{c \in C} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
 \]
@@
 
-\pagebreak
 We will need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
@@
 
-\enlargethispage{.3cm}
 We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
@@
 
-\enlargethispage{.5cm}
 Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
@@
 
-We now define two families of vectors, illustrated in \cref{fig:pseudotriangulationMatrices}.
+We first define the $\b{g}$-vectors, illustrated in \cref{fig:ggMatrices}.
 %
 \begin{figure}
-\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\hat{\b{g}}$-matrix~$\hat{\b{g}}(T)$ and $4$ times the $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ and $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
-The colors of the columns match the colors of the wiggly arcs.}
-\label{fig:pseudotriangulationMatrices}
+\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/ggmatrices}}
+\caption{The $\hat{\b{g}}$-matrix~$\hat{\b{g}}(T)$ and $\b{g}$-matrix~$\b{g}(T)$ of a wiggly pseudotriangulation~$T$.
+The $i$th column of these matrices are the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ and the $\b{g}$-vector~$\b{g}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+The colors of the columns match the colors of the wiggly arcs.
+The $\b{g}$-vectors are the orthogonal projections of the $\hat{\b{g}}$-vectors on the hyperplane~$\HH_{2n}$.}
+\label{fig:ggMatrices}
 \end{figure}
@@
 
-Observe that the $\hat{\b{g}}$-matrices of \cref{exm:specialGMatrices} have rank~$2n-1$.
-More generally, we will see in \cref{coro:basis} that~$\b{g}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis.
+We will see in \cref{coro:basis} that~$\b{g}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis, illustrated in \cref{fig:gcMatrices}.
+%
+\begin{figure}
+\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
+\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
+The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
+The colors of the columns match the colors of the wiggly arcs.
+The $\b{g}$-vectors and $\b{c}$-vectors form dual bases of~$\HH_{2n}$.}
+\label{fig:gcMatrices}
+\end{figure}
 
@@
 
-\pagebreak
 Recall from~\cref{rem:incompatibility-deg} that two wiggly arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.

### 2025-01-04 MZ/answerReferee.tex
more corrections

@@
 \item We have split Figure 12 into two figures.
-Figure 12 now presents the $\hat{g}$-vectors and the \mbox{$g$-vectors} of a wiggly pseudotriangulation side to side, so that the projection is clearer.
-Figure~13 presents the $g$-vectors and the $c$-vectors of a wiggly pseudotriangulation side to side, so that the duality is visible.
+Figure 13 now presents the $\hat{g}$-vectors and the \mbox{$g$-vectors} of a wiggly pseudotriangulation side to side, so that the projection is clearer.
+Figure~14 presents the $g$-vectors and the $c$-vectors of a wiggly pseudotriangulation side to side, so that the duality is visible.
 \item We made clear in Example 48 and the caption of Table 1 that we represent here the $\hat{g}$-matrices.
@@
 This is actually the way this decomposition was found: we first worked it out on wiggly permutations and transported it back to wiggly pseudotriangulations through the bijection.
-TODO
+We agree that examples will help here. We have decided to include the following:
+\begin{itemize}
+\item In Remark 14, we have added Figure 6 with some examples of wiggly pseudotriangulations obtained by added one more wiggly pseudotriangle.
+\item In Remark 28, we have added an example listing all wiggly permutations of $[10]$ obtained from the wiggly permutation~$78621354$ of~$[8]$.
+\item We also extended Remark 41 to explicitly point to these particular examples.
+\end{itemize}
 
@@
 \item \textsl{\color{gray} pg.\,9 (C1): Maybe this is standard abuse of notation, but technically you’ve provided the clique graph and not the complex itself.} \\
-TODO
+You are right, except that we provide here a little more than the graph as we embed the full complex in the plane.
+To make it explicit, we have added the sentence ``We have embedded the wiggly complex~$\mathrm{WC}_2$ in the plane, so that all triangles (including the external one) form a face of~$\mathrm{WC}_2$.''.
 
@@
 \item \textsl{\color{gray} Figures in §3.2 and §3.3*: As mentioned in the previous section, all $g(T)$ in figures should be replaced by the correct $g$-matrices (whose column vectors are in~$\mathbb{H}_{2n}$).} \\
-We now have the $\hat{g}$-matrix and $g$-matrix side by side in Figure 12.
+We now have the $\hat{g}$-matrix and $g$-matrix side by side in Figure 13.
 For Table~1, we have chosen to keep the $\hat{g}$-matrices (but we made it clear in the caption).

### 2025-01-04 draft/wigglyhedra.tex
more corrections

@@
 \pagebreak
+\cref{fig:pseudotriangulationsCounting} illustrates this decomposition.
+%
+\begin{figure}
+\centerline{\includegraphics[scale=1.3]{pseudotriangulationCounting}}
+\caption{Some wiggly pseudotriangulations of~$7$ points obtained from the top left wiggly pseudotriangulation of~$6$ points by inserting a wiggly pseudotriangle with hinge at~$5$ as described in \cref{rem:numberWigglyPseudotriangulations}.
+Those on the first line contain the wiggly arc~$(5, 6, \varnothing, \varnothing)$ and are thus obtained by inserting the head of the wiggly pseudotriangle with hinge at~$5$ in one of the final wiggly arcs.
+Those on the second line do not contain the wiggly arc~$(5, 6, \varnothing, \varnothing)$ and are thus obtained by inserting the two legs of the wiggly pseudotriangle with hinge at~$5$ in two of the final wiggly arcs.
+The coloring of the wiggly arcs is supposed to help visualizing in which wiggly arcs the head or legs of the new wiggly pseudotriangle were inserted.}
+\label{fig:pseudotriangulationsCounting}
+\end{figure}
+%
 This translates to the recursive formula %for all~$n \ge 1$,
@@
 \centerline{\includegraphics[scale=1.1]{wigglyComplex}}
-\caption{The wiggly complex~$\wigglyComplex_2$ (left) and the wiggly flip graph~$\wigglyFlipGraph_2$ (right).}
+\caption{The wiggly complex~$\wigglyComplex_2$ (left) and the wiggly flip graph~$\wigglyFlipGraph_2$ (right).
+We have embedded the wiggly complex~$\wigglyComplex_2$ in the plane, so that all triangles (including the external one) form a face of~$\wigglyComplex_2$.}
 \label{fig:wigglyComplex}
@@
 \end{itemize}
+For instance, the wiggly permutation~$78621354$ of~$[8]$ has admissible gaps~$\bullet 7 \bullet 8 \bullet 62135 \bullet 4 \bullet$ and thus gives rise to the wiggly permutations
+\[
+9\mathrm{X}78621354, \quad 79\mathrm{X}8621354, \quad 789\mathrm{X}621354, \quad 78621359\mathrm{X}4, \quad 786213549\mathrm{X}
+\]
+of~$[10]$ where the $9$ appears before~$10$, and the wiggly permutations
+\begin{align*}
+& \mathrm{X}978621354, \quad \mathrm{X}798621354, \quad \mathrm{X}789621354, \quad \mathrm{X}786213594, \quad \mathrm{X}786213549, \\
+& 7\mathrm{X}98621354, \quad 7\mathrm{X}89621354, \quad 7\mathrm{X}86213594, \quad 7\mathrm{X}86213549, \quad 78\mathrm{X}9621354, \\
+& 78\mathrm{X}6213594, \quad 78\mathrm{X}6213549, \quad 7862135\mathrm{X}94, \quad 7862135\mathrm{X}49, \quad 78621354\mathrm{X}9
+\end{align*}
+of~$[10]$ where the $10$ appears before~$9$ (for brievety, we have replaced $10$ by $\mathrm{X}$ in the permutations).
 We thus obtain the same recursive equation on~$wp_n(x)$ as in \cref{rem:numberWigglyPseudotriangulations}.
@@
 
+\pagebreak
 Finally, consider a cover relation~$\sigma \lessdot \sigma^j$ in the wiggly lattice~$\wigglyLattice_n$ as described in~\cref{lem:wigglyCoverRelation}.
@@
 The map~$\Phi$ sends wiggly pseudotriangulations with $i$ final internal wiggly arcs to wiggly permutations with $i$ admissible gaps, explaining the similarities of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
+For instance, the wiggly pseudotriangulations of \cref{fig:pseudotriangulationsCounting} illustrating the description of \cref{rem:numberWigglyPseudotriangulations} correspond to the wiggly permutations
+\[
+\begin{array}{cccc}
+78621354 & 9\mathrm{X}78621354 & 789\mathrm{X}621354 & 78621359\mathrm{X}4 \\
+\mathrm{X}786213594 & 7\mathrm{X}89621354 & 78\mathrm{X}6213549 & 7862135\mathrm{X}49
+\end{array}
+\]
+illustrating the description of \cref{rem:numberWigglyPermutations}.
 \end{remark}
@@
 
+\pagebreak
 \section{Wiggly fan and wigglyhedron}
@@
 
+\enlargethispage{.6cm}
 Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
@@
 
+\pagebreak
 We denote by~$(\b{e}_i)_{i \in [d]}$ the standard basis of~$\R^d$.
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 We thank Anand Deopurkar and Anthony M. Licata for many useful conversations and ideas.
+Finally, we are grateful to an anonymous referee for many relevant suggestions on the presentation of the paper.
 

### 2025-01-04 draft/wigglyhedra.tex
missing files

@@
 
-We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$.
+We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
+\afterpage{
+\begin{figure}
+\centerline{\includegraphics[scale=.75]{wigglyFan}}
+\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.}
+\label{fig:wigglyFan}
+\end{figure}
+}
 

### 2025-01-06 MZ/answerReferee.tex
missing files
Added most of the edits.

@@
 Similar issue appears in Proposition 97, where as is currently stated, there may or may not be an extension depending on the choice of $X, X', Y, Y'$.} \\
-TODO
+  Indeed, the correct functor to use here is not \(\mathrm{Ext}^1\), but rather a direct sum over \(\mathrm{Ext}^1\)s from \(X\) to all level-zero shifts of \(X'\).
+  This has been corrected along the lines you suggested, and the new functor is denoted \(\mathbb{E}^1\).
 
@@
 \item \textsl{\color{gray} pg.\,26 (C1): The definition of zigzag algebra as it is would not be correct for $m = 2$; adding in the relation (superfluous for $m > 2$) ``all paths of length $3$ and above are killed'' should suffice.} \\
-TODO
+Thanks! Fixed.
 
 \item \textsl{\color{gray} pg.\,27 (C1): I'd add the adjective ``full''.} \\
-TODO
+Thanks! Fixed and updated to full and isomorphism-closed.
 
@@
 \item \textsl{\color{gray} pg.\,30 (C1): Is ``irrelevant'' meant to be ``external''? I’m not sure where ``irrelevant wiggly arc'' was defined.} \\
-TODO
+Thanks! Fixed.
 
 \item \textsl{\color{gray} pg.\,31 (C1)*: As mentioned in the previous section.} \\
-TODO
+Thanks! Fixed as above.
 
 \item \textsl{\color{gray} pg.\,31 (C2): ``up to equivalence'' should probably also include ``up to scalar multiplication''; same for ``unique element''.} \\
-TODO
+Thanks! Fixed.
 
 \item \textsl{\color{gray} pg.\,32 (C1)*: As mentioned in the previous section, some sort of ``up to appropriate shift in gradings'' should be included.} \\
-TODO
+Thanks! Fixed.
 
 \end{itemize}
+
+Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan, and we have corrected a few additional typos.
 

### 2025-01-06 draft/wigglyhedra.tex
Added most of the edits.

@@
 \begin{definition}
-The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
+The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by all paths of length at least \(3\), together with the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
 \end{definition}
@@
 \begin{definition}
-The category \(\mathcal{C}_m\) is defined to be the smallest triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
+The category \(\mathcal{C}_m\) is defined to be the smallest full, isomorphism-closed triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
 \end{definition}
@@
     \(T\) is a subset of a wiggly pseudotriangulation,
-  \item \(T\) contains at most one of the two irrelevant wiggly arcs.
+  \item \(T\) contains at most one of the two external wiggly arcs.
   \end{enumerate}
@@
 
+For two objects \(X\) and \(X'\) of \(\mathcal{C}_m\), let \(\mathbb{E}^\ell(X,X')\) denote the direct sum over all level-\(\ell\) morphisms from \(X\) to \(X'\).
+That is,
+\[\mathbb{E}^\ell(X,X') = \bigoplus_{g + h = \ell}\Hom^{g,h}(X,X').\]
+
 Recall that two wiggly arcs \(\alpha\) and \(\alpha'\) are said to be compatible (as in~\cref{def:compatible}) if they are non-crossing and pointed.
@@
 Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible if and only if \(\Ext^1(X, X') = 0\).
-  More generally, the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\Ext^1(X,X')\).
+  Then \(\alpha\) and \(\alpha'\) are compatible if and only if \(\mathbb{E}^1(X, X') = 0\).
+  More generally, the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\mathbb{E}^1(X,X')\).
 \end{proposition}
@@
   We can thus obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
-    The dimension of \(\Ext^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
-
-It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence) of level one; that is, a unique element of \(\Ext^1\).
-Morphisms arising from other intersections do not contribute to \(\Ext^1\).
+    The dimension of \(\mathbb{E}^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
+
+It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence and scalar multiplication) of level one; that is, a unique element (up to scalar multiplication) of \(\mathbb{E}^1\).
+Morphisms arising from other intersections do not contribute to \(\mathbb{E}^1\).
 This calculation proves the proposition.
@@
   As stated,~\cref{prop:ext1} in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
-  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two spherical objects with a non-trivial \(\Ext^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
+  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two spherical objects with a non-trivial \(\mathbb{E}^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
   However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
@@
 Let \(X\), \(X'\), \(Y\) and~\(Y'\) be spherical objects in the standard heart that correspond to \(\alpha\), \(\alpha'\), \(\beta\) and~\(\beta'\) respectively.
-First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial extension between the corresponding objects of the standard heart.
+First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial \(\mathbb{E}^1\) between the corresponding objects of the standard heart.
 Next, let us understand~\(Y\) and \(Y'\) categorically.
@@
 \begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then we have extensions
-  \[0 \to X' \to Y \to X \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X' \to 0,\]
-\item if \(\alpha\) and \(\alpha'\) are crossing, then we have an extension
-  \[0 \to X' \to (Y \oplus Y') \to X \to 0.\]
+\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some \(g\) and \(g'\), we have extensions
+  \[0 \to X' \to Y \to X\langle g \rangle[-g] \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X'\langle g' \rangle[-g'] \to 0;\]
+\item if \(\alpha\) and \(\alpha'\) are crossing, then for some \(g\), we have an extension
+  \[0 \to X' \to (Y \oplus Y') \to X\langle g \rangle[-g]\to 0.\]
 \end{itemize}
@@
   Suppose we have a collection of spherical objects in the standard heart \(\mathcal{A}_m\) that satisfy the compatibility condition of~\cref{prop:ext1}.
-  That is, the \(\Ext^1\) between any pair of objects in this collection is zero.
+  That is, the \(\mathbb{E}^1\) between any pair of objects in this collection is zero.
   \begin{enumerate}

### 2025-01-07 MZ/answerReferee.tex
Made some technical changes.

@@
 Similar issue appears in Proposition 97, where as is currently stated, there may or may not be an extension depending on the choice of $X, X', Y, Y'$.} \\
-  Indeed, the correct functor to use here is not \(\mathrm{Ext}^1\), but rather a direct sum over \(\mathrm{Ext}^1\)s from \(X\) to all level-zero shifts of \(X'\).
+  Thank you for catching this. Indeed, it was written imprecisely in the previous version.
+  The correct functor to use here is not \(\mathrm{Ext}^1\), but rather a direct sum over \(\mathrm{Ext}^1\)s from \(X\) to all level-zero shifts of \(X'\).
   This has been corrected along the lines you suggested, and the new functor is denoted \(\mathbb{E}^1\).
@@
 \item \textsl{\color{gray} pg.\,27 (C1): I'd add the adjective ``full''.} \\
-Thanks! Fixed and updated to full and isomorphism-closed.
+  Thanks! Fixed. However, we have changed the Definition 84, and the category is now defined as the bounded homotopy category of projective modules.
+  The statement that it is a full subcategory of \(D^b(A_m\mathrm{-mod})\) is now written as a remark after this definition.
 
 \item \textsl{\color{gray} pg.\,29 (C1): Given your setting, I assume you meant ``derived category'' instead?} \\
-TODO
+We believe this should be left as-is. Definition 84 has been updated to better match the wording in this figure.
 

### 2025-01-07 draft/wigglyhedra.tex
Made some technical changes.

@@
 
-We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-That is, a subcategory of the bounded derived category of finitely generated \(A_m\)-modules.
+% We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
+We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a certain finite-dimensional algebra \(A_m\). 
+It is a full subcategory of \(D^b(A_m\text{-grmod})\), the bounded derived category of finitely generated graded \(A_m\)-modules.
 The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
@@
 For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-There is an embedding of \(A_m\text{-mod}\) into \(D^b(A_m\text{-mod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
-In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-mod})\).
 
 \begin{definition}
-The category \(\mathcal{C}_m\) is defined to be the smallest full, isomorphism-closed triangulated subcategory of \(D^b(A_m\text{-mod})\) containing all the objects \(P_i\langle j \rangle\).
+The category \(\mathcal{C}_m\) is defined to be the homotopy category of bounded complexes of finitely-generated graded projective \(A_m\)-modules.
 \end{definition}
+Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
+In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-grmod})\).
+\(\mathcal{C}_m\) is thus the smallest full triangulated subcategory of \(D^b(A_m\text{-grmod})\) containing all the objects \(P_i\langle j \rangle\).
 

### 2025-01-08 draft/wigglyhedra.tex
Minor edits.

@@
 % We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a certain finite-dimensional algebra \(A_m\). 
-It is a full subcategory of \(D^b(A_m\text{-grmod})\), the bounded derived category of finitely generated graded \(A_m\)-modules.
-The algebra~\(A_m\), called the \defn{zigzag algebra}, is defined as a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
+We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a finite-dimensional algebra \(A_m\). 
+The algebra~\(A_m\), called the \defn{zigzag algebra}, is a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
 Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
@@
 \end{definition}
+Let \(D^b(A_m\text{-grmod})\) denote the bounded derived category of graded \(A_m\)-modules.
 Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
@@
 \begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some \(g\) and \(g'\), we have extensions
+\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some integers \(g\) and \(g'\), we have extensions
   \[0 \to X' \to Y \to X\langle g \rangle[-g] \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X'\langle g' \rangle[-g'] \to 0;\]
-\item if \(\alpha\) and \(\alpha'\) are crossing, then for some \(g\), we have an extension
+\item if \(\alpha\) and \(\alpha'\) are crossing, then for some integer \(g\), we have an extension
   \[0 \to X' \to (Y \oplus Y') \to X\langle g \rangle[-g]\to 0.\]

### 2025-01-09 draft/wigglyhedra.tex
typographic changes

@@
 \begin{definition}
-The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by all paths of length at least \(3\), together with the relations \((i-1, i, i+1) = 0 = (i+1, i, i-1)\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
+The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by all paths of length at least \(3\), together with the relations \((i-1, i, i+1) = 0\), \((i+1, i, i-1)=0\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
 \end{definition}
@@
 Let \(\alpha\) be any curve, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
-Recall that for any integer \(j\), the cohomology object \(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
+Recall that for any integer \(j\), the cohomology object~\(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
 \begin{enumerate}
@@
   \begin{enumerate}
-  \item a map \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\), namely multiplication on the right by the path \((i,i\pm1)\), which does not change the level; or
-  \item a map \(P_i\langle g \rangle[h] \to P_{i}\langle g+2 \rangle[h-1]\), namely multiplication on the right by the ``loop'' path \((i,i\pm1, i)\), which raises the level by one.
+  \item a map \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\), namely multiplication on the right by the path~\((i,i\pm1)\), which does not change the level; or
+  \item a map \(P_i\langle g \rangle[h] \to P_{i}\langle g+2 \rangle[h-1]\), namely multiplication on the right by the ``loop'' path~\((i,i\pm1, i)\), which raises the level by one.
   \end{enumerate}
-  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the \((i-1)\)th point.
+  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the~\((i-1)\)th point.
   The second possibility appears each time the curve makes a U-turn around the right of \(i\)th or the left of the \((i-1)\)th point.
@@
   In this case, we take the portion of \(\alpha\) between \(p_0\) and \(p_1\), calling it \(\alpha_1\), and setting its endpoints to be \(p_0\) and \(p_1\) respectively.
-  Note that \(p_0 \neq p_1\) because \(\alpha\) is \(x\)-monotone between \(p_0\) and \(p_1\).
+  Note that \(p_0 \neq p_1\) because \(\alpha\) is \(x\)-monotone between~\(p_0\) and~\(p_1\).
   We continue with the remainder of \(\alpha\) starting at \(p_1\), greedily taking the maximal \(x\)-monotone portion each time, to obtain pieces \(\alpha_1,\alpha_2, \ldots, \alpha_k\), which are all wiggly arcs.
@@
   The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of curves on the disk with marked points.
-  Let \(X_1, \ldots, X_k\) be the objects in \(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
-  Let \(\beta = (i,j,A,B)\) and \(\beta' = (i',j', A',B')\) be two distinct wiggly arcs among \(\{\alpha_1, \ldots,\alpha_k\}\).
+  Let \(X_1, \ldots, X_k\) be the objects in~\(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
+  Let \(\beta = (i,j,A,B)\) and \(\beta' = (i',j', A',B')\) be two distinct wiggly arcs among~\(\{\alpha_1, \ldots,\alpha_k\}\).
   We check that \(\beta\) and \(\beta'\) are compatible in the sense of~\cref{def:compatible}.
@@
   Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
-  These must then connect to each other, resulting in \(\alpha\) having a separate closed component that winds around the outside of the \(n+2\) points.
+  These must then connect to each other, resulting in~\(\alpha\) having a separate closed component that winds around the outside of the \(n+2\) points.
   This is not possible because \(\alpha\) is a connected curve with two endpoints.
@@
   We can thus obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
-    The dimension of \(\mathbb{E}^1(X,X')\), is therefore the coefficient of \(q\) under this specialisation.
-
-It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence and scalar multiplication) of level one; that is, a unique element (up to scalar multiplication) of \(\mathbb{E}^1\).
-Morphisms arising from other intersections do not contribute to \(\mathbb{E}^1\).
+    The dimension of \(\mathbb{E}^1(X,X')\), is therefore the coefficient of~\(q\) under this specialisation.
+
+It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence and scalar multiplication) of level one; that is, a unique element (up to scalar multiplication) of~\(\mathbb{E}^1\).
+Morphisms arising from other intersections do not contribute to~\(\mathbb{E}^1\).
 This calculation proves the proposition.
@@
 This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
-The \(\b{g}\)-vector of an object \(X\) corresponding to a wiggly arc \(\alpha\) can, of course, be reconstructed from \(\alpha\).
+The \(\b{g}\)-vector of an object~\(X\) corresponding to a wiggly arc \(\alpha\) can, of course, be reconstructed from \(\alpha\).
 However, at the moment we do not have a purely categorical construction of the \(\b{g}\)-vector of \(X\) that does not refer to \(\alpha\), and it would be interesting to find this.

### 2025-01-09 MZ/answerReferee.tex
improve two pictures

@@
 
-Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan, and we have corrected a few additional typos.
+Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan with vertices labeled by the corresponding wiggly arcs, and we have labeled the vertices of the wigglyhedron in Figure 16 by the corresponding wiggly pseudotriangulations.
+We have also corrected a few additional typos.
 

### 2025-01-09 draft/wigglyhedra.tex
improve two pictures

@@
 \begin{figure}
-\centerline{\includegraphics[scale=.75]{wigglyFan}}
-\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.}
+\centerline{\includegraphics[scale=.75]{wigglyFanLabeled}}
+\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.
+The vertices of the projection are rays of~$\wigglyFan_2$ and are labeled by the corresponding wiggly arcs.
+Compare with \cref{fig:wigglyComplex}\,(left).}
 \label{fig:wigglyFan}
@@
 \begin{figure}
-\centerline{\input{wigglyhedron}}
-\caption{The wigglyhedron~$\wigglyhedron_2$.}
+%\centerline{\input{wigglyhedron}}
+\centerline{\includegraphics[scale=.75]{wigglyhedron}}
+\caption{The wigglyhedron~$\wigglyhedron_2$.
+The vertices are labeled by the corresponding wiggly pseudotriangulations.
+Compare to \cref{fig:wigglyComplex}\,(right) and \cref{fig:wigglyLattice}\,(left).}
 \label{fig:wigglyhedron}

### 2025-01-09 draft/wigglyhedra.tex
increase picture size

@@
 
-We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
+We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan} when~$n = 2$.
 \afterpage{
 \begin{figure}
-\centerline{\includegraphics[scale=.75]{wigglyFanLabeled}}
+\centerline{\includegraphics[scale=1.1]{wigglyFanLabeled}}
 \caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.
@@
 %\centerline{\input{wigglyhedron}}
-\centerline{\includegraphics[scale=.75]{wigglyhedron}}
+\centerline{\includegraphics[scale=1.1]{wigglyhedron}}
 \caption{The wigglyhedron~$\wigglyhedron_2$.
@@
 
+\pagebreak
   We have four possible combinations:

### 2025-01-09 MZ/answerReferee.tex
minor

--- 2025-01-07 MZ/answerReferee.tex
@@
 
-Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan, and we have corrected a few additional typos.
+Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan with vertices labeled by the corresponding wiggly arcs, and we have labeled the vertices of the wigglyhedron in Figure~16 by the corresponding wiggly pseudotriangulations.
+We have also corrected a few additional typos.
 

### 2025-01-31 wigglyPointSets/wigglyhedraPointSets.tex
point sets

--- 2025-01-09 draft/wigglyhedra.tex
@@
 
-\title{Wigglyhedra}
+\title{Wigglyhedra for planar point sets}
 
 \thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
-  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}
+VP was partially supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French project CHARMS (ANR-19-CE40-0017), and by the French--Austrian project PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
+
+\author{David Alcantara}
+\address{Universidad de Cantabria}
+\email{david.alcantara@unican.es}
+%\urladdr{\url{}}
 
@@
 
+\author{Francisco Santos}
+\address{Universidad de Cantabria}
+\email{francisco.santos@unican.es}
+\urladdr{\url{https://personales.unican.es/santosf/}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-Motivated by categorical representation theory, we define the wiggly complex, whose vertices are arcs wiggling around $n+2$ points on a line, and whose faces are sets of wiggly arcs which are pairwise pointed and non-crossing.
-The wiggly complex is a $(2n-1)$-dimensional pseudomanifold, whose facets are wiggly pseudotriangulations.
-We show that wiggly pseudotriangulations are in bijection with wiggly permutations, which are permutations of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
-These permutations define the wiggly lattice, an induced sublattice of the weak order.
-We then prove that the wiggly complex is isomorphic to the boundary complex of the polar of the wigglyhedron, for which we give explicit and simple vertex and facet descriptions.
-Interestingly, we observe that any Cambrian associahedron is normally equivalent to a well-chosen face of the wigglyhedron.
-Finally, we recall the correspondence of wiggly arcs with objects in a category, and we develop categorical criteria for a subset of wiggly arcs to form a face of the wiggly complex.
+We study the wiggly complex of a planar point set.
 \end{abstract}
@@
 
-\centerline{\includegraphics[scale=1.75]{wigglyFlipGraph}}
-
-\tableofcontents
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Introduction}
+\section{Wiggly complex and wiggly pseudotriangulations of a planar point set}
+\label{sec:wigglyComplex}
 
-In this paper we consider wiggly pseudotriangulations, which are built from arcs wiggling around points on a line.
-We study their combinatorics in detail, construct polyhedral realizations of their flip graph, and interpret them in terms of categorical representation theory.
+\vincent{This is copy-pasted from the wigglyhedron paper. The definition is actually inexact. To be improved.}
 
-\bigskip
-\para{Combinatorics}
-Fix $n \ge 1$ and consider the~$n+2$ points on the horizontal axis labelled~${0, \dots, n+1}$.
-A \defn{wiggly arc} is an abscissa monotone curve starting at some point~$i$, ending at some point~$j$ (with~${0 \le i < j \le n+1}$), and passing above or below each point~$i+1, \dots, j-1$.
-Two wiggly arcs are \defn{compatible} if they are pointed (the left endpoint of one is not the right endpoint of the other) and non-crossing (the interiors of the curves are disjoint).
-A \defn{wiggly dissection} is a collection of pairwise compatible wiggly arcs, and a \defn{wiggly pseudotriangulation} is an inclusion maximal wiggly dissection.
-The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of wiggly dissections (minus their external wiggly arcs).
-We first establish the following result.
-
-\begin{proposition*}
-The wiggly complex~$\wigglyComplex_n$ is a $(2n-1)$-dimensional pseudomanifold without boundary.
-\end{proposition*}
-
-In particular, all wiggly pseudotriangulations have $2n-1$ internal wiggly arcs, each of which can be \defn{flipped}.
-We actually describe the flip in terms of wiggly diagonals in wiggly pseudoquadrangles.
-We also orient this flip graph in a canonical way, which we call the \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$.
-The wiggly increasing flip graph on wiggly pseudotriangulations of $4$ points is the front page illustration of this paper (throughout the paper, we implicitly orient the graphs and posets from bottom to top).
-
-We then make a small detour to permutations.
-A \defn{wiggly permutation} is a permutation of~$[2n]$ avoiding the patterns~$(2j-1) \cdots i \cdots (2j)$ for~$i < 2j-1$ and~$(2j) \cdots k \cdots (2j-1)$ for~$k > 2j$.
-Our main result on wiggly permutations is the following.
-
-\begin{proposition*}
-The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, which we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
-Moreover, its Hasse diagram is regular of degree~$2n-1$.
-\end{proposition*}
-
-We then connect wiggly pseudotriangulations to wiggly permutations.
-
-\begin{proposition*}
-The increasing flip graph on wiggly pseudotriangulations~$\wigglyIncreasingFlipGraph_n$ is isomorphic to the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-In particular, the wiggly pseudotriangulations admit a lattice structure.
-\end{proposition*}
-
-\para{Polyhedral geometry}
-We then switch to geometric realizations of the wiggly complex~$\wigglyComplex_n$.
-Our constructions are inspired by similar constructions for generalized associahedra~\cite{HohlwegLangeThomas,HohlwegPilaudStella} of finite type cluster algebras~\cite{FominZelevinsky-ClusterAlgebrasI,FominZelevinsky-ClusterAlgebrasII}, and for gentle associahedra~\cite{PaluPilaudPlamondon-nonkissing} of support \mbox{$\tau$-tilting} complexes~\cite{AdachiIyamaReiten} on gentle algebras~\cite{ButlerRingel}.
-Namely, we first construct a fan supported by certain $\b{g}$-vectors associated to the wiggly arcs.
-
-\begin{theorem*}
-The cones generated by the $\b{g}$-vectors of wiggly pseudodissections form a complete simplicial fan, called \defn{wiggly fan}~$\wigglyFan_n$, realizing the wiggly complex~$\wigglyComplex_n$.
-\end{theorem*}
-
-The proof of this result is based on a fine understanding of the linear dependences between \mbox{$\b{g}$-vectors}.
-We further use this understanding to find a height function~$\kappa$ on wiggly arcs which satisfies all wall-crossing inequalities of the wiggly fan~$\wigglyFan_n$.
-Without entering the details of the definition of~$\kappa$ at the moment, let us just mention that it is obtained by summing some compatibility degrees of wiggly arcs, analogously to the constructions for cluster algebras~\cite{HohlwegPilaudStella} and gentle algebras~\cite{PaluPilaudPlamondon-nonkissing}.
-Using the $\b{c}$-vectors of each pseudotriangulation, defined to form the dual basis of the $\b{g}$-vectors, we obtain our main result.
-
-\begin{theorem*}
-The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
-\begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
-\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
-\end{itemize}
-\end{theorem*}
-
-Moreover, as for the classical permutahedron and associahedron, we recover our lattice structure by a suitable linear orientation of the graph of the wigglyhedron.
-
-\begin{proposition*}
-The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ (or equivalently, the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$) is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in a suitable direction.
-\end{proposition*}
-
-\para{Further topics}
-The wigglyhedron has interesting connections in lattice theory and discrete geometry.
-We first connect the wigglyhedron to the (type~$A$) Cambrian world.
-
-\begin{theorem*}
-For any~$\delta \in \{-,+\}^n$,
-\begin{itemize}
-\item the $\delta$-Cambrian lattice of~\cite{Reading-CambrianLattices} is an interval in the wiggly lattice~$\wigglyLattice_n$,
-\item the $\delta$-Cambrian fan of~\cite{ReadingSpeyer} is a link in the wiggly fan~$\wigglyFan_n$,
-\item the $\delta$-associahedron of~\cite{HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$.
-\end{itemize}
-\end{theorem*}
-
-We then define the wiggly complex~$\wigglyComplex_P$ of an arbitrary planar point set~$P$ (not necessarily aligned along the horizontal axis, nor necessarily in general position).
-Our definition recovers:
-\begin{itemize}
-\item when $P$ consists of $n+2$ collinear points, the wiggly complex~$\wigglyComplex_n$ considered in this~paper,
-\item when~$P$ is in general position, the pseudodissection complex of~$P$ considered in discrete and computational geometry~\cite{PocchiolaVegter,RoteSantosStreinu-pseudotriangulations}, and realized by the pseudotriangulation polytope in~\cite{RoteSantosStreinu-polytope} using rigidity and expansive motions.
-\end{itemize}
-These two families of examples motivate the following conjecture.
-
-\begin{conjecture*}
-For any point set~$P$ in the plane, the wiggly complex~$\wigglyComplex_P$ is the boundary complex of a simplicial polytope.
-\end{conjecture*}
-
-We also present a few open questions related to this conjecture, concerning in particular the possible interpretation of the wiggly complex~$\wigglyComplex_P$ in terms of dual pseudoline arrangements, and the extension to multi wiggly complexes and arbitrary finite Coxeter groups.
-
-\pagebreak
-\para{Categorical interpretation}
-Each wiggly arc on \(n+2\) points corresponds to an object of an abelian category, such that morphisms and extensions between objects in the category are captured by minimal intersection numbers between the wiggly arcs.
-In fact, this correspondence holds for more general curves, which then correspond to objects of a larger triangulated category~\cite{kho.sei:02}.
-
-A general curve can be decomposed into wiggly arcs simply by cutting along its U-turns.
-We interpret this operation categorically as the decomposition of an object of the triangulated category into its cohomology pieces, from which we deduce the following.
-
-\begin{proposition*}
-The set of wiggly arcs corresponding to the cohomology pieces of an object represented by a general arc is a face of the wiggly complex.
-\end{proposition*}
-
-Furthermore, we characterize categorically when two objects in the abelian category are compatible, that is, their corresponding wiggly arcs are compatible.
-
-\begin{proposition*}
-Two wiggly arcs are compatible if and only if there are no extensions between the corresponding objects in the abelian category.
-\end{proposition*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Wiggly pseudotriangulations and wiggly permutations}
-\label{sec:combinatorics}
-
-Fix an integer~$n \ge 1$.
-In this section, we define two combinatorial families, the wiggly pseudotriangulations of~$n+2$ points (\cref{subsec:wigglyPseudotriangulations}) and the wiggly permutations of~$[2n]$ (\cref{subsec:wigglyPermutations}), and we prove that they are in bijection (\cref{subsec:bijection}).
-These two perspectives enable us to endow these combinatorial families with additional structures: the wiggly pseudotriangulations are actually the facets of the wiggly complex, while the wiggly permutations are actually the elements of the wiggly lattice.
-We conclude with a few questions and conjectures on graph properties of the wiggly flip graph (\cref{subsec:graphProperties}).
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly pseudotriangulations and the wiggly complex}
-\label{subsec:wigglyPseudotriangulations}
-
-We start with wiggly pseudodissections of $n+2$ points on a line.
-The following two definitions are illustrated in \cref{fig:incompatible}.
-
-\begin{definition}
-A \defn{wiggly arc} is a quadruple $\alpha \eqdef (i,j,A,B)$ where $0 \le i < j \le n+1$ and the sets~$A$ and~$B$ form a partition of~${]i,j[} \eqdef \{i+1, \dots, j-1\}$.
-We represent $\alpha$ by an abscissa monotone curve wiggling around the horizontal axis, starting at point~$i$, ending at point~$j$, and passing above the points of~$A$ and below the points of~$B$.
-The wiggly arcs~$\alpha_\mathrm{top} \eqdef (0, n+1, [n], \varnothing)$ and~${\alpha_\mathrm{bot} \eqdef (0, n+1, \varnothing, [n])}$ are called \defn{external}, all other wiggly arcs are called \defn{internal}.
-\end{definition}
-
-\begin{remark}
-\label{rem:numberWigglyArcs}
-The number of wiggly arcs is~$\sum_{\ell = 0}^n 2^\ell (n+1-\ell) = 2^{n+2}-n-3$.
-\end{remark}
-
-\begin{definition}
-\label{def:compatible}
-Two wiggly arcs~$(i,j,A,B)$ and~$(i',j',A',B')$ are 
-\begin{itemize}
-\item \defn{non pointed} if~$i = j'$ or~$i' = j$,
-\item \defn{crossing} if~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) \ne \varnothing \ne (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, that is, if the corresponding curves cross (\ie any isotopy representatives must cross),
-\item \defn{incompatible} if they are non pointed or crossing, and \defn{compatible} otherwise.
-\end{itemize}
-%
-\begin{figure}[b]
-\centerline{\includegraphics[scale=1.3]{incompatible}}
-\caption{Some incompatible wiggly arcs: non pointed (left) and crossing (right).}
-\label{fig:incompatible}
-\end{figure}
-\end{definition}
-
-\begin{remark}
-We want to stress out that our notion of compatibility on wiggly arcs of \cref{def:compatible} might seem similar to, but fundamentally differs from the notion of compatibility used by N.~Reading to define noncrossing arc diagrams~\cite{Reading-arcDiagrams}.
-Namely, our wiggly arcs and our crossing condition coincide with that of~\cite{Reading-arcDiagrams}.
-However, we forbid an arc to start where another arc ends but allow two arcs to start or end at the same point,
-%for two wiggly arcs~$\alpha$ and~$\alpha'$ to be compatible, we forbid the left endpoint of~$\alpha$ to coincide with the right endpoint of~$\alpha'$, but allow $\alpha$ and~$\alpha'$ to have the same left endpoints or the same right endpoints,
-while N.~Reading does precisely the opposite in~\cite{Reading-arcDiagrams}.
-%This results in very different objects.
-\end{remark}
-
-We then consider pairwise compatible sets of wiggly arcs.
-The following two definitions are illustrated~in~\cref{fig:pseudodissections}.
-
-\begin{definition}
-A \defn{wiggly pseudodissection}~$D$ is a set of pairwise compatible wiggly arcs which contains the exterior wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$.
-We denote by~$D^\circ \eqdef D \ssm \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.5]{wigglyPseudodissections}}
-\caption{Three wiggly pseudodissections for~$n = 7$.
-The left one has three wiggly cells, of respective degrees $3$ (red), $8$ (green), and $4$ (blue).
-The other two have $7$ wiggly pseudotriangles, and are obtained from each other by flipping the wiggly arc separating their yellow and dark blue wiggly pseudotriangles.}
-\label{fig:pseudodissections}
-\end{figure}
-\end{definition}
-
-%\vincent{Here, I am using the fact that a set of pairwise non-crossing wiggly arcs can be drawn simultaneously non-crossing. I am not sure I want to enter these details.}
-
-\begin{definition}
-A wiggly pseudodissection~$D$ decomposes the digon bounded by~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ into cells, that we call \defn{wiggly cells}.
-The \defn{degree}~$\delta_c$ of a wiggly cell~$c$ is~$\delta_c \eqdef \beta_c/2+2\kappa_c-1$ where~$\beta_c$ is the number of wiggly arcs on the boundary of~$c$ (counted twice if they appear twice along the boundary of~$c$), and~$\kappa_c$ is the number of connected components of the boundary of~$c$.
-Two consecutive wiggly arcs along the boundary of~$c$ define a \defn{corner} (resp.~a \defn{hinge}) of~$c$ if they bound a convex (resp.~concave) angle of~$c$.
-Note that two corners of~$c$ can coincide at the same point~$i \in [n]$.
-%The \defn{concave chains} of~$c$ are the maximal sequences of wiggly arcs on the external boundary of~$c$ connected by hinges of~$c$.
-\end{definition}
-
-\begin{remark}
-\label{rem:degree}
-Consider a wiggly cell~$c$ in a wiggly pseudodissection~$D$.
-Note that~$\beta_c$ is always even as the arcs of~$D$ are pairwise pointed, so that~$\beta_c/2$ is an integer.
-Moreover, we have~$\beta_c \ge 2$ and~$\kappa_c \ge 1$, where at least one of the two inequalities is strict (as otherwise, the two wiggly arcs bounding~$c$ would coincide).
-%We conclude that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$.
-We thus obtain on the one hand that~$\delta_c = \beta_c/2+2\kappa_c-1 \ge 3$ with equality if and only if~$\beta_c = 4$ and~$\kappa_c = 1$, and on the other hand that~$\beta_c/2+\kappa_c-1 \ge 2$.
-\end{remark}
-
-\begin{definition}
-A \defn{wiggly pseudotriangle} (resp.~\defn{pseudoquadrangle}) is a wiggly cell of degree~$3$ (resp.~$4$).
-\end{definition}
-
-\begin{remark}
-\label{rem:descriptionPseudotrianglesPseudoquadrangles}
-As illustrated in \cref{fig:pseudotriangles}, a wiggly pseudotriangle~$t$ has no point in its interior and $4$ points on its boundary, $3$ corners and $1$ hinge (two corners can coincide at the same point~$i \in [n]$).
-%Hence, it has two corners oriented in the same direction, which we call the \defn{twin corners}.
-As illustrated in \cref{fig:pseudoquadrangles}, a wiggly pseudoquadrangle~$q$ can have
-\begin{enumerate}
-\item either one point in its interior and~$2$ points on its boundary, both corners,
-\item or no point in its interior and $6$ points on its boundary, $4$ corners and $2$ hinges (two corners can coincide at the same point~$i \in [n]$).
-We then distinguish three situations, depending on the position of the two pairs~$p, p'$ of wiggly arcs incident to the two hinges of~$c$, as illustrated in \cref{fig:pseudoquadrangles} (where~$p$ and~$p'$ are colored in red and orange):
-\begin{enumerate}[(a)]
-\item those where $p$ and $p'$ are not consecutive along~$c$, and do not overlap vertically,
-\item those where $p$ and $p'$ are not consecutive along~$c$, but overlap vertically,
-\item those where~$p$ and~$p'$ are consecutive along~$c$.
-\end{enumerate}
-\end{enumerate}
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{pseudotriangles}}
-\caption{Four wiggly pseudotriangles.}
-\label{fig:pseudotriangles}
-\end{figure}
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{pseudoquadrangles}}
-\vspace{-.3cm}
-\caption{Four types of wiggly pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
-\label{fig:pseudoquadrangles}
-\end{figure}
-\end{remark}
-
-\begin{proposition}
-\label{prop:wigglyPseudotriangulations}
-Any wiggly pseudodissection~$D$ contains at most~$2n-1$ internal wiggly arcs and at most~$n$ wiggly cells.
-Moreover, the following assertions are equivalent:
-\begin{enumerate}[(i)]
-\item all wiggly cells of~$D$ are wiggly pseudotriangles,
-\item $D$ contains~$n$ wiggly cells and is connected,
-\item $D$ contains $2n-1$ internal wiggly arcs,
-\item $D$ is an inclusion maximal wiggly pseudodissection.
-\end{enumerate}
-We then say that~$D$ is a \defn{wiggly pseudotriangulation}.
-\end{proposition}
-
-\begin{proof}
-Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components (where $D$ is viewed as the edge set of the graph with vertex set given by the marked points $0$ to $n+1$).
-Euler's formula gives~$(n+2)-(\iota+2)+(\gamma+1)=(\kappa+1)$, hence~$n - \iota + \gamma = \kappa$.
-Moreover, denoting by~$C$ the set of wiggly cells of~$D$, we have~$\sum_{c \in C} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$ (we count a wiggly arc~$\alpha$ with multiplicity~$2$ if it appears twice along the boundary of~$c$), and~${\sum_{c \in C} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus obtain that~$2\gamma \le \sum_{c \in C} (\beta_c/2+\kappa_c-1) = \iota+\kappa = n+\gamma$.
-We conclude that~$\gamma \le n$ and~$\iota = n+\gamma-\kappa \le 2n-1$.
-
-%Consider a wiggly pseudodissection~$D$ with~$\iota$ internal wiggly arcs, $\gamma$ wiggly cells, and~$\kappa$~connected components.
-%Observe that~$\sum_{c \in C} \beta_c/2 = 1+\iota$ since each external (resp.~internal) wiggly arc bounds precisely one (resp.~two) wiggly cell of~$D$, and that~${\sum_{c \in C} \big( \kappa_c-1 \big) = \kappa-1}$ since the boundary of each internal connected component of~$D$ is one of the internal connected components of the boundary of precisely one wiggly cell of~$D$.
-%As~$2 \le \beta_c/2+\kappa_c-1$ for any wiggly cell~$c$ by \cref{rem:degree}, we thus get~$2 \gamma \le \sum_{c \in C} (\beta_c/2+\kappa_c-1) = \iota+\kappa$.
-%As~$D$ is a planar graph with~$v = n+2$ vertices, $e = \iota+2$ edges, $f = 1+\gamma$ faces, and $\kappa$ connected components, Euler's formula~$1+\kappa = v-e+f$ yields~$2(1+\kappa) = 2(n+2)-2(\iota+2)+2(1+\gamma) \le 2n-2\iota+2+\iota+\kappa$, so that~$\iota \le 2n-\kappa \le 2n-1$ and~$\gamma \le (\iota+\kappa)/2 \le n$.
-
-To prove the second part of the statement, we show that~(i) $\Rightarrow$ (ii) $\Rightarrow$ (iii) $\Rightarrow$ (iv) $\Rightarrow$ (i).
-
-\para{(i) $\Rightarrow$ (ii)}
-For any wiggly cell~$c$, we have~$\delta_c = 3$, so that~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}, hence~$2 = \beta_c/2+\kappa_c-1$.
-Therefore~$\kappa = 1$ ($D$ is connected) and~$2\gamma = \iota+1 = n+\gamma$, so that~$\gamma=n$.
-
-\para{(ii) $\Rightarrow$ (iii)}
-As $\gamma=n$ and~$\kappa=1$, we have~$\iota = n+\gamma-\kappa = 2n-1$.
-
-%\para{(i) $\Rightarrow$ (ii)}
-%We have~$\delta_c = 3$ for any wiggly cell~$c$.
-%Hence~$\beta_c = 4$ and~$\kappa_c = 1$ by \cref{rem:degree}.
-%Therefore~$2\gamma = \iota+1$ and~$\kappa = 1$ (so that~$D$ is connected).
-%Applying Euler's formula as before, we get~$2 = (n+2)-(\iota+2)+(1+\gamma) = n-\gamma+2$, so that~$\gamma=n$.
-%
-%\para{(ii) $\Rightarrow$ (iii)}
-%As $\gamma=n$ and~$\kappa=1$, we have~$2n = 2\gamma \le \iota+\kappa = \iota+1$, so that~$\iota = 2n-1$.
-
-\para{(iii) $\Rightarrow$ (iv)}
-If~$D$ already contains~$2n-1$ internal wiggly arcs, it has maximal cardinality among all wiggly pseudodissections, hence it is certainly inclusion maximal.
-
-\para{(iv) $\Rightarrow$ (i)}
-We now consider a wiggly pseudodissection~$D$ containing a wiggly cell~$c$ which is not a wiggly pseudotriangle, and we prove that~$D$ is not inclusion maximal.
-%
-Assume first that the external boundary of~$c$ is a digon bounded by the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i, j, A', B')$.
-Denote by~$m$ the maximum of the points~$(A \symdif A') \cup (B \symdif B')$ located inside this digon (where~$\symdif$ denotes the symmetric difference).
-Then the wiggly arc~$\beta \eqdef \big( i, m, {]i,m[} \cap (A \cup A'), {]i,m[} \cap (B \cap B') \big)$ is compatible with~$D$ (any wiggly arc incompatible with~$\beta$ crosses~$\alpha$ or~$\alpha'$) and is not in~$D$ (it connects the boundary of~$c$ with one of its internal connected components).
-%Indeed, for any wiggly arc~$\gamma \eqdef (k, \ell, X, Y)$ inside~$c$, we have
-%\begin{itemize}
-%\item $i < k < \ell \le m$ so that~$\beta$ and~$\gamma$ are pointed,
-%\item $Y \subseteq {]i,m[} \cap B \cap B'$ so that~$\beta$ and~$\gamma$ are non-crossing.
-%\end{itemize}
-
-Assume now that the external boundary of~$c$ is a not digon.
-Consider a hinge~$j$ of~$c$.
-Assume by symmetry that the boundary of~$c$ contains two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j, A', B')$, such that~$\alpha$ is below~$\alpha'$.
-% (\ie $k \in A'$ or~$k' \in B$).
-Let~$\gamma \eqdef (k, \ell, X, Y)$ denote the uppermost wiggly arc of the boundary of~$c$ such that~$j \in Y$ (it exists since~$j$ is a  hinge of~$c$), and let~$X' \eqdef {]j,\ell[} \cap X$ and~$Y' \eqdef {]j,\ell[} \cap Y$.
-Then the two wiggly arcs~$\beta \eqdef \big( i, \ell, A \cup X', B \cup \{j\} \cup Y')$ and~$\beta' \eqdef \big( i', \ell, A'  \cup \{j\} \cup X', B \cup Y')$ are both compatible with~$D$ (any wiggly arc incompatible with~$\beta$ is incompatible with~$\alpha$ or~$\gamma$, and similarly for~$\beta'$) and cannot both belong to~$D$ (otherwise, $c$ would be a wiggly pseudotriangle bounded by~$\alpha, \alpha', \gamma', \gamma$).
-\end{proof}
-
-\pagebreak
-\begin{remark}
-Note that in the proof of \cref{prop:wigglyPseudotriangulations}, we actually obtained that
-\[
-\sum_{c \in C} (\delta_c-3) = \sum_{c \in C} \beta_c/2 + 2 \sum_{c \in C} (\kappa_c-1) - 2\gamma = (1+\iota) + 2(\kappa-1) - 2(\iota+\kappa-n) = 2n-1-\iota.
-\]
-\end{remark}
-
-\begin{example}
-\label{exm:allSmallWigglyPseudotriangulations}
-For~$n = 1$, the $2$ wiggly pseudotriangulations of $3$ points are \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation1}}} and \smash{\raisebox{-.3cm}{\includegraphics[scale=.8]{wigglyPseudotriangulation2}}}.
-For~${n = 2}$, the $14$ wiggly pseudotriangulations of $4$ points are \\[.2cm]
-\centerline{\includegraphics[scale=.8]{wigglyPseudotriangulations}}
-\end{example}
-
-\begin{example}
-\label{exm:specialWigglyPseudotriangulations}
-The following wiggly pseudotriangulations are illustrated in \cref{fig:specialWigglyPseudotriangulations}:
-\begin{align*}
-T_\downarrow & \eqdef \set{(i-1, n+1, \varnothing, {[i,n]})}{i \in [n+1]} \cup \set{(0, n+1, [i], {]i,n]})}{i \in [n]}, \\
-T_\uparrow & \eqdef \set{(0, i, \varnothing, {[i-1]})}{i \in [n+1]} \cup \set{(0, n+1, {]i,n]}, [i])}{i \in [n]}, \\
-T_\leftarrow & \eqdef \{(0, 1, \varnothing, \varnothing)\} \cup \set{(0, i+1, \varnothing, [i])}{i \in [n]} \cup \set{(0, i+1, [i], \varnothing)}{i \in [n]}, \\
-T_\rightarrow & \eqdef \{(n, n+1, \varnothing, \varnothing)\} \cup \set{(i-1, n+1, \varnothing, [i,n])}{i \in [n]} \cup \set{(i-1, n+1, [i,n], \varnothing)}{i \in [n]}.
-\end{align*}
-%
-\begin{figure}[h]
-\centerline{\includegraphics[scale=1.3]{specialWigglyPseudotriangulations}}
-\caption{The wiggly pseudotriangulations~$T_\downarrow$ (left), $T_\uparrow$ (middle left), $T_\leftarrow$ (middle right), and $T_\rightarrow$ (right) of \cref{exm:specialWigglyPseudotriangulations} for~$n = 7$.}
-\label{fig:specialWigglyPseudotriangulations}
-\end{figure}
-\end{example}
-
-\begin{remark}
-\label{rem:numberWigglyPseudotriangulations}
-The number~$wp_n$ of wiggly pseudotriangulations of~$n+2$ points is given by
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
-\hline
-wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
-\end{array}
-\]
-To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ \defn{final} internal wiggly arcs (\ie ending at the last point~$n+1$).
-For instance,
-\begin{align*}
-%	wp_0(x) & = 1, \\
-	wp_1(x) & = x + 1, \\
-	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-\end{align*}
-We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPseudotriangulations}.
-We use this additional variable~$x$ to obtain a recursive formula for~$wp_n(x)$.
-%Indeed, any wiggly pseudotriangulation on~$n+1$ points can be obtained from a wiggly pseudotriangulation on~$n+2$ points by collapsing the points~$n$ and~$n+1$.
-Indeed, any wiggly pseudotriangulation of~$n+2$ points can be obtained from a wiggly pseudotriangulation of~$n+1$ points by inserting a single wiggly pseudotriangle with a hinge at~$n$.
-%There are two kinds of wiggly pseudotriangulations of~$n+2$ points:
-%\begin{itemize}
-%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
-%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
-%\end{itemize}
-Each wiggly pseudotriangulation of~$n+1$ points with $i$ final internal wiggly arcs contributes to:
-\begin{itemize}
-\item $i+2$ wiggly pseudotriangulations of~$n+2$ points with $i+2$ final internal wiggly arcs, containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,
-\item $j+1$ wiggly pseudotriangulations of~$n+2$ points with $j$ final internal wiggly arcs, not containing the wiggly arc~$(n, n+1, \varnothing, \varnothing)$,  for all~$0 \le j \le i+1$.
-\end{itemize}
-\pagebreak
-\cref{fig:pseudotriangulationsCounting} illustrates this decomposition.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{pseudotriangulationCounting}}
-\caption{Some wiggly pseudotriangulations of~$7$ points obtained from the top left wiggly pseudotriangulation of~$6$ points by inserting a wiggly pseudotriangle with hinge at~$5$ as described in \cref{rem:numberWigglyPseudotriangulations}.
-Those on the first line contain the wiggly arc~$(5, 6, \varnothing, \varnothing)$ and are thus obtained by inserting the head of the wiggly pseudotriangle with hinge at~$5$ in one of the final wiggly arcs.
-Those on the second line do not contain the wiggly arc~$(5, 6, \varnothing, \varnothing)$ and are thus obtained by inserting the two legs of the wiggly pseudotriangle with hinge at~$5$ in two of the final wiggly arcs.
-The coloring of the wiggly arcs is supposed to help visualizing in which wiggly arcs the head or legs of the new wiggly pseudotriangle were inserted.}
-\label{fig:pseudotriangulationsCounting}
-\end{figure}
-%
-This translates to the recursive formula %for all~$n \ge 1$,
-\begin{align*}
-wp_{n}(x) & = \overbracket[.5pt]{x \cdot \frac{\partial}{\partial x} \big( x^2 wp_{n-1}(x) \big)}^{\substack{\text{wiggly pseudotriangulations} \\ \text{containing } (n, n+1, \varnothing, \varnothing)}} + \overbracket[.5pt]{\frac{\partial}{\partial x}\Big( \smash{\frac{wp_{n-1}(1)-x^3wp_{n-1}(x)}{1-x}} \Big)}^{\substack{\qquad\; \text{wiggly pseudotriangulations} \qquad\;  \\ \text{not containing } (n, n+1, \varnothing, \varnothing)}} \\
-& = \frac{1}{(1 - x)^2} \big( wp_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) wp_{n-1}(x) + x^4 (x - 1) wp_{n-1}’(x) \big).
-\end{align*}
-This enables us to quickly compute~$wp_n(x)$ and we obtain the numbers of wiggly pseudotriangulations~$wp_n$ by evaluating~$wp_n(x)$ at~$x = 1$.
-%This enables us to quickly compute the generating series of the number of wiggly pseudotriangulations
-%\[
-%\sum_{n \ge 0} wp_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
-%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
-%\dots
-%\]
-\end{remark}
-
-Our next statement prepares for the definition of flips in wiggly pseudotriangulations, and is illustrated in \cref{fig:diagonalsPseudoquadrangles}.
-
-\begin{definition}
-A \defn{wiggly diagonal} of a wiggly cell~$c$ is a wiggly arc inside~$c$ and compatible with all wiggly arcs of~$c$.
-\end{definition}
-
-\begin{proposition}
-\label{prop:diagonalsPseudoquadrangle}
-Any wiggly pseudoquadrangle has exactly two wiggly diagonals.
-Moreover, these two wiggly diagonals either cross precisely once, or are non pointed.
-\end{proposition}
-
-\begin{proof}
-Depending on the four types of pseudoquadrangles described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}:
-\begin{enumerate}
-\item the two diagonals are the two wiggly arcs inside~$q$, incident to the point in the interior~of~$q$,
-\item[(2a)] the two diagonals connect the two pairs of opposite corners of~$q$,
-\item[(2b)] one of two diagonals connects two opposite corners of~$q$ while the other connects the two hinges~of~$q$,
-\item[(2c)] one of the diagonals connects two opposite corners of~$q$ while the other connects an hinge of~$q$ to a corner of~$q$.
-\end{enumerate}
-See \cref{fig:diagonalsPseudoquadrangles} where the two diagonals appear in red and orange.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{diagonalsPseudoquadrangles}}
-\caption{The two diagonals in each of the four types of wiggly pseudoquadrangles.} % described in \cref{rem:descriptionPseudotrianglesPseudoquadrangles}.}
-\label{fig:diagonalsPseudoquadrangles}
-\end{figure}
-%Let~$q$ be a wiggly pseudoquadrangle.
-%We distinguish two situations depending on~$\kappa(q)$:
-%\begin{description}
-%\item[$\kappa(q) = 1$] Then the boundary of~$c$ is a single wiggly hexagon, so that it has~$4$ concave points. We distinguish again two situations:
-%	\begin{description}
-%	\item 
-%	\end{description}
-%\item[$\kappa(q) = 2$] Then~$q$ is a digon bounded by two wiggly arcs~$(i, k, A, B \cup \{j\})$ and~$(i, k, A \cup \{j\}, B)$ for some~$1 < i < j < k \le n$ and~$A \sqcup B = {]i,j[} \cup{]j,k[}$.
-Hence, the only two wiggly arcs in the interior of~$q$ are~$(i, j, {]i,j[} \cap A, {]i,j[} \cap B)$ and~$(j, k, {]j,k[} \cap A, {]j,k[} \cap B)$, which are both compatible with~$q$ and are not pointed.
-%\end{description}
-\end{proof}
-
-%\vincent{Asilata has an alternative description of the flip...}
-
-We are now ready to consider the wiggly flip graph and the wiggly complex.
-The following definition is illustrated in \cref{fig:wigglyComplex}\,(right) when~$n = 2$.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.1]{wigglyComplex}}
-\caption{The wiggly complex~$\wigglyComplex_2$ (left) and the wiggly flip graph~$\wigglyFlipGraph_2$ (right).
-We have embedded the wiggly complex~$\wigglyComplex_2$ in the plane, so that all triangles (including the external one) form a face of~$\wigglyComplex_2$.}
-\label{fig:wigglyComplex}
-\end{figure}
-
-\begin{definition}
-\label{def:wigglyFlipGraph}
-The \defn{wiggly flip graph}~$\wigglyFlipGraph_n$ is the graph with a vertex for each wiggly pseudotriangulation, and with an edge between two wiggly pseudotriangulations~$T$ and~$T'$ if there are wiggly arcs~$\alpha \in T$ and~$\alpha' \in T'$ such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-\end{definition}
-
-\begin{proposition}
-\label{prop:wigglyFlipGraph}
-The wiggly flip graph~$\wigglyFlipGraph_n$ is regular of degree~$2n-1$ and connected.
-\end{proposition}
-
-\begin{proof}
-Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
-Then~${Q \eqdef T \ssm \{\alpha\}}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
-By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, namely $\alpha$ and another one~$\alpha'$.
-As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
-We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
-This shows that any internal wiggly arc in any wiggly pseudotriangulation can be flipped, hence that the wiggly flip graph is regular of degree~$2n-1$ by \cref{prop:wigglyPseudotriangulations}\,(iii).
-
-There are various possible proofs for the connectedness.
-For instance, it will follow easily from \cref{prop:bijection}.
-To avoid relying on this forward reference, we sketch an alternative direct proof by induction on~$n$.
-We claim that if a wiggly pseudotriangulation has a non-zero number of final internal wiggly arcs (\ie ending at the last point~$n+1$), then at least one of them can be flipped to a non-final wiggly arc.
-This implies that any wiggly pseudotriangulation can be transformed by flips to a wiggly pseudotriangulation with no final internal wiggly arc.
-All wiggly pseudotriangulations with no final internal wiggly arc contain the arcs~$(0,n,\varnothing,[n-1])$ and~$(0,n,[n-1],\varnothing)$, since the latter are compatible with all internal wiggly arcs but the final ones.
-Hence, they induce a subgraph of~$\wigglyFlipGraph_n$ isomorphic to~$\wigglyFlipGraph_{n-1}$, which is connected by induction.
-We conclude that~$\wigglyFlipGraph_n$ is itself connected.
-
-To see the claim, let~$i$ be maximal such that~$T$ contains two distinct wiggly arcs starting at~$i$ and ending at~$n+1$ (it is well-defined as we have the external wiggly arcs~$\alpha_\mathrm{top}$ and~$\alpha_\mathrm{bot}$ for~$i = 0$).
-Consider a final internal wiggly arc~$\alpha$ of~$T$ starting weakly after~$i$, and let~$\alpha'$ be the wiggly arc obtained by flipping~$\alpha$ in~$T$.
-If~$\alpha'$ is final, then by~\cref{prop:diagonalsPseudoquadrangle}, at least one pseudotriangle~$t$ of~$T$ incident to~$\alpha$ has two corners at~$n+1$.
-Let~$h$ be the hinge of~$t$ and~$\beta, \beta'$ be the two wiggly arcs of~$t$ joining~$h$ to~$n+1$.
-As~$i < h \le n$ the maximality of~$i$ imposes that~$\beta = \beta'$.
-Flipping $\beta = \beta'$ in~$T$ thus yields a wiggly arc ending at~$h \le n$, hence a non-final arc.
-\end{proof}
-
-We will also consider an oriented version of the wiggly flip graph~$\wigglyFlipGraph_n$.
-The following definition is illustrated in \cref{fig:incompatible2}.
-
-\begin{definition}
-\label{def:wigglyIncreasingFlipGraph}
-Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two wiggly arcs and~$T$ and~$T'$ be two wiggly pseudotriangulations, such that~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-We say that the flip from~$T$ to~$T'$ is \defn{increasing} if 
-\begin{itemize}
-\item $\alpha$ starts where~$\alpha'$ ends (that is, $i = j'$), or 
-\item $\alpha$ crosses~$\alpha'$ from north-west to south-east (that is, there exists~$1 \le k < \ell \le n$ such that $k \in (A \cap B') \cup (\{i\} \cap B') \cup (A \cap \{i'\})$ and~$\ell \in (A' \cap B) \cup (\{j'\} \cap B) \cup (A' \cap \{j\})$).
-\end{itemize}
-The \defn{wiggly increasing flip graph}~$\wigglyIncreasingFlipGraph_n$ is the directed graph with a vertex for each wiggly pseudotriangulation and an edge for each increasing~flip.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{incompatible2}}
-\caption{The wiggly arcs~$\alpha$ and~$\alpha'$ of \cref{def:wigglyIncreasingFlipGraph}.}
-\label{fig:incompatible2}
-\end{figure}
-\end{definition}
-
-We will need the following observation about exchangeable arcs, illustrated in \cref{fig:incompatible3}.
-
-\begin{proposition}
-\label{prop:uerp}
-Let~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ be two exchangeable wiggly arcs.
-Then any wiggly arc compatible with both~$\alpha$ and~$\alpha'$ is also compatible with the wiggly~arcs:
-\begin{itemize}
-\item $\beta \eqdef (i, j', A \cup A', B \cup B' \cup \{j\})$ and~$\beta' \eqdef (i, j', A \cup A' \cup \{j\}, B \cup B')$ if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$,
-(In other words, ~$\beta$ and~$\beta'$ are the two wiggly arcs starting at~$\min(i,i')$ and ending at~$\max(j,j')$ which follow $\alpha$ on~$]i,j[$ and~$\alpha'$ on~$]i',j'[$.)
-\item $\beta \eqdef \big( i', j, {]i,j'[} \ssm (B \cup B'), {]i,j'[} \cap (B \cup B') \big)$ and~$\beta' \eqdef \big( i, j', {]i',j[} \cap (A \cup A'), {]i',j[} \ssm (A \cup A') \big)$ if~$\alpha$ and~$\alpha'$ are crossing and $\alpha$ crosses~$\alpha'$ from north-west to south-east.
-(In other words, $\beta$ is the wiggly arc starting at~$i'$ and ending at~$j$ which follows the lower hull of~$\alpha$ and~$\alpha'$, and~$\beta'$ is the wiggly arc starting at~$i$ and ending~at~$j'$ which follows the upper hull of~$\alpha$ and~$\alpha'$.)
-\end{itemize}
-%See \cref{fig:incompatible3} for illustrations.
-(By exchanging~$\alpha$ and~$\alpha'$, similar statements hold if~$\alpha$ and~$\alpha'$ are non pointed with~$j = i'$, or if~$\alpha$ crosses~$\alpha'$ from south-east to north-west.)
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.3]{incompatible3}}
-\caption{The wiggly arcs~$\beta$ and~$\beta'$ of \cref{prop:uerp}.}
-\label{fig:incompatible3}
-\end{figure}
-\end{proposition}
-
-\begin{proof}
-Any wiggly arc non pointed with~$\beta$ would be non pointed with~$\alpha$ or~$\alpha'$ (as the endpoints of~$\beta$ are endpoints of~$\alpha$ or~$\alpha'$).
-Any wiggly arc crossing~$\beta$ would be either non pointed or crossing~$\alpha$ or~$\alpha'$ (as~$\beta$ follows~$\alpha$ or~$\alpha'$, except at the point~$j = i'$ in the first situation).
-\end{proof}
-
-Finally, we define the wiggly complex~$\wigglyComplex_n$, illustrated in \cref{fig:wigglyComplex}\,(left) when~$n = 2$.
-
-\begin{definition}
-\label{def:wigglyComplex}
-The \defn{wiggly complex}~$\wigglyComplex_n$ is the simplicial complex of pairwise pointed and non-crossing subsets of internal wiggly arcs.
-In other words, it is the clique complex of the compatibility graph on internal wiggly arcs.
-\end{definition}
-
-\begin{proposition}
-The wiggly complex~$\wigglyComplex_n$ is a flag $(2n-1)$-dimensional pseudomanifold without boundary.
-\end{proposition}
-
-\begin{proof}
-It is a flag simplicial complex because it is a clique complex.
-It is pure of dimension $2n-1$ by the implication (iv) $\Rightarrow$ (iii) of \cref{prop:wigglyPseudotriangulations}.
-Finally, it is a pseudomanifold without boundary by \cref{prop:wigglyFlipGraph}.
-\end{proof}
-
-\begin{remark}
-$\wigglyComplex_1$ contains two isolated points.
-$\wigglyComplex_2$ is a simplicial $3$-dimensional associahedron (this coincidence fails for~$n > 2$).
-Here are the first few $f$-vectors:
-\begin{align*}
-f(\wigglyComplex_1) & = (1, 2), \\
-f(\wigglyComplex_2) & = (1, 9, 21, 14), \\
-f(\wigglyComplex_3) & = (1, 24, 154, 396, 440, 176), \\
-f(\wigglyComplex_4) & = (1, 55, 729, 4002, 10930, 15684, 11312, 3232), \\
-f(\wigglyComplex_5) & = (1, 118, 2868, 28110, 140782, 400374, 673274, 662668, 352728, 78384),
-\intertext{and the first few $h$-vectors:}
-h(\wigglyComplex_1) & = (1, 1), \\
-h(\wigglyComplex_2) & = (1, 6, 6, 1), \\
-h(\wigglyComplex_3) & = (1, 19, 68, 68, 19, 1), \\
-h(\wigglyComplex_4) & = (1, 48, 420, 1147, 1147, 420, 48, 1), \\
-h(\wigglyComplex_5) & = (1, 109, 1960, 11254, 25868, 25868, 11254, 1960, 109, 1).
-\end{align*}
-Note that the number of vertices and facets of~$\wigglyComplex_n$ were already discussed in \cref{rem:numberWigglyArcs,rem:numberWigglyPseudotriangulations}.
-\end{remark}
-
-%\begin{remark}
-%Note that the number of vertices of~$\wigglyComplex_n$ is the number~$\sum_{j = 0}^n 2^j (n+1-j)$ of wiggly arcs on~$n+2$ points.
-%The number of facets of~$\wigglyComplex_n$ is the number of wiggly pseudotriangulations of~$n+2$ points, which is a bit harder to compute.
-%For this, denote by $f_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly pseudotriangulations of~$n+2$ points with~$i$ internal wiggly arcs ending at the last point~$n+1$.
-%For instance,
-%\begin{align*}
-%	f_0(x) & = 1, \\
-%	f_1(x) & = x + 1, \\
-%	f_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-%	f_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-%	f_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-%\end{align*}
-%We use this additional variable~$x$ to obtain a recursive formula for~$f_n(x)$, discussing on the wiggly pseudotriangle~$t_n$ with a hinge at~$n$.
-%Namely, there are two types of wiggly pseudotriangulations of~$n+2$ points:
-%\begin{itemize}
-%\item those with the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the position of the only corner of~$t_n$ which is not at~$n+1$,
-%\item those without the wiggly arc~$(n, n+1, \varnothing, \varnothing)$ are obtained from a wiggly pseudotriangulation of~$n+1$ points by choosing the positions of the two corners of~$t_n$ which are not at~$n+1$.
-%\end{itemize}
-%Hence we obtain for all~$n \ge 1$,
-%\[
-%f_{n}(x) = \frac{1}{(1 - x)^2} \big( f_{n-1}(1) + x^2 (2 x^2 - 2 x - 1) f_{n-1}(x) + x^4 (x - 1) f_{n-1}’(x) \big).
-%\]
-%This enables to quickly compute the generating series of the number of wiggly pseudotriangulations
-%\[
-%\sum_{n \ge 0} f_n(1) y^n = 1 + 2 y + 14 y^2 + 176 y^3 + 3232 y^4 + 78384 y^5 + 2366248 y^6 + 85534176 y^7 + 3602770400 y^8 + 
-%% 173300710720 y^9 + 9373542317760 y^10 + 563142033172480 y^11 + 37206559614499840 y^12 + 2681213937595142656 y^13 +
-%\dots
-%\]
-%\end{remark}
-
-\begin{remark}
-\label{rem:wigglyComplexAutomorphism}
-The vertical and horizontal reflections provide two obvious automorphisms of the wiggly complex~$\wigglyComplex_n$ (and thus of the wiggly flip graph~$\wigglyFlipGraph_n$).
-Moreover, the vertical reflection is an anti-automorphism of the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ (while the horizontal reflection is not).
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly permutations and the wiggly lattice}
-\label{subsec:wigglyPermutations}
-
-We now consider wiggly permutations of~$[2n]$, defined as follows.
-
-\begin{definition}
-\label{def:wigglyPermutation}
-A \defn{wiggly permutation} is a permutation of~$[2n]$ which avoids the patterns
-\begin{itemize}
-\item $(2j-1) \cdots i \cdots (2j)$ for~$j \in [n]$ and~$i < 2j-1$,
-\item $(2j) \cdots k \cdots (2j-1)$ for~$j \in [n]$ and~$k > 2j$.
-\end{itemize}
-\end{definition}
-
-\begin{example}
-\label{exm:allSmallWigglyPermutations}
-For~$n = 1$, the $2$ wiggly permutations of~$[2]$ are~$12$ and~$21$.
-For~$n = 2$, the $14$ wiggly permutations of~$[4]$ are
-\[
-1234, 1243, 1342, 1423, 1432, 2134, 2143, 3412, 3421, 4123, 4132, 4213, 4312, 4321.
-\]
-%The wiggly permutations of~$[6]$ are
-%\begin{gather*}
-%123456, 213456, 134256, 124356, 123564, 123465, 342156, 214356, 213564, 213465, 341256, 143256, \\
-%134562, 134265, 142356, 125643, 124365, 135642, 125634, 123654, 123645, 432156, 345621, 342165, \\
-%421356, 215643, 214365, 356421, 215634, 213654, 213645, 431256, 341562, 341265, 413256, 143562, \\
-%143265, 134652, 134625, 412356, 156423, 142365, 156243, 126543, 126435, 356412, 156342, 136542, \\
-%156234, 126534, 126354, 136425, 126345, 435621, 432165, 346521, 346215, 564213, 421365, 562143, \\
-%216543, 216435, 563421, 365421, 562134, 216534, 216354, 364215, 216345, 431562, 431265, 345612, \\
-%341652, 341625, 413562, 413265, 156432, 143652, 143625, 136452, 564123, 412365, 561423, 165423, \\
-%164235, 561243, 165243, 162543, 162435, 563412, 365412, 561342, 165342, 163542, 561234, 165234, \\
-%162534, 162354, 364125, 163425, 162345, 564321, 436521, 436215, 364521, 654213, 642135, 652143, \\
-%621543, 621435, 653421, 635421, 652134, 621534, 621354, 634215, 621345, 435612, 431652, 431625, \\
-%346512, 346152, 346125, 564132, 413652, 413625, 561432, 165432, 164352, 164325, 364152, 163452, \\
-%654123, 641235, 651423, 615423, 614235, 651243, 615243, 612543, 612435, 653412, 564312, 635412, \\
-%651342, 615342, 613542, 651234, 615234, 612534, 612354, 634125, 613425, 612345, 654321, 643521, \\
-%643215, 634521, 436512, 436152, 436125, 364512, 654132, 641352, 641325, 651432, 615432, 614352, \\
-%614325, 634152, 613452, 654312, 643125, 643512, 643152, 634512.
-%\end{gather*}
-\end{example}
-
-\begin{example}
-\label{exm:specialWigglyPermutations}
-The permutations
-\[
-\sigma_\downarrow \eqdef 1 2 \cdots (2n),
-\quad
-\sigma_\uparrow \eqdef (2n) \cdots 2 1,
-\quad
-\sigma_\leftarrow \eqdef (2n) \cdots 2 1 \cdots (2n-1),
-\quad
-\sigma_\rightarrow \eqdef 1 \cdots (2n-1) (2n) \cdots 2
-\]
-are wiggly permutations of~$[2n]$.
-\end{example}
-
-\begin{remark}
-\label{rem:numberWigglyPermutations}
-The number~$wp_n$ of wiggly permutations of~$[2n]$ is given by
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \dots \\
-\hline
-wp_n & 2 & 14 & 176 & 3232 & 78384 & 2366248 & 85534176 & 3602770400 & \dots
-\end{array}
-\]
-To compute~$wp_n$, denote by $wp_n(x)$ the polynomial where the coefficient of~$x^i$ is the number of wiggly permutations of~$[2n]$ with $i$ \defn{admissible gaps} (\ie gaps~$\gamma$ between two consecutive positions such that there is no~$j \in [n]$ such that the value~$2j$ appears before the gap~$\gamma$ while the value~$2j-1$ appears after the gap~$\gamma$).
-For instance,
-\begin{align*}
-%	wp_0(x) & = 1, \\
-	wp_1(x) & = x + 1, \\
-	wp_2(x) & = 3 x^3 + 5 x^2 + 4 x + 2, \\
-	wp_3(x) & = 15 x^5 + 35 x^4 + 44 x^3 + 40 x^2 + 28 x + 14, \\
-	wp_4(x) & = 105 x^7 + 315 x^6 + 520 x^5 + 630 x^4 + 620 x^3 + 514 x^2 + 352 x + 176.
-\end{align*}
-We invite the reader to check the expressions of~$wp_1(x)$ and~$wp_2(x)$ with \cref{exm:allSmallWigglyPermutations}.
-Any wiggly permutation of~$[2n]$ can be obtained from a wiggly permutation of~$[2n-2]$ by inserting the last values~$2n-1$ and~$2n$.
-Each wiggly permutation of~$[2n-2]$ with $i$ admissible gaps contributes to:
-\begin{itemize}
-\item $i+2$ wiggly permutations of~$[2n]$ with $i+2$ admissible gaps and where~$2n-1$ appears before~$2n$ (they must appear consecutively),
-\item $j+1$ wiggly permutations of~$[2n]$ with $j$ admissible gaps and where $2n$ appears before~$2n-1$, for all~$0 \le j \le i+1$.
-\end{itemize}
-For instance, the wiggly permutation~$78621354$ of~$[8]$ has admissible gaps~$\bullet 7 \bullet 8 \bullet 62135 \bullet 4 \bullet$ and thus gives rise to the wiggly permutations
-\[
-9\mathrm{X}78621354, \quad 79\mathrm{X}8621354, \quad 789\mathrm{X}621354, \quad 78621359\mathrm{X}4, \quad 786213549\mathrm{X}
-\]
-of~$[10]$ where the $9$ appears before~$10$, and the wiggly permutations
-\begin{align*}
-& \mathrm{X}978621354, \quad \mathrm{X}798621354, \quad \mathrm{X}789621354, \quad \mathrm{X}786213594, \quad \mathrm{X}786213549, \\
-& 7\mathrm{X}98621354, \quad 7\mathrm{X}89621354, \quad 7\mathrm{X}86213594, \quad 7\mathrm{X}86213549, \quad 78\mathrm{X}9621354, \\
-& 78\mathrm{X}6213594, \quad 78\mathrm{X}6213549, \quad 7862135\mathrm{X}94, \quad 7862135\mathrm{X}49, \quad 78621354\mathrm{X}9
-\end{align*}
-of~$[10]$ where the $10$ appears before~$9$ (for brievety, we have replaced $10$ by $\mathrm{X}$ in the permutations).
-We thus obtain the same recursive equation on~$wp_n(x)$ as in \cref{rem:numberWigglyPseudotriangulations}.
-\end{remark}
-
-Recall that the \defn{inversion set} and \defn{non-inversion set} of a permutation~$\sigma$ of~$[2n]$ are the sets
-\begin{align*}
-\inv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) > \sigma(j)}, \\
-\ninv(\sigma) & \eqdef \set{\big( \sigma(i), \sigma(j) \big)}{1 \le i < j \le 2n \text{ and } \sigma(i) < \sigma(j)}.
-\end{align*}
-Note that~$\inv(\sigma)$ and~$\ninv(\sigma)$ are transitive: $\{(c,b), (b,a)\} \subseteq \inv(\sigma)$ implies~$(c,a) \in \inv(\sigma)$ for all~${1 \le a < b < c \le 2n}$, and similarly for~$\ninv$.
-The inversion sets of wiggly permutations are characterized as follows.
-
-\begin{lemma}
-\label{lem:inversionSetsWigglyPermutations}
-A permutation~$\sigma$ of~$[2n]$ is a wiggly permutation if and only if for all~$j \in [n]$,
-\begin{itemize}
-\item $(2j-1, i) \in \inv(\sigma)$ implies $(2j, i) \in \inv(\sigma)$ for all~$i < 2j-1$, and
-\item $(k, 2j-1) \in \inv(\sigma)$ implies $(k, 2j) \in \inv(\sigma)$ for all~$k > 2j$.
-\end{itemize}
-A similar characterization holds for~$\ninv(\sigma)$ by exchanging~$2j-1$ and~$2j$.
-\end{lemma}
-
-\begin{proof}
-Immediate as it corresponds to the pattern avoidance description of \cref{def:wigglyPermutation}.
-\end{proof}
-
-The (left) \defn{weak order} on permutations of~$[2n]$ is defined as the inclusion order of their inversion sets (or equivalently, the reverse inclusion of their non-inversion sets).
-Its cover relations are given by the exchanges of two entries at consecutive positions.
-It is a (congruence uniform) lattice, and the join and meet satisfy
-\[
-\inv(\sigma \join \tau) = \big( \inv(\sigma) \cup \inv(\tau) \big)^\textrm{tc}
-\qquad\text{and}\qquad
-\ninv(\sigma \meet \tau) = \big( \ninv(\sigma) \cup \ninv(\tau) \big)^\textrm{tc}
-\]
-where~$X^\mathrm{tc}$ denotes the transitive closure of~$X$.
-
-The following statements are illustrated on \cref{fig:wigglyLattice}\,(right) when~${n = 2}$.
-%
-\begin{figure}
-\centerline{\includegraphics[scale=1.1]{wigglyLattice}}
-\caption{The wiggly lattice~$\wigglyLattice_2$ on wiggly pseudotriangulations (left) and on wiggly permutations (right).}
-\label{fig:wigglyLattice}
-\end{figure}
-
-\begin{proposition}
-The wiggly permutations induce a sublattice of the weak order on permutations of~$[2n]$, that we call the \defn{wiggly lattice}~$\wigglyLattice_n$.
-\end{proposition}
-
-\begin{proof}
-Consider two wiggly permutations~$\rho$ and~$\sigma$ of~$[2n]$, and let~$\tau = \rho \join \sigma$.
-Assume that there is~$1 \le i < 2j-1 < 2n$ such that~$(2j-1, i) \in \inv(\tau)$.
-As $\inv(\tau) = \big( \inv(\rho) \cup \inv(\sigma) \big)^\textrm{tc}$, there exist~$i \le i' < 2j-1$ such that~$(i', i) \in \inv(\tau)$ and~$(2j-1, i') \in \inv(\rho) \cup \inv(\sigma)$.
-Since~$\rho$ and~$\sigma$ are wiggly permutations, we obtain by \cref{lem:inversionSetsWigglyPermutations} that~$(2j, i') \in \inv(\rho) \cup \inv(\sigma) \subseteq \inv(\tau)$.
-As~$(i', i) \in \inv(\tau)$ and~$(2j, i') \in \inv(\tau)$ and~$\inv(\tau)$ is transitive, we conclude that~$(2j,i) \in \inv(\tau)$.
-A similar argument shows that~$(k, 2j-1) \in \inv(\tau)$ implies~$(k, 2j) \in \inv(\tau)$ for all~$1 < 2j < k \le 2n$.
-By \cref{lem:inversionSetsWigglyPermutations}, we conclude that~$\tau = \rho \join \sigma$ is a wiggly permutation.
-The proof is similar for~$\rho \meet \sigma$, using $\ninv$ instead of~$\inv$.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyLatticeAntiIsomorphism}
-The map~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_n)$ obviously provides an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$.
-\end{remark}
-
-We now aim at describing the cover relations of the wiggly lattice.
-Recall that an \defn{ascent} (resp.~\defn{descent}) in a permutation~$\sigma$ is a position~$j$ such that~$\sigma(j) < \sigma(j+1)$ (resp.~$\sigma(j) > \sigma(j+1)$).
-
-\begin{lemma}\label{lem:wigglyCoverRelation}
-Consider an ascent~$j$ of a wiggly permutation~$\sigma$ of~$[2n]$.
-Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
-Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
-Then
-\[
-\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n).
-\]
-is the minimal wiggly permutation such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\sigma^j)$.
-\end{lemma}
-
-\begin{proof}
-We start with a few observations.
-Let~$i < p \le j$ (resp.~$j+1 \le q < k$).
-As~$\sigma$ is a wiggly permutation, we have~$\sigma(p) < \sigma(i)$ (resp.~$\sigma(q) > \sigma(k)$).
-Hence~$\big( \sigma(i), \sigma(p) \big)$ (resp.~$\big( \sigma(q), \sigma(k) \big)$) belongs to~$\inv(\sigma)$.
-Moreover, since~$j$ is an ascent of~$\sigma$, we obtain that~$\sigma(p) < \sigma(q)$ for all~${i \le p \le j < q \le k}$.
-Hence, $\inv(\sigma^j) = \inv(\sigma) \cup \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}$.
-
-We now prove that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$.
-We consider~$v \in [n]$ and~$u < 2v-1$ such that~$(2v-1, u) \in \inv(\sigma^j)$, and we show that~$(2v, u) \in \inv(\sigma^j)$.
-If~$(2v, u) \in \inv(\sigma)$, we are done as~$\inv(\sigma) \subset \inv(\sigma^j)$.
-If~$(2v, u) \not\in \inv(\sigma)$, then~$(2v-1, u) \not\in \inv(\sigma)$ by \cref{lem:inversionSetsWigglyPermutations}, and~$i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v-1) \le k$ since~${\inv(\sigma^j) \ssm \inv(\sigma) = \bigset{ \big( \sigma(q), \sigma(p) \big) }{i \le p \le j < q \le k}}$.
-We have~$\sigma^{-1}(2v) \le k$ since~$\sigma$ is a wiggly permutation.
-As~$(2v, u) \not\in \inv(\sigma)$ and~$\sigma(p) < \sigma(q)$ for all~$i \le p \le j < q \le k$, we conclude that~$j < \sigma^{-1}(2v) < k$.
-Hence, we obtain that ${i \le \sigma^{-1}(u) \le j < \sigma^{-1}(2v) \le k}$, so that~$(2v,u) \in \inv(\sigma^j)$.
-Similarly~${(w, 2v-1) \in \inv(\sigma^j)}$ implies~$(w, 2v) \in \inv(\sigma^j)$ for all~$v \in [n]$ and~$w > 2v$.
-We conclude that~$\sigma^j$ is indeed a wiggly permutation of~$[2n]$ by \cref{lem:inversionSetsWigglyPermutations}.
-
-Consider now any wiggly transposition~$\tau$ such that~$\inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\} \subseteq \inv(\tau)$.
-By \cref{lem:inversionSetsWigglyPermutations}, we obtain that~$\inv(\tau)$ also contains % both~$\big( \sigma(j+1), \sigma(i) \big)$ and~$\big( \sigma(k), \sigma(j) \big)$, hence also~
-$\big( \sigma(k), \sigma(i) \big)$.
-Since~$\inv(\sigma) \subset \inv(\tau)$ and~$\inv(\sigma)$ contains~$\big( \sigma(i), \sigma(p) \big)$ and~$\big( \sigma(q), \sigma(k) \big)$ for all~$i < p \le j$ and~$j+1 \le q < k$, we conclude by transitivity that~$\inv(\tau)$ contains~$\big( \sigma(q), \sigma(p) \big)$ for all~$i \le p \le j < q \le k$.
-\end{proof}
-
-\begin{proposition}
-Each wiggly permutation~$\sigma$ covers (resp.~is covered by) as many wiggly permutations as its number of descents (resp.~ascents).
-Hence, the cover graph of~$\wigglyLattice_n$ is regular of degree~$2n-1$ and connected.
-\end{proposition}
-
-\begin{proof}
-%Consider an ascent~$j$ of~$\sigma$.
-%Let~$i \eqdef \min \big( j, \sigma^{-1} \big( \sigma(j)+1 \big) \big)$ if~$\sigma(j)$ is odd, and $i \eqdef j$ otherwise.
-%Let~$k \eqdef \max \big( j+1, \sigma^{-1} \big( \sigma(j+1)+1 \big) \big)$ if~$\sigma(j+1)$ is odd, and $k \eqdef j+1$ otherwise.
-%Let~$\sigma^j \eqdef \sigma(1) \dots \sigma(i-1) \sigma(j+1) \dots \sigma(k) \sigma(i) \dots \sigma(j) \sigma(k+1) \dots \sigma(2n)$.
-%Then~$\sigma^j$ is the minimal wiggly permutation such that~$\inv(\sigma^j) \supseteq \inv(\sigma) \cup \big\{ \big( \sigma(j+1), \sigma(j) \big) \big\}$.
-Observe that~$\sigma^j \ne \sigma^{j'}$ for distinct ascents~$j \ne j'$.
-As any permutation~$\sigma'$ larger than~$\sigma$ satisfies~${\inv(\sigma') \supseteq \inv(\sigma) \cup \{\sigma(j+1), \sigma(j)\}}$ for some ascent~$j$ of~$\sigma$, we thus obtain that~$j \to \sigma^j$ is a bijection from the ascents of~$\sigma$ to the wiggly permutations covering~$\sigma$.
-The proof is symmetrical for the bijection from descents of~$\sigma$ to wiggly permutations covered by~$\sigma$.
-\end{proof}
-
-%%%%%%%%%%%%
-
-\subsection{Bijection}
-\label{subsec:bijection}
-
-We now prove that wiggly pseudotriangulations and wiggly permutations are in bijection, and that this bijection induces an isomorphism from the wiggly flip graph to the cover graph of the wiggly lattice.
-The following two definitions are illustrated in \cref{fig:wigglyLattice,fig:bijection}.
-
-\begin{figure}
-\centerline{\includegraphics[scale=1.7]{bijection}}
-\caption{The bijection between wiggly pseudotriangulations and wiggly permutations.}
-\label{fig:bijection}
-\end{figure}
-
-\begin{definition}
-\label{def:bijection1}
-Consider a wiggly pseudotriangulation~$T$.
-Following each wiggly pseudotriangle of~$T$ in counterclockwise direction, we label by~$2h-1$ (resp.~$2h$) the corner immediately preceding (resp.~following) the hinge~$h$ (the remaining corner remains unlabelled).
-We define~$\Phi(T)$ as the permutation obtained by reading these labels from bottom to top, meaning that for each internal wiggly arc~$\alpha$ of~$T$, the label incident to~$\alpha$ and below~$\alpha$ appears just before the label incident to~$\alpha$ and above~$\alpha$.
-\end{definition}
-
-\begin{example}
-The map~$\Phi$ sends the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} to the wiggly permutations of \cref{exm:specialWigglyPermutations}.
-Namely, $\Phi(T_\downarrow) = \sigma_\downarrow$, $\Phi(T_\uparrow) = \sigma_\uparrow$, $\Phi(T_\leftarrow) = \sigma_\leftarrow$, and~$\Phi(T_\rightarrow) = \sigma_\rightarrow$.
-\end{example}
-
-\begin{definition}
-\label{def:bijection2}
-For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef ( i, j, A, B)$ with
-\begin{align*}
-i & \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i}, \\
-j & \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1}, \\
-A & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \subseteq \sigma([k])}, \\
-B & \eqdef \set{\ell \in {]i,j[}}{\{2\ell-1, 2\ell\} \cap \sigma([k]) = \varnothing}.
-\end{align*}
-\end{definition}
-
-\begin{example}
-The map~$\Psi$ sends the wiggly permutations of \cref{exm:specialWigglyPermutations} to the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-Namely, $\Psi(\sigma_\downarrow) = T_\downarrow$, $\Psi(\sigma_\uparrow) = T_\uparrow$, $\Psi(\sigma_\leftarrow) = T_\leftarrow$, and~$\Psi(\sigma_\rightarrow) = T_\rightarrow$.
-\end{example}
-
-\begin{proposition}
-\label{prop:bijection}
-The maps~$\Phi$ of \cref{def:bijection1} and $\Psi$ of \cref{def:bijection2} define inverse bijections between the wiggly pseudotriangulations and the wiggly permutations, which induce a directed graph isomorphism between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-\end{proposition}
-
-\begin{proof}
-First, we show that \(\Phi(T)\) is a well-defined wiggly permutation for each wiggly pseudotriangulation \(T\).
-As every~$j \in [n]$ is the hinge of precisely one pseudotriangle of~$T$, we obtain that~\(\Phi(T)\) is by construction a permutation~$\sigma$ of~$[2n]$.
-For any \(j \in [n]\), let \(t_j\) be the pseudotriangle of \(T\) that has hinge \(j\).
-Suppose that \(2j-1\) appears before \(2j\) in \(\sigma\) for some fixed \(j \in [n]\).
-This means that the pseudotriangle~\(t_j\) has its unlabelled corner to the left of its labelled corners.
-In other words, its hinge opens to the right (see \eg $t_2$ in~\cref{fig:bijection}).
-Consider any label \(i\) that we encounter as we traverse from \(2j-1\) to \(2j\).
-This label belongs to some pseudotriangle \(t_h\) with~$h > j$.
-In other words, \(\sigma\) avoids the pattern \(2j-1 \cdots i \cdots 2j\) for \(i < 2j-1\).
-The other case (in which \(2j\) appears before \(2j-1\) in \(\sigma\)) is symmetric.
-
-Next, we show that \(\Psi(\sigma)\) is a wiggly pseudotriangulation for each wiggly permutation \(\sigma\).
-Observe first that for any~$1 \le u < v \le n$, we cannot see~$\{2u, 2v-1\}$ before~$\{2u-1, 2v\}$ in~$\sigma$ as it contains no forbidden pattern of \cref{def:wigglyPermutation}.
-Using the notations of \cref{def:bijection2}, this implies that~$i < j$ and that~${]i,j[} = A \sqcup B$, so that~$\alpha(\sigma,k) \eqdef (i, j, A, B)$ is indeed a wiggly arc for each~$k \in [2n-1]$.
-By~\cref{prop:wigglyPseudotriangulations}, it thus suffices to check that for each \(k \neq k'\) in \([2n-1]\), the wiggly arcs 
-\(\alpha(\sigma,k)\) and~\(\alpha(\sigma,k')\) are distinct and compatible.
-\begin{enumerate}
-\item \textbf{Distinctness.}
-Suppose by contradiction that \(\alpha(\sigma,k) = (i,j,A,B) = \alpha(\sigma,k')\) for some~\({k < k'}\).
-Let~${\ell \in \sigma([k'] \ssm [k])}$ and~$\bar\ell \eqdef \lceil \ell/2 \rceil$.
-As~$\ell \notin \sigma([k])$, we have~$\bar\ell \notin A$.
-As~$\ell \in \sigma([k'])$, we have~$\bar\ell \notin B$.
-As~$\{2i-1, 2j\} \subseteq \sigma([k])$ and~$\{2i, 2j-1\} \cap \sigma([k']) = \varnothing$ and~$\sigma$ avoids the forbidden pattern of \cref{def:wigglyPermutation}, we have~$2i < \ell < 2j-1$, so that~$i < \bar\ell < j$.
-This contradicts the fact that~${]i,j[} = A \sqcup B$.
-
-\item \textbf{Compatibility.}
-Let $\alpha(\sigma, k) = (i,j,A,B)$ and $\alpha(\sigma, k') = (i',j',A',B')$ for some \(k < k'\).
-It is clear from the definition that \(i \neq j'\), as the sets over which we take the $\max$ and $\min$ to define \(i\) and \(j'\) respectively are disjoint.
-Similarly, \(j \neq i'\).
-Hence, the two wiggly arcs are pointed.
-To check that the wiggly arcs are non-crossing, we show that~$(A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\}) = \varnothing$.
-Indeed~$A \cap B' = \varnothing$ since~$A \subseteq A'$ because~$\sigma([k]) \subseteq \sigma([k'])$.
-Moreover, \(\{i,j\} \cap B' = \emptyset\) since~\(\{2i - 1, 2j\} \subseteq \sigma([k]) \subseteq \sigma([k'])\).
-Finally, \(A \cap \{i',j'\} = \emptyset\) since~\(\{2i', 2j'-1\} \cap \sigma([k]) \subseteq \{2i', 2j'-1\} \cap \sigma([k']) = \varnothing\).
-\end{enumerate}
-
-Next, we show that the maps \(\Phi\) and \(\Psi\) are inverse bijections.
-Let \(\sigma\) be a wiggly permutation, so that \(\Psi(\sigma)\) is a wiggly pseudotriangulation.
-Let~$k \in [2n-1]$ and~$m \eqdef \lceil \sigma(k)/2 \rceil$.
-Then observe~that
-\begin{itemize}
-\item if $\{2m, 2m-1\} \subseteq \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ passes above the point~$m$,
-\item if~$\sigma(k) = 2m$ and~$2m-1 \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has right endpoint~$m$,
-\item if~$\sigma(k) = 2m-1$ and~$2m \notin \sigma([k])$, then~$k$ is minimal such that~$\alpha(\sigma,k)$ has left endpoint~$m$.
-\end{itemize}
-It follows that in the wiggly pseudotriangulation~\(\Psi(\sigma)\), the wiggly arc \(\alpha(\sigma, k)\) is precisely the wiggly arc lying immediately above the angle labelled by~\(\sigma(k)\).
-Therefore, we have~\(\Phi(\Psi(\sigma)) = \sigma\).
-
-Conversely, let \(T\) be a wiggly pseudotriangulation, so that \(\sigma = \Phi(T)\) is a wiggly permutation.
-Then for any \(k \in [2n-1]\), the wiggly arc immediately above the angle of~$T$ labelled by~$\sigma(k)$ is precisely the one constructed as~\(\alpha(\sigma, k)\).
-This shows that \(\Psi(\Phi(T)) = T\).
-
-\pagebreak
-Finally, consider a cover relation~$\sigma \lessdot \sigma^j$ in the wiggly lattice~$\wigglyLattice_n$ as described in~\cref{lem:wigglyCoverRelation}.
-Using the notations of~\cref{lem:wigglyCoverRelation}, observe that
-\begin{itemize}
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell)$ for all~$\ell < i$ or~$\ell > k$,
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell+k-j)$ for all~$i \le \ell < j$, and
-\item $\alpha(\sigma^j, \ell) = \alpha(\sigma, \ell-j+i-1)$ for all~$j < \ell \le k$.
-\end{itemize}
-Hence, $\Psi(\sigma) \ssm \{\alpha(\sigma, j)\} = \Psi(\sigma^j) \ssm \{\alpha(\sigma^j, j)\}$.
-This implies that~$\Psi$ is a directed graph morphism from the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ to the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$.
-As the underlying undirected graphs are both regular of degree~$2n-1$, we conclude that~$\Phi$ and~$\Psi$ induce directed graph isomorphisms between the wiggly increasing flip graph~$\wigglyIncreasingFlipGraph_n$ and the Hasse diagram of the wiggly lattice~$\wigglyLattice_n$.
-\end{proof}
-
-\begin{remark}
-Transporting the wiggly lattice~$\wigglyLattice_n$ via the map~$\Psi$ to the wiggly pseudotriangulation, note that the minimal wiggly pseudotriangulation is~$\Psi(\sigma_\downarrow) = T_\downarrow$ while the maximal wiggly pseudotriangulation is~$\Psi(\sigma_\uparrow) = T_\uparrow$.
-See \cref{exm:specialWigglyPseudotriangulations,fig:specialWigglyPseudotriangulations} for illustrations.
-\end{remark}
-
-\begin{remark}
-The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
-\end{remark}
-
-\begin{remark}
-The map~$\Phi$ sends wiggly pseudotriangulations with $i$ final internal wiggly arcs to wiggly permutations with $i$ admissible gaps, explaining the similarities of \cref{rem:numberWigglyPseudotriangulations,rem:numberWigglyPermutations}.
-For instance, the wiggly pseudotriangulations of \cref{fig:pseudotriangulationsCounting} illustrating the description of \cref{rem:numberWigglyPseudotriangulations} correspond to the wiggly permutations
-\[
-\begin{array}{cccc}
-78621354 & 9\mathrm{X}78621354 & 789\mathrm{X}621354 & 78621359\mathrm{X}4 \\
-\mathrm{X}786213594 & 7\mathrm{X}89621354 & 78\mathrm{X}6213549 & 7862135\mathrm{X}49
-\end{array}
-\]
-illustrating the description of \cref{rem:numberWigglyPermutations}.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Graph properties}
-\label{subsec:graphProperties}
-
-We conclude this combinatorial section with two open questions and a conjecture on graphical properties of the wiggly flip graph~$\wigglyFlipGraph_n$ (or equivalently of the cover graph of the wiggly lattice~$\wigglyLattice_n$), motivated by the relevance of similar questions for the associahedron.
-
-First, we are interested in the graph diameter~$\delta_n$ of~$\wigglyFlipGraph_n$.
-It is clearly bounded below by~$2n-1$ (as~$T_\leftarrow \cap T_\rightarrow = \{\alpha_\mathrm{top}, \alpha_\mathrm{bot}\}$, all $2n-1$ internal wiggly arcs must sometimes be flipped at least once) and above by~$\binom{2n}{2}$ (as we have a sublattice of the weak order on permutations of~$[2n]$).
-The first few values of~$\delta_n$ are
-\[
-\begin{array}{c|ccccccccc}
-n & 1 & 2 & 3 & 4 & 5 & \dots \\
-\hline
-\delta_n & 1 & 4 & 8 & 14 & 20 & \dots
-\end{array}
-\]
-but they might be misleading as for the associahedron~\cite{Pournin}.
-This raises the following question.
-
-\begin{question}
-Compute (or estimate) the diameter~$\delta_n$ of the wiggly flip graph~$\wigglyFlipGraph_n$.
-\end{question}
-
-Related to the estimation of the diameter~$\delta_n$ is the study of the properties of the geodesic paths in~$\wigglyFlipGraph_n$.
-We refer to~\cite{CeballosPilaud-diameterDAssociahedron} for a discussion on geodesic properties in a polytope, in connection to the revisiting path property and the complexity of the simplex algorithm~\cite{Santos-surveyHirsch,Santos-Hirsch}.
-
-\begin{question}
-Does the wiggly complex has the non-leaving face property of~\cite{CeballosPilaud-diameterDAssociahedron}?
-\end{question}
-
-Finally, we checked the following conjecture computationally up to~$n = 3$.
-
-\begin{conjecture}
-\label{conj:Hamiltonian}
-The wiggly flip graph~$\wigglyFlipGraph_n$ admits an Hamiltonian path (or even cycle).
-\end{conjecture}
-
-Note that unfortunately, wiggly permutations do not form a zigzag language in the sense of~\cite{HartungHoangMutzeWilliams} (which would have guarantied the existence of a Gray code).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\pagebreak
-\section{Wiggly fan and wigglyhedron}
-\label{sec:geometry}
-
-In this section, we use $\b{g}$- and $\b{c}$-vectors (\cref{subsec:gcvectors}) to define the wiggly fan (\cref{subsec:wigglyFan}) and the wigglyhedron (\cref{subsec:wigglyhedron}), which provide geometric realizations of the wiggly complex and of the wiggly lattice.
-
-%%%%%%%%%%%%
-
-\subsection{Polyhedral geometry}
-\label{subsec:polyhedralGeometry}
-
-We refer to \cite{Ziegler-polytopes} for a reference on polyhedral geometry, and only remind the basic notions needed later in the paper.
-
-A (polyhedral) \defn{cone} is the positive span~$\R_{\ge 0}\b{R}$ of a finite set~$\b{R}$ of vectors of~$\R^d$ or equivalently, the intersection of finitely many closed linear half-spaces of~$\R^d.$ 
-The \defn{faces} of a cone are its intersections with its supporting hyperplanes. 
-The \defn{rays} (resp.~\defn{facets}) are the faces of dimension~$1$ (resp.~ codimension~$1$).
-A cone is \defn{simplicial} if its rays are linearly independent.
-A (polyhedral) \defn{fan}~$\Fan$ is a set of cones such that any face of a cone of~$\Fan$ belongs to~$\Fan$, and any two cones of~$\Fan$ intersect along a face of both. 
-A fan is \defn{essential} if the intersection of its cones is the origin, \defn{complete} if the union of its cones covers~$\R^d$, and \defn{simplicial} if all its cones are simplicial.
-
-Note that a simplicial fan defines a simplicial complex on its rays (the simplices of the simplicial complex are the subsets of rays which span a cone of the fan).
-Conversely, given a simplicial complex~$\Delta$ with ground set~$V$, one can try to realize it geometrically by associating a ray~$\b{r}_v$ of~$\R^d$ to each~$v \in V$, and the cone~$\R_{\ge 0}\b{R}_\triangle$ generated by the set~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ to each~$\triangle \in \Delta$.
-To show that the resulting cones indeed form a fan, we will need the following statement, which can be seen as a reformulation of~\cite[Coro.~4.5.20]{DeLoeraRambauSantos}.
-
-\begin{proposition}
-\label{prop:characterizationFan}
-Consider a simplicial $(d-1)$-dimensional pseudomanifold~$\Delta$ without boundary on a ground set~$V$ and a set of vectors~$(\b{r}_v)_{v \in V}$ of~$\R^d$, and define~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ for any~$\triangle \in \Delta$.
-Then the collection of cones~$\set{\R_{\ge 0}\b{R}_\triangle}{\triangle \in \Delta}$ forms a complete simplicial fan of~$\R^d$ if and~only~if
-\begin{itemize}
-\item there exists a vector~$\b{v}$ of~$\R^d$ contained in only one of the cones~$\R_{\ge 0}\b{R}_\triangle$ for~$\triangle \in \Delta$,
-\item for any two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, we have~$\lambda_v \lambda_{v'} > 0$~where
-\[
-\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
-\]
-denotes the unique (up to rescaling) linear dependence on~$\b{R}_{\triangle \cup \triangle'}$.
-\end{itemize}
-\end{proposition}
-
-A \defn{polytope} is the convex hull of finitely many points of~$\R^d$ or equivalently, a bounded intersection of finitely many closed affine half-spaces of~$\R^d$.
-The \defn{faces} of a polytope are its intersections with its supporting hyperplanes.
-The \defn{vertices} (resp.~\defn{edges}, resp.~\defn{facets}) are the faces of dimension~$0$ (resp.~dimension~$1$, resp.~codimension~$1$).
-
-The \defn{normal cone} of a face~$\polytope{F}$ of a polytope~$\polytope{P}$ is the cone generated by the normal vectors to the supporting hyperplanes of~$\polytope{P}$ containing~$\polytope{F}$.
-Said differently, it is the cone of vectors~$\b{c}$ of~$\R^d$ such that the linear form~$\b{x} \mapsto \dotprod{\b{c}}{\b{x}}$ on~$\polytope{P}$ is maximized by all points of the face~$\polytope{F}$.
-The \defn{normal fan} of~$\polytope{P}$ is the set of normal cones of all its faces.
-
-\enlargethispage{.6cm}
-Consider now a complete simplicial fan~$\Fan$ of~$\R^d$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~${\triangle \in \Delta}$, where~$\b{R}_\triangle \eqdef \set{\b{r}_v}{v \in \triangle}$ as in \cref{prop:characterizationFan}.
-To realize the fan~$\Fan$, one can try to pick a height vector~$\b{h} \eqdef (h_v)_{v \in V} \in \R^V$ and consider the polytope
-\(
-\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}.
-\)
-The following classical statement characterizes the height vectors~$\b{h}$ for which the fan~$\Fan$ is the normal fan of this polytope~$\polytope{P}_{\b{h}}$.
-We borrow the formulation from~\cite[Lem.~2.1]{ChapotonFominZelevinsky}.
-
-\begin{proposition}
-\label{prop:characterizationPolytopalFan}
-Let~$\Fan$ be an essential complete simplicial fan in~$\R^n$ with rays~$(\b{r}_v)_{v \in V}$ and cones~$\R_{\ge 0} \b{R}_\triangle$ for~$\triangle \in \Delta$.
-Then the following are equivalent for any height vector~$\b{h} \in \R^V$:
-\begin{itemize}
-\item The fan~$\Fan$ is the normal fan of the polytope~$\polytope{P}_{\b{h}} \eqdef \set{\b{x} \in \R^d}{\dotprod{\b{r}_v}{\b{x}} \le h_v \text{ for all } v \in V}$.
-\item For two adjacent facets~$\triangle, \triangle'$ of~$\Delta$ with~$\triangle \ssm \{v\} = \triangle' \ssm \{v'\}$, the height vector~$\b{h}$ satisfies the \defn{wall crossing inequality}
-\[
-\lambda_v \, h_v + \lambda_{v'} \, h_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, h_w > 0,
-\]
-where
-\[
-\lambda_v \, \b{r}_v + \lambda_{v'} \, \b{r}_{v'} + \sum_{w \in \triangle \cap \triangle'} \lambda_w \, \b{r}_w = 0
-\]
-denotes the unique linear dependence on~$\b{R}_{\triangle \cup \triangle'}$ such that~$\lambda_v + \lambda_{v'} = 2$.
-\end{itemize}
-\end{proposition}
-
-\pagebreak
-We denote by~$(\b{e}_i)_{i \in [d]}$ the standard basis of~$\R^d$.
-For~$I \subseteq [d]$, we define~$\one_I \eqdef \sum_{i \in I} \b{e}_i$, and we often shorten~$\one_{[d]}$ by~$\one_d$.
-We denote by~$\HH_d$ the hyperplane of~$\R^d$ defined by the equation~$\dotprod{\b{x}}{\one_d} = 0$, and we denote by~$\pi : \R^d \to \HH_d$ the orthogonal projection on~$\HH_d$, that is~$\pi(\b{x}) \eqdef \b{x} - (\dotprod{\b{x}}{\one_d} / d) \one_d$.
-
-%%%%%%%%%%%%
-
-\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
-\label{subsec:gcvectors}
-
-We first define the $\b{g}$-vectors, illustrated in \cref{fig:ggMatrices}.
-%
-\begin{figure}
-\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/ggmatrices}}
-\caption{The $\hat{\b{g}}$-matrix~$\hat{\b{g}}(T)$ and $\b{g}$-matrix~$\b{g}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ and the $\b{g}$-vector~$\b{g}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
-The colors of the columns match the colors of the wiggly arcs.
-The $\b{g}$-vectors are the orthogonal projections of the $\hat{\b{g}}$-vectors on the hyperplane~$\HH_{2n}$.}
-\label{fig:ggMatrices}
-\end{figure}
-
-\begin{definition}
-\label{def:gvectors}
-The \defn{$\b{g}$-vector} of a wiggly arc~$\alpha \eqdef (i, j, A, B)$ is the vector~$\b{g}(\alpha)$ of~$\HH_{2n}$ defined as the projection~$\pi \big( \hat{\b{g}}(\alpha) \big)$ of the vector~$\hat{\b{g}}(\alpha) \eqdef \one_{\alpha^+} - \one_{\alpha^-}$ where
-\begin{align*}
-\alpha^+ & \eqdef \big(\{2i-1, 2j\} \ssm \{-1, 2n+2\} \big) \cup \set{2a-1}{a \in A} \cup \set{2a}{a \in A},
-\\
-\alpha^- & \eqdef \big(\{2i, 2j-1\} \ssm \{0, 2n+1\} \big) \cup \set{2b-1}{b \in B} \cup \set{2b}{b \in B}.
-\end{align*}
-If we place the coordinate~$2p-1$ on the left and the coordinate~$2p$ on the right of point~$p$, then~$\hat{\b{g}}(\alpha)$ has a $1$ outside its two endpoints and on both sides of points in~$A$, and a~$-1$ inside its two endpoints and on both sides of points in~$B$.
-Note that ${\hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = \one_{2n} = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)}$, so that~${\b{g} \big( (0, n+1, [n], \varnothing) \big) = \b{0} = \b{g} \big( (0, n+1, \varnothing, [n]) \big)}$.
-We define~$\b{g}(D) \eqdef \set{\b{g}(\alpha)}{\alpha \in D^\circ}$ for a set~$D$ of wiggly arcs.
-\end{definition}
-
-\begin{example}
-\label{exm:specialGMatrices}
-\cref{table:specialGMatrices} gathers the $\hat{\b{g}}$-matrices (\ie matrices whose columns are the $\hat{\b{g}}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
-
-\begin{table}[p]
-	\begingroup
-	\fontsize{10}{10}\selectfont
-	\setlength\arraycolsep{2pt}
-	\begin{alignat*}{3}
-%	\b{g}(T_\downarrow) & = \begin{pmatrix}
-%		1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & 0 & \dots & 0 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & 1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		-1 & -1 & \dots & 0 & 0 & -1 & -1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & 1 & 0 & -1 & -1 & \dots & -1 & 1 \\
-%		-1 & -1 & \dots & -1 & 0 & -1 & -1 & \dots & -1 & 1 \\
-%		-1 & -1 & \dots & -1 & 1 & -1 & -1 & \dots & -1 & -1 \\
-%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\hat{\b{g}}(T_\downarrow) & = \begin{pmatrix}
-		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
-	\end{pmatrix}
-	\qquad &
-%	\b{g}(T_\leftarrow) & = \begin{pmatrix}
-%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & -1 & \dots & -1 & -1 & -1 & 1 & \dots & 1 & 1 \\
-%		0 & 1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & -1 & -1 & 0 & -1 & \dots & 1 & 1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & -1 & -1 & 0 & 0 & \dots & -1 & 1 \\
-%		0 & 0 & \dots & 1 & -1 & 0 & 0 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & 1 & 0 & 0 & \dots & 0 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\hat{\b{g}}(T_\leftarrow) & = \begin{pmatrix}
-		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
-		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
-		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-	\end{pmatrix}
-	\\[.3cm]
-%	\b{g}(T_\uparrow) & = \begin{pmatrix}
-%		-1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%		1 & -1 & \dots & -1 & -1 & -1 & -1 & \dots & -1 & -1 \\
-%		0 & -1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
-%		0 & 1 & \dots & -1 & -1 & 1 & -1 & \dots & -1 & -1 \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & -1 & -1 \\
-%		0 & 0 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & -1 \\
-%		0 & 0 & \dots & 1 & -1 & 1 & 1 & \dots & 1 & -1 \\
-%		0 & 0 & \dots & 0 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%		0 & 0 & \dots & 0 & 1 & 1 & 1 & \dots & 1 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\hat{\b{g}}(T_\uparrow) & = \begin{pmatrix}
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & -1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & -1 & 1 \\
-		-1 & -1 & -1 & -1 & \dots & -1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 1 & 1 & 0 \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		-1 & -1 & -1 & -1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & -1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & -1 & 1 & 1 & \dots & 0 & 1 & 0 \\
-		-1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-		1 & 1 & 0 & 1 & \dots & 0 & 1 & 0 \\
-	\end{pmatrix}
-	\qquad &
-%	\b{g}(T_\rightarrow) & = \begin{pmatrix}
-%		1 & 0 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		-1 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
-%		-1 & 1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & -1 & \dots & 0 & 0 \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		-1 & -1 & \dots & 0 & 0 & 1 & 1 & \dots & -1 & 0 \\
-%		-1 & -1 & \dots & 1 & 0 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & -1 & 0 & 1 & 1 & \dots & 1 & -1 \\
-%		-1 & -1 & \dots & -1 & 1 & 1 & 1 & \dots & 1 & 1 \\
-%		-1 & -1 & \dots & -1 & -1 & 1 & 1 & \dots & 1 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	\hat{\b{g}}(T_\rightarrow) & = \begin{pmatrix}
-		1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -1 \\
-		-1 & 1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & -1 & 1 \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots  & \ddots & \vdots & \vdots \\
-		-1 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & 1 & 0 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 0 & -1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & 1 & 1 & \dots & 1 & 1 \\
-		-1 & -1 & \dots & -1 & -1 & 1 & \dots & 1 & 1 \\
-	\end{pmatrix}
-	\end{alignat*}
-	\endgroup
-	\caption{The $\hat{\b{g}}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\hat{\b{g}}(T)$ is the $\hat{\b{g}}$-vector~$\hat{\b{g}}(\alpha)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
-}
-	\label{table:specialGMatrices}
-\end{table}
-\end{example}
-
-We will see in \cref{coro:basis} that~$\b{g}(T)$ forms a basis of~$\HH_{2n}$ for any wiggly pseudotriangulation~$T$, which enables us to define its dual basis, illustrated in \cref{fig:gcMatrices}.
-%
-\begin{figure}
-\centerline{\raisebox{-1.8cm}{\includegraphics[scale=2]{pseudotriangulationMatrices}} \quad \input{figures/gcmatrices}}
-\caption{The $\b{g}$-matrix~$\b{g}(T)$ and $\b{c}$-matrix~$\b{c}(T)$ of a wiggly pseudotriangulation~$T$.
-The $i$th column of these matrices are the $\b{g}$-vector~$\b{g}(\alpha)$ and $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).
-The colors of the columns match the colors of the wiggly arcs.
-The $\b{g}$-vectors and $\b{c}$-vectors form dual bases of~$\HH_{2n}$.}
-\label{fig:gcMatrices}
-\end{figure}
-
-\begin{definition}
-\label{def:cvectors}
-The \defn{$\b{c}$-vector} of an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$ is the vector~$\b{c}(\alpha, T)$ of~$\HH_{2n}$ such that~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha)} = 1$ and~$\dotprod{\b{c}(\alpha, T)}{\b{g}(\alpha')} = 0$ for all interior wiggly arcs~$\alpha' \ne \alpha$ of~$T$.
-In other words, $\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ is the dual basis of~$\b{g}(T)$~in~$\HH_{2n}$.
-\end{definition}
-
-\begin{remark}
-The $\b{c}$-vector~$\b{c}(\alpha, T)$ can also be described combinatorially.
-Namely, label the the corners of~$T$ as in \cref{def:bijection1}, and denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-Then the $\b{c}$-vector~$\b{c}(\alpha, T)$ has coordinates
-\begin{itemize}
-\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
-\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
-\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
-\end{itemize}
-The tedious proof of this description is not needed here as we only use the dual basis property.
-\end{remark}
-
-\begin{example}
-\label{exm:specialCMatrices}
-\cref{table:specialCMatrices} gathers the $\b{c}$-matrices (\ie matrices whose columns are the $\b{c}$-vectors) of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations} illustrated in \cref{fig:specialWigglyPseudotriangulations}.
-
-\begin{table}
-	\begingroup
-	\fontsize{10}{10}\selectfont
-	\setlength\arraycolsep{2pt}
-	\begin{alignat*}{3}
-%	4\b{c}(T_\downarrow) & = \begin{pmatrix}
-%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
-%		-2 & 0 & \dots & 0 & 0 & 2 & 0 & \dots & 0 & 0 \\
-%		0 & 2 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & 0 \\
-%		0 & -2 & \dots & 0 & 0 & -1 & 2 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & -1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 2 & 0 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & -1 & 2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & -1 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\downarrow) & = \begin{pmatrix}
-		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
-		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
-		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		0 & 0 & 0& 0 & \dots & 2 & 0 & 0 \\
-		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
-	\end{pmatrix}
-	\quad &
-%	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
-%		-2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		2 & -1 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & -2 & 1 & \dots & 0 & 0 \\
-%		0 & 2 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & -2 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & -1 & 0 & 0 & 0 & \dots & 1 & 0 \\
-%		0 & 0 & \dots & 0 & -1 & 0 & 0 & \dots & -2 & 1 \\
-%		0 & 0 & \dots & 2 & -1 & 0 & 0 & \dots & 0 & 1 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & -2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\leftarrow) & = \begin{pmatrix}
-		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
-		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
-		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-	\end{pmatrix}
-	\quad
-	\\[.3cm]
-%	4\b{c}(T_\uparrow) & = \begin{pmatrix}
-%		-2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
-%		2 & 0 & \dots & 0 & 0 & -1 & 0 & \dots & 0 & -1 \\
-%		0 & -2 & \dots & 0 & 0 & 2 & -1 & \dots & -1 & 2 \\
-%		0 & 2 & \dots & 0 & 0 & 0 & -1 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 2 & \dots & 2 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -1 & 0 \\
-%		0 & 0 & \dots & -2 & 0 & 0 & 0 & \dots & 2 & -1 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 0 & -1 \\
-%		0 & 0 & \dots & 0 & -2 & 0 & 0 & \dots & 0 & 2 \\
-%		0 & 0 & \dots & 0 & 2 & 0 & 0 & \dots & 0 & 0 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\uparrow) & = \begin{pmatrix}
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & -2 \\
-		0 & 0 & 0 & 0 & \dots & 0 & -1 & 2 \\
-		0 & 0 & 0 & 0 & \dots & -2 & 2 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 2 & 0 & 0 \\
-		0 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		\vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots \\
-		0 & 0 & 0 & -1 & \dots & 0 & 0 & 0 \\
-		0 & -1 & -2 & 2 & \dots & 0 & 0 & 0 \\
-		0 & -1 & 2 & 0 & \dots & 0 & 0 & 0 \\
-		-2 & 2 & 0 & 0 & \dots & 0 & 0 & 0 \\
-		2 & 0 & 0 & 0 & \dots & 0 & 0 & 0 \\
-	\end{pmatrix}
-	\quad &
-%	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
-%		2 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & -2 & 0 & \dots & 0 & 0 \\
-%		-1 & 2 & \dots & 0 & 0 & 1 & 0 & \dots & 0 & 0 \\
-%		-1 & 0 & \dots & 0 & 0 & 1 & -2 & \dots & 0 & 0 \\
-%		0 & -1 & \dots & 0 & 0 & 0 & 1 & \dots & 0 & 0 \\
-%		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & -2 & 0 \\
-%		0 & 0 & \dots & 2 & 0 & 0 & 0 & \dots & 1 & 0 \\
-%		0 & 0 & \dots & 0 & 0 & 0 & 0 & \dots & 1 & -2 \\
-%		0 & 0 & \dots & -1 & 2 & 0 & 0 & \dots & 0 & 1 \\
-%		0 & 0 & \dots & -1 & -2 & 0 & 0 & \dots & 0 & 1 \\
-%	\end{pmatrix}
-%	\qquad &
-	4\b{c}(T_\rightarrow) & = \begin{pmatrix}
-		2 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & -2 \\
-		-1 & 2 & \dots & 0 & 0 & 0 & \dots & 0 & 1 \\
-		-1 & 0 & \dots & 0 & 0 & 0 & \dots & -2 & 1 \\
-		0 & -1 & \dots & 0 & 0 & 0 & \dots & 1 & 0 \\
-		\vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
-		0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 2 & 0 & 0 & \dots & 0 & 0 \\
-		0 & 0 & \dots & 0 & 0 & -2 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & 2 & 1 & \dots & 0 & 0 \\
-		0 & 0 & \dots & -1 & -2 & 1 & \dots & 0 & 0 \\
-	\end{pmatrix}
-	\end{alignat*}
-	\endgroup
-	\caption{$4$ times the $\b{c}$-matrices of the wiggly pseudotriangulations of \cref{exm:specialWigglyPseudotriangulations}.
-The $i$th column of~$\b{c}(T)$ is $4$ times the $\b{c}$-vector~$\b{c}(\alpha, T)$ of the $i$th wiggly arc~$\alpha$ of~$T$ (ordered from bottom to top).}
-	\label{table:specialCMatrices}
-\end{table}
-\end{example}
-
-%\begin{definition}
-%\label{def:cvectors}
-%Consider a wiggly pseudotriangulation~$T$, and label the corners as in \cref{def:bijection1}.
-%Consider an interior wiggly arc~$\alpha$ in a wiggly pseudotriangulation~$T$, denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-%The \defn{$\b{c}$-vector} of~$\alpha$ in~$T$ is the vector~$\b{c}(\alpha, T)$ with coordinates
-%\begin{itemize}
-%\item $\b{c}(\alpha, T)_{2w-1} = - \b{c}(\alpha, T)_{2w} = (-1)^{w \in A} (-1)^{u>v}/4$ for all~$w$ strictly between~$\bar u$ and~$\bar v$,
-%\item $\b{c}(\alpha, T)_u = 1/2$ if~$\bar u = \bar v$, or if~$\bar v$ and the wiggly arcs incident to~$\bar u$ are on the same side of~$\bar u$, and $\b{c}(\alpha, T)_{2\bar u-1} = \b{c}(\alpha, T)_{2\bar u} = 1/4$ otherwise,
-%\item $\b{c}(\alpha, T)_v = -1/2$ if~$\bar u = \bar v$, or if~$\bar u$ and the wiggly arcs incident to~$\bar v$ are on the same side of~$\bar v$, and $\b{c}(\alpha, T)_{2\bar v-1} = \b{c}(\alpha, T)_{2\bar v} = -1/4$ otherwise,
-%\item $\b{c}(\alpha, T)_w = 0$ for all other coordinates.
-%\end{itemize}
-%Set~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$
-%\end{definition}
-%
-%\begin{proposition}
-%\label{prop:dualBases}
-%For any wiggly pseudotriangulation~$T$, the sets~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases~of~$\HH_{2n}$.
-%\end{proposition}
-%
-%\begin{proof}
-%We claim that~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for~$\alpha, \alpha' \in T$, where~$\delta$ is the Kronecker~$\delta$.
-%Note that, with~$\alpha = (0, n+1, [n], \varnothing)$, it implies that~$\dotprod{\one_{2n}}{\b{c}(\alpha', T)} = 0$ for any~${\alpha' \in T}$.
-%Hence, we obtain that~$\dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \dotprod{\pi(\hat{\b{g}}(\alpha))}{\b{c}(\alpha', T)} = \dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \delta_{\alpha, \alpha'}$ for any~$\alpha, \alpha' \in T$.
-%We conclude that~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ and~$\b{c}(T) \eqdef \set{\b{c}(\alpha, T)}{\alpha \in T^\circ}$ form dual bases of~$\HH_{2n}$.
-%
-%The proof of the claim is a boring case analysis.
-%Let~$i < j$ be the endpoints of~$\alpha$, and let~$u$ and~$v$ the labels (in the corner labeling of~$T$) incident to~$\alpha'$ and respectively below and above~$\alpha'$, and~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-%By symmetry, we can assume that~$u < v$ so that~$\bar u \le \bar v$.
-%Let us write~$\hat{\b{g}}(\alpha) \eqdef (g_1, \dots, g_{2n})$ and~$\b{c}(\alpha', T) \eqdef (c_1, \dots, c_{2n})$, and define~$gc_k \eqdef g_{2k-1}c_{2k-1} + g_{2k}c_{2k}$.
-%Hence, we have~$\dotprod{\hat{\b{g}}(\alpha)}{\b{c}(\alpha', T)} = \sum_{k \in [n]} gc_k = \sum_{k \in \{i, j, \bar u, \bar v\}} gc_k$.
-%Indeed, the last equality holds since~$g_{2k-1} = g_{2k}$ for all~$k \in [n] \ssm \{i,j\}$ and~$c_{2k-1} = -c_{2k}$ for all~$k \in [n] \ssm \{\bar u, \bar v\}$.
-%
-%Assume first that~$\alpha = \alpha'$.
-%Hence, we have~$i \le \bar u \le \bar v \le j$.
-%We distinguish two cases:
-%\begin{enumerate}
-%\item If~$i = \bar u = \bar v < j$, then~$u = 2i-1$ and~$v = 2i$, so that~$gc_i = 1 \cdot 1/2 + (-1) \cdot (-1/2) = 1$ and~$gc_j = 0$, thus~$\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = gc_i + gc_j = 1$.
-%\item Otherwise, $i \le \bar u < \bar v \le j$.
-%If~$i = \bar u$, we have~$u = 2i-1$ so that~$gc_{\bar u} = 1 \cdot 1/2 + (-1) \cdot 0 = 1/2$.
-%If~$i < \bar u$, we have~$gc_i = 0$ (since~$c_{2i-1} = c_{2i} = 0$) and~$gc_{\bar u} = 1/2$ (since~$g_{2\bar u-1} = g_{2\bar u} = 1$ and~${c_{2\bar u-1} + c_{2\bar u} = 1/2}$).
-%In both cases, we get that~$\sum_{k \in \{i, \bar u\}} gc_k = 1/2$.
-%By symmetric arguments, we conclude~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = \sum_{k \in \{i, \bar u\}} gc_k + \sum_{k \in \{j, \bar v\}} gc_k = 1/2 + 1/2 = 1}$.
-%\end{enumerate}
-%
-%Assume now that~$\alpha \ne \alpha'$.
-%\vincent{I am really unhappy with this proof. I can do the case analysis, but it is really unsatisfactory. I am waiting to see if I find another idea...}
-%We distinguish ten cases:
-%\begin{enumerate}
-%\item If~$j < \bar u$, then~$c_{2i-1} = c_{2i} = c_{2j-1} = c_{2j} = 0$ and~$g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-%\item If~$j = \bar u < \bar v$, then~$c_{2i-1} \! = \! c_{2i} \! = \! 0$, $g_{2j-1} \! = \! -g_{2j}$ and~$c_{2j-1} \! = \! c_{2j}$,  and~${g_{2 \bar v-1} \! = \! g_{2 \bar v} = 0}$.
-%\item If~$i < \bar u < j < \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2 \bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$, and~$g_{2 \bar v-1} = g_{2 \bar v} = 0$.
-%\item If~$i < \bar u < j = \bar v$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = 1$ and~$c_{2 \bar u-1} + c_{2\bar u} = 1/2$, $g_{2j-1} = -g_{2j} = -1$ and~$c_{2j-1} - c_{2j} = 1/2$.
-%\item If~$i < \bar u \le \bar v < j$, then~$c_{2i-1} = c_{2i} = 0$, $g_{2 \bar u-1} = g_{2 \bar u} = g_{2 \bar v-1} = g_{2 \bar v}$ and~$c_{2 \bar u-1} + c_{2\bar u} + c_{2j-1} + c_{2j} = 0$, and~$c_{2j-1} = c_{2j} = 0$.
-%\item If~$i = \bar u < j < \bar v$, then \dots
-%\item If~$i = \bar u < j = \bar v$, then \dots
-%\item If~$i = \bar u < \bar v < j$, then \dots
-%\item If~$\bar u < i < j < \bar v$, then \dots
-%\item If~$\bar u < i < j = \bar v$, then \dots
-%\item If~$\bar u < i < \bar v < j$, then \dots
-%\item If~$\bar u < i = \bar v < j$, then \dots
-%\item If~$\bar u < \bar v < i < j$, then \dots
-%\end{enumerate}
-%(Note that~$\bar u = \bar v$ implies that~$\{i,j\} \notin \bar u$.)
-%In all cases, we check that~${\sum_{k \in \{i, j, \bar u, \bar v\}} gc_k = 0}$.
-%\end{proof}
-
-\begin{remark}
-\label{rem:gcvectorsSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism}, note that the vertical and horizontal symmetries on wiggly arcs translate on $\b{g}$- and $\b{c}$-vectors to the isometries sending~$(x_1, x_2, \dots, x_{2n-1}, x_{2n}) \in \HH_{2n}$ to~$(x_{2n}, x_{2n-1}, \dots, x_2, x_1)$ and to~$(-x_2, -x_1, \dots, -x_{2n}, -x_{2n-1})$ respectively.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly fan}
-\label{subsec:wigglyFan}
-
-We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
-\afterpage{
-\begin{figure}
-\centerline{\includegraphics[scale=.75]{wigglyFan}}
-\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.}
-\label{fig:wigglyFan}
-\end{figure}
-}
-
-\begin{theorem}
-\label{thm:wigglyFan}
-The collection of cones~$\R_{\ge 0} \b{g}(D) $ for all wiggly dissections~$D$ in the wiggly complex~$\wigglyComplex_n$ forms a complete simplicial fan of~$\HH_{2n}$, called the \defn{wiggly fan}~$\wigglyFan_n$.
-\end{theorem}
-
-To prove \cref{thm:wigglyFan}, we just need to check the conditions of \cref{prop:characterizationFan}.
-We first find a vector contained in the cone~$\R_{\ge 0} \b{g}(T)$ for a single wiggly pseudotriangulation~$T$.
-
-\begin{lemma}
-\label{lem:-+...-+}
-Let~$\b{v} \eqdef \sum_{k \in [n]} (\b{e}_{2k} - \b{e}_{2k-1}) = (-1, 1, \dots, -1, 1)$, let~$\alpha_0 \eqdef (0, 1, \varnothing, \varnothing)$, and for~${i \in [n]}$, let~$\underline{\alpha}_i \eqdef (0, i+1, [i], \varnothing)$ and~$\overline{\alpha}_i \eqdef (0, i+1, \varnothing, [i])$.
-Then~$T_\leftarrow \eqdef \{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$ is the only wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
-\end{lemma}
-
-\begin{proof}
-Observe first that, for any wiggly arc~$\alpha \eqdef (i, j, A, B)$ and any~$k \in [n]$, we have
-%\begin{itemize}
-%\item $\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = 1$ if~$k = i$, $-1$ if~$k = j$, and~$0$ otherwise,
-%\item $\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = 2$ if~$k \in A$, $-2$ if~$k \in B$, and~$0$ otherwise.
-%\end{itemize}
-\[
-\hat{\b{g}}(\alpha)_{2k-1} - \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 2 & \text{if~$k = i$,} \\ -2 & \text{if~$k = j$,} \\ 0 & \text{otherwise}, \end{cases}
-\qquad\text{and}\qquad
-\hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} = \begin{cases} 2 & \text{if~$k \in A$,} \\ -2 & \text{if~$k \in B$,} \\ 0 & \text{otherwise}. \end{cases}
-\]
-
-Assume now that~$\b{v} = \sum_\alpha \lambda_\alpha \, \hat{\b{g}}(\alpha)$ where the sum ranges over all wiggly arcs~$\alpha$ for some positive scalars~$\lambda_\alpha \ge 0$ such that~$\lambda_\alpha \cdot \lambda_{\alpha'} = 0$ for all incompatible wiggly arcs~$\alpha$ and~$\alpha'$.
-For~$k \in [n]$, let~$\underline{\Lambda}_k$ (resp.~$\overline{\Lambda}_k$) denote the sum of~$\lambda_\alpha$ over the wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$k \in A$ (resp.~$k \in B$).
-Note that~$\underline{\Lambda}_k = \overline{\Lambda}_k$ since~$0 = \b{v}_{2k-1} + \b{v}_{2k} = \sum_\alpha \lambda_\alpha \big( \hat{\b{g}}(\alpha)_{2k-1} + \hat{\b{g}}(\alpha)_{2k} \big) = 2\underline{\Lambda}_k - 2\overline{\Lambda}_k$.
-
-As~$\b{v}_1 - \b{v}_2 = -2$ and~$\hat{\b{g}}(\alpha)_1 - \hat{\b{g}}(\alpha)_2 \ge 0$ except if~$\alpha = \alpha_0$, we have~$\lambda_{\alpha_0} > 0$, and thus~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$1$.
-%As~$\b{g}(\alpha)_1 - \b{g}(\alpha)_2 = 0$ for all wiggly arcs~$\alpha$ with no endpoint at~$1$, we thus obtain that~$\lambda_{\alpha_0} = 1$.
-We then prove by induction on~$i \in [n-1]$ that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$ and that~$\lambda_\alpha = 0$ for all wiggly arcs starting at~$i+1$.
-Consider~$i \in [n-1]$ and assume that we proved it for~$i-1$.
-As~$\smash{\lambda_{\underline{\alpha}_{i-1}} \cdot \lambda_{\overline{\alpha}_{i-1}} > 0}$, we already have~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ ending at~$i+1$, except if~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
-As~$\b{v}_{2i+1} - \b{v}_{2i+2} = -2$, this implies that~$\smash{\lambda_{\underline{\alpha}_i} + \lambda_{\overline{\alpha}_i} = 1}$.
-This already implies that~$\lambda_{\alpha} = 0$ for all wiggly arcs~$\alpha$ starting at~$i+1$.
-Moreover, assume for instance that~$\lambda_{\overline{\alpha}_i} > 0$.
-Hence, $\lambda_\alpha = 0$ for all wiggly arcs~$\alpha \eqdef (i, j, A, B)$ with~$i \in A$ and~$i+1 \in B$.
-We thus obtain that~$\underline{\Lambda}_i - \lambda_{\underline{\alpha}_i} \le \underline{\Lambda}_{i+1}$ and~$\overline{\Lambda}_i - \lambda_{\overline{\alpha}_i} \ge \overline{\Lambda}_{i+1}$.
-As~$\underline{\Lambda}_i = \overline{\Lambda}_i$ and~$\underline{\Lambda}_{i+1} = \overline{\Lambda}_{i+1}$, we thus obtain that~$\lambda_{\underline{\alpha}_i} \ge \lambda_{\overline{\alpha}_i} > 0$, hence that~$\lambda_{\underline{\alpha}_i} \cdot \lambda_{\overline{\alpha}_i} > 0$.
-We conclude that~$\lambda_\alpha = 0$ for all wiggly arcs~$\alpha$ except if~$\alpha = \alpha_0$ or~$\alpha \in \{\underline{\alpha}_i, \overline{\alpha}_i\}$ for some~$i \in [n]$.
-
-Consider now a wiggly pseudotriangulation~$T$ such that~$\b{v} \in \R_{\ge 0} \b{g}(T)$.
-Write~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \b{g}(\alpha)$ with~$\lambda_\alpha \ge 0$ for all~$\alpha \in T^\circ$.
-Let~$\mu \eqdef \sum_{\alpha \in T^\circ} \lambda_\alpha \dotprod{\hat{\b{g}}(\alpha)}{\one_{2n}}$.
-As~$\b{v} = \sum_{\alpha \in T^\circ} \lambda_\alpha \, \hat{\b{g}}(\alpha) - \mu \, \one_{2n}$ and~$\one_{2n} = \hat{\b{g}} \big( (0, n+1, [n], \varnothing) \big) = - \hat{\b{g}} \big( (0, n+1, \varnothing, [n]) \big)$, we thus conclude from the previous paragraph that~$T = T_\leftarrow$.
-%\{\alpha_0\} \cup \bigcup_{i \in [n]} \{\underline{\alpha}_i, \overline{\alpha}_i\}$.
-\end{proof}
-
-We now describe the unique linear dependence between the $\b{g}$-vectors of two adjacent facets of the wiggly complex~$\wigglyComplex_n$.
-The following statement is illustrated in \cref{fig:incompatible3}.
-
-\begin{lemma}
-\label{lem:linearDependences}
-Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
-Then~$\{\beta, \beta'\} \in T \cap T'$ and
-\begin{itemize}
-\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\b{g}(\alpha) + \b{g}(\alpha') = \big( \b{g}(\beta) + \b{g}(\beta') \big) / 2$,
-\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-In both situations, we will just prove that the same linear dependence holds on the vectors~$\hat{\b{g}}(\alpha), \hat{\b{g}}(\alpha'), \hat{\b{g}}(\beta), \hat{\b{g}}(\beta')$, which will imply the statement as~$\pi$ is a linear map.
-
-If~$\alpha$ and~$\alpha'$ are non pointed, then we have
-\[
-\alpha^+ \sqcup \alpha'^+ = \beta^+ \sqcup \{2j-1, 2j\} = \beta'^+
-\qquad\text{and}\qquad 
-\alpha^- \sqcup \alpha'^- = \beta^- = \beta'^- \sqcup \{2j-1, 2j\}.
-\]
-We thus obtain that
-\[
-\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\beta^+} + \b{e}_{2j-1} + \b{e}_{2j} = \one_{\beta'^+}
-\qquad\text{and}\qquad 
-\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} = \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}.
-\]
-hence
-\begin{align*}
-2 \big( \hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') \big)
-& = 2(\one_{\alpha^+} - \one_{\alpha^-}) + 2(\one_{\alpha'^+} - \one_{\alpha'^-})
-= 2(\one_{\alpha^+} + \one_{\alpha'^+}) - 2(\one_{\alpha^-} + \one_{\alpha'^-}) \\
-& = (\one_{\beta^+} + \one_{\beta'^+} + \b{e}_{2j-1} + \b{e}_{2j}) - (\one_{\beta^-} + \one_{\beta'^-} + \b{e}_{2j-1} + \b{e}_{2j}) \\
-& = (\one_{\beta^+} + \one_{\beta'^+}) - (\one_{\beta^-} + \one_{\beta'^-})
-= (\one_{\beta^+} - \one_{\beta^-}) + (\one_{\beta^-} + \one_{\beta'^-})
-= \hat{\b{g}}(\beta) + \hat{\b{g}}(\beta').
-\end{align*}
-
-If~$\alpha$ and~$\alpha'$ cross, then we have
-\begin{gather*}
-\alpha^+ \cup \alpha'^+ = \beta^+ \cup \beta'^+ \qquad\text{and}\qquad \alpha^+ \cap \alpha'^+ = \beta^+ \cap \beta'^+, \\
-\alpha^- \cup \alpha'^- = \beta^- \cup \beta'^- \qquad\text{and}\qquad \alpha^- \cap \alpha'^- = \beta^- \cap \beta'^-.
-\end{gather*}
-We thus obtain that
-\[
-\one_{\alpha^+} + \one_{\alpha'^+} = \one_{\alpha^+ \cup \alpha'^+} + \one_{\alpha^+ \cap \alpha'^+} = \one_{\beta^+ \cup \beta'^+} + \one_{\beta^+ \cap \beta'^+} = \one_{\beta^+} + \one_{\beta'^+}
-\]
-and similarly~$\one_{\alpha^-} + \one_{\alpha'^-} = \one_{\beta^-} + \one_{\beta'^-}$, so that~$\hat{\b{g}}(\alpha) + \hat{\b{g}}(\alpha') =\hat{\b{g}}(\beta) + \hat{\b{g}}(\beta')$.
-\end{proof}
-
-\begin{corollary}
-\label{coro:basis}
-For any wiggly pseudotriangulation~$T$, the set~$\b{g}(T) \eqdef \set{\b{g}(\alpha)}{\alpha \in T^\circ}$ is a basis of~$\HH_{2n}$.
-\end{corollary}
-
-\begin{proof}
-Observe that the $\b{g}$-matrix~$\b{g}(T_\leftarrow)$ presented in \cref{exm:specialGMatrices} has full rank (it is very easy to check for~$\b{g}(T_\leftarrow)$, but any other would do).
-The statement thus follows from \cref{lem:linearDependences} and the connectedness of the flip graph on wiggly pseudotriangulations.
-\end{proof}
-
-Finally, we wrap up \cref{thm:wigglyFan}.
-
-\begin{proof}[Proof of \cref{thm:wigglyFan}]
-Directly follows from \cref{prop:characterizationFan,lem:-+...-+,lem:linearDependences}.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyFanSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define linear automorphisms of the wiggly fan~$\wigglyFan_n$.
-\end{remark}
-
-\begin{remark}
-By definition, each wall of the wiggly fan is normal to a $\b{c}$-vector.
-Hence, the wiggly fan coarsens the \defn{$\b{c}$-vector fan}, defined by the arrangement of hyperplanes~$\set{\b{x} \in \HH_{2n}}{\dotprod{\b{x}}{\b{c}(\alpha, T}}$ for all wiggly arcs~$\alpha$ and wiggly pseudotriangulations~$T$ with~$\alpha \in T$.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wigglyhedron}
-\label{subsec:wigglyhedron}
-
-We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
-%
-\afterpage{
-\begin{figure}
-\centerline{\input{wigglyhedron}}
-\caption{The wigglyhedron~$\wigglyhedron_2$.}
-\label{fig:wigglyhedron}
-\end{figure}
-}
-
-\begin{definition}
-\label{def:incompatibilityDegree}
-The \defn{incompatibility degree}~$\delta(\alpha, \alpha')$ of two wiggly arcs~$\alpha \eqdef (i, j, A, B)$ and~$\alpha' \eqdef (i', j', A', B')$ is given by
-\begin{itemize}
-\item $0$ if~$\alpha$ and~$\alpha'$ are pointed and non-crossing,
-\item $1$ is~$\alpha$ and~$\alpha'$ are not pointed (\ie $i = j'$ or~$i' = j$),
-\item the number of crossings of~$\alpha$ and~$\alpha'$ if they are crossing (\ie the number of~$p \in \{0, \dots, n\}$ with $p \in (A \cap B') \cup (\{i,j\} \cap B') \cup (A \cap \{i',j'\})$ and~$p+1 \in (A' \cap B) \cup (\{i',j'\} \cap B) \cup (A' \cap \{i,j\})$, or the opposite).
-\end{itemize}
-The \defn{incompatibility number} of a wiggly arc~$\alpha$ is~$\kappa(\alpha) \eqdef \sum_{\alpha'} \delta(\alpha, \alpha')$.
-\end{definition}
-
-\begin{remark}\label{rem:incompatibility-deg}
-Note that~$\delta$ is indeed an incompatibility degree in the sense that
-\begin{itemize}
-\item $\alpha$ and~$\alpha'$ are compatible if and only if~$\delta(\alpha, \alpha') = 0$,
-\item $\alpha$ and~$\alpha'$ are exchangeable if and only if~$\delta(\alpha, \alpha') = 1$.
-\end{itemize}
-Observe also that~$\delta$ (and thus~$\kappa$) is preserved by the automorphisms of \cref{rem:wigglyComplexAutomorphism}.
-\end{remark}
-
-%\vincent{The incompatibility degree is the number of ``close'' minors of the form~$\begin{bmatrix} 1 & -1 \\ -1 & 1 \end{bmatrix}$ or~$\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}$ in the matrix obtained from the two $\b{g}$-vectors of the wiggly arcs.}
-
-\begin{example}
-Observe that
-$\kappa \big( (0, j, {[1,j[}, \varnothing) \big) 
-= \kappa \big( (0, j, \varnothing, {[1,j[}) \big) 
-%= \kappa \big( (n+1-j, n+1, {]n+1-j, n]}, \varnothing) \big) 
-%= \kappa \big( (n+1-j, n+1, \varnothing, {]n+1-j, n]}) \big) 
-= (2^j-1)(2^{n+1-j}-1)$.
-\end{example}
-
-\begin{lemma}
-\label{lem:wallCrossingInequalities}
-Let~$T$ and~$T'$ be two adjacent wiggly pseudotriangulations with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$, and let~$\beta$ and~$\beta'$ be the wiggly arcs defined in \cref{prop:uerp}.
-Then
-\begin{itemize}
-\item if $\alpha$ and~$\alpha'$ are not pointed, then~$\kappa(\alpha) + \kappa(\alpha') > \big( \kappa(\beta) + \kappa(\beta') \big) / 2$,
-\item if~$\alpha$ and~$\alpha'$ are crossing, then~${\kappa(\alpha) + \kappa(\alpha') > \kappa(\beta) + \kappa(\beta')}$.
-\end{itemize}
-\end{lemma}
-
-\begin{proof}
-Any crossing between a wiggly arc~$\gamma$ and~$\beta$ or~$\beta'$ translates to a crossing with~$\alpha$ or~$\alpha'$.
-When~$\alpha$ and~$\alpha'$ are not pointed, a crossing with~$\alpha$ or~$\alpha'$ can correspond to a crossing with~$\beta$ and a crossing with~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \big( \delta(\beta, \gamma) + \delta(\beta', \gamma) \big) / 2$.
-When~$\alpha$ and~$\alpha'$ are crossing, then there is a correspondence between the crossings with~$\alpha$ or~$\alpha'$ and the crossings with~$\beta$ or~$\beta'$, so that~$\delta(\alpha, \gamma) + \delta(\alpha', \gamma) \ge \delta(\beta, \gamma) + \delta(\beta', \gamma)$.
-Moreover, both inequalities are strict for~$\gamma = \alpha'$ since~$\delta(\alpha,\alpha') = 1$ while~$\delta(\beta, \alpha') = \delta(\beta, \alpha') = 0$.
-The result thus follows by summation.
-\end{proof}
-
-\begin{theorem}
-\label{thm:wigglyhedron}
-The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
-\begin{itemize}
-\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \! \le \! \kappa(\alpha)}$ for all internal wiggly~arcs~$\alpha$,
-\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
-\end{itemize}
-\end{theorem}
-
-\begin{proof}
-By \cref{prop:characterizationPolytopalFan,lem:linearDependences,lem:wallCrossingInequalities}, the wiggly fan is indeed the normal fan of the polytope~$\wigglyhedron_n$ defined by the inequalities~$\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$.
-For any wiggly pseudotriangulation~$T$ and any wiggly arc~$\alpha$ of~$T$, we have~$\dotprod{\b{g}(\alpha)}{\b{p}(T)} = \sum_{\alpha' \in T} \kappa(\beta) \dotprod{\b{g}(\alpha)}{\b{c}(\alpha', T)} = \kappa(\alpha)$ since~$\b{g}(T)$ and~$\b{c}(T)$ are dual bases by \cref{def:cvectors}.
-Hence, $\b{p}(T)$ is indeed the point of~$\wigglyhedron_n$ corresponding to~$T$, which is located at the intersection of the hyperplanes~$\dotprod{\b{g}(\alpha)}{\b{x}} = \kappa(\alpha)$ for all internal wiggly arcs~$\alpha$ in~$T$.
-\end{proof}
-
-In fact, the wigglyhedron even recovers the wiggly lattice of \cref{subsec:wigglyPermutations}.
-
-\begin{proposition}
-The Hasse diagram of the wiggly lattice~$\wigglyLattice_n$ is isomorphic to the graph of the wigglyhedron~$\wigglyhedron_n$ oriented in the direction
-\(
-\b{\omega} \eqdef \sum_{i \in [n]} 4ni (\b{e}_{2i-1} + \b{e}_{2i}) + \sum_{j \in [2n]} j \b{e}_j.
-\)
-\end{proposition}
-
-\begin{proof}
-Consider an increasing flip~$T \to T'$ between two wiggly pseudotriangulations~$T$ and~$T'$ with~$T \ssm \{\alpha\} = T' \ssm \{\alpha'\}$.
-Denote by~$u$ and~$v$ the labels incident to~$\alpha$ and respectively below and above~$\alpha$ in the corner labeling of~$T$ described in \cref{def:bijection1}, and let~$\bar u \eqdef \lceil u/2 \rceil$ and~$\bar v \eqdef \lceil v/2 \rceil$.
-We have~$u < v$ because the flip~$T \to T'$ is increasing, so that~$\bar u \le \bar v$.
-
-Observe now that~${\b{p}(T') - \b{p}(T)}$ is orthogonal to the $(2n-2)$-dimensional cone of the wiggly fan generated by the $\b{g}$-vectors of the wiggly arcs in~$T \cap T'$, and points from the side containing~$\b{g}(\alpha)$ to the side containing~$\b{g}(\alpha')$.
-Hence, $\b{p}(T') - \b{p}(T)$ is a positive multiple of~$-\b{c}(\alpha, T)$.
-From \cref{def:cvectors}, we observe that
-\begin{itemize}
-\item $\dotprod{\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} = 1/2$ if~$i = \bar u \ne \bar v$, $-1/2$ if~$i = \bar v \ne \bar u$, and $0$ otherwise,
-\item $|\dotprod{\b{c}(\alpha, T)}{\b{e}_j}| \le 1/2$ for all~$j \in [2n]$.
-\end{itemize}
-We now distinguish two situations.
-If~$\bar u \ne \bar v$, then
-\[
-\dotprod{-\b{c}(\alpha, T)}{\b{\omega}} = \sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} \ge 2n(\bar v - \bar u) - n > 0.
-\]
-If~$\bar u = \bar v$, then~$u = 2k-1$ and~$v = 2k$ for some~$k \in [n]$, and we have
-\[
-\dotprod{\b{c}(\alpha, T)}{\b{\omega}} = \!\!
-\sum_{i \in [n]} 4ni \dotprod{-\b{c}(\alpha, T)}{\b{e}_{2i-1} + \b{e}_{2i}} + \!\!
-\sum_{j \in [2n]} j \dotprod{-\b{c}(\alpha, T)}{\b{e}_j} = \frac{2k}{2}-\frac{2k-1}{2} = 1/2 > 0.
-\]
-We conclude in both cases that~$\dotprod{\b{c}(\alpha, T)}{\b{\omega}} > 0$, so that we recover the increasing flip graph by orienting the graph of the wigglyhedron~$\wigglyhedron_n$ in direction~$\b{\omega}$.
-\end{proof}
-
-\begin{remark}
-\label{rem:wigglyhedronSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries}, note that the vertical and horizontal symmetries on wiggly arcs define isometries of the wigglyhedron~$\wigglyhedron_n$.
-\end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Further topics}
-\label{sec:furtherTopics}
-
-In this section, we explore two further topics on the wigglyhedron.
-We first observe that any (type~$A$) Cambrian associahedron~\cite{Reading-CambrianLattices,HohlwegLange} is normally equivalent to a face of the wigglyhedron~$\wigglyhedron_n$ (\cref{subsec:CambrianConsiderations}).
-We then raise the question to extend our construction to wiggly complexes of arbitrary planar point sets (\cref{subsec:planarPointSets}).
-
-%%%%%%%%%%%%
-
-\subsection{Cambrian considerations}
-\label{subsec:CambrianConsiderations}
-
-In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, we set~$\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
-We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice of \cref{sec:combinatorics} and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron of \cref{sec:geometry}.
-\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.
-
-\begin{figure}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian1}}
-\vspace{-.3cm}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian2}}
-\vspace{-.5cm}
-\centerline{\includegraphics[scale=1.1]{wigglyCambrian3}}
-\caption{Cambrian lattices as intervals of wiggly lattices.}
-\label{fig:wigglyCambrian}
-\end{figure}
-
-\begin{definition}
-\label{def:CambrianTriangulations}
-The \defn{$\delta$-gon} is a convex $(n+2)$-gon with a point with abscissa~$i$ and with ordinate of the same sign as~$\delta_i$  for all~$0 \le i \le n+1$.
-A \defn{$\delta$-triangulation} is a triangulation of the $\delta$-gon.
-The \defn{$\delta$-triangulation lattice} is the transitive closure of the slope increasing flip graph on $\delta$-triangulations.
-%If~$T$ and~$T'$ are two $\delta$-triangulations with~$T \ssm \{d\} = T' \ssm \{d'\}$, then the flip from~$T$ to~$T'$ is \defn{increasing} if the slope of~$d$ is smaller than the slope of~$d'$.
-\end{definition}
-
-\begin{definition}
-\label{def:CambrianPermutations}
-A \defn{$\delta$-permutation} is a permutation of~$[n]$ which avoids~$\cdots ik \cdots j \cdots$ with~$i < j < k$ and~$\delta_j = -$, and~$\cdots j \cdots ki \cdots$ with~$i < j < k$ and~$\delta_j = +$.
-The \defn{$\delta$-permutation lattice} is the sublattice of the weak order induced by $\delta$-permutations.
-\end{definition}
-
-\begin{definition}
-\label{def:CambrianWigglyPseudotriangulations}
-The \defn{$\delta$-wiggly arcs} are the arcs~$(0, j, {[1,j[}, \varnothing)$ for~$\delta_j = {+}$ and~$(0, j, \varnothing, {[1,j[})$ for~$\delta_j = {-}$.
-A \defn{$\delta$-wiggly pseudotriangulation} is a wiggly pseudotriangulation containing all $\delta$-wiggly arcs.
-The \defn{$\delta$-wiggly pseudotriangulation lattice} is the transitive closure of the increasing flip graph on $\delta$-wiggly pseudotriangulations.
-\end{definition}
-
-\begin{definition}
-\label{def:CambrianWigglyPermutations}
-A \defn{$\delta$-wiggly permutation} is a wiggly permutation~$\sigma$ of~$[2n]$ such that
-% for all~$j \in [n]$, we have~ and~$\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$i \in [2j-2]$.
-%\begin{itemize}
-%\item $\sigma^{-1}(2j-1) > \sigma^{-1}(2j)$ for all~$j \in [n]$,
-%\item $\sigma^{-1}(i) < \sigma^{-1}(2j-1)$ if~$\delta_j > 0$ and~$\sigma^{-1}(i) > \sigma^{-1}(2j)$ if~$\delta_j < 0$ for all~$j \in [n]$ and~$i \in [2j-2]$.
-%\end{itemize}
-\[
-\delta_j = {+} \quad \Longrightarrow \quad \sigma^{-1}(i) \le \sigma^{-1}(2j-1)
-\qquad\text{and}\qquad
-\delta_j = {-} \quad \Longrightarrow \quad \sigma^{-1}(2j) \le \sigma^{-1}(i)
-\]
-%$\delta_j > 0 \implies \sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ and~$\delta_j < 0 \implies \sigma^{-1}(i) \ge \sigma^{-1}(2j)$
-for all~$1 \le i \le 2j \le 2n$.
-The \defn{$\delta$-wiggly permutation lattice} is the interval of the wiggly lattice~$\wigglyLattice_n$ given by $\delta$-wiggly permutations.
-\end{definition}
-
-\begin{remark}
-We had to make a choice in \cref{def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations}.
-For~$\delta_j = {+}$, we could replace ``$(0, j, {[1,j[}, \varnothing)$'' by~``$(j, n+1, {]j,n]}, \varnothing)$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(i) \le \sigma^{-1}(2j-1)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
-Independently, for~$\delta_j = {-}$, we could replace ``$(0, j, \varnothing, {[1,j[})$'' by~``$(j, n+1, \varnothing, {]j,n]})$'' in \cref{def:CambrianWigglyPseudotriangulations}, and ``$\sigma^{-1}(2j) \le \sigma^{-1}(i)$ for~$1 \le i \le 2j$'' by ``$\sigma^{-1}(2j-1) \le \sigma^{-1}(i)$ for~$2j-1 \le i \le 2n$'' in \cref{def:CambrianWigglyPermutations}.
-\cref{prop:CambrianLattice,prop:CambrianFan} would still hold.
-\end{remark}
-
-\begin{remark}
-\label{rem:CambrianSymmetries}
-Following \cref{rem:wigglyComplexAutomorphism,rem:gcvectorsSymmetries,rem:wigglyFanSymmetries,rem:wigglyhedronSymmetries}, note that the vertical and horizontal symmetries send $\delta \eqdef \delta_1 \dots \delta_n$ to~$\delta_n \cdots \delta_1$ and $(-\delta_1) \cdots (-\delta_n)$ respectively.
-\end{remark}
-
-\begin{proposition}
-\label{prop:CambrianLattice}
-For any signature~$\delta \in \{+,-\}^n$, the $\delta$-triangulation lattice, $\delta$-permutation lattice, \mbox{$\delta$-wiggly} pseudotriangulation lattice, and $\delta$-wiggly permutation lattice are all isomorphic, and are known as the \defn{$\delta$-Cambrian lattice}~\cite{Reading-CambrianLattices}.
-\end{proposition}
-
-\begin{proof}
-We only describe the following bijections
-\begin{center}
-\begin{tikzcd}[column sep=3cm]
-\text{$\delta$-triangulations} \arrow[d] & \text{$\delta$-permutations} \arrow[l] \\
-\text{$\delta$-wiggly pseudotriangulations} \arrow[r] & \text{$\delta$-wiggly permutations} \arrow[u]
-%\text{$\delta$-triangulations} \arrow[d, "\lambda"'] & \text{$\delta$-permutations} \arrow[l, "\zeta"'] \\
-%\text{$\delta$-wiggly pseudotriangulations} \arrow[r, "\mu"'] & \text{$\delta$-wiggly permutations} \arrow[u, "\nu"']
-\end{tikzcd}
-\end{center}
-illustrated in \cref{fig:wigglyCambrian}.
-We let the readers convince themselves that they are well-defined, that they compose to the identity, and that they preserve the flip structure.
-We also invite the reader to work out the explicit description of the 8 missing arrows.
-For~$I \subseteq [n]$, we set~$I^+ \eqdef \set{i \in I}{\delta_i = {+}}$ and~$I^- \eqdef \set{i \in I}{\delta_i = {-}}$.
-
-\para{From $\delta$-triangulations to $\delta$-wiggly pseudotriangulations}
-Replace each diagonal~$(i,j)$ of the $\delta$-gon by the wiggly arc~$(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
-
-\para{From $\delta$-wiggly pseudotriangulations to $\delta$-wiggly permutations}
-Specialization of \cref{def:bijection1}.
-
-\para{From $\delta$-wiggly permutations to $\delta$-permutations}
-For all~$j \in [n]$, erase~$2j-1$ and replace~$2j$ by~$j$ if~$\delta_j = {+}$, and erase~$2j$ and replace~$2j-1$ by~$j$ if~$\delta_j = {-}$.
-
-\para{From $\delta$-permutations to $\delta$-triangulations}
-Already described in~\cite{Reading-CambrianLattices}.
-Given a permutation~$\pi$, construct the union of the upper hulls of the point sets~$[n]^- \symdif \pi([j])$ for all~$j \in \{0, \dots, n\}$.
-\end{proof}
-
-Recall that the $\delta$-Cambrian lattice can be realized by the $\delta$-Cambrian fan~\cite{ReadingSpeyer} and the $\delta$-associahedron of~\cite{HohlwegLange}.
-Namely, to each diagonal~$(i,j)$ of the $\delta$-gon, we associate the subset~$X(\delta)$ of points of the $\delta$-gon distinct from~$0$ and~$n+1$, and located below the line~$(i,j)$, including~$i$ if and only if~$\delta_i = {+}$ and~$j$ if and only if~$\delta_j = {+}$.
-The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
-The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \ge \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
-
-\begin{proposition}
-\label{prop:CambrianFan}
-The $\delta$-associahedron~$\Asso_\delta$ is normally equivalent to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly arcs.
-\end{proposition}
-
-\begin{proof}
-Following the proof of \cref{prop:CambrianLattice}, consider the map~$\zeta$ sending a diagonal~$(i,j)$ of the $\delta$-gon to the wiggly arc $(0, j, [i] \cup {]i,j[}^-, {]i,j[}^+)$ if~$\delta_i \ge 0$ and~$(0, j, {]i,j[}^-, [i] \cup {]i,j[}^+)$ if~$\delta_i \le 0$.
-Let~$a \eqdef (i,j)$ and~$a' \eqdef (i',j')$ be two crossing diagonals of the~$\delta$-gon.
-Then any $\delta$-triangulations~$T$ and~$T'$ with~$T \ssm \{a\} = T' \ssm \{a'\}$ contain the diagonals~$b \eqdef (i',j)$ and~$b' \eqdef (i,j')$ of the $\delta$-gon, and~$\b{g}(a) + \b{g}(a') = \b{g}(b) + \b{g}(b')$.
-Moreover, if~$\alpha \eqdef \zeta(a)$, $\alpha' \eqdef \zeta(a')$, $\beta \eqdef \zeta(b)$ and~$\beta' \eqdef \zeta(b')$, then~$\b{g}(\alpha) + \b{g}(\alpha') = \b{g}(\beta) + \b{g}(\beta')$.
-We thus conclude that $\zeta$ preserves the linear dependences among $\b{g}$-vectors.
-Hence, there is a linear map~$Z : \HH_n \to \HH_{2n}$ such that~$Z \big( \b{g}(d) \big) = \b{g} \big( \zeta(d) \big)$ for all diagonals~$d$ of the $\delta$-gon.
-This map is a normal equivalence from the $\delta$-associahedron~$\Asso_\delta$ to the face of the wigglyhedron~$\wigglyhedron_n$ corresponding to the wiggly pseudodissection formed by the $\delta$-wiggly~arcs.
-\end{proof}
-
-%\vincent{todo: find an explicit affine map between the Hohlweg-Lange $\delta$-associahedron and the face of the wigglyhedron corresponding to all $\delta$-wiggly arcs.}
-
-\begin{remark}
-In their work on polytopal realizations of $\b{g}$-vector fans of finite type cluster algebras~\cite{HohlwegPilaudStella}, C.~Hohlweg, V.~Pilaud and S.~Stella already constructed a \defn{universal associahedron}~$\polytope{U}_n$ which somehow contains all Cambrian fans (actually all $\b{g}$-vector fans from any initial cluster seed).
-More precisely, the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$  appears as a section of the normal fan of the universal associahedron~$\polytope{U}_n$, which is a $(n^2+n-4)/2$-dimensional polytope.
-In contrast, \cref{prop:CambrianFan} states that the $\delta$-Cambrian fan for each~$\delta \in \{+,-\}^n$ appears as a link of the normal fan of the wigglyhedron~$\wigglyhedron_n$, which is a $(2n-1)$-dimensional polytope.
-There seem to be no connection between these two universal polytopes.
-However, this certainly raises the question to construct analogues of the wigglyhedron for all finite Coxeter groups.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Wiggly pseudotriangulations of planar point sets}
-\label{subsec:planarPointSets}
-
-We now consider \cref{thm:wigglyhedron,conj:Hamiltonian} for wiggly pseudotriangulations of arbitrary point sets in the plane (neither necessarily aligned, nor necessarily in general position).
+We consider an arbitrary point set~$P$ in the plane (neither necessarily aligned, nor necessarily in general position).
 
@@
 \begin{itemize}
-\item \cref{def:wigglyComplex,def:wigglyFlipGraph} in the case of aligned points, and
+\item the wiggly complex of~\cite{BapatPilaud} in the case of aligned points, and
 \item the pseudodissection complex of~$P$ and pseudotriangulation flip graph of~$P$ in the case of points~$P$ in general position.
@@
 However, we make the following ambitious conjecture.
+\vincent{The goal of this new paper is to solve this conjecture.}
 
@@
 
-In \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of \cref{thm:wigglyhedron}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
+In \cref{conj:polytopality}, the case of aligned points is given by the wigglyhedron of~\cite{BapatPilaud}, while the case of points in general position is given by the pseudotriangulation polytope of~\cite{RoteSantosStreinu-polytope}.
 This raises in particular the following question.
@@
 \begin{question}
-Can the construction of \cref{thm:wigglyhedron} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (\aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
+Can the constructions of~\cite{BapatPilaud} be adapted to provide a more combinatorial construction of the polytope of pseudotriangulations~\cite{RoteSantosStreinu-polytope}, that would only depend on the order type (\aka oriented matroid~\cite{BjornerLasVergnasSturmfelsWhiteZiegler}) of the point configuration?
 \end{question}
@@
 
-Finally, it is natural to consider the extension of \cref{conj:Hamiltonian}.
+Finally, it is natural to consider the extension of~\cite[Conj.~44]{BapatPilaud}.
 
@@
 \end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Categorical interpretation of wiggly pseudotriangulations}
-\label{sec:categoricalInterpretation}
-
-The aim of this section is to explain a categorical interpretation of wiggly arcs.
-We first present a particular triangulated category (\cref{subsec:category}), and recall results of Khovanov--Seidel~\cite{kho.sei:02} (\cref{subsec:KSCurveModel}) that interpret the objects of this category as wiggly arcs, such that intersections between wiggly arcs correspond to morphisms in this category.
-We then explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of objects (\cref{subsec:cohomologyFiltrations}).
-We also discuss categorical conditions for two wiggly arcs to be compatible as in~\cref{def:compatible} (\cref{subsec:categoricalCompatibility}).
-
-%%%%%%%%%%%%
-
-\subsection{A triangulated category associated to a quiver}
-\label{subsec:category}
-
-% We begin by describing the category of interest, which is a subcategory of \(D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
-We begin by describing the category of interest, which is the bounded homotopy category of finitely-generated graded projective modules over a finite-dimensional algebra \(A_m\). 
-The algebra~\(A_m\), called the \defn{zigzag algebra}, is a quotient of the path algebra of the quiver \(Q_m\) with \(m\) vertices depicted in~\cref{fig:am-quiver}.
-Let \(kQ_m\) be the path algebra of \(Q_m\), graded by path length.
-Let~\(e_i\) denote the idempotent path at the vertex \(i\), and let \((i, j)\) denote the arrow from vertex \(i\) to a (neighbouring) vertex \(j\).
-A longer path, which is a composition of arrows, will be denoted by~\((i_1, i_2, \dots, i_n)\).
-
-\begin{figure}[h]
-	\centering
-	\begin{tikzcd}
-		1 \arrow[bend left]{r} & 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
-	\end{tikzcd}
-	\caption{The quiver \(Q_m\). The algebra \(A_m\) is a quotient of the path algebra \(kQ_m\).}
-	\label{fig:am-quiver}
-\end{figure}
-
-\begin{definition}
-The \defn{zigzag algebra} \(A_m\) corresponding to the quiver \(Q_m\) depicted in~\cref{fig:am-quiver} is the quotient of \(kQ_m\) by all paths of length at least \(3\), together with the relations \((i-1, i, i+1) = 0\), \((i+1, i, i-1)=0\) and \((i, i-1, i) = (i, i+1, i)\) for all~\(1 < i < m\).
-\end{definition}
-
-\begin{remark}
-The definition of the zigzag algebra as used here originally appeared in~\cite[Sect.~3]{hue.kho:01}.
-This is the ``un-signed'' zigzag algebra.
-It is technically better to use a ``signed'' zigzag algebra, and the comparison between the two is discussed in~\cite[Rem.~6.6]{bap.deo.lic:20}.
-As the two versions are isomorphic in our example, we ignore this technicality and use the easier definition.
-\end{remark}
-
-Let \(P_i\) denote the indecomposable projective \(A_m\)-module defined as \(P_i = A_m\cdot e_i\).
-For any integer~\(j\), let \(P_i \langle j \rangle\) denote its graded shift by \(j\).
-
-\begin{definition}
-The category \(\mathcal{C}_m\) is defined to be the homotopy category of bounded complexes of finitely-generated graded projective \(A_m\)-modules.
-\end{definition}
-Let \(D^b(A_m\text{-grmod})\) denote the bounded derived category of graded \(A_m\)-modules.
-Note that there is an embedding of \(A_m\text{-grmod}\) into \(D^b(A_m\text{-grmod})\), which sends any \(A_m\)-module as a complex of \(A_m\)-modules that is concentrated in degree \(0\).
-In particular, the objects \(P_i\langle j \rangle\) can be regarded as objects of \(D^b(A_m\text{-grmod})\).
-\(\mathcal{C}_m\) is thus the smallest full triangulated subcategory of \(D^b(A_m\text{-grmod})\) containing all the objects \(P_i\langle j \rangle\).
-
-For further discussion on the construction, see \eg~\cite[Sect.~2.3.3]{bap.deo.lic:22}.
-The category \(\mathcal{C}_m\) is \(k\)-linear and triangulated, where \([1]\) denotes the triangulated shift.
-For \(X, Y \in \mathcal{C}_m\), let \(\Hom^{g,h}(X,Y)\) denote the space of morphisms in \(\mathcal{C}_m\) of internal degree \(g\) and homological degree \(h\).
-In other words, we have
-\[
-\Hom^{g,h}(X,Y) = \Hom(X,Y\langle g \rangle[h]).
-\]
-Furthermore, for any integers \(a\) and \(b\), we have
-\[
-\Hom^{g,h}(X\langle g' \rangle[h'], Y\langle g' \rangle[h']) = \Hom^{g,h}(X,Y).
-\]
-
-\begin{remark}
-\label{rem:generating-morphisms}
-The generating objects \(P_i\) (and hence their graded and homological shifts) satisfy \(\Hom^{0,0}(P_i,P_i) = \Hom^{2,0}(P_i,P_i) = \Hom^{1,0}(P_i,P_{i\pm1}) = k\) and \(\Hom^{g,h}(P_i, P_j) = 0\) in all other cases.
-\end{remark}
-
-We now describe the \(t\)-structure induced by the full subcategory of \defn{linear complexes} of \(\mathcal{C}_m\).
-A variant of this construction is also described in~\cite[Sect.~2.5]{lic.que:21}.
-It is convenient to think of an object \(P^{\bullet}\) of \(\mathcal{C}_m\) as a bigraded (projective) \(A_m\)-module equipped with a differential \(d \colon P^{\bullet} \to P^{\bullet}\).
-More precisely, we can write
-\[
-P^{\bullet} = \bigoplus_{g,h,i} M_i\langle g \rangle[h],
-\]
-where \(g\) is the internal grading shift, \(h\) is the homological grading shift, and 
-each object \(M_i\) is a direct sum of copies of objects in \(\{P_1,\ldots, P_m\}\).
-Set \(P^h\) to be the direct sum of all summands that have homological grading shift \(h\).
-That is, in the notation above, we have
-\[
-P^{h} = \bigoplus_{g,i} M_i\langle g \rangle[h].
-\]
-
-\begin{warning}
-  By convention, if \(M_i\) is an \(A_m\)-module, then the object \(M_i[h]\) is placed in homological degree \(-h\).
-  Since the differential \(d\) raises the homological degree by one, it lowers the homological shift by one.
-  That is, we have
-  \[d \colon M_i\langle g \rangle[h] \to \bigoplus_{g',i'} M_{i'}\langle g' \rangle[h-1].\]
-  In other words, \(d\) maps \(P^h\) to \(P^{h-1}\).
-\end{warning}
-
-\begin{definition}
-\label{def:linear-complex}
-Let \(P^{\bullet}\) be an object of \(\mathcal{C}_m\), described as a bigraded module
-\[
-P^{\bullet} = \bigoplus M_i\langle g \rangle[h]
-\]
-together with an internal differential \(d \colon P^{\bullet} \to P^{\bullet}\) as above.
-We say that \(P^{\bullet}\) has \defn{level \(\ell\)} for some~\(\ell \in \mathbb{Z}\) if for each bigraded piece \(M_i \langle g \rangle[h]\) of \(P^{\bullet}\), we have \(g + h = \ell\).
-We say that \(P^{\bullet}\) is \defn{linear} if \(P^{\bullet}\) has level \(\ell = 0\).
-\end{definition}
-
-For any integer \(N\), let \(\mathcal{C}_m^{\le N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\geq -N\).
-For any integer \(N\), let \(\mathcal{C}_m^{\geq N} \subset \mathcal{C}_m\) be the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, containing all complexes of level \(\leq -N\).
-
-We refer the reader to \eg~\cite[Sect.~1.3]{bel.ber.del:82} for the definition of a \(t\)-structure on a triangulated category.
-The following proposition is easily checked using the calculations in~\cref{rem:generating-morphisms} and standard techniques involving categories of complexes; we omit the proof.
-
-\begin{proposition}
-The pair of subcategories \((\mathcal{C}_m^{\leq 0}, \mathcal{C}_m^{\geq 0})\) forms a bounded \(t\)-structure on \(\mathcal{C}_m\).
-\end{proposition}
-
-We call this \(t\)-structure the \defn{standard \(t\)-structure} on \(\mathcal{C}_m\).
-Set \(\mathcal{A}_m \eqdef \mathcal{C}^{\leq 0}_m \cap \mathcal{C}_m^{\geq 0}\) to be the heart of this \(t\)-structure; this is the smallest full subcategory of \(\mathcal{C}_m\) closed under isomorphism, which contains all linear complexes.
-It follows that \(\mathcal{A}_m\) is abelian.
-
-Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}
-
-\begin{defprop}
-\label{defprop:cohomology}
-Let \((\mathcal{C}^{\le 0}, \mathcal{C}^{\geq 0})\) be a \(t\)-structure on a triangulated category \(\mathcal{C}\) with heart~\(\mathcal{A} \eqdef \mathcal{C}^{\leq 0} \cap \mathcal{C}^{\geq 0}\).
-For each integer \(i\), we have the \(i\)th truncation functors
-\[
-\tau^{\leq i} \colon \mathcal{C} \to \mathcal{C}^{\leq i} \quad\text{and}\quad \tau^{\geq i} \colon \mathcal{C} \to \mathcal{C}^{\geq i},
-\]
-which are right and left adjoint respectively to the inclusion functors \(\mathcal{C}^{\leq 0} \to \mathcal{C}\) and \(\mathcal{C}^{\geq 0} \to \mathcal{C}\).
-The \(i\)th \defn{cohomology functor} is defined to be the composition \(\tau^{\leq i} \circ \tau^{\geq i}\).
-It is canonically isomorphic to the composition \(\tau^{\geq i} \circ \tau^{\leq i}\), and maps an object of \(\mathcal{C}\) to an object of \(\mathcal{A}\).
-\end{defprop}
-
-The next statement, easy to check from the definitions, is mentioned \eg in~\cite[Sect.~3.3]{bayer2011tour}.
-
-\begin{defprop}
-\label{defprop:cohomology-filtration}
-Let \(\mathcal{C}\) be any triangulated category, and \(\mathcal{A} \subset \mathcal{C}\) the heart of a bounded \(t\)-structure on \(\mathcal{C}\).
-Let \(X\) be a non-zero object of \(\mathcal{C}\), and let \(k\) and \(\ell\) be the maximum and minimum integers respectively for which \(H^k(X)\) and \(H^\ell(X)\) are non-zero.
-Then \(X\) has a unique \defn{cohomology filtration}, which is the unique filtration of the form
-\[
-\begin{tikzcd}[column sep=0.1cm]
-	0  \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k+1} \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-	& H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} && \cdots \arrow[dashed]{ul} &&H^k(X)[-k] \arrow[dashed]{ul}{+1}
-\end{tikzcd}
-\]  
-\end{defprop}
-
-%%%%%%%%%%%%
-
-\subsection{The Khovanov--Seidel curve model}
-\label{subsec:KSCurveModel}
-
-\afterpage{
-\begin{figure}
-\centerline{
-	\begin{tabular}{c@{\qquad}c@{\qquad}c}
-		Spherical objects in bounded 
-		&
-		&
-		\\
-		homotopy category of graded projective 
-		&
-		$\smash{\xrightarrow[\quad\text{combinatorial model}\quad]{}}$
-		&
-		Curves
-		\\
-		modules over the zigzag algebra
-		&
-		&
-                \\
-		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
-			\&           \& P_3 \langle -1 \rangle\arrow{dr} \& \\
-			\&           \&                      \& P_2\\
-			P_1\langle -5 \rangle\arrow{r}    \& P_1\langle -3 \rangle\arrow{r}   \& P_1 \langle -1 \rangle\arrow{ur} \& 
-		\end{tikzcd}
-		&
-		&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve1}}
-		\\[.5cm]
-		{\scriptsize cohomology} $\Bigg\downarrow$ {\scriptsize filtration}
-		&
-		&
-		$\Bigg\downarrow$ {\scriptsize cut}
-		\\[.5cm]
-		Heart of the standard $t$-structure
-		&
-		$\xrightarrow[\quad\text{combinatorial model}\quad]{}$
-		&
-		Wiggly arcs
-		\\
-		\begin{tikzcd}[ampersand replacement=\&, row sep=-0.1cm, column sep=0.5cm]
-			P_1\langle -1 \rangle \arrow{dr}\& \\
-			\& P_2 \\
-			P_3 \langle -1 \rangle \arrow{ur}
-		\end{tikzcd}
-		&
-          	&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve2}}
-		\\
-		\(P_1\)
-		&
-		&
-		\raisebox{-.5cm}{\includegraphics[scale=1.3]{curve3}	}
-	\end{tabular}
-}
-\caption{An illustration of the Khovanov--Seidel curve model and \cref{prop:cohomology-pieces}.}
-\label{fig:curveModel}
-\end{figure}
-}
-
-In this section we briefly recall how to recover an object of \(\mathcal{C}_{n+1}\) from a wiggly arc on \(n+2\) points on a line.
-In fact, the procedure works on more general curves as well (namely, those that are not necessarily \(x\)-monotone).
-
-Consider \(n+2\) points arranged in a straight horizontal line, and labelled \(0,1, \ldots, n+1\) as in~\cref{sec:combinatorics}.
-In addition to the wiggly arcs, consider isotopy classes of curves whose endpoints lie on distinct marked points, and which do not cross themselves or any marked point in their interior.
-For convenience, we refer to such an isotopy class as a \defn{curve}.
-
-The Khovanov--Seidel correspondence (explained in Section 4 of~\cite{kho.sei:02}) associates objects of~\(\mathcal{C}_{n+1}\) (up to an overall grading and homological shift) to curves on a configuration of \(n+2\) marked points arranged in a straight line.
-We illustrate this correspondence and~\cref{prop:cohomology-pieces} in~\cref{fig:curveModel}.
-In particular, the line segment joining point \(i\) to point \(i+1\) is sent to the object \(P_{i+1}\) in the category \(\mathcal{C}_{n+1}\).
-Moreover, the minimal intersection number between any pair of curves is the number of morphisms between the associated objects~\cite[Prop.~4.9]{kho.sei:02}.
-In fact, the proposition in~\cite{kho.sei:02} is a stronger result: by considering \emph{bigraded curves}, we obtain \emph{bigraded intersection numbers} between the two associated objects.
-
-Any object \(X\) obtained via the Khovanov--Seidel correspondence is~\defn{spherical}; that is, \(\Hom^{g,0}(X,X)\) is \(k\) when \(g = 0,2\), and \(\Hom^{g,h}(X,X) = 0\) in all other cases.
-A spherical object \(X\) is necessarily indecomposable as \(\Hom^{0,0}(X,X) = k\).
-
-\begin{proposition}
-\label{prop:cohomology-pieces}
-Let \(\alpha\) be any curve, and let \(X = X^{\bullet}\) be a chain complex that corresponds to \(\alpha\) under the Khovanov--Seidel reconstruction.
-Recall that for any integer \(j\), the cohomology object~\(H^j(X)\) is an object of \(\mathcal{A}_m\), and hence a direct sum of indecomposable objects of \(\mathcal{A}_m\).
-\begin{enumerate}
-\item The object \(X\) is a (spherical) object of \(\mathcal{A}_m\) up to shift if and only if \(\alpha\) is a wiggly arc.
-In this case, \(H^j(X) \neq 0\) for exactly one \(j\), such that \(X \cong H^j(X)[-j]\).
-\item If \(\alpha\) is a general curve, each indecomposable summand of \(H^j(X)\) for any \(j\) is a spherical object of \(\mathcal{A}_m\) that arises from a wiggly arc, up to shift.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  Let \(X\) be a complex built from an arbitrary (not necessarily wiggly) curve \(\alpha\).
-  Recall from~\cite{kho.sei:02} that \(X\) is spherical, and hence indecomposable.
-  Let us now analyse the indecomposable summands of its cohomology objects.
-
-  We recall that the procedure to build up \(X\) from \(\alpha\) explicitly describes the differential.
-  We analyse the possible non-zero components of the differential, checking how each interacts with the level.
-  The only two possibilities are as follows:
-  \begin{enumerate}
-  \item a map \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\), namely multiplication on the right by the path~\((i,i\pm1)\), which does not change the level; or
-  \item a map \(P_i\langle g \rangle[h] \to P_{i}\langle g+2 \rangle[h-1]\), namely multiplication on the right by the ``loop'' path~\((i,i\pm1, i)\), which raises the level by one.
-  \end{enumerate}
-  The first possibility appears each time the curve wiggles either above the \(i\)th point or below the~\((i-1)\)th point.
-  The second possibility appears each time the curve makes a U-turn around the right of \(i\)th or the left of the \((i-1)\)th point.
-
-  Computing the \(j\)th cohomology \(H^j(X)\) simply amounts to truncating the complex to level \(j\).
-  Explicitly, the truncation is a new chain complex in which we only keep the terms of \(X\) that have level \(j\), together with all maps between them, and forget all the other terms.
-  From the calculation above, we see that the resulting complex only has components in its differential of the first type, namely \(P_i\langle g \rangle[h] \to P_{i\pm1}\langle g+1 \rangle[h-1]\) where \(g + h = j\).
-  We kill all components of the second type (the ``loop'' components).
-  The resulting chain complex breaks up into indecomposable summands, each of which is an object of~\(\mathcal{A}_m[j]\), and this direct sum is \(H^j(X)[j]\).
-
-  The object \(X\) is in the heart up to shift if and only if it is concentrated in a single level \(j\).
-  Truncating to level \(j\) as described above, we do not delete any of the terms of \(X\).
-  This can happen if and only if the differential of \(X\) contains no ``loop'' components,
-  which appear in the complex if and only if \(\alpha\) makes a U-turn around one of the \(n+2\) points.
-  Thus \(X\) is in the heart up to shift if and only if \(\alpha\) is  \(x\)-monotone.
-  This proves the first part of the proposition.
-
-  More generally, consider the indecomposable pieces of the level-\(j\) truncations of \(X\) for various~\(j\), up to shift.
-  As explained above, in terms of the curve \(\alpha\), this corresponds to breaking up the curve~\(\alpha\) into \(x\)-monotone portions.
-  More precisely, we begin at an endpoint \(p_0\) of \(\alpha\) and follow the curve until it either ends at a point \(p_1\), or stops being \(x\)-monotone by making a U-turn around a point \(p_1\).
-  In this case, we take the portion of \(\alpha\) between \(p_0\) and \(p_1\), calling it \(\alpha_1\), and setting its endpoints to be \(p_0\) and \(p_1\) respectively.
-  Note that \(p_0 \neq p_1\) because \(\alpha\) is \(x\)-monotone between~\(p_0\) and~\(p_1\).
-  We continue with the remainder of \(\alpha\) starting at \(p_1\), greedily taking the maximal \(x\)-monotone portion each time, to obtain pieces \(\alpha_1,\alpha_2, \ldots, \alpha_k\), which are all wiggly arcs.
-  These wiggly arcs correspond to complexes \(X_1, \ldots, X_k\), which are spherical objects of \(\mathcal{A}_m\), up to shift.
-  It is clear from the construction of the associated complex that these objects, up to shift, are exactly the indecomposable pieces of the cohomology truncations \(H^j(X)\) for various \(j\).
-  This argument proves the second part of the proposition.
-\end{proof}
-
-%%%%%%%%%%%%
-
-\subsection{Cohomology filtrations of spherical objects}
-\label{subsec:cohomologyFiltrations}
-
-In this section we explain how wiggly pseudotriangulations govern the combinatorial structure of a natural categorical decomposition of spherical objects of \(\mathcal{C}_m\).
-
-For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
-However, it turns out that the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
-
-\begin{proposition}
-\label{prop:hn-filtration}
-  Let \(X \in \mathcal{C}_{n+1}\) be a spherical object.
-  Consider its cohomology filtration
-  \[
-    \begin{tikzcd}[column sep=0.3cm]
-      0 \arrow{rr} && X_{-\ell} \arrow{dl} \arrow{rr} && \cdots \arrow{rr} \arrow{dl} && X_{-k} = X \arrow{dl}\\
-      & H^\ell(X)[-\ell] \arrow[dashed]{ul}{+1} && H^{\ell+1}(X)[-\ell-1] \arrow[dashed]{ul}{+1} & \cdots & H^k(X)[-k] \arrow[dashed]{ul}{+1}
-    \end{tikzcd}
-  \]
-  Consider the set of all possible indecomposable summands of the cohomology objects \(\{H^j(X)\}\) taken without multiplicity.
-  Let \(T\) be corresponding set of wiggly arcs, as explained in~\cref{prop:cohomology-pieces}.~Then
-  \begin{enumerate}
-  \item 
-    \(T\) is a subset of a wiggly pseudotriangulation,
-  \item \(T\) contains at most one of the two external wiggly arcs.
-  \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  The proof of this proposition is an easy consequence of analysing the cohomology filtration from the point of view of curves on the disk with marked points.
-  Let \(X_1, \ldots, X_k\) be the objects in~\(T\) without repetition, which arise from wiggly arcs \(\alpha_1, \ldots, \alpha_k\) as explained in the proof of~\cref{prop:cohomology-pieces}.
-  Let \(\beta = (i,j,A,B)\) and \(\beta' = (i',j', A',B')\) be two distinct wiggly arcs among~\(\{\alpha_1, \ldots,\alpha_k\}\).
-  We check that \(\beta\) and \(\beta'\) are compatible in the sense of~\cref{def:compatible}.
-
-  Recall that \(\beta\) and \(\beta'\) are two pieces of the curve \(\alpha\).
-  Therefore \(\beta\) and \(\beta'\) cannot cross, because~\(\alpha\) does not cross itself.
-  Suppose that \(\beta\) and \(\beta'\) are non pointed, and without loss of generality, suppose that \(i' = j\).
-  This means that the piece \(\beta\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because \(\alpha\) loops around the right of the point \(i'\).
-  Moreover, if \(i'\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(i'\) lies to the left of \(i'\).
-
-  Similarly, the piece \(\beta'\) was cut from \(\alpha\) either because \(i' = j\) is an endpoint of \(\alpha\), or because~\(\alpha\) loops around the left of the point \(j\).
-  Moreover, if \(j\) is an endpoint of \(\alpha\), then the portion of \(\alpha\) closest to \(j\) lies to the right of \(j\).
-
-  We have four possible combinations:
-  \begin{enumerate}
-  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\);
-  \item \(i' = j\) is an endpoint such that \(\alpha\) travels left starting at \(i'\), and \(\alpha\) loops around the left of the point \(j\);
-  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(i' = j\) is an endpoint such that \(\alpha\) travels right starting at \(j\); 
-  \item \(\alpha\) loops around the right of the point \(i' = j\), and \(\alpha\) loops around the left of the point \(j\).
-  \end{enumerate}
-  It is clear that none of these possibilities can occur within the curve \(\alpha\), and hence \(\beta\) and \(\beta'\) must be pointed.
-  Therefore \(T = \{\alpha_1, \ldots, \alpha_k\}\) is a subset of a wiggly pseudotriangulation.
-
-  Now suppose for contradiction that \(T\) contains both external edges.
-  Then some portion of \(\alpha\) curves around each of the extreme endpoints \(0\) and \(n+1\).
-  Consider the outermost strands of \(\alpha\) that curve around \(0\) and \(n+1\) respectively.
-  These must then connect to each other, resulting in~\(\alpha\) having a separate closed component that winds around the outside of the \(n+2\) points.
-  This is not possible because \(\alpha\) is a connected curve with two endpoints.
-  Therefore \(T\) cannot contain both external edges.
-\end{proof}
-
-\begin{remark}
-Note that in \cref{def:wigglyComplex}, we adopted the convention that the faces of the wiggly complex contain none of the two external wiggly arcs.
-In contrast, the wiggly dissections of \cref{prop:hn-filtration} contain at most one of the two external wiggly arcs.
-Combinatorially, this is just the Cartesian product of the wiggly complex with an edge.
-\end{remark}
-
-%%%%%%%%%%%%
-
-\subsection{Categorical constraints on compatibility of curves}
-\label{subsec:categoricalCompatibility}
-
-In this section, we give a categorical criterion for two wiggly arcs to be compatible as in~\cref{def:compatible}.
-As such, this section is somewhat dual to the previous section: the criterion in this section determines whether a pair of wiggly arcs can belong together in a single wiggly pseudotriangulation, whereas the previous section generated a wiggly pseudotriangulation given any object of the category.
-
-For two objects \(X\) and \(X'\) of \(\mathcal{C}_m\), let \(\mathbb{E}^\ell(X,X')\) denote the direct sum over all level-\(\ell\) morphisms from \(X\) to \(X'\).
-That is,
-\[\mathbb{E}^\ell(X,X') = \bigoplus_{g + h = \ell}\Hom^{g,h}(X,X').\]
-
-Recall that two wiggly arcs \(\alpha\) and \(\alpha'\) are said to be compatible (as in~\cref{def:compatible}) if they are non-crossing and pointed.
-The incompatibility degree of \(\alpha\) and \(\alpha'\) (as in~\cref{def:incompatibilityDegree}) is \(1\) if \(\alpha\) and \(\alpha'\) are non pointed, and the number of crossings of \(\alpha\) and \(\alpha'\) otherwise.
-\begin{proposition}
-\label{prop:ext1}
-Let \(X\) and \(X'\) be objects in the standard heart \(\mathcal{A}_m\) corresponding to two wiggly arcs \(\alpha\) and \(\alpha'\) respectively.
-  Then \(\alpha\) and \(\alpha'\) are compatible if and only if \(\mathbb{E}^1(X, X') = 0\).
-  More generally, the incompatibility degree of \(\alpha\) and \(\alpha'\) is the dimension of \(\mathbb{E}^1(X,X')\).
-\end{proposition}
-
-\begin{proof}
-  The proof follows from a specialisation of the bigraded intersection number calculations that appear in Sections 3 and 4 of~\cite{kho.sei:02}.
-  The bigraded intersection number as defined in~\cite[Sect.~3d]{kho.sei:02} between the curves \(\alpha\) and \(\alpha'\) is a polynomial in the variables \(q_1^{\pm}\), \(q_2^{\pm}\).
-  It follows from~\cite[Prop.~4.9]{kho.sei:02} that this bigraded intersection number equals the Poincar{\'e} polynomial of the morphisms between \(X\) and \(X'\), namely the expression
-  \begin{equation}
-    \label{eq:bigraded-homs}
-  \sum_{s_1,s_2}\dim(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1]))q_1^{s_1}q_2^{s_2}.    
-\end{equation}
-However, the grading convention in~\cite{kho.sei:02} is not the same as ours --- our grading is by path length, while the grading in~\cite{kho.sei:02} is one for arrows in one direction and zero for arrows in the opposite direction.
-So we have to modify the gradings when we construct the complexes.
-In particular, the table in~\cite[Lem.~3.20]{kho.sei:02} that computes the bigraded intersection numbers will change, and so will the table in~\cite[Lem.~4.12]{kho.sei:02} that computes the Poincar{\'e} polynomials of \(\Hom(P_k,-)\).
-
-With our path-length grading, note that a morphism in \(\Hom_{\mathcal{C}_m}(X,X'\langle -s_2 \rangle[s_1])\) has level \(s_1 - s_2\); that is, it takes an object \(X\) of level \(0\) to the object \(X'\langle -s_2 \rangle[s_1]\) of level \(s_1 - s_2\).
-  We can thus obtain the dimension of all morphisms of level \(\ell\) by setting \(q_1 = q\) and \(q_2 = q^{-1}\) and taking the coefficient of \(q^{\ell}\) in the expression~\eqref{eq:bigraded-homs}.
-    The dimension of \(\mathbb{E}^1(X,X')\), is therefore the coefficient of~\(q\) under this specialisation.
-
-It can be checked that under the path-length grading, the space of morphisms arising from an intersection of curves of ``crossing'' type as well as ``non pointed'' type contains exactly one morphism (up to equivalence and scalar multiplication) of level one; that is, a unique element (up to scalar multiplication) of~\(\mathbb{E}^1\).
-Morphisms arising from other intersections do not contribute to~\(\mathbb{E}^1\).
-This calculation proves the proposition.
-\end{proof}
-
-\begin{remark}
-  \cref{prop:ext1} is very similar to the condition of being compatible in a cluster-tilting object of a cluster category (see, \eg~\cite[Cor.~4.3]{bua.mar.rei.ea:06}) or in a $\tau$-tilting object (see, \eg~\cite{AdachiIyamaReiten}).
-  The condition in terms of crossings of curves already appears for some specializations (see, \eg~\cite{FominShapiroThurston, PaluPilaudPlamondon-surfaces}).
-  However, in \cref{prop:ext1}, it depends on shifting the objects~\(X\) and~\(X'\) so that they both lie in the standard heart, which is an auxiliary step that is not required in cluster-tilting and $\tau$-tilting theory.
-\end{remark}
-
-\begin{remark}
-  As stated,~\cref{prop:ext1} in combination with~\cref{prop:hn-filtration} is not expected to be true in greater generality.
-  For instance, for the zigzag algebra of Dynkin type~\(D_4\), one can find two spherical objects with a non-trivial \(\mathbb{E}^1\) that nevertheless appear together in the cohomology filtration of another spherical object.
-  However, we expect to see similar constraints on compatibility, which we hope to turn to in forthcoming work.
-\end{remark}
-
-Recall from~\cref{rem:incompatibility-deg} that two wiggly arcs \(\alpha\) and \(\alpha'\) are exchangeable if and only if their incompatibility degree is one.
-Recall from~\cref{prop:uerp} the wiggly arcs \(\beta\) and \(\beta'\) associated to \(\alpha\) and \(\alpha'\).
-Finally, recall from~\cref{lem:linearDependences} that the \(\b{g}\)-vectors of the wiggly arcs \(\alpha\), \(\alpha'\), \(\beta\), and \(\beta'\) satisfy a linear dependence, depending on their type.
-Let us interpret this dependence categorically.
-
-Let \(X\), \(X'\), \(Y\) and~\(Y'\) be spherical objects in the standard heart that correspond to \(\alpha\), \(\alpha'\), \(\beta\) and~\(\beta'\) respectively.
-First, note by~\cref{prop:ext1} that \(X\) and \(X'\) are exchangeable if and only if there is a unique non-trivial \(\mathbb{E}^1\) between the corresponding objects of the standard heart.
-Next, let us understand~\(Y\) and \(Y'\) categorically.
-
-\begin{proposition}\label{prop:extensions}
-For \(\alpha\), \(\alpha'\), \(\beta\), \(\beta'\), and \(X\), \(X'\), \(Y\), \(Y'\) as just discussed,
-\begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then for some integers \(g\) and \(g'\), we have extensions
-  \[0 \to X' \to Y \to X\langle g \rangle[-g] \to 0 \quad \text{and}\quad 0 \to X \to Y' \to X'\langle g' \rangle[-g'] \to 0;\]
-\item if \(\alpha\) and \(\alpha'\) are crossing, then for some integer \(g\), we have an extension
-  \[0 \to X' \to (Y \oplus Y') \to X\langle g \rangle[-g]\to 0.\]
-\end{itemize}
-\end{proposition}
-
-\begin{proof}
-  The proof is once again a consequence of analysing the extensions explicitly via the complexes from the Khovanov--Seidel reconstruction.
-  We do not reproduce the proof here, as the argument is contained in the proof of~\cite[Thm.~5.5]{tho:06}.
-  (See also~\cite[Fig.~4]{tho:06}.)
-\end{proof}
-Note that if we write down the relations in the Grothendieck group of our category that correspond to the extensions from each case of~\cref{prop:extensions}, then we obtain precisely the linear dependences that appear between the \(\b{g}\)-vectors in~\cref{lem:linearDependences}.
-More precisely, we have that
-\begin{itemize}
-\item if \(\alpha\) and \(\alpha'\) are not pointed, then
-  \([Y] = [X] + [X'] = [Y']\),
-  from which we see \([X] + [X'] = ([Y] + [Y'])/2\);
-\item if \(\alpha\) and \(\alpha'\) are crossing, then
-  \([X] + [X'] = [Y] + [Y'].\)
-\end{itemize}
-This suggests that there should be a way to construct the \(\b{g}\)-vectors categorically in such a way that the \(\b{g}\)-vectors also map to the Grothendieck group of the category.
-The \(\b{g}\)-vector of an object~\(X\) corresponding to a wiggly arc \(\alpha\) can, of course, be reconstructed from \(\alpha\).
-However, at the moment we do not have a purely categorical construction of the \(\b{g}\)-vector of \(X\) that does not refer to \(\alpha\), and it would be interesting to find this.
-
-\begin{question}
-  Suppose we have a collection of spherical objects in the standard heart \(\mathcal{A}_m\) that satisfy the compatibility condition of~\cref{prop:ext1}.
-  That is, the \(\mathbb{E}^1\) between any pair of objects in this collection is zero.
-  \begin{enumerate}
-  \item Can we prove properties about a maximal such collection without reference to curves?
-  \item In particular, can we understand the combinatorics of maximal such collections without reference to curves?
-  \item Given a maximal compatible collection of objects, can we always find a larger spherical object such that the factors of the cohomology filtration of that object are precisely shifts of the objects in the given collection?
-  \end{enumerate}
-\end{question}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-This work started during the \emph{Winterbraids XIII: School on low dimensional topology, braid groups and interactions}.
-We are grateful to the organizers Bérénice Delcroix-Oger, Peter Feller, Vincent Florens, Hoel Queffelec for this fruitful event.
-We thank Anand Deopurkar and Anthony M. Licata for many useful conversations and ideas.
-Finally, we are grateful to an anonymous referee for many relevant suggestions on the presentation of the paper.
 

### 2025-01-31 programmation/wigglyPseudotriangulationsPointSets.py

@@ -1,0 +1,609 @@
+from collections import defaultdict
+from functools import cmp_to_key
+
+### WIGGLY COMPLEX ON ARCS
+
+@cached_function
+def side_points(P, i, j, k):
+    r"""
+    Return the relative position of P[i], P[j], P[k].
+    This is 1, -1, or 0.
+
+    EXAMPLES::
+        sage: P = ((0,0), (1,1), (3,0), (0,3), (3,3))
+        sage: for (i,j,k) in Subsets(range(5), 3):
+        ....:     print(i, j, k, side_points(P, i, j, k))
+        ....:
+        0 1 2 -1
+        0 1 3 1
+        0 1 4 0
+        0 2 3 1
+        0 2 4 1
+        0 3 4 -1
+        1 2 3 1
+        1 2 4 1
+        1 3 4 -1
+        2 3 4 -1
+    """
+    return sign(Matrix([[P[i][0], P[i][1], 1], [P[j][0], P[j][1], 1], [P[k][0], P[k][1], 1]]).determinant())
+
+@cached_function
+def position(P, i, j, k):
+    r"""
+    Return the relative position of P[i], P[j], P[k].
+    This is 1 or -1 if the points are not aligned, and True or False if the points are aligned (False means that k lies in the interior of the segment joining i to j).
+
+    EXAMPLES::
+        sage: P = ((0,0), (1,1), (3,0), (0,3), (3,3))
+        sage: for (i,j,k) in Subsets(range(5), 3):
+        ....:     print(i, j, k, position(P, i, j, k))
+        ....:
+        0 1 2 -1
+        0 1 3 1
+        0 1 4 True
+        0 2 3 1
+        0 2 4 1
+        0 3 4 -1
+        1 2 3 1
+        1 2 4 1
+        1 3 4 -1
+        2 3 4 -1
+    """
+    d = Matrix([[P[i][0], P[i][1], 1], [P[j][0], P[j][1], 1], [P[k][0], P[k][1], 1]]).determinant()
+    if d != 0: return sign(d)
+    return i == k or j == k or any((P[i][c] - P[k][c])*(P[j][c] - P[k][c]) > 0 for c in [0,1])
+
+@cached_function
+def intermediate_points(P, i ,j):
+    r"""
+    Return the indices k such that P[k] lies in the open segment joining P[i] to P[j].
+
+    EXAMPLES::
[…]

### 2025-02-03 programmation/wigglyPseudotriangulations_draft.py
missing py file

@@ -1,0 +1,266 @@
+@cached_function
+def number_arcs(n):
+    return add(2**j * (n+1-j) for j in range(n+1)) - 2
+
+@cached_function
+def arcs(n):
+    return [(i, j, A, Set(range(i+1, j)).difference(A)) for j in range(n+2) for i in range(j) for A in Subsets(range(i+1, j))]
+
+def tuplize(arc):
+    return (arc[0], arc[1], tuple(sorted(arc[2])), tuple(sorted(arc[3])))
+
+@cached_function
+def relevant_arcs(n):
+    return [(i, j, A, Set(range(i+1, j)).difference(A)) for j in range(n+2) for i in range(j) for A in Subsets(range(i+1, j)) if j-i < n+1 or len(A) not in [0, n]]
+
+def are_crossing(arc1, arc2):
+    (i1, j1, A1, B1) = arc1
+    C1 = Set([i1, j1])
+    (i2, j2, A2, B2) = arc2
+    C2 = Set([i2, j2])
+    return (A1.intersection(B2) or C1.intersection(B2) or A1.intersection(C2)) and (B1.intersection(A2) or C1.intersection(A2) or B1.intersection(C2))
+
+@cached_function
+def wiggly_crossing_graph(n):
+    return Graph([arcs(n), are_crossing])
+
+def compatible(arc1, arc2):
+    (i1, j1, A1, B1) = arc1
+    (i2, j2, A2, B2) = arc2
+    return arc1 != arc2 and i1 != j2 and j1 != i2 and not are_crossing(arc1, arc2)
+
+@cached_function
+def wiggly_compatibililty_graph(n):
+    return Graph([relevant_arcs(n), compatible])
+
+def wiggly_incompatibility_number(arc1, arc2):
+    (i1, j1, A1, B1) = arc1
+    C1 = Set([i1, j1])
+    (i2, j2, A2, B2) = arc2
+    C2 = Set([i2, j2])
+    X = (A1.intersection(B2).union(C1.intersection(B2)).union(A1.intersection(C2)))
+    Y = (B1.intersection(A2).union(C1.intersection(A2)).union(B1.intersection(C2)))
[…]

### 2025-02-06 programmation/wigglyPseudotriangulationsPointSets.py
code

@@ -93,6 +93,23 @@ def is_coherently_labeled(P):
     """
     return all(position(P, i, j, k) for (i,j,k) in [sorted(s) for s in Subsets(range(len(P)), 3)])
 
+def coherently_relabel(P):
+    r"""
+    Return a permutation of the point set P which is coherently labeled.
+    It suffices to sort in lexicographic order of coordinates.
+
+    EXAMPLES::
+        sage: P = ((0,0), (2,0), (0,2), (2,2), (1,1))
+        sage: is_coherently_labeled(P)
+        False
+        sage: Q = coherently_relabel(P)
+        sage: Q
+        ((0, 0), (0, 2), (1, 1), (2, 0), (2, 2))
+        sage: is_coherently_labeled(Q)
+        True
+    """
+    return tuple(sorted(P))
+
 def arc(i, j, A, B):
     r"""
     Creates an arc.

### 2025-02-14 wigglyAligned/wigglyhedra.tex
minor correction acknowledgments

--- 2025-01-09 draft/wigglyhedra.tex
@@
 \thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
-  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}
+VP was partially supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Spanish--German project COMPOTE (AEI PCI2024-155081-2 \& DFG 541393733), by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), and by the French--Austrian project PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
 
@@
 
-\centerline{\includegraphics[scale=1.75]{wigglyFlipGraph}}
+\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}}
 
@@
 
-Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}
+Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}.
 

### 2025-02-14 wigglyPointSets/wigglyhedraPointSets.tex
missing py file
minor correction acknowledgments

@@
 \thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
-VP was partially supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French project CHARMS (ANR-19-CE40-0017), and by the French--Austrian project PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
+VP was partially supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Spanish--German project COMPOTE (AEI PCI2024-155081-2 \& DFG 541393733), by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), and by the French--Austrian project PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}
 
@@
 \begin{figure}[!h]
-\centerline{\includegraphics[scale=1]{wigglyComplexSquare}}
+\centerline{\includegraphics[scale=1]{wigglyComplexSquare1}}
 \caption{The wiggly complex~$\wigglyComplex_P$ (left) and the wiggly flip graph~$\wigglyFlipGraph_P$ (right) of a point set~$P$.}
-\label{fig:wigglyComplexSquarre}
+\label{fig:wigglyComplexSquarre1}
 \end{figure}

### 2025-03-11 wigglyAligned/wigglyhedra.tex
expand Remark 33

@@
 \author{Vincent Pilaud}
-\address{Universitat de Barcelona}
+\address[Vincent Pilaud]{Universitat de Barcelona \& Centre de Recerca Matemàtica, Barcelona, Spain}
 \email{vincent.pilaud@ub.edu}
@@
 
-\begin{remark}
-\label{rem:wigglyLatticeAntiIsomorphism}
-The map~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_n)$ obviously provides an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$.
-\end{remark}
-
 We now aim at describing the cover relations of the wiggly lattice.
@@
 \end{proof}
+
+\begin{remark}
+\label{rem:wigglyLatticeAntiIsomorphism}
+Let~$\varepsilon$ be the permutation of~$[2n]$ exchanging~$2j-1$ with~$2j$ for all~$j \in [n]$.
+Then the maps~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_{2n})$ and~$\sigma_1 \dots \sigma_{2n} \mapsto \varepsilon(\sigma_{2n}) \dots \varepsilon(\sigma_1)$ are two obvious bijections on wiggly permutations of~$[2n]$.
+Moreover, the first map is an anti-isomorphism of the wiggly lattice~$\wigglyLattice_n$ (while the second map is not).
+\end{remark}
 
@@
 \begin{remark}
-The map~$\Phi$ sends the wiggly complex automorphism of \cref{rem:wigglyComplexAutomorphism} given by the vertical reflection to the wiggly lattice anti-isomorphism of \cref{rem:wigglyLatticeAntiIsomorphism}.
+The map~$\Phi$ sends the wiggly complex automorphisms of \cref{rem:wigglyComplexAutomorphism} to the bijections on wiggly permutations of \cref{rem:wigglyLatticeAntiIsomorphism}.
+In particular, it sends the vertical reflection on wiggly pseudotriangulations to the wiggly lattice anti-isomorphism on wiggly permutations given by~$\sigma_1 \dots \sigma_{2n} \mapsto (2n+1-\sigma_1) \dots (2n+1-\sigma_{2n})$.
 \end{remark}
